

# Places {#sec-venues}

```{r}
# Access custom defined functions
targets::tar_source("../R_functions")
```



```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "taco", color = "dark_green", shape = 4)


```

Of the $604$ locations at which participant had physical or sexual contact in a group setting (contact venues), about two out of five were private residences, and about a quarter were dance parties. More than half of the contact venues were in Manhattan, while less than a third were in the Brooklyn. A quarter of all contact venues were in the same community as the participant's residence, a third were in a different borough, and the remainder were in the same borough as home, but a different community district.

```{r tbl_places_descriptives}
#| fig-cap: "Participants in MPX NYC Study by Sex / Physical Contact in Congregate Setting in past 4 weeks"
#| label: fig-places-descriptives

targets::tar_read(data_bipartite_graph_collected) |>
        tidygraph::activate(edges) |>
        data.frame() |>
        dplyr::filter(!home) |>
        dplyr::select("placeSex", "placeType", "place_borough", "distanceFromHome") |>
        gtsummary::tbl_summary(by = placeSex) |>
 gtsummary::add_overall(last = TRUE) |>
    gtsummary::modify_spanning_header(c("stat_1", "stat_2", "stat_0") ~ "**Sexual contact at contact venue**") |>
  gtsummary::add_p() |>
  gtsummary::modify_header(label ~ "**Variable**") |>
  gtsummary::bold_labels() |>
        gtsummary::as_gt() |>
        gt::tab_source_note(gt::md("*Data source: MPX NYC 2022*")) 

```

Contact venues at which participants had sexual contact (rather than non-sexual physical contact) were overwhelmingly private residences whereas contact venues at which they had non-sexual physical contact were mostly dance parties (see @fig-places-distance-sexcontact). The closer to home a location was, the more likely it was to be a private residence and the more likely it was the site of sexual contact. By contrast, the further from home a contact venue was, the more likely it was to be a dance party.

```{r fig_places_distance_sexcontact}
#| fig-cap: "MPX NYC contact venue type by distance from home and sexual contact"
#| label: fig-places-distance-sexcontact
#| fig-width: 9
#| fig-height: 9

make_table_freq3(placeType, placeSex, distanceFromHome, person_analysis = FALSE) |>
  dplyr::filter(!is.na(level)) |>
  plot_radar_stratified2() |>
  apply_style_radar_facet_plot()

```
