

# Gatherings {#sec-venues}

```{r include=FALSE}
targets::tar_source("../R_functions")
```




### {.unnumbered}


```{r}
#| tbl-cap: Gatherings attended by MPX NYC participants
#| label: tbl-gatherings

make_tabledata_gatherings <- function(){
  targets::tar_read(data_bipartite_graph_collected) |>
    tidygraph::activate(edges)|>
    data.frame() |>
    dplyr::group_by(place_borough, place_community, place_neighborhood) |>
    dplyr::summarize(count = dplyr::n()) |>
    dplyr::rename(borough = place_borough, community = place_community, neighborhood = place_neighborhood) |>
    dplyr::arrange(-count) |>
    dplyr::ungroup() |>
    dplyr::filter(!is.na(borough)) |>
    dplyr::mutate(proportion = count / sum(count))
}


scale_labels <- c("0", "1-10", "11-20", "21-30", "31+")

mpxnyc::neighborhood_sf_obj |>
   sf::st_as_sf() |>
  dplyr::left_join(make_tabledata_gatherings(), by = "neighborhood") |>
  dplyr::mutate(count = ifelse(is.na(count), 0, count)) |>
  dplyr::mutate(count_cat = cut(count, c(-1,0,10,20,30,100), scale_labels)) |>
  dplyr::arrange(-count) |>
  ggplot2::ggplot() +
  ggplot2::geom_sf(data = mpxnyc::community_sf_obj, fill = "white", linewidth = 0, color = NA) +
  ggplot2::geom_sf(data = mpxnyc::community_sf_obj, fill = "#F73C95", linewidth = 0, color = NA, alpha = 0.1) +
  ggplot2::geom_sf(ggplot2::aes(alpha = count_cat), linewidth = 0, fill = "#F73C95", color = "#FF99C5") +
  ggplot2::geom_sf(data = mpxnyc::community_sf_obj, fill = NA, linewidth = 0.3, color = "black") +
  ggplot2::scale_alpha_discrete("Gatherings\ncount") +
  theme_mpxnyc_blank(
    plot.background = ggplot2::element_rect(fill = "white"),
    legend.position = "right"
    )
```

MPX NYC participants reported 604 total locations where they had physical or sexual contact in a group setting—what we call *gatherings*. Nearly two in five gatherings occurred in private residences, and about a quarter took place at dance parties. Over half of gatherings were in Manhattan, while roughly one-third occurred in Brooklyn.  



::: {.callout-note collapse=true icon=false}
# Show Table 7.4: Gatherings

{{< include tbl-gatherings.qmd >}}
:::






## Sexual contact and distance from home 

About a quarter of all gatherings happened within the same community district as the participant’s home, one-third were in another borough, and the remainder were in a different community district within the same borough.


```{r}
#| fig-cap: !expr 'get_figure_details("fig-places-distance-sexcontact")'
#| label: fig-placetype-bar-grid
#| fig-width: 8
#| fig-height: 10


make_plotdata_placetype_bar_grid() |>
  dplyr::mutate(proportion = abs(proportion)) |>
  plot_bar_stratified2() +
    ggplot2::coord_polar() +
  scale_axis_mpxnyc() +
  ggplot2::scale_y_continuous(limits = c(-0.3, 0.84)) +
  scale_fill_mpxnyc(name = "") +
  ggplot2::geom_label(ggplot2::aes(label = scales::percent(proportion, accuracy = 1), x = level, y = 0.5 ), border.color = "white", label.size = 0, size = 3.5) +
  theme_mpxnyc_bar_places(
      plot.margin = ggplot2::unit(c(0,0,0,0), "cm"), 
      panel.spacing = ggplot2::unit(0, "cm"),
      legend.position = "bottom",
      panel.grid.major.y = ggplot2::element_blank(),
      panel.grid.major.x = ggplot2::element_blank(),
      axis.text.x = ggplot2::element_blank(),
      strip.text.y.left = ggplot2::element_text(angle = 90)
      )

  #theme_mpxnyc_bar_places(
  #    plot.margin = ggplot2::unit(c(0,0,0,0), "cm"), 
  #    panel.spacing = ggplot2::unit(0, "cm")
  #    ) 



```

Gatherings that involved sexual contact were overwhelmingly private residences, whereas non-sexual physical gatherings—such as parties, performances, or sports events—were mostly dance parties (@fig-placetype-bar-grid).
The closer a venue was to a participant’s home, the more likely it was to be a private residence and to include sexual contact. Conversely, the farther the venue, the more likely it was a dance party.


## Gayborhoods

The neighborhoods most frequently mentioned as gathering locations included Hell’s Kitchen and Chelsea in Manhattan, and East Williamsburg, Bushwick, and Bedford-Stuyvesant in Brooklyn.







```{r}

table_data <- make_tabledata_gatherings() |>
  dplyr::filter(count > 16) |>
  dplyr::ungroup() |>
  dplyr::select(neighborhood, community, borough, count, proportion) 

labelled::var_label(table_data$neighborhood) <- "Neighborhood"
labelled::var_label(table_data$community) <- "Community district"
labelled::var_label(table_data$borough) <- "Borough"
labelled::var_label(table_data$count) <- "Count of gatherings"
labelled::var_label(table_data$proportion) <- "Proportion of gatherings"

table_data |>
  gt::gt()|>
  gt::tab_header(
    title = "Most popular neighborhoods for gatherings",
    subtitle = "MPX NYC 2022"
  ) |>
   gt::fmt_percent(proportion, decimals = 0)

```



```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "taco", color = "dark_green", shape = 4)
```
