```{r include=FALSE}
targets::tar_source("../R_functions")
```

##### Social catchment

Social catchment is a place-node characteristic which measures the number of relations with person nodes. 

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-social-catchment
#| fig-width: 8
#| fig-height: 5




make_reach_diagram_data(focal_node = "Community c", alter_nodes = c("Person 8", "Person 4", "Person 7", "Person 5")) |>
  plot_reach_diagram(reached_color = "#F73C95") +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```

Social catchment of place $j$ among subgroup $A$ is defined as the
number of connections the focal community district has with participants
who belong to subgroup $A \subset \mathscr{N}_P$. Social catchment of
place $j$ is defined as $C_{j} = C_{j\rightarrow \mathscr{N}_P}$

$$
C_{j\rightarrow A} = \sum_{i } { \Psi (i, j) A_i}
$$
