

##### Person graph {.unnumbered}

The MPX NYC participant network has participants as nodes. A pair of nodes is connected by a weighted edge if each of the individuals represented by the nodes has at least one contact venue or residence in the same, shared community district. The weight of the edge is given by the count of community districts the pair of nodes have in common. 



```{r}
#| fig-cap: Sample person-person network visualizatoin
#| label: fig-example-participant
#| fig-width: 8
#| fig-height: 4



make_example_network_data("people") |>
  plot_example_projection_network() +
  theme_mpxnyc_blank(legend.position = "right") +
  ggplot2::scale_size_manual(name = "Node type", values = c(7)) +
  scale_color_mpxnyc(name = "Node type", option = "dark") +
  ggraph::scale_edge_width()  +
  ggraph::scale_edge_width_manual(name = "Weight", values = c(1,2,3))






```



 

```{r  include=FALSE}
#| label: tbl-example-participant-nodes
#| layout-ncol: 2
#| tbl-cap: Sample person-person network data
#| tbl-subcap:  
#| - "Nodes"
#| - "Edges"

make_example_network_data("people") |>
  data.frame() |>
  dplyr::transmute(Name = label, Type = type) |>
  gt::gt()

make_example_network_data("people") |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(From = from_name, To = to_name, Weight = weight) |>
  gt::gt()

```



