
```{r include=FALSE}
targets::tar_source("../R_functions")
```

# SSNAC IV: Analysis {#sec-appendix-network-analysis}







```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "devil", color = "dark_orange", shape = 16, alpha = 0.1)

```


::: {#acknowledgements}
[Acknowledgements]{.underline}: The analytic framework for this project developed over an extended period of time, beginning during my PhD dissertation (Harvard University, 2021, under the supervision of Lisa Berkman, Eric Tchetgen Tchetgen, and a former mentor I no longer contact). In particular, the analysis borrows from the central paper in my dissertation, which shows how the wealth of non-coresident extended family members is protective against mortality.... (Continued at bottom of page)


[Lead author]{.underline}: Keletso Makofane, MPH, PhD. [Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).
:::




In this appendix we describe the main data objects of the MPX NYC study -- the Person-place graph, the Person graph and the Place graph -- as well as the statistics we used to analyze them. 


{{< include B_1__data.qmd >}}
{{< include B_2__measures.qmd >}}
<!--


-->





::: {#acknowledgements}
[Acknowledgements]{.underline}: The analytic framework for this project developed over an extended period of time, beginning during my PhD dissertation (Harvard University, 2021, under the supervision of Lisa Berkman, Eric Tchetgen Tchetgen, and a former mentor I no longer contact). In particular, the analysis borrows from the central paper in my dissertation, which shows how the wealth of non-coresident extended family members is protective against mortality.

This work was part of U.S. government-funded research conducted in South Africa through the HAALSA study, which has since been defunded by the Trump administration. It is path-breaking because it shows an approach to using a large scale (over 100,000 people observed over three decades) dataset as a family network. There are many more datasets that could be analyzed using these methods. Any investigator who ever hosted a study at the Agincourt surveillance site in the north-east of South Africa, for instance, can use these methods to interpret their own data in light of family networks. It has the potential to illustrate the value of deep collaboration between U.S. and South African researchers. It is also of pedagogical value. I wrote the appendices of my dissertation in the same style as these appendices -- with students and teachers of epidemiology in mind. 

**Unfortunately, my PhD dissertation paper is a hostage of the American Journal of Epidemiology’s former editor-in-chief, Ichiro Kawachi, who is a colleague of my former mentor.**

After taking some time away from work to recover from the social violence I experienced at the hands of my former mentor, I was surprised to find that the edits that had held up publication of my dissertation paper (with implications for my ability to get an academic job) were minor copy edits. The "technical review" itself, which is misleadingly labelled, was riddled with errors, by the admission of the handling editor. Many tedious things happened after that, but the result of them is that the editors of the American Journal of Epidemiology have the final version of my manuscript, which I copy edited myself after arranging for the journal to receive thousands of dollars in publication fees... after spending years conducting the research and months responding to peer review. I submitted the manuscript by email after the handling editor agreed to receive it by email. 

Mysteriously, the manuscript remains unpublished. Ichiro Kawachi remains a member of the editorial board of the Journal. The Journal is associated with the Society of Epidemiologic Research, whose meetings were an important venue for the development of the SSNAC framework. 

**For publication-ready copies of the paper referenced below, which was accepted on 19 October 2023, please contact the editorial board of the American Journal of Epidemiology directly. Please share your correspondence with members of the Society of Epidemiologic Research and any South African and U.S. researchers you think might have an interest in seeing the work in print.**

> Makofane, K., Tchetgen Tchetgen, E. J., Bassett, M. T., Berkman, L. F. (Accepted 2023, final manuscript submitted January 2025). Networked wealth and mortality in the Agincourt Health and Demographic Surveillance System 2009 – 2018. *American Journal of Epidemiology*.
:::





