
```{r include=FALSE}
targets::tar_source("../R_functions")
```

# SSNAC IV: Analysis {#sec-appendix-network-analysis}





```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "taco", color = "dark_purple", shape = 0)

```


::: {#acknowledgements}
[Acknowledgements]{.underline}: The analytic framework for this project developed over an extended period of time, beginning with my PhD dissertation (Harvard, 2021, under the supervision of Lisa Berkman, Eric Tchetgen Tchetgen, and a former mentor I no longer have contact with). In particular, the analysis borrows from the central paper in my PhD dissertation which shows how the wealth of non-coresident extended family members is protective against mortality. This work was part of U.S. funded research conducted in South Africa through the HAALSI study, which has since been defunded.  The work is path-breaking because it shows an approach to using a large scale (over 100,000 people) dataset as a family network. There are many more datasets that could be analyzed using these methods.  

Unfortunately, this paper was a hostage of the *American Journal of Epidemiology*'s former editor in chief Ichiro Kawachi, who is a colleague of the former mentor. He remains a member of the editorial board of the journal. The journal is associated with the Society of Epidemiologic Research, whose meetings were an important venue for the development of the SSNAC framework. For publication-ready copies of the paper referenced below, which I submitted in January of 2025, please contact the editorial board of AJE directly. Please share your correspondence with members of the Society of Epidemiologic Research.

Makofane, K., Tchetgen Tchetgen, E. J., Bassett, M. T., Berkman, L. F. (Accepted 2023, final manuscript submitted January 2025). Networked wealth and mortality in the Agincourt Health and Demographic Surveillance System 2009 – 2018. *American Journal of Epidemiology*.

[Lead author]{.underline}: Keletso Makofane, MPH, PhD. [Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).
:::


In this appendix we describe the main data objects of the MPX NYC study -- the Person-place graph, the Person graph and the Place graph -- as well as the statistics we used to analyze them. 



{{< include B_0__preface.qmd >}}
{{< include B_1__data.qmd >}}
{{< include B_2__measures.qmd >}}








