```{r  include=FALSE}
targets::tar_source("../R_functions")
```

### Causal reasoning with DAGs and SWIGs {.unnumbered}

##### The FFRCISTG model


At its core, the system epidemiologists increasingly depend on for reasoning about abstract quantities such as causal effects is a statistical model called the Finest Fully Randomized Causally Interpretable Structured Tree Graph (FFRCISTG). A FFRCISTG is a collection of non-parametric structural equation models which mimic the causal process that produced the variables under investigation. At the very least it is a collection of two NPSEMs: a model of the observed data (observed data model) and a model of what the data would be under some intervention (counterfactual data model). The most common type of intervention in this framework is one which sets the value of one or more variables in the system (the exposures) with the goal of influencing the value of some set of variables in the system (the outcomes). The counterfactual data model is used to calculate quantities like causal effects. The observed data model is used to express those quantities as statistics that can be estimated using data.

A non-parametric structural equation model with independent errors is a system of equations that relates all the entries in a given vector-valued random variable to each other. It does so without specifying parametric functions for each equation in the system. An example of such a model is shown by @eq-fullly-connected-dag. In this set of equations, values that are produced by equations higher up in the list serve as inputs to equations lower down on the list. The functions $f_*$ are deterministic. The arguments $U_*$ represent error terms -- random variables that are independent of each other within and across observational units.

Consider a FFRCISTG modelling an intervention where we set formal dress $A_1$ to $a_1$, $A_2$ to $a_2$, and $A_3$ to $a_3$. The observed data model would be:

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, A_1) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, A_1, A_2) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1, Y_2) \\
\end{aligned}
$$ {#eq-fullly-connected-dag}

In the counterfactual data model (shown in @eq-fullly-connected-swig below), the values set by the investigator through intervention supercede the values that would have been generated had the experimenter not intervened. The experimenter-set values are used in subsequent equations in the model. 

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2^{(a_1)} &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, a_1) \\
A_3^{(a_1, a_2)} &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, a_1, a_2) \\
Y_1^{(a_1, a_2, a_3)} &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, a_1, a_2, a_3) \\
Y_2^{(a_1, a_2, a_3)} &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, a_1, a_2, a_3, Y_1^{(a_1, a_2, a_3)}) \\
Y_3^{(a_1, a_2, a_3)} &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, a_1, a_2, a_3, Y_1^{(a_1, a_2, a_3)}, Y_2^{(a_1, a_2, a_3)}   ) \\
\end{aligned}
$$ {#eq-fullly-connected-swig}




 

##### Model restrictions

Whereas parametric models are characterized by their probability mass or density functions, non-parametric models of this type are usually characterized by model restrictions in the form of conditional independencies. 

Restrictions are crucial: to fully characterize the NPSEM specified in @eq-fullly-connected-dag using observed data, we would need to estimate nine functions using one observation of the nine-dimensional joint distribution that gave rise to the participants' observations. Recruiting an additional person to the study would not ease this problem; it would add three new equations to the model and we would end up with a similar problem than the one we began with. We would have to estimate 12 functions using one observation of a 12-dimensional joint distribution.

We can simplify this system of equations by making assumptions that leave us with fewer functions to estimate and more observations per function. These assumptions are called model restrictions because they restrict the set of distributions that could possibly be represented by the NPSEM. For instance, if we add the restriction that all the measures are independent (or equivalently, that the DAG has no arrows), the resulting model would not be able to represent data from a causal system where some of the measures are correlated. By adding the restriction of independence, we would be eliminating the correlated data distribution from consideration as a possibility for how the data we are modelling are truly distributed.

It is possible to deduce the conditional independence restrictions of an NPSEM using the structural equations themselves. For instance, we can check whether two variables are (conditionally) independent by checking whether both variables are a function of the same common error term $U_*$. It turns out that queries like this are much simpler to deduce through a graphical representation of the NPSEM than through the NPSEM itself, however. Directed acyclic graphs allow the efficient communication of conditional independence assumptions that define NPSEMs. 


##### DAGs and SWIGs

A causal directed acyclic graph (DAG) (@fig-fullly-connected-dag) is a graph whose nodes represent the variables in an observational non-parametric structural equation model with independent errors (@eq-fullly-connected-dag). Directed edges point from the arguments to the result of each structural equation. 




```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-dag
#| fig-cap: "Fully connected causal DAG"

make_dag("fully_connected")         |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```

A single world intervention graph (SWIG) (@fig-fullly-connected-swig) is a DAG whose nodes represent the variables in a counterfactual non-parametric structural equation model with independent errors (@eq-fullly-connected-swig). Directed edges point from the arguments to the result of each structural equation. 





```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-swig
#| fig-cap: "Fully connected SWIG"

make_swig("fully_connected")      |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```

DAGs and SWIGs are useful because they encode statistical relationships among the variables in an NPSEM through a set of graphical rules called d-separation. Two variables in an NPSEM are (conditionally) independent if they are (conditionally) d-separated in the causal DAG representing the NPSEM.



##### D-separation

D-separation is a set of rules for translating DAGs into conditional independence statements. A pair of nodes is d-separated if all the paths linking them are closed or if there is no path that links them. A pair of nodes is conditionally d-separated if all the paths linking them are closed after conditioning on some set of nodes. 

A **path** is a sequence of nodes that starts with an origin node and ends with a terminal node. Consecutive entries in the sequence are connected in the DAG. A path of length one is open by definition. A path of length two or more is open if all its triangles are open.

A **triangle** is a sub-sequence of a path which contains three consecutive nodes from the path. A canonical triangle is one in which we do not condition on the apex node. A conditional triangle is one in which we do condition.

A **fork** is a triangle whose apex variable has two outgoing edges. A canonical fork is open and a conditional fork is closed. The apex variable of a fork is commonly referred to as a "confounder."

A **spoon** is a triangle whose apex variable has two incoming edges. A canonical spoon is closed and a conditional spoon is open. The apex variable of a spoon is commonly referred to as a "collider."

A **chopstick** is a triangle whose apex variable has one incoming edge and one outgoing edge. A canonical chopstick is open and a conditional chopstick is closed. The apex variable of a chopstick is commonly referred to as a "mediator."








