### D-separation {.unnumbered}

D-separation is a set of rules for translating DAGs into (conditional) independence statements involving the variables represented on the DAG. If two variables are "d-separated" in the DAG, then they are (conditionally) independent of one another.

#### Paths

A path linking two nodes (say *Node A* and *Node B*) in a DAG is a sequence of nodes that start with *A* and ends with *B* where each successive node in the sequence is connected to the former and the subsequent nodes in the DAG. Two nodes are d-separated if all the paths linking them are closed or if there is no path that links them.

A path of length one (an edge connecting two nodes) is open by definition. A path of length two or more can be analyzed in terms of its consecutive sub-sequences of three, which we call triangles. A path is open if all the triangles in that path are open. We can therefore check whether any path is closed or open by examining the triangles.

#### Triangles

A path in a DAG can be analyzed in terms of three types of triangle - the fork, the spoon, and the chopstick, which we describe below. When we do not condition for any variable in the triangle, we call it the "canonical triangle". When we condition by the intermediate variable in a the triangle, we call it the "conditional triangle". We indicate stratification (or conditioning) using a box around the node. 

##### Fork

In the sub-graph shown below, B is a cause of A and also a cause of C. By definition, a canonical fork is open and a conditional fork is closed. 


```{r fork}
#| fig-height: 2.5
#| fig-width: 2.5
#| fig-align: center
#| fig-cap: "Cannonical fork (common cause)"
#| 
make_dag_subgraph <- function(graph_type_input = "fork"){
  
  graph_nodes_list                           <- list() 
  
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A", label = r"($A$)"        , x = 2, y = 1,   node_shape = "covariate", graph_type = "fork")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "B", label = r"($B$)"        , x = 1, y = 2,   node_shape = "covariate", graph_type = "fork")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "C", label = r"($C$)"        , x = 2, y = 3,   node_shape = "covariate", graph_type = "fork")))
  
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A", label = r"($A$)"        , x = 1, y = 1,   node_shape = "covariate", graph_type = "spoon")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "B", label = r"($B$)"        , x = 2, y = 2,   node_shape = "covariate", graph_type = "spoon")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "C", label = r"($C$)"        , x = 1, y = 3,   node_shape = "covariate", graph_type = "spoon")))
  
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A", label = r"($A$)"        , x = 1, y = 1,   node_shape = "covariate", graph_type = "chopstick")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "B", label = r"($B$)"        , x = 2, y = 2,   node_shape = "covariate", graph_type = "chopstick")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "C", label = r"($C$)"        , x = 3, y = 3,   node_shape = "covariate", graph_type = "chopstick")))

  
  
  graph_nodes <- graph_nodes_list |>
    dplyr::bind_rows() |>
    dplyr::mutate(node_radius = 0.2) |>
    dplyr::mutate(label = latex2exp::TeX(label, output = "character")) |>
    dplyr::mutate(node_type = node_shape) |>
    dplyr::mutate(node_type = ifelse(node_shape == "preintervention", "covariate", node_shape)) |>
    dplyr::filter(graph_type == graph_type_input)
  
  
  
  graph_edges_list <- list()
  
  graph_edges_list[["fork"]] <- data.frame(
    from                 = c("B", "B"),
    to                   = c("A", "C")
  )
  
  graph_edges_list[["spoon"]] <- data.frame(
    from                 = c("A", "C"),
    to                   = c("B", "B")
  ) 
  
  graph_edges_list[["chopstick"]] <- data.frame(
    from                 = c("A", "B"),
    to                   = c("B", "C")
    )
  
  
  
  
  graph_edges <- graph_edges_list[[graph_type_input]]
  
  
  
  tidygraph::tbl_graph(nodes = graph_nodes, edges = graph_edges)  
  
}

make_dag_subgraph("fork") |>
  plot_swig(node_radius = 0.2)  +
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```


##### Spoon

In the sub-graph shown below, A is a cause of B and C is also a cause of B. By definition, a canonical spoon is closed and a conditional spoon is open. Spoons are commonly referred to as "colliders" in causal inference literature. 


```{r spoon}
#| fig-height: 2.5
#| fig-width: 2.5
#| fig-align: center
#| fig-cap: "Cannonical spoon (common effect)"

make_dag_subgraph("spoon") |>
  plot_swig(node_radius = 0.2)  +
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```



##### Chopstick

In the sub-graph shown below, A causes B and B causes C. By definition, a canonical chopstic is open and a conditional chopstick is closed. 



```{r chopstick}
#| fig-height: 2.5
#| fig-width: 3.5
#| fig-align: center
#| fig-cap: "Cannonical chopstick (mediator)"
#| 
make_dag_subgraph("chopstick") |>
  plot_swig(node_radius = 0.2)  +
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()
```



##### Rules

To summarize, canonical forks and chopsticks are open and conditional forks and chopsticks are closed. By contrast, canonical spoons are closed and conditional spoons are open. A path is open if it is of length one or if all the triangles in the path are open. If at least one triangle in the path is closed, the path is closed. Two nodes in a DAG are d-separated if all the paths between them are closed. Two variables in the NPSEM-IE represented by the DAG are (conditionally) independent if they are (conditionally) d-separated. 

```{r}

data.frame(
                            triangle    = c("Fork", "Spoon", "Chopstick"),
                            description = c(
                                            "Intermediate node is a common cause",
                                            "Intermediate node is a common effect",
                                            "Intermediate node is a mediator"
                                          ),
                            canonical  = c(
                                          "not d-separated",
                                          "d-separated",
                                          "not d-separated"
                                          ),
                            conditional = c(
                                          "d-separated",
                                          "not d-separated",
                                          "d-separated"
                                          )
                          ) |>
                    gt::gt()  |>
  gt::cols_label(
      triangle = "Type",
      canonical = "Canonical",
      conditional = "Conditional",
      description = "Description"
    ) 




```


