```{r  include=FALSE}
targets::tar_source("../R_functions")
```

### Causal reasoning with DAGs and SWIGs {.unnumbered}

At its core, the system we use in epidemiology to reason about counterfactual quantities such as causal effects is a statistical model called the Finest Fully Randomized Causally Interpretable Structured Tree Graph (FFRCISTG). In this current section (@sec-classic-causal-inference) we describe the assumptions of the FFRCISTG model using language that will aid their extension in @sec-network-causal-inference. This note is a brief overview of the FFRCISTG.

#### Finest, fully randomized, causally interpretable structured tree graph (FFRCISTG)

A FFRCISTG is a collection of non-parametric structural equation models which mimic the causal process that produced the variables under investigation. At the very least it is a collection of two NPSEMs -- a model of the observed data (observed data model) and a model of what the data would be under some intervention (counterfactual data model). The most common type of intervention in this framework is one which sets the value of one or more variables in the system (the exposures) with the goal of influencing the value of some set of variables in the system (the outcomes). The counterfactual data model is used to calculate quantities like causal effects. The observed data model is used to express those quantities in terms of statistics that can be estimated 

A non-parametric structural equation model with independent errors is a system of equations that relates all the entries in a given vector-valued random variable to each other. It does so without specifying parametric functions for each equation in the system. An example of such a model is shown by @eq-fullly-connected-dag. In this set of equations, values that are produced by equations higher up in the list serve as inputs to equations lower down on the list. The functions $f_*$ are deterministic, though their form is not necessarily known. The arguments $U_*$ represent error terms -- random variables that are independent of each other within and across observational units.

Consider a FFRCISTG modelling an intervention where we set formal dress $A_1$ to $a_1$, $A_2$ to $a_2$, and $A_3$ to $a_3$. The observed data model would be:

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, A_1) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, A_1, A_2) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1, Y_2) \\
\end{aligned}
$$ {#eq-fullly-connected-dag}

The counterfactual data model would be:

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2^{(a_1)} &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, a_1) \\
A_3^{(a_1, a_2)} &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, a_1, a_2) \\
Y_1^{(a_1, a_2, a_3)} &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, a_1, a_2, a_3) \\
Y_2^{(a_1, a_2, a_3)} &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, a_1, a_2, a_3, Y_1^{(a_1, a_2, a_3)}) \\
Y_3^{(a_1, a_2, a_3)} &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, a_1, a_2, a_3, Y_1^{(a_1, a_2, a_3)}, Y_2^{(a_1, a_2, a_3)}   ) \\
\end{aligned}
$$ {#eq-fullly-connected-swig}

::: {.aside}
Notice how in @eq-fullly-connected-swig, the values set under the intervention supercede the values that would have been generated had the experimenter not intervened. The former values are used in subsequent equations in the model whereas the latter values are not. 
:::

 





*Causal DAGs and SWIGS*

A causal directed acyclic graph (DAG) is a graph whose nodes represent the variables in an observational non-parametric structural equation model with independent errors. Directed edges point from the arguments to the result of each structural equation. 






```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-dag
#| fig-cap: "Fully connected causal DAG"

make_dag("fully_connected")         |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```

A single world intervention graph (SWIG) is a graph whose nodes represent the variables in a counterfactual non-parametric structural equation model with independent errors. Directed edges point from the arguments to the result of each structural equation. 



```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-swig
#| fig-cap: "Fully connected SWIG"

make_swig("fully_connected")      |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```



#### Model restrictions

Whereas parametric models are characterized by their probability density functions, non-parametric models of this type are usually characterized by their conditional independencies. For instance, if we add the restriction that all the measures are independent (or equivalently, that the DAG has no arrows), the resulting model would not be able to represent data from a causal system where some of the measures are correlated. By adding the restriction of independence, we would be eliminating the correlated data distribution from consideration as a possibility for how the data we are modelling are truly distributed.

It is possible to check whether two variables in a NPSEM are (conditionally) independent using the structural equations themselves by checking whether both variables are a function of the same error term $U_*$. DAGs and SWIGs are useful because they simplify this task by encoding the statistical relationships through a set of graphical rules called d-separation. Two variables in an NPSEM are conditionally independent if they are d-separated in the causal DAG representing the NPSEM.


Restrictions are crucial: to fully characterize the NPSEM specified in @eq-fullly-connected-dag using observed data, we would need to estimate 9 functions using one observation of the 9-dimensional joint distribution that gave rise to the participants' observations. Recruiting an additional person to the study would not ease this problem; it would add three new equations to the model and we would end up with a similar problem than the one we began with. We would have to estimate 12 functions using one observation of a 12-dimensional joint distribution.

In practice, we simplify this system of equations by making assumptions that leave us with fewer functions to estimate and more observations per function. These assumptions are called model restrictions because they restrict the set of distributions that could possibly be represented by the NPSEM.

