---
editor: 
  markdown: 
    wrap: 72
---

```{r  include=FALSE}
targets::tar_source("../R_functions")

```

# SSNAC IV: Measurement {#sec-data}

::: {#leading}
We describe the process of designing and testing a novel survey
questionnaire tool we call the MPX NYC person-place mapper. We show the
questions participants were presented with in the survey.
:::

## Person–Place Network Mapper

We designed, tested, and implemented the MPX NYC Person–Place Network
Mapper to address practical and ethical challenges in collecting
sensitive spatial data in an anonymous survey. Our aim was to capture
information on venues participants visited, including those where group
sex occurred, while minimizing the risk of re-identification through
location data.

### Requirements

We engaged a web-developer to create a survey tool which: a) collects
self-reported health and demographic information, b) collects
information on sexual and social networks through link tracing, c)
collects information on important geographic locations without burdening
the user, d) does not collect any identifying information from the user
including name, email, phone number, ip adress, or spatial coordinates.

![Example of a user prompt for a forced-response question in the custom
designed MPX NYC survey instrument](images/clipboard-3128943148.png)

### Place Mapping

Because participants were unlikely to recall precise addresses or zip
codes, we used the Google Maps API to allow them to identify locations
by landmarks, cross-streets, subway stations, neighborhood names, etc.
The map displayed detailed geographic information with standard
navigation tools (see Figure D.1).

![Map input question format developed for MPX
NYC](../_const/images/image_app_graphic.png){#fig-mapinputformat}

Participants were prompted to identify specific types of places, such as
their primary residence, and then to select additional locations where
they had physical or sexual contact in group settings. Each tap on the
map placed a marker, which triggered follow-up questions about activity
at that site and the type of venue.

### Link Tracing

Using URL parameters, we developed a link tracing system to anonymously
build a network of participants. At the start of the survey, each
participant received a unique identifier card containing a QR code and
word combination, which they were asked to save.

![Survey dialogue for sharing pre-written study recruitment messages
with social/sexual contact](/_const/images/share_screen.png)

Towards the end of the survey, participants were prompted to share a
pre-written invitation with a unique URL with social or sexual contacts.
If a contact used the link, an edge was added between the two
respondents in the graph database. When a new participant connected with
someone who had already completed the survey, the existing participant
could confirm their identity using information shown on their identifier
card, allowing the system to link their nodes without revealing their
identities.

### Implementation

To reduce the risk of identifying participants through their responses,
spatial data were coarsened before storage. Spatial coordinates were
converted to census tract identifiers before being transmitted from the
participant's device to the study database.

The tool’s front end was built as a single-page React/NextJS application
hosted on Vercel, with design based on the MPX NYC style guide. The back
end used a custom Neo4j graph database. Standard survey formats
(multiple choice, text, etc.) were integrated alongside the place
mapping and link tracing components.

Data flow proceeded as follows: the front end loaded questions from a
JSON file, parsed referral identifiers and language settings from the
URL, and requested a public identifier from the API. The API generated
and stored public/private identifier pairs in a secure table, returned
the public identifier and QR code to the participant, and transformed
identifiers before sending responses to the graph database.

For spatial inputs, the front end queried the FCC API, which returned
census block identifiers. These were truncated to census tract
identifiers before being stored in the study database. We conducted two
rounds of user testing with about ten participants each time to improve
usability.

## References

-   Vercel. 2024. *NextJS Documentation*. https://nextjs.org/docs.
-   Neo4j. 2024. *Neo4j Documentation*. https://neo4j.com/docs.
-   US Census Bureau. 2022. *Census Geography*.\
-   Federal Communications Commission (FCC). 2022. *API for Census Block
    Data*.

::: {#acknowledgements}
[Acknowledgements]{.underline}: The survey instrument was designed by
Keletso Makofane and coded by Keletso Makofane (front end) and Imran
Ansari (back end). Sudipta Saha found the web service that allowed us to
safely collect spatial data. Seema Kara wrote the initial technical
specifications for the instrument. neo4j granted a concessionary licence
for the graph database system we used for the back end. Pedro Carneiro
and Nguyen Tran led the development of survey questions. Cody Nolan and
Anton Antón Castellanos Usigli conducted translation from English to
Spanish. Robert Pitts helped to design questions on suspected mpox
symptoms.

[Lead author]{.underline}: Keletso Makofane, MPH, PhD.
[Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).
:::

```{r}
#| fig-width: 3
#| fig-height: 3
#| fig-align: center


plot_icon(icon_name = "taco", color = "light_purple", shape = 16, alpha = 0,  size = 100, image_size = 0.2)

```
