

```{r  include=FALSE}
targets::tar_source("../R_functions")

```

# MPX NYC: Measurement {#sec-measurement}

::: {#leading}
As part of the MPX NYC survey, we developed a digital tool called the MPX NYC Person–Place Network Mapper. We describe its design, functionality, and implementation.
:::

{{< include /C_ssnac3_causality/fig-plot-icon-droplets.qmd >}} 

## Person–Place Network Mapper 

We designed, tested, and implemented the MPX NYC Person–Place Network
Mapper to meet practical and ethical challenges in collecting sensitive
spatial data within an anonymous survey. Our goal was to capture
information on venues visited by participants—including those where
sexual activity occurred—while minimizing the risk of reidentification
through location data.

### Requirements {.unnumbered}

Working in partnership with a back-end web developer, we led the design
of a survey tool capable of collecting:

1.  Self-reported health and demographic information through multiple
    question types;
2.  Sexual and social network data through link tracing; and
3.  Information on relevant geographic locations.

Throughout, we sought to reduce participant burden and ensure that no
identifying information was collected.

![Example of a user prompt for a forced-response question in the custom
designed MPX NYC survey
instrument](images/clipboard-3128943148.png){fig-align="center"
width="498"}

### Place Mapping {.unnumbered}

Because participants were unlikely to recall precise addresses or ZIP
codes, we integrated the Google Maps API to allow them to identify
locations by business name, landmark, cross-street, subway station, or
neighborhood. The map displayed standard navigation tools and detailed
geographic information to aid orientation (see @fig-mapinputformat).

![Map input question format developed for MPX
NYC](../_const/images/image_app_graphic.png){#fig-mapinputformat
fig-align="center" width="488"}

At the beginning of the survey, participants were asked to locate their
primary residence on the map. Later, they identified venues where they
had physical or sexual contact in group settings. Each map tap placed a
marker and triggered follow-up questions about the type of venue and
activities that occurred there.

### Link Tracing {#sec-link-tracing .unnumbered}

We developed an anonymous link-tracing system using URL parameters to
construct a participant network. At survey initiation, each respondent
received a unique identifier card containing a QR code and word
combination.

![Survey dialogue for sharing pre-written study recruitment messages
with social/sexual
contact](/_const/images/share_screen.png){fig-align="center"
width="489"}

At the end of the survey, participants were invited to share a
pre-written recruitment message containing their unique URL with social
or sexual contacts. When a contact completed the survey using this link,
an edge was automatically added between the two respondents in the Neo4j
graph database. If a new participant shared a link with someone who had
already completed the survey, the latter could confirm the connection by
entering the code from their identifier card, linking their nodes
without revealing identities.

### Implementation {.unnumbered}

The tool’s front end was developed by the principal investigator as a
single-page React/Next.js application hosted on Vercel, with design
elements based on the MPX NYC style guide. Standard survey question
formats (e.g., multiple choice, free text) were combined with the custom
place-mapping and link-tracing components. The back end comprised a
custom Neo4j graph database connected to the front end through a study
API.

## Safety 

###  {.unnumbered}

Survey questions were carefully designed to avoid collecting any direct
or indirect identifiers, such as names, email addresses, IP addresses,
or exact geographic coordinates. Age was recorded as a categorical
variable rather than an integer to further reduce identifiability.

To protect participant privacy, geographic coordinates were converted
into census tract identifiers on the participant’s device before
transmission to the database. Census tracts represent U.S. geographic
areas containing 2,500–8,000 residents.

### Public and Private Identifiers  {.unnumbered}

When a participant began the survey, the front end parsed referral
identifiers and language settings from the access URL. This information
was sent to the study API, which generated a public–private identifier
pair and stored it in a secure table. The API then returned the public
identifier to the participant.

Upon survey completion, responses were transmitted to the API, which
replaced public identifiers with private ones before saving the data to
the database. The identifier-pair table was stored separately and
deleted after data collection concluded.

### Sensitive Spatial Data  {.unnumbered}

Each spatial input generated precise coordinates through the Google Maps
API. These were immediately processed on the front end through the FCC
API to obtain census block identifiers, which were then truncated to
census tracts. Only the census tract identifiers were transmitted to the
study database.

### Testing and Ethical Review  {.unnumbered}

We conducted two rounds of usability testing with approximately ten
participants each to refine the survey interface and workflow. The final
instrument and study protocol were reviewed and approved by the Harvard
T.H. Chan School of Public Health Institutional Review Board
(IRB22-0761).




{{< include C_2__questionnaire.qmd >}}


## References

-   Vercel. 2024. *NextJS Documentation*. https://nextjs.org/docs.
-   Neo4j. 2024. *Neo4j Documentation*. https://neo4j.com/docs.
-   US Census Bureau. 2022. *Census Geography*.\
-   Federal Communications Commission (FCC). 2022. *API for Census Block
    Data*.





::: {#acknowledgements}
[Acknowledgements]{.underline}: The survey instrument was designed by
Keletso Makofane and coded by Keletso Makofane (front end) and Imran
Ansari (back end). Sudipta Saha found the web service that allowed us to
safely collect spatial data. Seema Kara wrote the initial technical
specifications for the instrument. neo4j granted a concessionary licence
for the graph database system we used for the back end. Pedro Carneiro
and Nguyen Tran led the development of survey questions. Cody Nolan and
Anton Antón Castellanos Usigli conducted translation from English to
Spanish. Robert Pitts helped to design questions on suspected mpox
symptoms.

[Lead author]{.underline}: Keletso Makofane, MPH, PhD.
[Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).
:::

```{r}
#| fig-width: 3
#| fig-height: 3
#| fig-align: center


plot_icon(icon_name = "taco", color = "light_purple", shape = 16, alpha = 0,  size = 100, image_size = 0.2)

```
