# Analysis {#sec-analysis}

```{r  include=FALSE}
targets::tar_source("R_functions")
```

## Descriptive Statistics

We summarized participant characteristics within strata defined by race–gender. Gathering characteristics were categorized by sexual contact and distance from home and summarized.

To visualize patterns of movement across the city, we categorized gatherings in terms of the containing community district and home community district and plotted the frequencies as a matrix.

To identify which districts tended to receive participants and which tended to send participants, we calculated the difference between the proportion of gatherings and the proportion of residences in each community district.

Finally, we computed the spatial mixing coefficient for subgroups defined by age, sexual orientation, and race–gender to quantify how these groups interacted across space.

## Vaccine strategy model

Building on the spatial patterns observed in the descriptive analysis, we modeled a hypothetical intervention in which community districts were immunized sequentially according to priority rankings. To immunize a district was to immunize all individuals who had either a residence or a gathering in that district. Once immunized, individuals were assumed to be fully protected from acquiring or transmitting infection, and each person could only be immunized once.

We evaluated two alternative strategies for ordering community districts for vaccination: a contact-neutralizing strategy, and a movement-neutralizing strategy. Each time a community district is immunized, we recalculate two key outcome measures: spatial efficiency and spatial network impact, each reflecting a different dimension of intervention performance.

[Control strategies]{.underline}: In the contact-neutralizing strategy, community districts were ranked by social catchment (the number of gatherings and residences they contained), counting only residences of participants who reported group contact and had not yet been immunized. This approach prioritizes districts with the highest concentration of sexual or physical contact, aiming to immunize as many individuals as possible while focusing on a minimal number of locations.

In the movement-neutralizing strategy, community districts were ranked according to their spatial catchment —- a measure of how strongly each district is connected to others across the city. This strategy prioritizes districts that function as spatial hubs for participant movement, targeting them early in the immunization sequence to contain potential city-wide spread.

[Public health outcomes]{.underline}: Spatial efficiency is defined as the total number of immunized individuals divided by the number of community districts immunized. To compare the two intervention strategies, we visualized the number of community districts required to immunize approximately 33% and 66% of the total population.

Spatial network impact was defined as the proportion of individuals belonging to the largest connected component of the MPX NYC Participant Network. This measure reflects the extent to which susceptiuble individuals remain embedded within the same transmission-relevant network after each intervention step. To compare strategies, we plotted, for each additional community district immunized, the proportions of individuals who were immunized, susceptible and still within the largest component, and susceptible but outside of the largest component.

## Statistical Inference

```{r}
number_reps <- targets::tar_read(config_list)[[1]][["settings"]][["n_reps_graph"]]
```

To quantify uncertainty around our network-based estimates, we used the bootstrap to calculate confidence intervals, assuming that the underlying data are a realization of a Bipartite Random Network Finest Fully Randomized Causally Interpretable Structured Tree Graph (BRNFFRCISTG) model (see @sec-social-spatial-networks).



Recalling that the MPX NYC person-place graph includes participant observations and community district observations as nodes, we resampled participant observations `r number_reps` times with replacement. An observation was defined as the complement of measures on a particular participant as well as all the edges that connect that participant to their community districts of residence and gatherings.

This approach provides robust, nonparametric inference by repeatedly drawing samples from the observed data to approximate sampling variability.
