---
title: "MPX NYC"
subtitle: "Key findings and recommendations"
author: "Keletso Lehola Lekoatsa"
date: 23 May 2024
prefer-html: true
execute:
  echo: false
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
format: 
  docx:
    toc: true
bibliography: bibliography.bib
---

```{r libraries, echo=FALSE}

library(tidyverse)
library(ggplot2)
#library(mpxnyc)
library(sf)
library(tidygraph)
library(ggraph)
library(igraph)

library(targets)

mpxnyc_colors <- mpxnyc::mpxnyc_colors
attach(mpxnyc_colors)

```

```{r scripts, echo=FALSE, warning=FALSE, message=FALSE, include= FALSE}
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/1_data_processing")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/2_data_summary")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/3_data_extract")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/4_plot")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/5_tables")


targets::tar_make() # Runs the data pipeline shown in _targets.R

```

# To Do

1.  Measures of centrality and density
2.  Results
3.  Introduction
4.  Discussion
5.  Appendices

# Methods

```{r text_variables}
start_date <- targets::tar_read(data_bipartite_graph_collected) %>% data.frame() %>% pull(createdAt) %>% min(na.rm= TRUE)
end_date   <- targets::tar_read(data_bipartite_graph_collected) %>% data.frame() %>% pull(createdAt) %>% max(na.rm= TRUE)

```

## Data Collection

Under the aegis of The Rapid Epidemiologic Study of Prevalence, Networks, and
Demographics of Monkeypox Infection (RESPND-MI), we implemented MPX NYC - a brief,
anonymous, online survey among transgender people and gay, bisexual, and
other men who have sex with men. Data were collected from 20 August 2022
to 15 November 2022 in New York City.

### RESPND-MI Community Forum

To elicit input about the study from queer and trans individuals and
organizations who do health-related work, we held a rapid consultation
meeting at the outset of the project. Investigators compiled a list of
53 invitees and invited them. To maximize uptake, we attempted to match
each invitee with an investigator they had a prior relationship with.

At the consultation meeting, participants requested that the RESPND-MI
team host a weekly meeting since there were no other venues for
discussing the outbreak from the perspectives of organizations that
deliver services to queer and trans individuals, and individuals who had
experienced mpox infection. We named the space the RESPND-MI Queer and
Trans Community Forum and held it weekly from June to August 2022.
Though the main purpose of the Community Forum was to share information
and allow organizations and individuals to coordinate political action ,
it was also used to consult on study-related decisions. About 80
individuals participated in the Community Forum over the 2-month period
we held it. Further details can be found in a previous publication
[@roth2023global].

### Recruitment

We collaborated with a marketing agency to design and implement a study
recruitment campaign in English and Spanish. The brief was to create a
name and visual identity that convey scientific rigor, build trust with
the community, and to stand out in a crowded online advertising space
(see @fig-requirements). As a starting point, we suggested a campaign
that playfully communicates using emojis that have sexual connotations.
Two campaign names and four marketing concepts (see @fig-options) were
developed by the marketing agency and presented to the RESPND-MI
Community Forum. The final concept and name were decided by consensus
during that meeting.

[![Requirements for MPX NYC
Study](images/clipboard-2397454480.png){#fig-requirements
fig-alt="Requirements for MPX NYC Study"}](https://www.mpxresponse.org)

Marketing materials included graphics, videos by queer influencers, and
a style guide (including colors, icons, and fonts) for all public-facing
materials of the MPX NYC study. We organized these materials into a
"social media toolkit" so that they would be easy for individuals and
organizations to share through their own social media accounts.
Advertisements were placed through Grindr, Twitter, Instagram, and
outdoor electronic billboards.

![Options for visual identity of MPX
NYC](images/clipboard-22126019.png){#fig-options
fig-alt="Options for visual identity of MPX NYC"}

### Data collection instrument

We designed and implemented a novel online survey instrument which
captures coarsened spatial information to maintain anonymity. Along with
standard question formats (multiple choice, single choice, text field
etc.) we developed a question format to elicit spatial data.

In the map-input question format, participants are prompted to indicate
all places of a particular type by tapping on a displayed map (see
@fig-mapinputformat). Each time the user taps on the map, a marker
appears and a pop-up window asks them to answer a series of questions
related to that location. Spatial data were coarsened by transforming
longitude-latitude coordinates into the identifiers of the census tract
that contain them. Census tracts are a spatial unit that exhaustively
divides the United States into areas ranging from $2500$ to $8000$ in
population size [@uscensus2022].

The look and feel of the data collection instrument was based on the MPX
NYC style guide. The front end was developed as a single-page web
application using the React/NextJS framework [@nextjsd2024]. It uses the
Google Maps [@google2024] and Federal Communications Commission
[@federal] APIs to collect and transform spatial data. The backend was a
custom-built neo4j graph database [@neo4j2024] hosted on a commercial
cloud server platform. The instrument underwent two rounds of user
testing before data collection started.

![Map input question format developed for MPX
NYC](images/clipboard-1908474363.png){#fig-mapinputformat}

### Inclusion and Exclusion Criteria

Potential participants were included in the study if they consented to
participate, were over 18 years of age, identified as transgender, gay,
bisexual, or as men who have sex with other men, and were in New York
City in the four weeks preceding the survey. Potential participants were
excluded if they were younger than 18 years of age or they withdrew
consent.

### Translation

All study materials were professionally translated from English to
Spanish. The translation was reviewed by six professionals in
health-related fields whose primary language is Spanish.

### Ethical Review

The study was reviewed and approved by the T.H. Chan School of Public
Health Institutional Review Board (IRB22-0761).

## Measures

### Participants

The brief (5 minute) questionnaire was implemented in English and
Spanish. It measured participant demographics, utilization of healthcare
services; and connection to queer or transgender community.

Gender identity was measured using a two-step approach: first, we
solicited the participant’s current gender (man, woman, trans man, trans
woman, non-binary, other), and then sex assigned at birth (male, female,
other). Those whose gender identity and sex assigned at birth were not
concordant were categorized as transgender. We used current gender to
further categorize transgender people into men and women.

Race was measured using a multiple selection question based on census
categories (white, black, latino/a/x, asian, pacific islander, other).
We combined gender identity and race to form a gender-race variable,
collapsing small cells across racial groups (white cisgender man, latinx
cisgender man, black cisgender man, other cisgender man, non-binary
person, transgender man, transgender woman, cisgender woman, another
demographic).

### Residence and Contact venues

Using the map-input question format, we solicited the census tract of
participants' primary residences. Among those who reported physical or
sexual contact in a group setting in the preceding 4 weeks, we solicited
the locations of the venues at which the contact happened. We refer to
these locations as "contact venues". For each contact venue (see
@fig-mapinputformat), participants indicated the type of place it was
(dance party, sex party, darkroom, sport game, concert, theatre/show,
private residence, sex club, bathhouse, park, something else) and
whether they had sexual (vs. non-sexual) contact there.

## Statistical Analysis

### Participant and contact venue characteristics

Participant characteristics were tabulated by contact in the preceding 4
weeks. We also tabulated contact venue characteristics by distance from
home and by sexual contact.

Census tract identifiers were converted into community district
identifiers. Census tracts are nested in community districts. They are
defined by the City of New York [@nycopendata2022]. For each contact
venue, we approximated the distance from home to that venue using an
ordinal variable with three levels: same community district as home;
different community district but same borough as home; different borough
than home.

### Spatial sorting and mixing

To understand how different demographic groups mix in physical space, we
defined $\psi_{a \rightarrow b} \in [-1,\infty]$ as the spatial
selection coefficient of subgroup $a$ for subgroup $b$. The spacial
selection coefficient is defined as the spacial selection ratio less 1.
The numerator for this ratio is the conditional probability of someone
in subgroup $a$ sharing a community district with someone in subgroup
$b$. The denominator is the marginal probability of having
characteristic $b$.

This measure is $0$ when contact venues and residences for subgroups $a$
and $b$ are distributed independently of each other in space; positive
if contact venues and residences for subgroup $a$ tend to be in the same
community districts as those for subgroup $b$; and negative if subgroup
$a$ tends to be in community districts that do not have contact venues
and residences for subgroup $b$.

### Participant spatial overlap network

We constructed a network where nodes are
participants and weighted ties indicate the number of community
districts shared by those participants. We say two participants share a
community district if both have a residence or contact venue in that
community district.

### Hypothetical immunization intervention

We examined the coverage efficiency and network impact of a hypothetical
intervention to slow down the wide dissemination of a novel pathogen.
The intervention a) lists community districts in decreasing order of
count of residences and contact venues, b) immunizes all individuals who
have a residence or contact venue in the top district, c) removes all
contact venues and residences for immunized individuals. We say the
hypothetical intervention is of order $k\in \mathbb{Z}$ if these steps are
completed $k$ times.

#### Efficiency

We examined coverage efficiency by plotting the proportion of immunized
individuals against the order of the hypothetical intervention ($k$)
carried out in community districts. For low $k$, the proportion of
immunized individuals will grow faster than the order of the
hypothetical intervention.

#### Network impact

We used the community district overlap network to understand how the
hypothetical intervention would likely affect transmission dynamics. In
that network, immunizing a community district removes all individuals
who have a residence or contact place in that that community district
from the network. (This is analogous to using a 100% efficacious vaccine and achieving 100% coverage in immunized community districts.) For each $k$, we calculated centrality
measures to show how the participant spatial overlap network would evolve as more community districts are
immunized.



### Statistical Inference

We used the non-parametric bootstrap to calculate point estimates and
95% confidence intervals (CI). Participants were re-sampled with
replacement `r targets::tar_read(initial_settings)$n_reps_graph` times.
For each measure, the lower and upper bound of confidence intervals were
calculated as the 0.025th and 0.975th quantiles of the empirical
distribution produced by re-sampling. @tbl-descriptives

# Results

## Participants

```{r table_1}
#| tbl-cap: "Participants in MPX NYC Study by Sex / Physical Contact in Congregate Setting in past 4 weeks"
#| label: tbl-descriptives

by_group_sex <- tar_read(data_bipartite_graph_collected) %>%
  make_table_1_datatable(by = groupSex, variables = c(overall, age, genderId, race, sexOrientation, channel, hivPrep, monkeypoxVaccine, monkeypoxTest, monkeypoxTest, countSex, countFriends, countPhysical, borough)) %>%
  mutate(stratum = stratum_groupSex) 

overall <- tar_read(data_bipartite_graph_collected) %>%
  mutate(groupSex = "overall") %>%
  make_table_1_datatable(by = groupSex, variables = c(overall, age, genderId, race, sexOrientation, channel, hivPrep, monkeypoxVaccine, monkeypoxTest, monkeypoxTest, countSex, countFriends, countPhysical, borough)) %>%
  mutate(stratum = stratum_groupSex) 


rbind(by_group_sex, overall) %>%
  draw_table_1(tar_read(factor_labels))


```

```{r sex_orientation}
#| fig-cap: "Sexual orientation of MPX NYC participants by race and gender"
#| label: fig-sexorientation-racegender
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(sexOrientation, demo_group) %>%
  plot_radar_grid() %>%
  apply_style_radar_grid_plot()
```

```{r prep_hiv}
#| fig-cap: "PrEP and HIV Status of MPX NYC participants by race and gender"
#| label: fig-prephiv-racegender
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(hivPrep, demo_group) %>%
  plot_radar_grid() %>%
  apply_style_radar_grid_plot()
```

## Contact venues

```{r placetype}
#| fig-cap: "MPX NYC contact venue type by distance from home and sexual contact"
#| label: fig-places-distance-sexcontact
#| fig-width: 9
#| fig-height: 9

make_table_freq3(placeType, placeSex, distanceFromHome, person_analysis = FALSE) %>%
  filter(!is.na(level)) %>%
  plot_radar_stratified2() %>%
  apply_style_radar_facet_plot()

```

## Participants connecting through contact venues

```{r movement}
#| fig-cap: "Movement between home and contact venues by MPX NYC participant"
#| label: fig-communities-movement
#| fig-width: 10
#| fig-height: 10

  make_table_movement_travel() %>%
    plot_matrix_movement() %>%
    apply_style_matrix_movement()
```

```{r netviz_places}
#| fig-cap: "Network of community districts connected by MPX NYC participants"
#| label: fig-communities-network
#| fig-width: 8
#| fig-height: 8


make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
  plot_network_viz() %>%
  apply_style_network_viz()
  
```






```{r}
#| fig-cap:  "Social mixing matrices for MPX NYC participants by race-gender (top), sexual orientation (bottom left), and age (bottom right)"
#| label: fig-subgroup-mixing
#| fig-width: 12
#| fig-height: 17

mixing_demo_group_panel          <- make_table_mixing(demo_group) %>%
                                      plot_matrix_mixing() %>%
                                      apply_style_matrix_mixing_plot()


mixing_sexOrientation_panel      <- make_table_mixing(sexOrientation) %>%
                                      plot_matrix_mixing() %>%
                                      apply_style_matrix_mixing_plot()


mixing_age_panel                 <- make_table_mixing(age) %>%
                                      plot_matrix_mixing() %>%
                                      apply_style_matrix_mixing_plot()

mixing_bottom_panel              <- cowplot::plot_grid(mixing_sexOrientation_panel, mixing_age_panel, nrow = 1)

cowplot::plot_grid(mixing_demo_group_panel, mixing_bottom_panel, ncol=1, rel_heights = c(2,1.1))


```

## Efficient and effective interventions

```{r map}
#| fig-cap: "High-coverage community districts"
#| label: fig-hiimpact-communities
#| fig-width: 10
#| fig-height: 10
#| 
map_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  plot_coverage_map()  %>%
                  apply_style_coverage_map()

bar_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  filter(group != "Group C") %>%
                  plot_coverage_bar() %>%
                  apply_style_coverage_bar() 

  cowplot::ggdraw(map_plot) +
  cowplot::draw_plot(bar_plot, x = .1, y = .55, width = 0.25, height = 0.25)

```




```{r}
#| fig-cap: "Evolution of spatial network centrality"
#| label: fig-centrality-measures
#| fig-width: 10
#| fig-height: 7


centrality_lcc         <- make_table_centrality() %>% 
                                plot_netimpact_bar() %>%
                                apply_style_line_plot() %>%
  {. + theme(legend.position = "top", axis.title.y = element_text(angle = 90, margin = margin(0, 20, 0, 0)), axis.title.x = element_text(margin = margin(20,0,0,0)), axis.text.x = element_text()) +
      scale_x_continuous("Intervention order") +
                                   scale_y_continuous("% Participants unvaccinated", labels = scales::percent)}

centrality_closeness   <- make_table_centrality() %>%
                                plot_centrality_bar(sd_closeness) %>%
                                apply_style_line_plot() %>%
  {. + 
                                    scale_y_continuous("Se. closeness centrality") + 
      theme(axis.title.y = element_text(angle = 90, margin = margin(0,20,0,0)), plot.margin = margin(80, 0, 40, 40), axis.title.x = element_text(margin = margin(20,0,0,0))) +
      scale_x_continuous("Intervention order")
    }


centrality_betweenness <- make_table_centrality() %>%
                                plot_centrality_bar(avg_betweenness) %>%
                                apply_style_line_plot()  %>%
  {. + 
                                    scale_y_continuous("Avg. betweenness centrality") + 
      theme(axis.title.y = element_text(angle = 90, margin = margin(0,20,0,0)), plot.margin = margin(40, 0, 80, 40), axis.title.x = element_text(margin = margin(20,0,0,0))) +
      scale_x_continuous("Intervention order")
    }


centrality_top         <- centrality_lcc

centrality_bottom      <- cowplot::plot_grid(centrality_closeness, centrality_betweenness, ncol = 1)

cowplot::plot_grid(centrality_top, centrality_bottom, nrow = 1, rel_widths = c(2,1))

```


# Acknowledgements

We are grateful to sponsors of the study: amfAR; Center for AIDS
Research at Harvard University; UCLA, and to the XX individual donors
who gave amounts ranging from XX to XX. LinkNYC and Grindr donated advertising to the study, neo4j donated a license for their proprietary database software. 

Consulted: Eric Tchetgen Tchetgen, Forrest W. Crawford, and Kenneth Mayer on technical aspects of the study

Translation: Cody Patrick Nolan coordinated translation of the survey instrument and marketing
materials. Antón Castellanos-Usiglu conducted the translation and verified them with Cody Patrick Nolan, Chema Jiménez, Juan Pablo Amaya Amaris, Santiago Aguilera Mijares, and María Andrea Santos Guzmán. 

Questionnaire Drafting: Keletso Makofane, Pedro Carneiro and Nguyen Tran drafted the questionnaire. 

Questionnaire Review: Lisa Berkman, Tom Carpino, David Barr, and Judy Auerbach reviewed the questionnaire.

Admin: Sudipta Saha coordinated study activities, Christian Urrutia extended the admin capabilities of PrEPP4All to the study, Keletso Makofane kept financial records

Keletso Makofane developed
and coded the survey instrument. The survey instrument uses the FCC Data
API but is not endorsed or certified by the FCC.

Most of all, we thank, and stand in solidarity with, the MPX NYC participants who gave of their time to make the study a success.

# References
