---
title: "MPX NYC"
subtitle: "Key findings and recommendations"
author: "Keletso Makofane"
date: 23 May 2024
execute:
  echo: false
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

```{r libraries, echo=FALSE}

library(tidyverse)
library(ggplot2)
#library(mpxnyc)
library(sf)
library(tidygraph)
library(ggraph)
library(igraph)

library(targets)

mpxnyc_colors <- mpxnyc::mpxnyc_colors
attach(mpxnyc_colors)

```

```{r scripts, echo=FALSE, warning=FALSE, message=FALSE, include= FALSE}
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/1_data_processing")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/2_data_summary")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/3_data_extract")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/4_plot")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/5_tables")


targets::tar_make() # Runs the data pipeline shown in _targets.R

```

# Methods

```{r text_variables}
start_date <- targets::tar_read(data_bipartite_graph_collected) %>% data.frame() %>% pull(createdAt) %>% min(na.rm= TRUE)
end_date   <- targets::tar_read(data_bipartite_graph_collected) %>% data.frame() %>% pull(createdAt) %>% max(na.rm= TRUE)

```

## Data Collection

As part of The Rapid Epidemiologic Study of Prevalence, Networks, and
Demographics of Monkeypox Infection (RESPND-MI), we implemented a brief,
anonymous, online survey. Data were collected from 20 August 2022 to 15
November 2022 among transgender people and gay, bisexual, and other men
who have sex with men in New York City.

### RESPND-MI Community Forum

To benefit from the practice-based knowledge held by individuals and
queer and trans organizations, and to ensure that we were not
duplicating efforts, we planned a rapid consultation meeting at the
outset of the project. Investigators compiled a list of 53 key
stakeholders in New York City. To maximize participation, these
individuals were invited via email by investigators with whom they had a
prior relationship (where possible).

At the consultation meeting on 27 June 2022, participants requested a
weekly meeting since there were no similar fora dedicated to mpox
epidemiology, research, and health programs at the time. We held the
RESPND-MI Queer and Trans Community Forum weekly from June to August
2022. Though the main purpose of the Community Forum was to share
information and coordinate response efforts, we also used the meeting to
consult about specific decisions. About 80 people participated in the
from June to August 2022.

### Recruitment

We collaborated with a marketing agency to develop and conduct a study
recruitment and health information campaign in English and Spanish. Our
brief to the ageny was to create a name and visual identity that convey
scientific rigor, build trust with the community we aimed to survey, and
to stand out in a crowded online advertising space (see
@fig-requirements). As a starting point, we suggested a campaign that
playfully communicates using emojis that are used to communicate about
sex on online hookup platforms. Four marketing concepts (see
@fig-options) and two campaign names were developed by the marketing
agency and presented to the RESPND-MI Community Forum. The final concept
and name were decided by consensus.

[![Requirements for MPX NYC
Study](images/clipboard-2397454480.png){#fig-requirements
fig-alt="Requirements for MPX NYC Study"}](https://www.mpxresponse.org)

Marketing materials included graphics for paid mobile ads, out-of-home
ads, videos by paid queer influencers, and a style guide for all
public-facing materials of the MPX NYC study (including colors, icons,
and fonts). We organized these materials into a "social media toolkit"
so that they would be easy for individuals and organizations to share
through their own social media accounts. Advertisements were placed
through Grindr, Twitter, Instagram, and electronic billboards.

![Options for visual identity of MPX
NYC](images/clipboard-22126019.png){#fig-options
fig-alt="Options for visual identity of MPX NYC"}

### Data collection instrument

We designed and implemented a novel online survey instrument which
captures detailed spatial information while maintaining anonymity. The
look and feel of the data collection instrument was based on the MPX NYC
style guide.

Along with standard question formats (multiple choice, single choice,
and text field etc.) we developed a novel question format (which we call
the map-input question format here) to elicit spatial information.

In map-input questions, participants are prompted to indicate all places
of a particular type by tapping on a map (see @fig-mapinputformat). Each
time the user taps on the map, a marker appears and a pop-up window asks
them to confirm the location. One confirmed, participants answer a
series of questions related to that location. Once those are answered,
the user is allowed to tap on the map again to indicate another location
or to move on the next question.

![Map input question format developed for MPX
NYC](images/clipboard-1908474363.png){#fig-mapinputformat}

To protect anonymity, spatial data were saved as census tract
identifiers rather than latitude-logitude coordinates. Census tracts are
a spatial unit that exhaustively divides the united states up into areas
ranging from XX to XXX in population size (CITE).

For each place that a user adds using the map-input question format, the
Google maps API (CITE) returns the latitude and longitude to the user's
device. The coordinates are sent from the user's device to the Federal
Communications Commission API (<https://geo.fcc.gov/api/census/>) which
returns the identifier for the census block containing the spatial
coordinates. The census black identifier is transformed into a census
tract identifier by truncating the last X digits (CITE), then it is
transmitted to the study database. Data were stored in a custom-built
graph database system hosted on a commercial cloud server platform. The
instrument underwent two rounds of user testing before data collection.

### Inclusion and Exclusion Criteria

Potential participants were included in the study if they consented to
participate, were over 18 years of age, identified as transgender, gay,
bisexual, or as men who have sex with other men, and were in New York
City in the four weeks preceding the survey. Potential participants were
excluded if they were younger than 18 years of age or they withdrew
consent.

### Translation

All study materials were professionally translated from English to
Spanish. The translation was reviewed by six professionals in
health-related fields whose primary language is Spanish.

### Ethical Review

The study was reviewed and approved by the T.H. Chan School of Public
Health Institutional Review Board (IRB22-0761).

## Measures

### Participants

The questionnaire was implemented in English and Spanish and designed to
take less than 5 minutes to complete. It measured participant
sociodemographics, utilization of healthcare services such as
pre-exposure prophylaxis (PrEP), HIV treatment and vaccination against
MPOX; connection to queer or transgender community through sex and
socializing; and location of primary residence.

Gender identity was measured using a two-step approach: first, we
solicited the participant’s current gender (man, woman, trans man, trans
woman, non-binary, Other), and then their sex assigned at birth (male,
female, other). Those whose gender identity was not concordant with the
gender commonly associated with their sex assigned at birth were
categorized as transgender. We used current gender to further categorize
transgender people into men and women.

Race was measured using a multiple selection question based on census
categories (White, Black, Latino/a/x, Asian, Pacific Islander, Other).

We defined gender-race subgroup as the combination of gender identity
and race, collapsing small cells across racial group (White Cisgender
Man, Latinx Cisgender Man, Black Cisgender Man, Other Cisgender Man,
Non-Binary Person, Transgender Man, Transgender Woman, Cisgender Woman,
Another Demographic).

### Residence and Contact venues

Using the map-input question format, we asked the location of
participants' primary residence. Among those who reported physical or
sexual contact at a congregate setting in the preceding 4 weeks, we
solicited the locations of the venues at which the contact happened. We
refer to these locations as "contact venues".

For each contact venue (see @fig-mapinputformat), participants indicated
the type of place it was (Dance party, Sex Party, Darkroom, Sport Game,
Concert, Theatre/Show, Private Residence, Sex Club, Bathhouse, Park,
Something Else) and whether they had sexual or (non-sexual) physical
contact there.

## Statistical Analysis

### Participant characteristics

Participant characteristics and contact venue characteristics were
tabulated.

### Contact venue characteristics

We tabulated contact venue characteristics by distance from home and by
sexual contact. Census tract identifiers were converted into community
district identifiers. Community districts are defined by the City of New
York (CITAION). Census tracts are nested in community districts.

We approximated the distance from home to each contact venue using an
ordinal variable with levels: same community district as home; different
community district but same borough as home; different borough than
home.

### Spatial sorting and mixing

To understand how different demographic groups mix in physical space, we
constructed a spatial overlap network. In this network, nodes are
participants and weighted ties indicate that number of community
districts shared by those participants. Two participants are said to
share community district if they each have at least one residence or
contact venue in that community district.

We define a spatial overlap ratio as the ratio of the two probabilities
to follow, less 1. The spatial overlap ratio from characteristic $a$ to
characteristic $b$ is the ratio of the conditional probability of
someone with characteristics $a$ sharing a community district with
someone with characteristic $b$ with the marginal probability of having
characteristic $b$. The spatial mixing coefficient is defined as this
ratio less 1. This measure ranges from -1 to 1. It is 0 when subgroups
$a$ and $b$ are perfectly mixed, positive if subgroup $a$ tends to share
community districts with subgroup $b$, and negative when subgroup $a$
tends to not share community districts with subgroup $b$.

As a crude measure of the distance between the contact venue and
participant residence, we categorized contact venues into those that are
in the same community as the residence, the same borough but different
community, or a different borough than the participant's residence.

We visualized the movement of study participants between home and
contact venues using a matrix plot.

### Intervention efficiency and network impact

We examined the efficiency and transmission impact of a hypothetical
intervention to stop the dissemination of a pathogen. The intervention
a) lists community districts in decreasing order of popularity (in terms
of residence and contact venues), b) renders all individuals in the top
$n$ community districts unable to acquire or transmit the pathogen (i.e.
immunize).

Because of spatial clustering, we would expect the first few community
districts to contain more people than the last few districts in the
list. i.e. for low $n$, the number of immunized individuals will grow
faster than the number of community districts vaccinated. This tendency
will be reinforced by the removal of individuals in unvaccinated
community districts who are associated with a community district that
has been vaccinated. In other words, vaccinating an individual in a
particular community district removes that individual from that district
and any other community districts they are associated with. We examined
intervention efficiency by plotting the proportion of immunized
individuals against $n$.

In the spatial overlap network, immunizing a community district removes
all individuals associated with that community district from the
network, possibly changing the structure of the network.

Efficiency was examined by understanding what the minimum number of
community districts to be vaccinated to cover 33% of the population, and
separately to cover 66% of the population.

Transmission impact was examined by understanding the impact of removing
community districts which have been vaccinated on the spatial overlap
network.

### Statistical Inference

We used the non-parametric bootstrap to calculate point estimates and
95% confidence intervals (CI). Participants were re-sampled with
replacement `r targets::tar_read(initial_settings)$n_reps_graph` times.
For each measure, the lower and upper bound of confidence intervals were
calculated as the 0.025th and 0.975th quantiles of the empirical
distribution produced by re-sampling.

# Results

## Participants

```{r table_1}
#| tbl-cap: "Participants in MPX NYC Study by Sex / Physical Contact in Congregate Setting in past 4 weeks"
#| label: tbl-descriptives-by-groupsex

by_group_sex <- tar_read(data_bipartite_graph_collected) %>%
  make_table_1_datatable(by = groupSex, variables = c(overall, age, genderId, race, sexOrientation, channel, hivPrep, monkeypoxVaccine, monkeypoxTest, monkeypoxTest, countSex, countFriends, countPhysical, borough)) %>%
  mutate(stratum = stratum_groupSex) 

overall <- tar_read(data_bipartite_graph_collected) %>%
  mutate(groupSex = "overall") %>%
  make_table_1_datatable(by = groupSex, variables = c(overall, age, genderId, race, sexOrientation, channel, hivPrep, monkeypoxVaccine, monkeypoxTest, monkeypoxTest, countSex, countFriends, countPhysical, borough)) %>%
  mutate(stratum = stratum_groupSex) 


rbind(by_group_sex, overall) %>%
  draw_table_1(tar_read(factor_labels))


```

```{r sex_orientation}
#| fig-cap: "Sexual orientation of MPX NYC participants by race and gender"
#| label: fig-descriptives-by-groupsex
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(sexOrientation, demo_group) %>%
  plot_radar_grid() %>%
  add_caption() %>%
  #add_title("Sexual orientation of MPX NYC participants by race and gender") %>%
  apply_style_radar_grid_plot()
```

```{r prep_hiv}
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(hivPrep, demo_group) %>%
  plot_radar_grid() %>%
  add_caption() %>%
  add_title("PrEP and HIV status of MPX NYC participants by race and gender") %>%
  apply_style_radar_grid_plot()
```

## Contact venues

```{r placetype}
#| fig-width: 9
#| fig-height: 9

make_table_freq3(placeType, placeSex, distanceFromHome, person_analysis = FALSE) %>%
  filter(!is.na(level)) %>%
  plot_radar_stratified2() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("MPX NYC contact venue type by distance from home and sexual contact") %>%
  apply_style_radar_facet_plot()

```

## Participants connecting in space

```{r movement}
#| fig-width: 13
#| fig-height: 12

  make_table_movement_travel() %>%
    plot_matrix_movement() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Movement between boroughs by MPX NYC Participants") %>%
    apply_style_matrix_movement()
```

```{r plot_matrix_mixing_age}
#| fig-width: 8.5
#| fig-height: 8.5


make_table_mixing(age) %>%
  plot_matrix_mixing() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Race-Gender of MPX NYC Participants") %>%
  apply_style_matrix_mixing_plot()



```

```{r plot_matrix_mixing_sexorientation}
#| fig-width: 9.5
#| fig-height: 9.5


make_table_mixing(sexOrientation) %>%
  plot_matrix_mixing() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Race-Gender of MPX NYC Participants") %>%
  apply_style_matrix_mixing_plot()



```

```{r plot_matrix_mixing_demo_group}
#| fig-width: 14
#| fig-height: 14


make_table_mixing(demo_group) %>%
  plot_matrix_mixing() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Race-Gender of MPX NYC Participants") %>%
  apply_style_matrix_mixing_plot()



```

## Efficient and effective interventions

```{r map}
#| fig-width: 10
#| fig-height: 10
#| 
map_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  plot_coverage_map()  %>%
                  apply_style_coverage_map()

bar_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  filter(group != "Group C") %>%
                  plot_coverage_bar() %>%
                  apply_style_coverage_bar() 

  cowplot::ggdraw(map_plot) +
  cowplot::draw_plot(bar_plot, x = .1, y = .55, width = 0.25, height = 0.25)

```

```{r netviz_places}
#| fig-width: 8
#| fig-height: 8


make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
  plot_network_viz() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Network of community districts connected by MPX NYC participants") %>%
  apply_style_network_viz()
  
```

```{r graph_connectedness}
#| fig-width: 8
#| fig-height: 5

make_table_centrality() %>%
  filter(intervention_ranking < 41) %>%
    plot_netimpact_bar() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Proportion of unreached in largest connected network component") %>%
    apply_style_bar_netimpact()

```

# Acknowledgements

LinkNYC and Grindr advertisements were provided as donations-in-kind.

Cody Patrick Nolan coordinated translation of the survey instrument and
marketing materials. Antón Castellanos-Usiglu, who was engaged as a
professional translator, conducted the translation and verifieed them
with Cody Patrick Nolan, Chema Jiménez, Juan Pablo Amaya Amaris,
Santiago Aguilera Mijares, and María Andrea Santos Guzmán.

Developed questionnaire:

-   Pedro Carneiro

-   Nguyen Tran

-   Keletso Makofane

Reviewed questionnaire:

-   Lisa Berkman

-   Tom Carpino

-   David Barr

-   Judy Auerbach

Neo4j gave us a free license
