---
title: "MPX NYC"
subtitle: "Key findings and recommendations"
author: "Keletso Lehola Lekoatsa"
date: 23 May 2024
prefer-html: true
execute:
  echo: false
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
format: 
  docx:
    toc: true
bibliography: bibliography.bib
---

```{r libraries, echo=FALSE, message=FALSE}

library(tidyverse)
library(ggplot2)
#library(mpxnyc)
library(sf)
library(tidygraph)
library(ggraph)
library(igraph)

library(targets)

mpxnyc_colors <- mpxnyc::mpxnyc_colors
attach(mpxnyc_colors)

```

```{r scripts, echo=FALSE, warning=FALSE, message=FALSE, include= FALSE}
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions")


targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/1_data_processing")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/2_data_summary")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/3_data_extract")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/4_plot")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/5_tables")


targets::tar_make() # Runs the data pipeline shown in _targets.R

```

# To Do

1.  Measures of centrality and density
2.  Results
3.  Introduction
4.  Discussion
5.  Appendices

# Methods

```{r text_variables}
start_date <- targets::tar_read(data_bipartite_graph_collected) %>% data.frame() %>% pull(createdAt) %>% min(na.rm= TRUE)
end_date   <- targets::tar_read(data_bipartite_graph_collected) %>% data.frame() %>% pull(createdAt) %>% max(na.rm= TRUE)

```

## Data Collection

Under the Rapid Epidemiologic Study of Prevalence, Networks, and
Demographics of Monkeypox Infection (RESPND-MI), we implemented MPX
NYC - a brief, anonymous, online survey among transgender people and
gay, bisexual, and other men who have sex with men. Data were collected
from 20 August 2022 to 15 November 2022 in New York City.

### RESPND-MI Community Forum

To elicit input about study design and recruitment from queer and trans
individuals and organizations in health-related fields, we held a rapid
consultation meeting at the outset. Investigators compiled a list of 53
invitees. To maximize uptake, invitations were sent via the email
accounts of investigators who had prior relationships with invitees
where possible.

At the initial consultation meeting on 27 June 2022, participants
requested that the RESPND-MI team host a weekly meeting since they had
no other venues for discussing the outbreak from the perspectives of
service organizations and individuals who had experienced mpox
infection. We named the space the RESPND-MI LGBTQ+ Community Forum and
held it weekly until August 2022. Though the main purpose of the
Community Forum was to share information and allow organizations and
individuals to coordinate political action, it was also used to consult
on study-related decisions. About 80 individuals participated in the
Community Forum over the 2-month period we held it. Further details can
be found in a previous publication [@roth2023global].

### Recruitment

We collaborated with a marketing agency to design and implement a study
recruitment campaign in English and Spanish. The initial brief was to
create a name and visual identity that convey scientific rigor, build
trust with the community, and stand out in a crowded online marketplace
(see @fig-requirements). As a starting point, we suggested a campaign
that playfully communicates using emojis that have sexual connotations.
Two campaign names and four marketing concepts (see @fig-options) were
developed by the marketing agency and presented to the RESPND-MI
Community Forum. The final concept (which used emojis) and name were
decided by consensus during that meeting.

[![Requirements for MPX NYC
Study](images/clipboard-2397454480.png){#fig-requirements
fig-alt="Requirements for MPX NYC Study"}](https://www.mpxresponse.org)

Marketing materials included graphics, videos by queer influencers, and
a style guide (including colors, icons, and fonts) for all public-facing
materials of the MPX NYC study. We organized these materials into a
"social media toolkit" so that they would be easy for individuals and
organizations to share through their own social media accounts.
Advertisements were placed through Grindr, Twitter, Instagram, and
outdoor electronic billboards.

The marketing campaign for MPX NYC won the XXXX award in 20XX, and the
RESPND-MI project was recognized thorugh the inclusion of the principal
investigator in the OUT100 list for 2022.

![Options for visual identity of MPX
NYC](images/clipboard-22126019.png){#fig-options
fig-alt="Options for visual identity of MPX NYC"}

### Data collection instrument

We rapidly designed, tested, and implemented a novel online survey
instrument which captures rich spatial information while protecting
participant anonymity. Along with standard question formats (multiple
choice, single choice, text field etc.) we developed the map-input
question format to elicit spatial data.

In the map-input question format, participants are prompted to indicate
all places of a particular type by tapping on a displayed map (see
@fig-mapinputformat). Each time the user taps, a marker appears and a
pop-up window prompts them to answer a series of questions related to
that location. To protect participant anonymity, spatial data are
coarsened by transforming longitude-latitude coordinates into
identifiers for the census tracts that contain them. Census tracts are a
spatial unit that exhaustively divides the United States into areas
ranging from $2500$ to $8000$ in population size [@uscensus2022].

The look and feel of the data collection instrument was based on the MPX
NYC style guide. The front end was developed as a single-page web
application using the React/NextJS framework [@nextjsd2024]. It uses the
Google Maps [@google2024] API to elicit spatial coordinates, and the
Federal Communications Commission [@federal] API to transform them into
census tract identifiers before data are transmitted to the back end.
The back end was hosted on a commercial cloud server platform. It
consisted of a Express.js server linked to custom-built neo4j graph
database [@neo4j2024]. The instrument underwent two rounds of user
testing before data collection started.

![Map input question format developed for MPX
NYC](images/clipboard-1908474363.png){#fig-mapinputformat}

### Inclusion and Exclusion Criteria

Potential participants were included in the study if they consented to
participate, were over 18 years of age, identified as transgender, gay,
bisexual, or as men who have sex with other men, and were in New York
City in the four weeks preceding the survey. Potential participants were
excluded if they were younger than 18 years of age or they withdrew
consent.

### Translation

All study materials were professionally translated from English to
Spanish. The translation was reviewed by six professionals in
health-related fields whose primary language is Spanish.

### Ethical Review

The study was reviewed and approved by the T.H. Chan School of Public
Health Institutional Review Board (IRB22-0761).

## Measures

### Participants

The brief (5 minute) questionnaire was implemented in English and
Spanish. It measured participant demographics, utilization of healthcare
services; and connection to queer or transgender community.

Gender identity was measured using a two-step approach: first, we
solicited the participant’s current gender (man, woman, trans man, trans
woman, non-binary, other), and then sex assigned at birth (male, female,
other). Those whose gender identity and sex assigned at birth were not
concordant were categorized as transgender. We used current gender to
further categorize transgender people into men and women.

Race was measured using a multiple selection question based on census
categories (white, black, latino/a/x, asian, pacific islander, other).
We combined gender identity and race to form a gender-race variable,
collapsing small cells across racial groups (white cisgender man, latinx
cisgender man, black cisgender man, other cisgender man, non-binary
person, transgender man, transgender woman, cisgender woman, another
demographic).

### Residence and Contact venues

Using the map-input question format, we solicited the census tract of
participants' primary residences. Among those who reported physical or
sexual contact in a group setting in the preceding 4 weeks, we solicited
the locations of the venues at which the contact happened. We refer to
these locations as "contact venues". For each contact venue (see
@fig-mapinputformat), participants indicated the type of place it was
(dance party, sex party, darkroom, sport game, concert, theatre/show,
private residence, sex club, bathhouse, park, something else) and
whether they had sexual (vs. non-sexual) contact there.

## Statistical Analysis

### Participant and contact venue characteristics

Participant characteristics were tabulated by contact in the preceding 4
weeks. We also tabulated contact venue characteristics by distance from
home and by sexual contact.

Census tract identifiers were converted into community district
identifiers. Census tracts are nested in community districts. They are
defined by the City of New York [@nycopendata2022]. For each contact
venue, we approximated the distance from home to that venue using an
ordinal variable with three levels: same community district as home;
different community district but same borough as home; different borough
than home.

### Spatial sorting and mixing

To understand how different demographic groups mix in physical space, we
defined $\psi_{a \rightarrow b} \in [-1,\infty]$ as the spatial
selection coefficient of subgroup $a$ for subgroup $b$. The spacial
selection coefficient is defined as the spacial selection ratio less 1.
The numerator for this ratio is the conditional probability of someone
in subgroup $a$ sharing a community district with someone in subgroup
$b$. The denominator is the marginal probability of having
characteristic $b$.

This measure is $0$ when contact venues and residences for subgroups $a$
and $b$ are distributed independently of each other in space; positive
if contact venues and residences for subgroup $a$ tend to be in the same
community districts as those for subgroup $b$; and negative if subgroup
$a$ tends to be in community districts that do not have contact venues
and residences for subgroup $b$.

### Participant spatial overlap network

We constructed a network where nodes are participants and weighted ties
indicate the number of community districts shared by those participants.
We say two participants share a community district if both have a
residence or contact venue in that community district.

### Hypothetical immunization intervention

We examined the coverage efficiency and network impact of a hypothetical
intervention to slow down the wide dissemination of a novel pathogen.
The intervention a) lists community districts in decreasing order of
count of residences and contact venues, b) immunizes all individuals who
have a residence or contact venue in the top district, c) removes all
contact venues and residences for immunized individuals. We say the
hypothetical intervention is of order $k\in \mathbb{Z}$ if these steps
are completed $k$ times.

#### Efficiency

We examined coverage efficiency by plotting the proportion of immunized
individuals against the order of the hypothetical intervention ($k$)
carried out in community districts. For low $k$, the proportion of
immunized individuals will grow faster than the order of the
hypothetical intervention.

#### Network impact

We used the community district overlap network to understand how the
hypothetical intervention would likely affect transmission dynamics. In
that network, immunizing a community district removes all individuals
who have a residence or contact place in that that community district
from the network. (This is analogous to using a 100% efficacious vaccine
and achieving 100% coverage in immunized community districts.) For each
$k$, we calculated centrality measures to show how the participant
spatial overlap network would evolve as more community districts are
immunized.

### Statistical Inference

We used the non-parametric bootstrap to calculate point estimates and
95% confidence intervals (CI). Participants were re-sampled with
replacement `r targets::tar_read(initial_settings)$n_reps_graph` times.
For each measure, the lower and upper bound of confidence intervals were
calculated as the 0.025th and 0.975th quantiles of the empirical
distribution produced by re-sampling.

# Results

```{r}
perc_sti <- "0%"

```
## Participants

The MPX NYC survey was open from 30 September to 15 November, 2022, and recruited a diverse group of participants. About 70% of participants were recruited over two two-day periods - half were recruited from 30 to 31 Aug, and another fifth from 10 to 11 September). Over 50% of participants were between the ages of 18-34 at the time of the survey. Two fifths were white cisgender men, about 15% were latinx cisgender men, and 10% were black cisgender men. About 5% of participants were transgender (with slightly over half being transgender men). Non-binary individuals comprised 7%. Two thirds of participants identified as gay, 14% as bisexual, and 12% as queer. Just under half of participants resided in the borough of Manhattan, and a third lived in Brooklyn.

In terms of health status, one in ten participants reported living with HIV - the overwhelming majority were virally suppressed. In addition, about `r perc_sti` reported at least one STI symptom. In terms of health services, two out of five participants were on PrEP at the time they took the survey, two-thirds had received the MPOX vaccine though only 8% had received MPOX testing. 

MPX NYC participants were deeply connected to queer and trans people in New York City. About two-thirds reported being in recent (preceding 4 weeks) contact with 1 - 10 friends in this community whereas only 20% reported not being in contact with queer and trans friends over the same period. About half of the participants had betwen 1 and 3 recent sex partners with 15% reporting over 5 partners. Related to sex partners, about one third reported spending less than 15 minutes on average when traveling to a hookup while a third spent 16-30 minutes. Almost one of four participants reported having physical (non-sexual) contact with over 5 individuals over the preceding four weeks, and one third reported having no recent contact. 

Participants who reported recent physical or sexual contact in a group setting were slightly younger than those who did not. They were more likely to identify as gay and less likely to identify as straight. Those who had contact were more likely to live in Manhattan and less likely to live in Queens. Surprisingly, they were less likely to have been recruited through a Grindr advertisement. They were also more likely to have been recruited before the first Grindr pop-up advertisement on 1 September 2022. 

Finally, those who reported recent contact in a group setting did not differ with those who did not in terms of their HIV status and viral suppression. They were more likely to have at least one STI symptom than those who did not have recent contact in a group setting. This group had higher utilization of PrEP, mpox testing, and mpox vaccine. They were more closely connected with the queer and trans community: they reported more contact with friends, more physical contact partners and more sexual contact partners. They spent more time travelling to hookups than participants who had not had recent contact in a group setting. 




```{r tbl_descriptives}
#| fig-cap: "Participants in MPX NYC Study by Sex / Physical Contact in Congregate Setting in past 4 weeks"
#| label: fig-descriptives

targets::tar_read(data_bipartite_graph_collected) %>%
  tidygraph::activate(nodes) %>%
  data.frame() %>%
  dplyr::filter(type) %>%
  dplyr::select(
    "age", "race", "genderId", "demo_group", "sexOrientation", "borough" , "channel", "createdAtCut",
    "countFriendsCut", "countPhysicalCut", "countSexCut", "travelTimeCut", "groupSex",
    "hivStatus", "hivSuppressed", "NumSymptomsCut", "hivPrep", "monkeypoxTest", "monkeypoxVaccine"
  ) %>%
gtsummary::tbl_summary(by = groupSex) %>%
  gtsummary::add_p() %>%
  gtsummary::add_overall() %>%
  gtsummary::add_n() %>%
  gtsummary::modify_header(label ~ "**Variable**") %>%
  gtsummary::modify_spanning_header(c("stat_1", "stat_2") ~ "**Physical or sexual contact in group setting in past 4 weeks**") %>%
  gtsummary::bold_labels() %>%
    gtsummary::as_gt() %>%
  gt::tab_source_note(gt::md("*Data source: MPX NYC 2022*")) 


```


Sexual orientation, however, varied accross sub-groups defined by race
and gender. Cisgender men tended to be predominantly gay identified
whereas non-binary persons, transgender men were predominantly queer.
Transgender and cisgender women straight or bisexual.

```{r fig_sex_orientation_racegender}
#| fig-cap: "Sexual orientation of MPX NYC participants by race and gender"
#| label: fig-sexorientation-racegender
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(sexOrientation, demo_group) %>%
  plot_radar_grid() %>%
  apply_style_radar_grid_plot()

```

There was varying access to services by race and gender. For example,
among white cisgender men, more were on PrEP than not whereas among
latinx and black men, more were not on PrEP than were. Strikingly,
unlike any other group, more black cisgender men were living with HIV
than on PrEP.

```{r fig_prephiv_racegender}
#| fig-cap: "PrEP and HIV Status of MPX NYC participants by race and gender"
#| label: fig-prephiv-racegender
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(hivPrep, demo_group) %>%
  plot_radar_grid() %>%
  apply_style_radar_grid_plot()
```

## Contact venues

From the $530$ participants who reported contact in the 4 weeks preceding
the survey, we solicited, XXX contact venues. The most popular venue for
contact was private residences. When we separate venues at which sexual
contact occured from other venues, we found that sexual contact in
congregate settings happened predominantly in private residences. By
contrast, among contact venues in which participants did not have sex,
dance parties predominated. The proportion of contact venues at which
sexual contact happened increased the closer to home the venues were.
The further away from home, the more likely contact venues were to be
dance paries or sex parties, though the overall proportion was still low
compared to private residences.

```{r fig_places_distance_sexcontact}
#| fig-cap: "MPX NYC contact venue type by distance from home and sexual contact"
#| label: fig-places-distance-sexcontact
#| fig-width: 9
#| fig-height: 9

make_table_freq3(placeType, placeSex, distanceFromHome, person_analysis = FALSE) %>%
  filter(!is.na(level)) %>%
  plot_radar_stratified2() %>%
  apply_style_radar_facet_plot()

```

## Participants connecting through contact venues

Movement between home and contact venues show that there is a strong
flow within Brooklyn and within Manhattan, with a substantial amount of
movement from Brooklyn homes to Manhattan contact venues. There was
substantial, though less, flow from Manhattan to Brooklyn venues.
Residents of the Bronx and Queens moved from their homes to contact
venues within their buroughs, and also moved to Manhattan and to a lower
extent, Brooklyn. Within Brooklyn, the community district of BK01
received the most visitors within Brooklyn, and within Manhattan the
district of MN04 was most visited. These include the neighborhoods X, X,
X, X in BK01, and X, X, X, X in MN04.

```{r fig_communities_movement}
#| fig-cap: "Movement between home and contact venues by MPX NYC participant"
#| label: fig-communities-movement
#| fig-width: 10
#| fig-height: 10


margin_to <-  make_table_movement_travel() %>%
                    group_by(to, to_borough) %>%
  summarize(weight = sum(weight)) %>%
  ungroup() %>%
                    mutate(weight =  100*weight / sum(weight))

margin_from <-  make_table_movement_travel() %>%
                    group_by(from, from_borough) %>%
  summarize(weight = sum(weight)) %>%
  ungroup() %>%
                    mutate(weight = 100*weight / sum(weight)) 

  main <- make_table_movement_travel() %>%
              ggplot() +
              geom_tile(aes(y = from, x = to, fill = from_borough), alpha = 0.3) +
    geom_point(aes(y = from, x = to, col = to_borough, size = weight)) +
    geom_segment(aes(y = from, xend =  weight + 60, x = 60, color = from_borough), data = margin_from, size = 3, alpha = 0.3 ) +
    #geom_point(aes(y = from, x = weight + 60, fill = from_borough, label = from, size = 1, color = from_borough), data = margin_from) +
        geom_point(aes(x = to, y = -weight - 5, fill = to_borough, label = to, size = 1, color = to_borough), data = margin_to) +

    geom_segment(aes(yend = - weight - 5, y = - 5, x = to, color = to_borough), data = margin_to) +
  theme_void() +
    theme(
      legend.position = "none",
      axis.text = element_text(),
      axis.text.x = element_text(angle = 90)
    ) +
    scale_x_discrete(position = "top") +
    scale_y_discrete(position = "left") +
    geom_segment(aes(x = xcord, y = 0, yend = 55), data = data.frame(xcord = 60 + 2* c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10)), size = 0.1) +
        geom_segment(aes(y = xcord, x = 0, xend = 55), data = data.frame(xcord = -2* c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10) - 5), size = 0.1) +
    geom_text(
      aes(y = xcord, x = 57, label = label), 
      data = data.frame(
        xcord = -2* c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9) - 5) %>% mutate(label = -1 * (xcord + 5)),
      size = 3,
      angle = 45
      ) +
    geom_text(
      aes(y = -2, x = xcord, label = label), 
      data = data.frame(
        xcord = 60 + 2* c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9)) %>% mutate(label =   (xcord - 60)),
      size = 3,
      angle = 45
      ) +
    geom_text(
      aes(y = -5, x = 70, label = "% residences"), 
      size = 3.5,
      fontface = "plain"
      ) +
    geom_text(
      aes(y = -15, x = 59.5, label = "% contact venues"), 
      size = 3.5,
      angle = -90,
          fontface = "plain"
      )  

  
  apply_style_matrix_movement(main)


```

The most popular community districts in Brooklyn and Manhattan were
connected via shared visitors or residents. Different sub-groups showed
different patterns of co-attendance of community districts. Overall, MPX
NYC participants showed spatial homophily - the spatial selection
coefficient from a given group to the same group was positive for all
levels of race-gender, sexual orientation, and age. In addition, black
cisgender men and non-binary persons tended to visit or live in
different neighborhoods than white cisgender men. Non-binary persons
also showed a preference for community districts in which transgender
men live. Gay identified participants preferred to live and play in
community districts where bisexual, straight and queer identified
participants did not live. Similarly, those groups selected against
community districts in which gay identified individuals live or play.

```{r fig_communities_network}
#| fig-cap: "Network of community districts connected by MPX NYC participants"
#| label: fig-communities-network
#| fig-width: 8
#| fig-height: 8


make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
  plot_network_viz() %>%
  apply_style_network_viz()
  
```

```{r fig_subgroup_mixing}
#| fig-cap:  "Social mixing matrices for MPX NYC participants by race-gender (top), sexual orientation (bottom left), and age (bottom right)"
#| label: fig-subgroup-mixing
#| fig-width: 12
#| fig-height: 17

mixing_demo_group_panel          <- make_table_mixing(demo_group) %>%
                                      plot_matrix_mixing() %>%
                                      apply_style_matrix_mixing_plot()


mixing_sexOrientation_panel      <- make_table_mixing(sexOrientation) %>%
                                      plot_matrix_mixing() %>%
                                      apply_style_matrix_mixing_plot()


mixing_age_panel                 <- make_table_mixing(age) %>%
                                      plot_matrix_mixing() %>%
                                      apply_style_matrix_mixing_plot()

mixing_bottom_panel              <- cowplot::plot_grid(mixing_sexOrientation_panel, mixing_age_panel, nrow = 1)

cowplot::plot_grid(mixing_demo_group_panel, mixing_bottom_panel, ncol=1, rel_heights = c(2,1.1))


```

## Efficient and effective interventions

Under the hypothetical intervention, it would take an intervention of
order 5 to reach 33% of survey participants with an intervention to slow
down the spread of a novel pathogen. These were MN04, BK01, MN10, BK03,
and QN01. MN04 includes the neighborhoods XXXXX, BK01 includes XXXXX,
MN10 includes XXXX, BK03 includes XXX, and QN01 includes XXXX. To reach
66% of participants with the intervention, it would be necessary to
mount an intervention of order 13. The additional community districts
would be MN12, BK04, MN02, BK08, MN07, MN09, BK02, and MN05. A table of
community districts and their constituent neightborhoods can be found in
Appendix X.

```{r fig_hiimpact_communities_contact}
#| fig-cap: "High-coverage community districts - Contact"
#| label: fig-hiimpact-communities
#| fig-width: 10
#| fig-height: 10
#| 
map_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  plot_coverage_map()  %>%
                  apply_style_coverage_map()

bar_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  filter(group != "Group C") %>%
                  plot_coverage_bar() %>%
                  apply_style_coverage_bar() 

  cowplot::ggdraw(map_plot) +
  cowplot::draw_plot(bar_plot, x = .1, y = .55, width = 0.25, height = 0.25)

```



```{r fig_hiimpact_communities_movement}
#| fig-cap: "High-coverage community districts - Movement"
#| label: fig-hiimpact-communities-movement
#| fig-width: 10
#| fig-height: 10
#| 
map_plot <- make_coverage_table(intervention_priority = "movement", intervention_stratification = "overall") %>%
                  plot_coverage_map()  %>%
                  apply_style_coverage_map()

bar_plot <- make_coverage_table(intervention_priority = "movement", intervention_stratification = "overall") %>%
                  filter(group != "Group C") %>%
                  plot_coverage_bar() %>%
                  apply_style_coverage_bar() 

  cowplot::ggdraw(map_plot) +
  cowplot::draw_plot(bar_plot, x = .1, y = .55, width = 0.25, height = 0.27)

```

```{r}
#| fig-cap: "Network impact"
#| label: fig-netimpact
#| fig-width: 8
#| fig-height: 5

tar_read(data_intervention_results_centrality_collected) %>%
  filter(intervention_stratification == "overall") %>%
  filter(intervention_ranking <= 40) %>%
  mutate(intervention_priority = factor(intervention_priority, c("contact", "movement"), c("Contact-based Prioritization", "Movement-based prioritization"))) %>%
  mutate(group = factor(group, c("n_vaccinated", "n_remainder", "n_lcc"), c("Vaccinated", "Unvaccinated in LCC", "Unvaccinated not in LCC"))) %>%
  ggplot() +
  geom_bar(aes(y = proportion, x = intervention_ranking, fill = group), stat = "identity", width = 1) +
  geom_hline(aes(yintercept = 0.5), size = 0.1) +
  geom_hline(aes(yintercept = 0.25), size = 0.1) +
  geom_hline(aes(yintercept = 0.75), size = 0.1) +
  geom_vline(aes(xintercept = 10), size = 0.1) +
  geom_vline(aes(xintercept = 20), size = 0.1) +
  geom_vline(aes(xintercept = 30), size = 0.1) +
  facet_grid( . ~ intervention_priority ) +
  #coord_polar(start = 0.5*pi) +
  scale_y_continuous("Proportion of participants", limits = c(0, 1), labels = scales::percent) +
  scale_x_continuous("Intervention order", limits = c(0, 40), breaks = c(0, 10, 20, 30, 40)) +
  theme_void() +
  scale_fill_manual("", values = c(light_blue, mid_blue, dark_blue)) +
  theme(
    axis.text = element_text(),
    axis.title = element_text(margin = margin(15,5,5,5)),
    axis.title.y = element_text(angle = 90), 
    legend.position = "bottom",
    plot.margin = margin(10,10,10,10),
    strip.text = element_text(margin = margin(10, 10, 10, 10))
  )


```



# Discussion

Group sex is ubiquitous. The sex happens in physical space, it is
important to study space and sex at the same time.

People who are more likely to have contact are also more likely to use
health-promoting interventions such as PrEP, mpox vaccination. But are
not more likely to access mpox testing. The latter is likely more about
the inadequate system for testing than its is about health behavior.

Targeting public group sex venues is an ineffective intervention in the
face of a growing threat of a deadly sexually transmitted infection.

Sexual activity and group sexual activity are not evenly distributed
across the city - there are few neighborhoods which, if intensely
covered with interventions could slow down transmission across the city
more generally.

There is spatial homophily by race-gender, sexual orientation, and age.
And there is some spatial separation between gay identified people and
people of other sexual orientations. This is likely to lead to some
containment among gay men.

People who had group contact were also likely to have more friends, more
one-on-one physical contact, and more one-on-one sexual contact than
others. Even as spatial networks are considered as conduits for the
transmission of pathogens, they should be conceptualized and conduits
for information and other health-promoting resources.

Network connectivity declines after about 10 community districts. We
have to assume that we are working on a well connected network and
conduct interventions concurrently instead of sequentially as we have
proposed here.

We must overreact in places which are hubs. Extend to international gay
travel.

Extend to contact tracing light.

Background in programming:

-   we make the asusmption of networking, but networks are not measured.

-   we talk a lot about empowering community, but we need to just ask
    organizations how much material resources they dedicate to active
    reponsive work like this, vs. covering overhead. Things are usually
    what they seem.

-   WE are called to reconsider the categorical imperative and move
    towards a network-based understanding of community.

-   Next step: This is a flavor of CLM. We call on UNAIDS and WHO to
    generate technical guidance to conduct these studies.

Reccomendations:

-   Gov:

    -   hire capable queer and tans people of different backgrounds to
        convene local groups to monitor the situation and make
        contingency plans

    -   defund centers for pandemic preparendess which have not done any
        work to prepare us for the onslaught and steer funding to
        coalitions of local activists, researchers, and government who
        wish to coordinate efforts to prepare

    -   Invest in success and not in prestigious and well-explained
        failure.

-   conduct this kind of survey every year to keep an up-to date map and
    study its evolution over time. We collected MPX NYC 2 data, which
    are currently being analysed.

-   convene groups to be ready for the new outbreak instead of wiating
    for it to kill people before we do anything

-   accept that under biden's presidency, activists were gaslighted into
    believing the administration is doing the utmost to slow the spread
    down whereas it was doing the least. If we are to prevent pain and
    suffering, we have to assume that city, state, and federal
    government will provide as much material support as they did through
    this ground-breaking initiative which was the only of its kind at
    the time we conducted it.

-   Do whatever you want - climate change is gonna hit us before you get
    tenure. go wild. have fund. be a freak.

Methodologically,

-   we spearheading technical innovation both in data collection -
    survey instrument.

-    and in data wrangling and analysis. use bipartite network to keep
    and wrangle the data. get to the core of the relational content of
    the work.

-   we also offer project management tools and skills to large
    organizations which have branded themselves as mpox-concerned, but
    have not contributed new knowledge or mounted useful programs.

-   Social network and spatial network analysis is the next fronteir. If
    we don't properly conceptualize the relational nature of public
    heatlh programs, we are doomed to host webinar after webinar of
    platitudes.

-   Can help with HIV and STIs and can help us to conceive of a pandemic
    prepareness program that extends beyond webinars conducted on unfair
    terms to queer and trans people doing work.

While many researchers have been paid by funding organizations to talk
about mpox, few have contributed anything that can help us stop it and
attend to community needs. Rec is for capable researchers to break rank
and do the research they think is necessary with the understanding that
people who usually get paid will get paid (professional researchers),
and people who usually do not get paid will not get paid (community
researchers).

Our most important recomendation is not to government, which has proven
itself to be what it appears to be in the face of actual emergencies,
and it is not to large HIV organizations and pundits. It is to queer and
trans people who have the skills to produce new and useful knowledge. WE
did it cheaper, quicker, and better than the large organizations that
have sucked up funding.

The RESPND-MI project commits to making as much of our workproduct
available as possible, and to be available for paid consultations to get
projects like these off the ground accross the country and across the
world.

# Acknowledgements

Sponsors: Greg Millet facilitated funding from amfAR; XXX allowed us to
apply for out-of-cylce funding from Center for AIDS Research at Harvard
University; Ian Holloway facilitated financial support from UCLA Luskin
Center; and individual donors gave funds.

Donors: LinkNYC and Grindr donated advertising to the study, neo4j
donated a license for their proprietary database software.

Technical: Eric Tchetgen Tchetgen, Forrest W. Crawford, and Kenneth
Mayer provided feedback on technical aspects of the study.

Translation: Cody Patrick Nolan coordinated translation of the survey
instrument and marketing materials. Antón Castellanos-Usiglu conducted
the translation. Cody Patrick Nolan, Chema Jiménez, Juan Pablo Amaya
Amaris, Santiago Aguilera Mijares, and María Andrea Santos Guzmán
validated the translation.

Questionnaire: Keletso Makofane, Pedro Carneiro and Nguyen Tran drafted
the questionnaire. Lisa Berkman, Tom Carpino, David Barr, and Judy
Auerbach reviewed the questionnaire.

Admin: Sudipta Saha coordinated study activities, Christian Urrutia and
Prep4All provided finance support, James Krellenstein and Joe Osmundson
participated in initial planning. Keletso Makofane kept financial
records. Lisa Berkman, Kenneth Mayer, and Eric Tchetgen Tchetgen were
academic advisors. Lisa Berkman acted as principal investigator for the
purpose of securing IRB approval while Keletso Makofane was principal
investigator in all other respects.

Web Development: Keletso Makofane conceptualized and coded the survey
instrument (front end - which uses the FCC Data API but is not endorsed
or certified by the FCC). Sudpipta Saha identified the FCC Data API,
which allowed us to implement the front end. Imran Khan coded the study
data server and database (back end). Seema Kara planned out the overall
process of web development.

Communications: Nick Diamond led marketing and communications efforts
including managing contracts with Burness marketing agency and
administering the LGBT+ Community Forum. Burness developed and
implemented the public-facing communications materials. Grant Roth,
Keletso Makofane, and Chris Wyman coordinated the initial invitations
for the LGBT+ Community Forum. Joe Osmundson shared epidemiologic
updates in early meetings of the Community Forum. Jennifer
Balenciaga-Barnes led our thinking on the use of gender-inclusive
language, Elle Lett and Nguyen Tran provided input on academic writing
on gender diversity, Keletso Makofane was responsible for the
operationalization and implementation of these ideas. Martez Smith led
in-person consultation with Black LGBT individuals in Harlem, New York.

Fundraising:

-   Sudpita saha drafted the grants that funded this work.

-   

Most of all, we thank, and stand in solidarity with, the MPX NYC
participants who gave of their time to make the study a success.

# References
