---
title: "MPX NYC"
subtitle: "Key findings and recommendations"
author: "Keletso Makofane"
date: 23 May 2024
execute:
  echo: false
  warning: false
  message: false
---



```{r libraries, echo=FALSE}

library(tidyverse)
library(ggplot2)
#library(mpxnyc)
library(sf)
library(tidygraph)
library(ggraph)
library(igraph)

library(targets)

mpxnyc_colors <- mpxnyc::mpxnyc_colors
attach(mpxnyc_colors)

```


```{r scripts, echo=FALSE, warning=FALSE, message=FALSE, include= FALSE}
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/1_data_processing")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/2_data_summary")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/3_data_extract")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/4_plot")
targets::tar_source(files = "/Users/keletso/Documents/_gitrepos/mpxnyc_data_analysis/R_functions/5_tables")


targets::tar_make() # Runs the data pipeline shown in _targets.R

```



# Methods

## Data Collection 
We conducted an annonymous cross-sectional online survey among people who identify as queer or trans and live in New York, and people who have had sexual contact with queer and trans people in New York City. Inclusion criteria were XXXX. Exclusion criteria were YYYYYY.  

### Recruitment
In collaboration with a marketing agency, we developed and implemented a study recruitment and health information campaign. The campaign provided basic information on MPOX and invites potential participants to take their survey. The camapaign had two components: paid advertisement on social media and strategic out-of-home locations (e.g. Electronic posters at the Fire Island Ferry Terminal building), and a social media toolkit containing materials that community members and organizations could share on their own social media accounts. We also paid queer influencers to record videos sharing information about the study and about mpox for the purpose of sharing these through paid ads and through the social media toolkit. The marketing campaign was conducted in Spanish and English. 

The overall marketing concept was decided during an open meeting of the RESPND-MI Community Forum through discussion with X participants of diverse backgrounds. a sub-committee from the community forum to act as a focus group for choosing which creative direction to use for graphic design. Paid queer influencers were chosen by solicing suggestions from community forum members. We made sure to have X, X, X, and X. 

### Questionnaire 
The questionnaire was designed to be completed in XX minutes. We describe the content below, and the process of developing it here. A team of X investigators developed the initial draft questionnaire prioritizing X, X, X. These were circulated among the investigator team for review and comment. The near-final questionnaire was circulated among community forum (?). 
 
### Data collection instrument 
We designed and implemented a novel online survey instrument which captures spatial information at a resolution fine enough to analyze overall patterns in social and sexual contact in the population but coarse enough to preserve the annonymity of the survey. 

This was accomplished through a user interface that resembles the google maps (r) search interface linked to the google maps API. To collect spatial data, participants were prompted to indicate all venues where they had had physical or sexual contact in a congregate setting over the preceding 4 weeks. The user interface allows the participant to search by neighborhood, place name, street address, and other markers which are admitted by the google maps search interface. When the user taps on a place in the map, a pop-up window asks them to confirm the location. If they do confirm, they receive a series of questions related to that particular venue. Once all the questions relating to a venue are answered, the user is allowed to tap on the map again to indicate a second venue, etc. 

In addition, the survey instrument collected data thorugh other question formats (multiple choice, single choice, etc.). The look and feel of the data colleciton instrument was consistent with the visual identity established by the campaign. Data were stored in a custom built graph database system hosted on a secure cloud server platform. 

The instrument was validated thorugh 3 rounds of user testing before data collection. Users were asked to comment on [AIRTABLE].

## Measures 
### Participants 
We solicited information on participant sociodemographics, utilization of healthcare services such as pre-exposure prophylaxis (PrEP), HIV treatment and vaccination against MPOX; connection to queer or transgender community through sex and socializing; and location of primary residence. 

Gender identity was measured using a two-step approach: first, we solicited the participant’s current gender (), and then their sex assigned at birth (). Those whose gender identity was not concordant with the gender commonly associated with their sex assigned at birth were categorized as transgender. We used current gender to further categorize transgender people into men and women. Race was measured using a multiple selection question based on census categories ().  We defined gender-race subgroup as the combination of gender identity and race. We collapsed small cells across racial groups. 

### Contact venues
We asked whether participants had engaged in group sex or had physical contact in a congregate setting in the four weeks before taking the survey. Among those who answered positively, we solicited the locations of the venues at which the contact happened. We refer to these locations as contact venues. 

For each contact venue, participants indicated the type of place it was () and whether they had sexual (vs. non-sexual physical) contact there. 

As a crude measure of the distance between the contact venue and participant residence, we categorized contact venues into those that are in the same neighborhood as the residence, the same borough but different neighborhood, or a different borough than the participant's residence.


### Spatial mixing 
To understand how the contact venues and residences of different kinds of participants are clustered in space, we examined the l


The spatial mixing coefficient from characteristic X to characteristic Y compares the conditional probability of someone with charestic X sharing a community district with someone with characteristic Y to the marginal probability of having characteristic Y. The spatial mixing coefficient is defined as the ratio between these two probabilities minus 1. 

We also contructed a spatial transmission network consisting of individuals. In this network, a pair of individuals has a tie between them if they share at least one community district. The weight of tie is proportional to the number of community districts they share. 


## Statistical Analysis
We tabulated participant responses to questions about healthcare access, connection with community, and demographics by report of contact. We also tabulated the characteristic of contact venues. We visualized the flow of study participants between home and contact venues using a matrix plot. We plotted this measure for subgroups defined by race-gender, sexual orientation, and age.

### Hypothetical Intervention
We examined the efficiency and transmission impact of a hypothetical intervention to prioritize community district according to the amount of contact and vaccinate those districts in order of that priorization. We assume that vaccinating a community district means rendering every individuals who lives in or has had contact in that community district unable to acquire or transmit a hypothetical pathogen.

Efficiency was examined by understanding what the minimum number of community districts to be vaccinated to cover 33% of the population, and separately to cover 66% of the population. 

Transmission impact was examined by understanding the impact on the underlying spatial transmission network of removing community districts which have been vaccinated. 

### Statistical Inference
We used the non-parametric bootstrap to calculate point estimates and 95% confidence intervals (CI). This was based on re-sampling individual participants with replacement.



# Results

```{r}


by_group_sex <- tar_read(data_bipartite_graph_collected) %>%
  make_table_1_datatable(by = groupSex, variables = c(overall, age, genderId, race, sexOrientation, channel, hivPrep, monkeypoxVaccine, monkeypoxTest, monkeypoxTest, countSex, countFriends, countPhysical, borough)) %>%
  mutate(stratum = stratum_groupSex) 

overall <- tar_read(data_bipartite_graph_collected) %>%
  mutate(groupSex = "overall") %>%
  make_table_1_datatable(by = groupSex, variables = c(overall, age, genderId, race, sexOrientation, channel, hivPrep, monkeypoxVaccine, monkeypoxTest, monkeypoxTest, countSex, countFriends, countPhysical, borough)) %>%
  mutate(stratum = stratum_groupSex) 


rbind(by_group_sex, overall) %>%
  draw_table_1(tar_read(factor_labels))


```




```{r eval = FALSE}
#| tbl-cap: "Participants in MPX NYC Study by Sex / Physical Contact in Congregate Setting in past 4 weeks"
#| label: tbl-descriptives-by-groupsex

list_labels_groupSex_table1 <- targets::tar_read(initial_settings)$labels_list


table_1_descriptives <- targets::tar_read(data_table_1_people_by_groupSex_raw) %>%
                                mutate(stratum = stratum_groupSex) %>%
                                dplyr::group_by(variable) %>%
                                dplyr::mutate(var_label = c(variable[1], rep(NA, length(variable) - 1))) %>%
                                dplyr::ungroup() %>%
                                mpxnyc::draw_table_1(list_labels_groupSex_table1)

table_1_descriptives
```





```{r sex_orientation}
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(sexOrientation, demo_group) %>%
  plot_radar_grid() %>%
  add_caption() %>%
  add_title("Sexual orientation of MPX NYC participants by race and gender") %>%
  apply_style_radar_grid_plot()
```

```{r prep_hiv}
#| fig-width: 10
#| fig-height: 8.5

make_table_freq2(hivPrep, demo_group) %>%
  plot_radar_grid() %>%
  add_caption() %>%
  add_title("PrEP and HIV status of MPX NYC participants by race and gender") %>%
  apply_style_radar_grid_plot()
```


```{r home_map}
make_table_freq1(community) %>%
  arrange(-proportion) %>%
  mutate(cum_proportion = cumsum(proportion)) %>%
  mutate(group = c(rep("First 5", 5), rep("Next 5", 5), rep("Remainder", n() - 10))) %>%
  mutate(stratum = "Overall") %>%
  plot_map_choro(group) %>%
  apply_style_chorofill_map(show.na = TRUE)

```

```{r home_by_race_map}
make_table_freq2(community, race) %>%
  filter(stratum %in% c("White", "Black", "Latinx")) %>%
  arrange(strata, -proportion) %>%
  group_by(stratum) %>%
  mutate(cum_proportion = cumsum(proportion)) %>%
  mutate(group = c(rep("First 5", 5), rep("Next 5", 5), rep("Remainder", n() - 10))) %>%
  plot_map_choro_stratified(group) %>%
  apply_style_chorofill_map(show.na = FALSE)

```









```{r placetype}
#| fig-width: 9
#| fig-height: 9

make_table_freq3(placeType, placeSex, distanceFromHome, person_analysis = FALSE) %>%
  filter(!is.na(level)) %>%
  plot_radar_stratified2() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("MPX NYC contact venue type by distance from home and sexual contact") %>%
  apply_style_radar_facet_plot()

```





```{r movement}
#| fig-width: 13
#| fig-height: 12

  make_table_movement_travel() %>%
    plot_matrix_movement() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Movement between boroughs by MPX NYC Participants") %>%
    apply_style_matrix_movement()
```



```{r plot_matrix_mixing_age}
#| fig-width: 8.5
#| fig-height: 8.5


make_table_mixing(age) %>%
  plot_matrix_mixing() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Race-Gender of MPX NYC Participants") %>%
  apply_style_matrix_mixing_plot()



```


```{r plot_matrix_mixing_sexorientation}
#| fig-width: 9.5
#| fig-height: 9.5


make_table_mixing(sexOrientation) %>%
  plot_matrix_mixing() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Race-Gender of MPX NYC Participants") %>%
  apply_style_matrix_mixing_plot()



```


```{r plot_matrix_mixing_demo_group}
#| fig-width: 14
#| fig-height: 14


make_table_mixing(demo_group) %>%
  plot_matrix_mixing() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Race-Gender of MPX NYC Participants") %>%
  apply_style_matrix_mixing_plot()



```

```{r netviz}
#| fig-width: 8
#| fig-height: 8


make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
  plot_network_viz() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Network of community districts connected by MPX NYC participants") %>%
  apply_style_network_viz()
  
```














```{r map}
#| fig-width: 10
#| fig-height: 10
#| 
map_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  plot_coverage_map()  %>%
                  apply_style_coverage_map()

bar_plot <- make_coverage_table(intervention_priority = "contact", intervention_stratification = "overall") %>%
                  filter(group != "Group C") %>%
                  plot_coverage_bar() %>%
                  apply_style_coverage_bar() 

  cowplot::ggdraw(map_plot) +
  cowplot::draw_plot(bar_plot, x = .1, y = .55, width = 0.25, height = 0.25)

```



```{r graph_connectedness}
#| fig-width: 8
#| fig-height: 5

make_table_centrality() %>%
  filter(intervention_ranking < 41) %>%
    plot_netimpact_bar() %>%
  add_caption("Data source: MPX NYC Survey (restricted to 1,304 residents of New York City). www.mpxresponse.org") %>%
  add_title("Proportion of unreached in largest connected network component") %>%
    apply_style_bar_netimpact()

```


