```{r update_mpxnyc_package}
#pat  <- tidyjson::read_json("_config.json")["..JSON"][[1]][["settings"]][["github-token"]] # update packages
#remotes::install_github("KeletsoMakofane/mpxnyc", auth_token = pat)
remotes::install_github("KeletsoMakofane/mpxtools")
```

```{r other_packages}
#install.packages(c("labelled", "tidygraph", "dplyr", "here", "ggimage", "rsvg", "ggraph", "ggplot2", "gt", "gtsummary", "latex2exp"))
```

```{r process_data}
targets::tar_source("R_functions") # Access custom defined functions
targets::tar_make(reporter = "silent") # Run data pipeline
```

# Welcome {.unnumbered .hidden}

:::: {.p-5 .pt-1 .mb-4 .rounded-3 .shadow-sm .hero-banner .centered layout-align="center"}
# Community and Connection {.unnumbered}

A rapid, community-led study of mpox, networks, and care—built by queer and trans New Yorkers, for queer and trans New Yorkers.

::: text-center
[Explore the Findings](#sec-participants){.btn .btn-outline-primary .m-1 .btn-sm} [Learn the Methods](#sec-data){.btn .btn-outline-primary .m-1 .btn-sm}
:::
::::

# Welcome

This book presents **MPX NYC**—an anonymous, web-based study that maps how LGBTQ+ people connect through the places we share. Using a custom survey platform, we **asked folks where they lived and gathered** in the preceding month (🪩🕺 and 🧑🧑🧑😈💦). For safety, we recorded **only census-tract labels**, not addresses. From this we built a city-scale **people–place network** and analyzed how connection shapes risk and care.

[ACTIVISM]{.emphasize}: We conducted MPX NYC under **Rapid Epidemiologic Study of Sexual Networks, Demography, and mpox Infection** (**RESPND-MI)**, a queer- and trans-led collaboration born during the 2022 outbreak. We drew on tools honed by **global HIV activists** to move fast, share information, and act together.

[ACTIONABLE INSIGHTS]{.emphasize}: **One big network** – most participants fell into a single interconnected web; sub-groups cluster by place. This is what we learned about stopping an outbreak: 1) **Private, not public.** Outreach limited to sex-positive venues will miss most contact—**homes drive exposure**. 2) **Geographic hubs.** Neighborhood clusters act as local and city-wide hubs for connection and spread. 3) **Speed wins.** When choosing between holding spread to new areas vs. **vaccinating as many people as fast as possible**, the latter performs better in our model.

[CAUSAL INFERENCE FOR NETWORKS]{.emphasize}: We introduce **SSNAC**—a framework for causal inference in social-spatial epidemiology. SSNAC adapts familiar ideas to allow researchers conceptualize, collect, and analyze data about **networks, not isolated individuals**.

# At a glance {.unnumbered}

::::::::::::::: {.grid .g-6 .mt-1}
::::: {.g-col-12 .g-col-md-12 .g-col-xl-12}
:::: {.card .h-100 .shadow-sm .text-center}
[MPX NYC RESULTS]{.emphasize}

**Residences and gatherings cluster** in Manhattan and North Brooklyn. Mixing shows strong homophily by age, race–gender, and sexual orientation. Simulated strategies trade off **rapid coverage** versus **faster network fragmentation**.

::: text-center
[People](#sec-participants){.btn .btn-sm .btn-outline-secondary} [Gatherings](#sec-venues){.btn .btn-sm .btn-outline-secondary} [Going out](#sec-movement){.btn .btn-sm .btn-outline-secondary} [Mixing](#sec-mixing){.btn .btn-sm .btn-outline-secondary} [Outbreaks](#sec-intervention){.btn .btn-sm .btn-outline-secondary} [Supplementary results](#sec-appendixresults){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::

::::: {.g-col-12 .g-col-md-12 .g-col-xl-12}
:::: {.card .h-100 .shadow-sm .text-center}
[MPX NYC METHODS]{.emphasize}

**Innovative survey platform** for collecting spatial and social data annonymously: **on-device data processing**, anonymous link-tracing, and **graph database**. Statistical tools for understanding and **describing social-spatial networks**.

::: text-center
[Data](#sec-data){.btn .btn-sm .btn-outline-secondary} [Measures](#sec-measures){.btn .btn-sm .btn-outline-secondary} [Analysis](#sec-analysis){.btn .btn-sm .btn-outline-secondary} [Measurement](#sec-measurement){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::

::::: {.g-col-12 .g-col-md-6 .g-col-xl-6}
:::: {.card .h-100 .shadow-sm .text-center}
[SSNAC FRAMEWORK]{.emphasize}

SSNAC updates causal inference statistical tools to deal with **interdependent observational units.** SSNAC helps researchers to learn from causal interference**.**

::: text-center
[Context](#sec-appendix-social-spatial){.btn .btn-sm .btn-outline-primary} [Description](#sec-appendix-analysis){.btn .btn-sm .btn-outline-primary} [Causality](#sec-causal-interpretation){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::

::::: {.g-col-12 .g-col-md-6 .g-col-xl-6}
:::: {.card .h-100 .shadow-sm .text-center}
[RESPND-MI]{.emphasize}

**How we organized around research**: weekly LGBTQ+ Community Forum, distributed leadership, and small, shared tasks—**redundancy as resilience**.

::: text-center
[Organizing](#sec-organizing){.btn .btn-sm .btn-outline-primary} [Marketing](#sec-marketing){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::
:::::::::::::::

# Open science {.unnumbered}

All code and analytic frameworks powering this site are public. We invite alliances of LGBTQ+ researchers and activists to adapt them for urgent questions on **housing, nutrition, violence, access to care, employment, and health**.

# Why this work matters {.unnumbered}

As support for LGBTQ+ health services contracts—and many queer public-health workers face layoffs—we need new ways to self-organize and deploy hard-won skills. Early in this project, queer and trans New Yorkers from across the city **joined hands to understand a new threat and act**. We showed that that rigorous epidemiology and community organizing can—and must—coexist.

Through the weekly **RESPND-MI LGBTQ+ Community Forum**, activists, clinicians, and researchers co-designed the study: refining language to avoid stigma, choosing outreach venues, and building bilingual campaigns. The project became not only a study *of* networks, but a network *itself*—a model of participatory, queer-led science built from abundance, care, and trust.

# Who we are {.unnumbered}

**Lead author:** Keletso Makofane, MPH, PhD\
**Co-authors:** Nicholas Diamond, MPH; Jennifer Barnes-Balenciaga; Elle Lett, MA, MBiostat, PhD; Ken Mayer, MD; Nguyen Tran, MPH, PhD

# Why self-publish

Unfunded and urgent, we prioritized making a **high-quality, reproducible** online book rather than a series of articles in academic journals. Our code and data are freely available, allowing researchers to easily reproduce our methods in order to engage in informed critique. We welcome academic journals and other publications interested in commissioning articles based on this work to contact us!

# How to support

This website was developed by **CTRL+F**—an LGBTQ+-led consultancy created to be an incubator for creative and urgent research and scholarship. We’re in our infancy and **need all the support we can get**.

[Here’s how you can help]{.strong}: [Sign up]{.emphasize} for our upcoming lecture series, **“The People’s Department of Health,”** where Dr. Keletso Makofane discusses the work with activists and researchers who serve LGBTQ+ communities. Please invite colleagues and friends.

```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center
plot_icon(icon_name = "peach", color = "dark_orange", shape = 0)
```

::: {#acknowledgements}
**RESPND-MI** [Principal investigator]{.underline}: Keletso Makofane, MPH, PhD. [Co-investigators]{.underline}: Jennifer Barnes-Balenciaga, Nicholas Diamond, MPH, Elle Lett, PhD, MA, MBiostat, Cody Nolan, MD, Martez Smith, LMSW, PhD, Nguyen Tran, MPH, PhD. [Former investigators]{.underline}: Pedro Botti Careneiro, MPH, PhD, Seema Kara, MPH, James Krellenstein, Ken Nadolski, MPH, Joseph Osmundson, PhD, Robert Pitts, MD, Grant Roth, MPH, Sudipta Saha, MS, Christian Urrutia, MBA, Chris Wyman. [Translator]{.underline}: Antón Castellanos Usigli, MPH, DrPH. [Reference group]{.underline}: Judith D. Auerbach, PhD (*University of California, San Francisco*), Lisa Berkman, PhD (*Harvard University*), Forrest W. Crawford, PhD (*Yale University*), William C. Goedel, PhD (*Brown University*), Gregg Gonsalves, PhD (*Yale University*), Ian W. Holloway, PhD, LCSW, MPH (*University of California, Los Angeles*), Louise Ivers, MB, BCh, MD, MPH, DTMH (*Massachusetts General Hospital*), Lawrence C. Long, MCom, PhD (*Boston University)*, Kenneth Mayer, MD (*The Fenway Institute*), Gregorio Millett, MPH (*amfAR*), Eric J. Tchetgen Tchetgen, PhD (*University of Pennsylvania*). [Research sponsors and funders]{.underline}: amfAR; Harvard Center for AIDS Research; National Institutes of Health; Neo4j; New York State Department of Health. [Marketing sponsors and funders]{.underline}: Grindr; Hub for Health Intervention, UCLA Luskin School of Public Affairs. [Administration]{.underline}: Christian Urrutia, MBA (PrEP4All); James Krellenstein (PrEP4All).

**CONTACT** Keletso Makofane (keletso\@controlf.info). Nicholas Diamond (nick\@controlf.info). [CTRL+F](https://www.controlf.info){target="_blank"}.

**SUGGESTED CITATION** Makofane, K., Diamond, N., Barnes-Balenciaga, J., Lett, E., Mayer, K., Tran, N. (2025). *Community and connection: A study on social connection among LGBTQ+ New Yorkers*. CTRL+F on behalf of RESPND-MI. New York City. Available: https://mpxresponse.org

**ACKNOWLEDGEMENTS** We thank PrEP4All for generous administrative support; our individual donors; Kenneth Mayer, Eric Tchetgen Tchetgen, and John Diamond for creating the conditions for this work; members of the RESPND-MI Community Forum and Reference Group for suggestions from fundraising to study design; and the LGBTQ people who gave time and care in crisis. We dedicate this work to those who responded—and those who will respond next.
:::
