```{r process_data}


targets::tar_make(reporter = "silent") # Run data pipeline

```

```{r}

targets::tar_source("R_functions") # Access custom defined functions
```

::: {#authors}
Keletso Makofane, Nick Diamond, Jennifer McQueen, Elle Lett, Nguyen Tran

RESPND-MI Collaboration
:::

::: {#date}
March 2024, New York City

https://www.mpxnyc.app
:::

1. How do people move?
2. Why do they move that way?
3. Who are these people?
4. Notes on community
5. Notes on mpox transmission
6. Notes on covid and the coming pandemics 
7. Join us


# Data Flow

Survey web app (free)
Survey data dashboard (free)
Custom data analysis and report



::: {#acknowledgements}
[Principal investigator]{.underline}: Keletso Makofane, MPH, PhD. [Co-investigators]{.underline}: Jennifer Barnes-Balenciaga, Nicholas Diamond, MPH, Elle Lett, PhD, MA, MBiostat, Cody Nolan, MD, Martez Smith, LMSW, PhD, Nguyen Tran, MPH, PhD. [Former investigators]{.underline}: Pedro Botti Careneiro, MPH, PhD, Seema Kara, MPH, James Krellenstein, Ken Nadolski, MPH, Robert Pitts, MD, Grant Roth, MPH, Sudipta Saha, MS, Christian Urrutia, Chris Wyman. [Translators]{.underline}: Antón Castellanos Usigli, MPH, PhD Referencegroup: Judith D. Auerbach, PhD (*University of California, San Francisco*), Lisa Berkman, PhD (*Harvard University*), Forrest W. Crawford, PhD (*Yale University*), William C. Goedel, PhD (*Brown University*), Gregg Gonsalves, PhD (*Yale University*), Ian W. Holloway, PhD, LCSW, MPH (*University of California, Los Angeles*), Louise Ivers, MB, BCh, MD, MPH, DTMH (*Massachusetts General Hospital)*, Lawrence C. Long, MCom, PhD (*Boston University)*, Kenneth Mayer, MD (*The Fenway Institute*), Gregorio Millett, MPH (*amfAR*), Eric J. Tchetgen Tchetgen, PhD (*University of Pennsylvania*). [Research sponsors and funders]{.underline}: amfAR, National Institutes of Health, neo4j,Marketing sponsors and funders: Grindr, Hub for Health Intervention, UCLA Luskin School of Public Affairs.Administration: Christian Urrutia (prep4all), James Krellenstein (prep4all).Report reviewers: ...
:::

{{ meta.title }}

# Welcome {.unnumbered .hidden}
