```{r process_data}

targets::tar_source("R_functions") # Access custom defined functions


```

```{r}
targets::tar_make(reporter = "silent") # Run data pipeline

```

::: {#authors}
Keletso Makofane, Nick Diamond, Jennifer McQueen, Elle Lett, Nguyen Tran

RESPND-MI Collaboration
:::

```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "peach", color = "dark_orange", shape = 0)

```


::: {#date}
March 2024, New York City

https://www.mpxnyc.app
:::




Welcome to the MPX NYC Study on the social and sexual connections of LGBTQ New Yorkers. Through this website we report data we collected among LGBTQ New Yorkers in the Fall of 2022 when the first global human mpox oubreak occured.

When we started, MPOX testing was not at all available. Our goal was to estimate the proportion of community members who experienced mpox-like symptoms. We also wanted to understand the structure of social and sexual networks that connect our community so that we could understand how to most effectively distribute MPOX vaccines. Within 5 months of conceiving the project, we had strated collecting data. We kept the survey open for about 1 month, obtaining about 1300 responses.

The data have proven useful - we started sharing periodic analyses with the New York City Department of Health, guiding their outreach activities. Preliminary analyses were shared at the IAS international conference in Montreal, and have through several presentations and public discussions since then.

As MPOX shifted from an outbreak to an epidemic, we took time to come up with the best way to make sense of these data and to convey them to different readers. This report is the result of that effort.

We have prioritized the reproducibility of our study findings and our study design. Our hope is that alliances of LGBTQ activists and researchers will use these methods to answer the pressing questions of their contexts. The data and code we used to make this report are available here [HYPERLINK TO GITHUB]. We have written detailed appendices on the methods we devised to make sense of our data.

The next section gives an overview of what scientists already know about the themes our research report touches on: the relationship between people’s social networks and their health, the infectious disease dynamics of a novel outbreak, the health of LGBTQ people, the measurement of spatial data, and the health of LGBTQ people.


1. Housing
2. Nutrition
3. Violence
4. Healthcare access
5. Employment
6. Health


::: {#acknowledgements}
[Principal investigator]{.underline}: Keletso Makofane, MPH, PhD. [Co-investigators]{.underline}: Jennifer Barnes-Balenciaga, Nicholas Diamond, MPH, Elle Lett, PhD, MA, MBiostat, Cody Nolan, MD, Martez Smith, LMSW, PhD, Nguyen Tran, MPH, PhD. [Former investigators]{.underline}: Pedro Botti Careneiro, MPH, PhD, Seema Kara, MPH, James Krellenstein, Ken Nadolski, MPH, Robert Pitts, MD, Grant Roth, MPH, Sudipta Saha, MS, Christian Urrutia, Chris Wyman. [Translators]{.underline}: Antón Castellanos Usigli, MPH, PhD Referencegroup: Judith D. Auerbach, PhD (*University of California, San Francisco*), Lisa Berkman, PhD (*Harvard University*), Forrest W. Crawford, PhD (*Yale University*), William C. Goedel, PhD (*Brown University*), Gregg Gonsalves, PhD (*Yale University*), Ian W. Holloway, PhD, LCSW, MPH (*University of California, Los Angeles*), Louise Ivers, MB, BCh, MD, MPH, DTMH (*Massachusetts General Hospital)*, Lawrence C. Long, MCom, PhD (*Boston University)*, Kenneth Mayer, MD (*The Fenway Institute*), Gregorio Millett, MPH (*amfAR*), Eric J. Tchetgen Tchetgen, PhD (*University of Pennsylvania*). [Research sponsors and funders]{.underline}: amfAR, National Institutes of Health, neo4j,Marketing sponsors and funders: Grindr, Hub for Health Intervention, UCLA Luskin School of Public Affairs.Administration: Christian Urrutia (prep4all), James Krellenstein (prep4all). [Report reviewers]{.underline}: ...
:::

# Welcome to MPX NYC {.unnumbered .hidden}






