```{r update_mpxnyc_package}
#pat  <- tidyjson::read_json("_config.json")["..JSON"][[1]][["settings"]][["github-token"]] # update packages
#remotes::install_github("KeletsoMakofane/mpxnyc", auth_token = pat)
remotes::install_github("KeletsoMakofane/mpxtools")
```

```{r other_packages}
#install.packages(c("labelled", "tidygraph", "dplyr", "here", "ggimage", "rsvg", "ggraph", "ggplot2", "gt", "gtsummary", "latex2exp"))
```

```{r process_data}
targets::tar_source("R_functions") # Access custom defined functions
targets::tar_make(reporter = "silent") # Run data pipeline
```








# Home {.hidden .unnumbered}

:::: {.p-5 .pt-1 .mb-4 .rounded-3 .shadow-sm .hero-banner .centered layout-align="center"}
# Community and Connection {.unnumbered}

A comprehensive report for MPX NYC — a rapid, community-led study of mpox, networks, and care built by queer and trans New Yorkers, for queer and trans New Yorkers.

October 2025

::: text-center
[Explore the Findings](#sec-participants){.btn .btn-outline-primary .m-1 .btn-sm} [Learn the Methods](#sec-data){.btn .btn-outline-primary .m-1 .btn-sm}
:::
::::



# Welcome {.unnumbered}

This online book presents **MPX NYC**—an anonymous, web-based study that maps how LGBTQ+ people connect through the places we share. Using a custom survey platform, we **asked folks where they lived and gathered** in the preceding month. For safety, we recorded **only census-tract labels**, not addresses. From this, we built a city-scale **people–place network** and analyzed how connection shapes risk and care.

[ACTIVISM]{.emphasize}: We conducted MPX NYC under **Rapid Epidemiologic Study of Sexual Networks, Demographics, and Mpox Infection** (**RESPND-MI)**, a queer- and trans-led collaboration born during the 2022 outbreak. We drew on tools honed by global HIV activists to move fast, share information, and act together.

[ACTIONABLE INSIGHTS]{.emphasize}: Some of what we learned about stopping an outbreak: 1) **Private, not public.** Outreach limited to sex-positive venues will miss most contact—**private residences drive exposure**. 2) **Geographic hubs.** Neighborhood clusters act as local and city-wide hubs for connection and spread. 3) **Speed wins.** In a decision between vaccinating to limiting geographic spread vs. **vaccinating as many people as fast as possible**, the latter performs better in our model.

[CAUSAL INFERENCE FOR NETWORKS]{.emphasize}: As a result of doing this study, we developed a framework for causal inference in social-spatial epidemiology. We introduce the Social and Spatial Network Analysis with Causal interpretation, or **SSNAC**. SSNAC adapts familiar ideas in biostaticis to allow researchers to conceptualize, collect, and analyze data about **networks, not isolated individuals**.

:::: {.alert .alert-secondary .p-t-2 .p-b-0 .m-t-10}
::: {.text-center}
**Secure your seat** for all four sessions of the [People's Department of Health Seminar Series](https://www.controlf.info/seminar-series){.external .emphasize target="_blank"}. Early-bird pricing ends on November 4. Space is limited.
:::
::::

# At a glance {.unnumbered}

::::::::::::::: {.grid .g-6 .mt-1}
::::: {.g-col-12 .g-col-md-12 .g-col-xl-12}
:::: {.card .h-100 .shadow-sm .text-center}
[MPX NYC RESULTS]{.emphasize}
**Residences and gatherings cluster** in Manhattan and North Brooklyn. Mixing shows strong homophily by age, race–gender, and sexual orientation. Simulated strategies trade off **rapid coverage** versus **faster network fragmentation**.


::: text-center
[People](#sec-participants){.btn .btn-sm .btn-outline-secondary} [Gatherings](#sec-venues){.btn .btn-sm .btn-outline-secondary} [Going out](#sec-movement){.btn .btn-sm .btn-outline-secondary} [Mixing](#sec-mixing){.btn .btn-sm .btn-outline-secondary} [Outbreaks](#sec-intervention){.btn .btn-sm .btn-outline-secondary} [Supplementary results](#sec-appendixresults){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::

::::: {.g-col-12 .g-col-md-12 .g-col-xl-12}
:::: {.card .h-100 .shadow-sm .text-center}
[MPX NYC METHODS]{.emphasize}

The study deploys an **innovative, privacy-preserving survey platform** to collect spatial and social data anonymously (**on-device processing**, anonymous link-tracing, **graph database**) and uses statistical tools to **describe social-spatial networks**.


::: text-center
[Data](#sec-data){.btn .btn-sm .btn-outline-secondary} [Measures](#sec-measures){.btn .btn-sm .btn-outline-secondary} [Analysis](#sec-analysis){.btn .btn-sm .btn-outline-secondary} [Measurement](#sec-measurement){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::

::::: {.g-col-12 .g-col-md-6 .g-col-xl-6}
:::: {.card .h-100 .shadow-sm .text-center}
[SSNAC FRAMEWORK]{.emphasize}

SSNAC updates causal-inference tools to address **interdependent observational units** and helps researchers learn from causal interference.


::: text-center
[Context](#sec-appendix-social-spatial){.btn .btn-sm .btn-outline-primary} [Description](#sec-appendix-analysis){.btn .btn-sm .btn-outline-primary} [Causality](#sec-causal-interpretation){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::

::::: {.g-col-12 .g-col-md-6 .g-col-xl-6}
:::: {.card .h-100 .shadow-sm .text-center}
[RESPND-MI]{.emphasize}

The project organized research through a **weekly LGBTQ+ Community Forum**, distributed leadership, and small, shared tasks—building **redundancy as resilience**.


::: text-center
[Organizing](#sec-organizing){.btn .btn-sm .btn-outline-primary} [Marketing](#sec-marketing){.btn .btn-sm .btn-outline-primary}
:::
::::
:::::
:::::::::::::::

# Open, accessible science {.unnumbered}

All code and analytic frameworks powering this site are public. We invite alliances of LGBTQ+ researchers and activists to adapt them for urgent questions on **housing, nutrition, violence, access to care, employment, and health**.

# Why this work matters {.unnumbered}

As support for LGBTQ+ health services contracts—and many queer public-health workers face layoffs—we need new ways to self-organize and deploy hard-won skills. Early in this project, queer and trans New Yorkers from across the city **joined hands to understand a new threat and act**. We showed that that rigorous epidemiology and community organizing can—and must—coexist.

Through the weekly **RESPND-MI LGBTQ+ Community Forum**, activists, clinicians, and researchers co-designed the study: refining language to avoid stigma, choosing outreach venues, and building bilingual campaigns. The project became not only a study *of* networks, but a network *itself*—a model of participatory, queer-led science built from abundance, care, and trust.

# Who we are {.unnumbered}

This website was developed by **Dr. Keletso Makofane**, who holds a PhD in social network epidemiology from Harvard University (2021), and a MPH in Biostatistics from Columbia University (2012) which he earned as a Fulbright scholar. Dr. Makofane is an **internationally recognized public health expert** in the global response to HIV. His focus is the **health and human rights of gay and bisexual men**. As a scholar Dr. Makofane develops **cutting-edge methods in network epidemiology** for use in community settings.

Dr. Makofane drafted the content for the website in consultation and discussion with **Nicholas Diamond**, MPH; **Jennifer Barnes-Balenciaga**; **Elle Lett**, MA, MBiostat, PhD; **Ken Mayer**, MD; and **Nguyen Tran**, MPH, PhD. It is a culmination of discussions held by members of the **RESPND-MI Investigator Group** (see below) over two years with early inputs from the RESPND-MI Reference Group. The **RESPND-MI** **LGBTQ+ Community Forum** guided the preparation of the study and helped us to make crucial decisions about study design collectively.

# Why self-publish

Unfunded and urgent, we prioritized making a **high-quality, reproducible** online book rather than a series of articles in academic journals. Our code and data are freely available, allowing researchers to easily reproduce our methods in order to engage in informed critique. We welcome academic journals and other publications interested in commissioning articles based on this work to contact us.

# Impact of MPX NYC

The MPX NYC team’s advocacy and research efforts have been shared through major media outlets: ***The New York Times,** The Atlantic, TIME, PBS NewsHour, CBS News, NPR, The Washington Post,* and ***STAT**,* as well as queer media such as ***The Body*** **and *POZ Magazine.*** International coverage in ***PLOS Global Public Health**, Out,* and *The Sunday Times* further extended the reach.

These stories shaped national conversations on health equity, stigma, and queer-led public health—positioning RESPND-MI as a trusted voice bridging science, activism, and policy in real time during the mpox emergency.

# People's Department of Health Seminar Series

This website was developed through [Ctrl+F](https://www.controlf.info/){.external target="_blank"}, a consulting group that combines creativity with rigor to address the public health challenges of our time. Secure your seat for all four sessions in [People's Department of Health Seminar Series](https://www.controlf.info/seminar-series){.external target="_blank"}. Presented by Ctrl+F, each live, expert-led session with Dr. Keletso Makofane explores a different dimension of the RESPND-MI project—from causal analysis to policy advocacy.

Early-bird registration is \$199 through November 4. The regular price of \$249 begins November 5. All sales are final. Registered participants will receive a Zoom link 24 hours before the seminar begins. A recording will be available to all registrants after the session concludes. Attendance is limited to ensure space for live Q&A. Please register early to secure your spot. For questions, contact [admin\@controlf.info](mailto:admin@controlf.info). 

```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center
plot_icon(icon_name = "peach", color = "dark_orange", shape = 0)
```

::: {#acknowledgements}
**RESPND-MI** [Principal investigator]{.underline}: Keletso Makofane, MPH, PhD. [Co-investigators]{.underline}: Jennifer Barnes-Balenciaga, Nicholas Diamond, MPH, Elle Lett, PhD, MA, MBiostat, Cody Nolan, MD, Martez Smith, LMSW, PhD, Nguyen Tran, MPH, PhD. [Former investigators]{.underline}: Pedro Botti Careneiro, MPH, PhD, Seema Kara, MPH, James Krellenstein, Ken Nadolski, MPH, Joseph Osmundson, PhD, Robert Pitts, MD, Grant Roth, MPH, Sudipta Saha, MS, Christian Urrutia, MBA, Chris Wyman. [Translator]{.underline}: Antón Castellanos Usigli, MPH, DrPH. [Backend web developer]{.underline}: Imran Ansari. [Reference group]{.underline}: Judith D. Auerbach, PhD (*University of California, San Francisco*), Lisa Berkman, PhD (*Harvard University*), Forrest W. Crawford, PhD (*Yale University*), William C. Goedel, PhD (*Brown University*), Gregg Gonsalves, PhD (*Yale University*), Ian W. Holloway, PhD, LCSW, MPH (*University of California, Los Angeles*), Louise Ivers, MB, BCh, MD, MPH, DTMH (*Massachusetts General Hospital*), Lawrence C. Long, MCom, PhD (*Boston University)*, Kenneth Mayer, MD (*The Fenway Institute*), Gregorio Millett, MPH (*amfAR*), Eric J. Tchetgen Tchetgen, PhD (*University of Pennsylvania*). [Research sponsors and funders]{.underline}: amfAR; Harvard Center for AIDS Research; National Institutes of Health; Neo4j; New York State Department of Health. [Marketing sponsors and funders]{.underline}: Grindr; Hub for Health Intervention, UCLA Luskin School of Public Affairs. [Administration]{.underline}: Christian Urrutia, MBA (PrEP4All); James Krellenstein (PrEP4All).

**CONTACT** Keletso Makofane (keletso\@controlf.info). Nicholas Diamond (nick\@controlf.info). [Ctrl+F](https://www.controlf.info){target="_blank"}.

**SUGGESTED CITATION** Makofane, K., Diamond, N., Barnes-Balenciaga, J., Lett, E., Mayer, K., Tran, N. (2025). *Community and connection: A study on social connection among LGBTQ+ New Yorkers*. Ctrl+F on behalf of RESPND-MI. New York City. Available: https://mpxresponse.org

**ACKNOWLEDGEMENTS** We thank PrEP4All for generous administrative support; our individual donors; Kenneth Mayer, Eric Tchetgen Tchetgen, and John Diamond for creating the conditions for this work; members of the RESPND-MI Community Forum and Reference Group for suggestions from fundraising to study design; and the LGBTQ+ people who gave time and care in crisis. We dedicate this work to those who responded—and those who will respond next.
:::
