```{r update_mpxnyc_package}
#pat  <- tidyjson::read_json("_config.json")[["..JSON"]][[1]][["settings"]][["github-token"]] # update packages
#remotes::install_github("KeletsoMakofane/mpxnyc", auth_token = pat)

remotes::install_github("KeletsoMakofane/mpxtools")

```

```{r other_packages}
#install.packages(c("labelled", "tidygraph", "dplyr", "here", "ggimage", "rsvg", "ggraph", "ggplot2", "gt", "gtsummary", "latex2exp))

```

```{r process_data}
targets::tar_source("R_functions") # Access custom defined functions
targets::tar_make(reporter = "silent") # Run data pipeline
```


::: {#date}
June 2025, New York City
:::




```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "peach", color = "dark_orange", shape = 0)

```


::: {#acknowledgements}
[Lead author]{.underline}: Keletso Makofane, MPH, PhD. [Editor]{.underline}: Nicholas Diamond, MPH. [Co-authors]{.underline}: Jennifer Barnes-Balenciaga, Elle Lett, MA, MBiostat, PhD, Ken Mayer, MD, Nguyen Tran, MPH, PhD. 
:::


MPX NYC is a campaign of Rapid Epidemiologic Study of Prevalence, Network, and Demographics of Mpox Infection (RESPND-MI), an anonymous, online study about social and sexual connection among LGBTQ+ New Yorkers. We collected these data in the summer of 2022 when the first global human mpox outbreak occurred. Since then, as mpox shifted from an outbreak to an epidemic, we took the time to develop cutting-edge epidemiologic methods to analyze and interpret the data. We will be sharing the results and methods on this website, starting with the methods. 

We present these in a framework named Social and Spatial Network Analysis with Causal interpretation (SSNAC), which we motivate in @sec-appendix-social-spatial and detail in @sec-causal-interpretation. 



::: {#acknowledgements}
**RESPND-MI** 
[Principal investigator]{.underline}: Keletso Makofane, MPH, PhD. 
[Co-investigators]{.underline}: Jennifer Barnes-Balenciaga, Nicholas Diamond, MPH, Elle Lett, PhD, MA, MBiostat, Cody Nolan, MD, Martez Smith, LMSW, PhD, Nguyen Tran, MPH, PhD. 
[Former investigators]{.underline}: Pedro Botti Careneiro, MPH, PhD, Seema Kara, MPH, James Krellenstein, Ken Nadolski, MPH, Joseph Osmundson, PhD, Robert Pitts, MD, Grant Roth, MPH, Sudipta Saha, MS, Christian Urrutia, MBA, Chris Wyman. 
[Translator]{.underline}: Antón Castellanos Usigli, MPH, DrPH.
[Reference group]{.underline}: Judith D. Auerbach, PhD (*University of California, San Francisco*), Lisa Berkman, PhD (*Harvard University*), Forrest W. Crawford, PhD (*Yale University*), William C. Goedel, PhD (*Brown University*), Gregg Gonsalves, PhD (*Yale University*), Ian W. Holloway, PhD, LCSW, MPH (*University of California, Los Angeles*), Louise Ivers, MB, BCh, MD, MPH, DTMH (*Massachusetts General Hospital*), Lawrence C. Long, MCom, PhD (*Boston University)*, Kenneth Mayer, MD (*The Fenway Institute*), Gregorio Millett, MPH (*amfAR*), Eric J. Tchetgen Tchetgen, PhD (*University of Pennsylvania*). 
[Research sponsors and funders]{.underline}: amfAR; Harvard Center for AIDS Research; National Institutes of Health;  neo4j, New York State Department of Health. [Marketing sponsors and funders]{.underline}: Grindr; Hub for Health Intervention, UCLA Luskin School of Public Affairs. [Administration]{.underline}: Christian Urrutia, MBA (PrEP4All); James Krellenstein (PrEP4All).
:::

::: {#acknowledgements}
**OPEN SCIENCE** All the code we developed as a part of this project, including the code for this website, will be publicly available. Our hope is that alliances of LGBTQ+ activists and researchers will use these methods to answer the pressing questions of their communities: housing, nutrition, violence, access to care, employment, health, and others. As government support for LGBTQ+ health diminishes, we will need to take it upon ourselves to conduct research and surveillance and use what we learn to respond to the needs of our communities. We include in this report a brief account of the steps we implemented to coordinate the volunteer work of over a dozen activists, academics, and community leaders.
:::

::: {#acknowledgements}
**CONTACT** Keletso Makofane (keletso@controlf.info). Nicholas Diamond (nick@controlf.info). [Ctrl+F](https://www.controlf.info){target="_blank"}.
:::

::: {#acknowledgements}
**SUGGESTED CITATION** Makofane, K., Diamond, N., Barnes-Balenciaga, J., Lett, E., Mayer, K., Tran, N. (2025). *Community and connection: A study on social connection among LGBTQ+ New Yorkers*. Ctrl+F on behalf of RESPND-MI. New York City. Available: https://mpxresponse.org
:::



# Welcome to RESPND-MI {.unnumbered .hidden}






