


```{r process_data}

targets::tar_make(reporter = "silent") # Run data pipeline

```

```{r}

targets::tar_source(files = paste0(here::here(), "/R_functions")) # Access custom defined functions
```

::: {#authors}
Keletso Makofane, Nick Diamond, Jennifer McQueen, Elle Lett, Nguyen Tran

RESPND-MI Collaboration
:::

::: {#date}
March 2024, New York City

https://www.mpxnyc.app
:::

```{r}
#| fig-width: 3
#| fig-height: 3
#| fig-align: center


plot_icon(icon_name = "peach", color = "light_orange", shape = 8)

```





::: {#contents}
| Section       | Page                     | Stage        | Help needed                                                                                                      |
|---------------|---------------|---------------|-----------------------------|
| Preliminaries | Welcome                  | Under Review |                                                                                                                  |
| Background    | 1_Introduction           | Outline      | Citations for relevant papers on infectious disease modelling, spatial epidemiology, social network epidemiology |
| Methods       | 2_Data Collection        | Under Review |                                                                                                                  |
| Methods       | 3_Measures               | Under Review | Achieving clarity and conciseness vs. confusing non-specialist readers                                           |
| Methods       | 4_Statistical Analysis   | Under Review | Achieving clarity and conciseness vs. confusing non-specialist readers                                           |
| Results       | 5_Participants           | Under Review | Ensuring that figures are clear, well labelled, well described.                                                  |
| Results       | 6_Contact venues         | Under Review | Ensuring that figures are clear, well labelled, well described.                                                  |
| Results       | 7_Movement               | Under Review | Ensuring that figures are clear, well labelled, well described.                                                  |
| Results       | 8_Spatial Mixing         | Under Review | Ensuring that figures are clear, well labelled, well described.                                                  |
| Results       | 9_Outbreak interventions | Under Review | Ensuring that figures are clear, well labelled, well described.                                                  |
| Discussion    | 10_Discussion            | Outline      |                                                                                                                  |
| About us      | 11_About us              | Outline      |                                                                                                                  |
| About us      | 12_Acknowledgements      | Outline      |                                                                                                                  |
| Appendices    | A_Supplementary Methods  | Under Review | Achieving clarity and conciseness while providing enough assistance for a student of epidemiology to understand. |
| Appendices    | B_Supplementary Results  | Under Review | Ensuring that figures are clear, well labelled, well described.                                                  |
| Appendices    | C_Study questionnaire    | Under Review | Usability for a reader of the report                                                                             |
| Appendices    | D_Causal intervention    | Outline      |                                                                                                                  |
:::


# Welcome {.unnumbered .hidden}

