---
title: "MPX NYC"
subtitle: "Key findings and recommendations"
author: "Keletso Makofane"
date: 23 May 2024

crossref: 
  thm-prefix: Box
  thm-title: Box
  tbl-prefix: Table
  tbl-title: Table
  fig-prefix: ""
  fig-title: ""
editor: visual
always_allow_html: true
prefer-html: true
fig-cap-location: top 
execute:
  echo: false
  warning: false
  message: false
format:
  revealjs:
    incremental: true
    scrollable: true
    fig-align: center
    align: center
---

```{r update_mpxnyc_package, include = FALSE, messages=FALSE, warning = FALSE}
remotes::install_github("KeletsoMakofane/mpxnyc", auth_token = "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")
```

```{r load_libraries, include = FALSE, messages=FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(mpxnyc)
library(sf)
library(tidygraph)
library(ggraph)
library(igraph)



mpxnyc_colors <- mpxnyc::mpxnyc_colors
attach(mpxnyc_colors)

```

```{r update_data_pipeline, include=FALSE, messages=FALSE, warning = FALSE}


targets::tar_make() # Runs the data pipeline shown in _targets.R


```



```{r}


targets::tar_source(files = "R_functions")

```


```{r plot_styling}
apply_style_spacing_descriptives <- function(plot, caption_hjust = 1){
  
  plot +
    theme_void() +
    scale_fill_manual("", values = c(
                                      dark_blue,
                                      dark_pink,
                                      dark_purple,
                                      light_blue,
                                      light_pink,
                                      light_purple,
                                      light_orange,
                                      dark_green,
                                      light_green,
                                      mid_blue,
                                      mid_purple,
                                      dark_brown,
                                      mid_brown,
                                      light_brown
                                    )) +
    theme(
        plot.title         = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
        plot.subtitle      = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
        axis.title.y       = element_text(angle = 90, margin = margin(0, 10, 0, 0, "mm")),
        plot.caption       = element_text(margin = margin(15, 0, 0, 0), hjust = caption_hjust),
        panel.margin       = margin(1,1,1,1, "cm"),
        plot.margin        = margin(1,1,1,1, "cm"),
        legend.position    = "none", 
        panel.grid.major.y = ggplot2::element_line(size = 0.1),
        axis.text.x        = element_text(),
        axis.text.y        = element_text()
    )
}

apply_style_spacing_remainder <- function(plot, caption_hjust = 0){
  
  plot +
    theme(
        plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
        plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
        axis.title.y  = element_text(angle = 90, margin = margin(0, 10, 0, 0, "mm")),
        plot.caption  = element_text( hjust = caption_hjust),
        panel.margin  = margin(1,1,1,1, "cm"),
        plot.margin   = margin(1,1,1,1, "cm")
    ) +
            scale_fill_manual("", values = c(
                                      dark_blue,
                                      dark_pink,
                                      dark_purple,
                                      light_blue,
                                      light_pink,
                                      light_purple,
                                      light_orange,
                                      dark_green,
                                      light_green,
                                      mid_blue,
                                      mid_purple,
                                      dark_brown,
                                      mid_brown,
                                      light_brown
                                    )) 
}

apply_style_spacing_place <- function(plot, caption_hjust = 0){
  
  plot +
        scale_fill_manual("", values = c(
                                      dark_blue,
                                      dark_pink,
                                      dark_purple,
                                      light_blue,
                                      light_pink,
                                      light_purple,
                                      light_orange,
                                      dark_green,
                                      light_green,
                                      mid_blue,
                                      mid_purple,
                                      dark_brown,
                                      mid_brown,
                                      light_brown
                                    )) +
     theme(
         plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
         plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
         plot.caption  = element_text( hjust = caption_hjust, margin = margin(1, 1, 1, 1, "cm")),
         plot.margin   = margin(1,1,1,1, "cm")
     )
}

apply_style_spacing_grouped_radar <- function(plot, caption_hjust = 0){
    
  plot +
        scale_fill_manual("", values = c(
                                      dark_blue,
                                      dark_pink,
                                      dark_purple,
                                      light_blue,
                                      light_pink,
                                      light_purple,
                                      light_orange,
                                      dark_green,
                                      light_green,
                                      mid_blue,
                                      mid_purple,
                                      dark_brown,
                                      mid_brown,
                                      light_brown
                                    )) +
     theme(
         plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
         plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
         plot.caption  = element_text( hjust = caption_hjust, margin = margin(1, 1, 1, 1, "cm")),
         plot.margin   = margin(1,1,1,1, "cm"),
         legend.position = "bottom"
     )
}

apply_style_spacing_heatmap <- function(plot, caption_hjust = 0){
  
  plot +
    theme(
        plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
        plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
        plot.caption  = element_text( hjust = caption_hjust),
        panel.margin  = margin(1,1,1,1, "cm"),
        plot.margin   = margin(1,1,1,1, "cm"),
        legend.position = "bottom"
    ) +
      scale_fill_gradient2("", trans = "log", low = dark_blue, mid = "white", high = dark_pink)  
}

apply_style_spacing_coverage <- function(plot, caption_hjust = 0){
  
  plot +
        scale_fill_manual("", values = c(
                                      dark_blue,
                                      dark_pink,
                                      light_blue
                                    )) +
    theme(
        plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
        plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
        axis.title.y  = element_text(angle = 90, margin = margin(0, 10, 0, 0, "mm")),
        plot.caption  = element_text( hjust = caption_hjust),
        panel.margin  = margin(1,1,1,1, "cm"),
        plot.margin   = margin(1,1,1,1, "cm"),
        legend.position = "none"
      
    )  
}

add_caption <- function(plot, plot_name){
  
  plot + 
  labs(
      title    = captions_and_titles(plot_name)$title,
      subtitle = captions_and_titles(plot_name)$subtitle,
      caption  = captions_and_titles(plot_name)$caption %>% str_wrap(110) %>% paste0("\n\n", captions_and_titles("common_caption") )
    )
}

```



```{r plot_data}


get_variable_labels <- function(variable_name, person_analysis = TRUE){
    
  variable_labels           <- targets::tar_read(initial_settings)[["labels_list"]][[variable_name]][["levels"]] %>% unlist()
  variable_levels           <- names(variable_labels)
  
  if (is.null(variable_labels)){
    if (person_analysis){
          variable_labels <- targets::tar_read(bipartite_graph) %>%
                          tidygraph::activate(nodes) %>%
                          tidygraph::filter(type) %>%
                          data.frame() %>%
                          {.[,variable_name]} %>%
                          unique()
    
    variable_levels <- variable_labels
    } else {
              
    variable_labels <- targets::tar_read(bipartite_graph) %>%
                          tidygraph::activate(edges) %>%
                          tidygraph::filter(type) %>%
                          data.frame() %>%
                          {.[,variable_name]} %>%
                          unique()
    
    variable_levels <- variable_labels
    }} 
  
  return(list(variable_levels = variable_levels, variable_labels = variable_labels))

}

make_commuting_network_data <- function(){
  
home_data <-  targets::tar_read(bipartite_graph) %>%
                activate(edges) %>%
                filter(home) %>%
                mutate(person_name = .N()$name[from]) %>%
                mutate(home_name = .N()$name[to]) %>%
                data.frame() %>%
                select(home_name, person_name)

place_data <-  targets::tar_read(bipartite_graph) %>%
                activate(edges) %>%
                filter(!home) %>%
                mutate(person_name = .N()$name[from]) %>%
                mutate(place_name = .N()$name[to]) %>%
                data.frame() %>%
                select(place_name, person_name)
    
  place_data %>% 
    left_join(home_data) %>%
      transmute(from = home_name, to = place_name) %>%
      group_by(from, to) %>%
      summarize(weight = n()) 
  
}

make_coattendance_network_data <- function(){
  
  targets::tar_read(bipartite_graph) %>%
    igraph::bipartite_projection(which = "false") %>%
    tidygraph::as_tbl_graph() %>%
    activate(edges) %>%
    mutate(from_name = .N()$name[from], to_name = .N()$name[to]) %>%
    data.frame() %>%
    transmute(from = from_name, to = to_name, weight = weight) %>%
    mutate(
      new_from =  ifelse(from > to, from, to), 
      new_to = ifelse(from > to, to, from)
      ) %>%
    transmute(from = new_from, to = new_to, weight = weight) %>%
    group_by(from, to) %>%
    summarize(weight = sum(weight))
  
  
}

make_3_way_table <- function(variable = overall,stratum_variable_a = overall, stratum_variable_b = overall, person_analysis = TRUE){
  variable           <- enquo(variable)
  stratum_variable_a <- enquo(stratum_variable_a)
  stratum_variable_b <- enquo(stratum_variable_b)

  variable_name           <- quo_name(variable)
  stratum_variable_a_name <- quo_name(stratum_variable_a)
  stratum_variable_b_name <- quo_name(stratum_variable_b)
  
  get_variable_labels(variable_name)
  
  variable_levels <- get_variable_labels(variable_name)[["variable_levels"]]
  variable_labels <- get_variable_labels(variable_name)[["variable_labels"]]
  
    stratum_variable_a_levels <- get_variable_labels(stratum_variable_a_name)[["variable_levels"]]
  stratum_variable_a_labels <- get_variable_labels(stratum_variable_a_name)[["variable_labels"]]
  
  
    stratum_variable_b_levels <- get_variable_labels(stratum_variable_b_name)[["variable_levels"]]
  stratum_variable_b_labels <- get_variable_labels(stratum_variable_b_name)[["variable_labels"]]
  
  if (person_analysis){
      original_data_raw  <- targets::tar_read(bipartite_graph_coverage) %>%
                                activate(nodes) %>%
                                filter(type == TRUE) 
      
      simulated_data_raw <- targets::tar_read(bipartite_graph_coverage_sim) %>%
                                activate(nodes) %>%
                                filter(type == TRUE) 
  } else {
      original_data_raw  <- targets::tar_read(bipartite_graph_coverage) %>%
                                activate(edges) 
      
      simulated_data_raw <- targets::tar_read(bipartite_graph_coverage_sim) %>%
                                activate(edges)
  }
  

  
  
  
  original_data <- original_data_raw %>%
                            data.frame() %>%
                            mutate(overall = "overall") %>%
                            mutate(
                              level           = {{variable}},
                              stratum_a       = {{stratum_variable_a}},
                              stratum_b       = {{stratum_variable_b}}
                            ) %>%
                            mutate(
                              level = factor(level, variable_levels, variable_labels),
                              stratum_a = factor(stratum_a, stratum_variable_a_levels, stratum_variable_a_labels),
                              stratum_b = factor(stratum_b, stratum_variable_b_levels, stratum_variable_b_labels)
                            ) %>%
                            group_by(level, stratum_a, stratum_b) %>%
                            summarize(count = n()) %>%
                            ungroup() %>%
                            group_by(stratum_a, stratum_b) %>%
                            mutate(proportion = count / sum(count)) 
  
    simulated_data <-   simulated_data_raw %>%
                            data.frame() %>%
                            mutate(overall = "overall") %>%
                            data.frame() %>%
                            mutate(
                              level           = {{variable}},
                              stratum_a       = {{stratum_variable_a}},
                              stratum_b       = {{stratum_variable_b}}
                            ) %>%
                            mutate(
                              level = factor(level, variable_levels, variable_labels),
                              stratum_a = factor(stratum_a, stratum_variable_a_levels, stratum_variable_a_labels),
                              stratum_b = factor(stratum_b, stratum_variable_b_levels, stratum_variable_b_labels)
                            ) %>%
                            group_by(rep, level, stratum_a, stratum_b) %>%
                            summarize(count = n()) %>%
                            ungroup() %>%
                            group_by(rep, stratum_a, stratum_b) %>%
                            mutate(proportion = count / sum(count)) %>%
                            ungroup() %>%
                            group_by(stratum_a, stratum_b, level) %>%
                            summarize(
                                      count_mean = mean(count), 
                                      count_ci_lb = quantile(count, 0.025),
                                      count_ci_ub = quantile(count, 0.975),
                                      proportion_mean = mean(proportion),
                                      proportion_ci_lb = quantile(proportion, 0.025),
                                      proportion_ci_ub = quantile(proportion, 0.975)
                                        )
    
    
    original_data %>%
      left_join(simulated_data) %>%
      arrange(stratum_a, stratum_b, level) %>%
      mutate(
        variable = variable_name,
        strata_a = stratum_variable_a_name,
        strata_b = stratum_variable_b_name) %>%
      ungroup() %>%
      select(variable, strata_a, strata_b, names(.)) 
  
}

make_2_way_table <- function(variable = overall, stratum_variable = overall, person_analysis = TRUE){
  
  make_3_way_table({{variable}}, {{stratum_variable}}, person_analysis = person_analysis) %>%
    select(-stratum_b, -strata_b) %>%
    rename(stratum = stratum_a, strata = strata_a)
}

make_1_way_table <- function(variable = overall, person_analysis = TRUE){
  
  make_2_way_table({{variable}}, person_analysis = person_analysis) %>%
    select(-stratum, -strata)
}



make_coverage_table_sim <- function(intervention_priority_input = "contact", intervention_stratification_input = "overall"){

  
    targets::tar_read(intervention_coverage_data_sim)[["place_coverage"]] %>%
    filter(
      intervention_priority == intervention_priority_input, 
      intervention_stratification == intervention_stratification_input
      ) %>%
    mutate(level = intervention_contact_place) %>%
        group_by(intervention_priority, intervention_ranking, intervention_stratification) %>%
    summarize(
              mean_count = mean(count), 
              count_ci_lb = quantile(count, 0.025), 
              count_ci_ub = quantile(count, 0.975),
              mean_proportion = mean(proportion),
              proportion_ci_lb = quantile(proportion, 0.025),
              proportion_ci_ub = quantile(proportion, 0.975),
              mean_cum_prop = mean(cum_prop),
              cum_prop_ci_lb = quantile(cum_prop, 0.025),
              cum_prop_ci_ub = quantile(cum_prop, 0.975)
              )

}


make_coverage_table <- function(intervention_priority_input = "contact", intervention_stratification_input = "overall"){
  targets::tar_read(intervention_coverage_data)[["place_coverage"]] %>%
    filter(
      intervention_priority == intervention_priority_input, 
      intervention_stratification == intervention_stratification_input
      ) %>%
    mutate(level = intervention_contact_place) 

}


make_contact_matrix_table <- function(variable){
  variable <- enquo(variable)
  
  variable_name <- quo_name(variable)
  
  
  data <- targets::tar_read(bipartite_graph) %>%
  filter(!(demo_group %in% c("missing", "other")) | !type) %>%
                    igraph::bipartite.projection(which = "true") %>%
                    as_tbl_graph(directed = FALSE) %>%
                    mutate(connection_var = {{variable}}) %>%
    mutate(connection_var = factor(connection_var, get_variable_labels(variable_name)[["variable_levels"]], get_variable_labels(variable_name)[["variable_labels"]])) %>%
                    activate(edges) %>%
                    mutate(
                      from_level = .N()$connection_var[from], 
                      to_level = .N()$connection_var[to]) %>%
                    data.frame() 

conditional <- data %>%
                    group_by(from_level, to_level) %>%
                    summarize(weight = sum(weight)) %>%
                    group_by(from_level) %>%
                    mutate(conditional = weight / sum(weight))

marginal <- data %>%
                    group_by(to_level) %>%
                    summarize(weight = sum(weight)) %>%
                    mutate(marginal = weight / sum(weight))

conditional %>%
  left_join(marginal, by = c("to_level")) %>%
  mutate(bias = conditional / marginal ) %>%
  ungroup()
}









```


```{r}

make_bar_plot <- function(data){
  
  ggplot2::ggplot(data) + 
    ggplot2::geom_bar(aes(x = level, fill = level, y = proportion), width = 1, stat = "identity", color = "black") + 
    ggplot2::geom_text(aes(x = level, y = proportion + 0.05, label = count), alpha = 0.7) +
    ggplot2::theme_void() + 
    ggplot2::scale_x_discrete(drop = FALSE) +
    ggplot2::scale_y_continuous("Proportion of participants", labels = scales::percent)
}

make_coverage_plot <- function(data){
  
  ggplot2::ggplot(data) + 
    ggplot2::geom_bar(aes(y = level, fill = group, x = proportion), width = 1, stat = "identity", color = "black") + 
    ggplot2::theme_void() + 
    ggplot2::scale_y_discrete(drop = FALSE, limits = rev) +
    ggplot2::scale_x_continuous("Proportion of participants", labels = scales::percent) + 
    ggplot2::theme(
              axis.text = element_text(),
        panel.grid.major.y = element_line()
    )

}

make_one_stratum_radar_plot <- function(data){
  
  data_n_counts <- data %>%
    group_by(stratum) %>%
    summarize(n = sum(count))
  data %>%
    mutate(prop_label = scales::percent(proportion, accuracy = 1)) %>%
    ggplot() +
    geom_bar(aes(x = level, y = proportion, fill = level), stat = "identity", width = 1, color = "black") +
    geom_text(aes(x = 0, y = -0.8, label = paste("n =", n)), data = data_n_counts, size = 5) +
    geom_text(aes(label = prop_label, x = level, y = proportion + 0.3), size = 3, face = "bold", alpha = 0.7) +
    facet_grid( . ~ stratum, switch = "y") +
    coord_polar(clip = FALSE) +
    theme_void() +
    theme(
      legend.position = "bottom",
      strip.text    = element_text( hjust = 0.5),
      strip.text.y  = element_text(),
      plot.title    = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5, margin = margin(1, 0, 15, 0, "mm")),
      plot.caption  = element_text( hjust = 0)
      ) +
    scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.8, 1))
}

make_two_stratum_radar_plot <- function(data){
    data_n_counts <- data %>%
    group_by(stratum_a, stratum_b) %>%
    summarize(n = sum(count))
  
    data %>%
          mutate(prop_label = scales::percent(proportion, accuracy = 1)) %>%
    ggplot() +
    geom_bar(aes(x = level, y = proportion, fill = level), stat = "identity", width = 1, color = "black") +
    geom_text(aes(x = 0, y = -0.8, label = paste("n =", n)), data = data_n_counts, size = 5) +
    geom_text(aes(label = prop_label, x = level, y = proportion + 0.3), size = 3, face = "bold", alpha = 0.7) +
    facet_grid( stratum_a ~ stratum_b, switch = "y") +
    coord_polar(clip = FALSE) +
    theme_void() +
    theme(
      legend.position = "bottom",
      strip.text    = element_text( hjust = 0.5),
      strip.text.y  = element_text(),
      plot.title    = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5, margin = margin(1, 0, 15, 0, "mm")),
      plot.caption  = element_text( hjust = 0)
      ) +
    scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.8, 1))
}

make_grouped_radar_plot <- function(data){
  data %>%
      filter(!is.na(stratum)) %>%
      ggplot() +
      geom_bar(aes(x = level, y = proportion, fill = level), stat = "identity", width = 1, color = "black") +
      facet_wrap(. ~ stratum) +
      coord_polar() +
      theme_void()  +
      scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.8, 1))
}

make_map_coverage_plot <- function(data){
  
  
  map_object <- mpxnyc::community_sf_obj %>%
                    rename(level = 1) %>%
                    left_join(data) 
                  
  
  ggplot(map_object) +
    geom_sf(fill = "grey") +
    geom_sf(aes(fill = group), color = "black") +
    theme_void() +
    theme(
      axis.text = element_blank(),
      legend.position = "bottom"
      ) 
  }


plot_place_network_matrix <- function(data){
  
   data_tiles <- mpxnyc::community_sf_obj %>%
   transmute(to = community, from = community) %>%
   expand(to, from)
   
   
  data %>% 
    ggplot() +
    geom_point(aes(y =from, x = to), data = data_tiles, color = "white") +
      geom_point(aes(y =from, x = to, size = weight), color = "black", alpha = 0.5) +
    theme_void() +
  theme(
    axis.text = element_text(size = 7, color = "black"),
    axis.text.x = element_text(angle = 90),
    axis.title = element_text(),
    axis.title.y = element_text(angle = 90),
    legend.position = "none"
  ) +
  scale_x_discrete("Destination community district", position = "top") +
  scale_y_discrete("Home community district",  limits=rev) 
}

plot_place_network_viz <- function(){
     graph <- targets::tar_read(data_vaccination_campaign_raw) %>%
                  purrr::keep(
                    function(graph){
                      intervention_priority <- graph %>% 
                                                    activate(nodes) %>%
                                                    pull(intervention_priority) %>%
                                                    {.[1]}
                      
                              intervention_setting <- graph %>% 
                                                    activate(nodes) %>%
                                                    pull(intervention_setting) %>%
                                {.[1]}
                              
                                strata <- graph %>% 
                                                    activate(nodes) %>%
                                                    pull(strata) %>%
                                                    {.[1]}
                              
                 intervention_priority == "contact" & intervention_setting == "home.social.sexual" & strata == "overall"
                              
                    }
                  )
  
  
    graph_data <- targets::tar_read(data_vaccination_coverage_raw) %>%
                      filter(intervention_priority == "contact", intervention_setting == "home.social.sexual") %>%
                      group_by(vax_place) %>%
                      summarize(count = n()) %>%
                      ungroup() %>%
                      arrange(-count) %>%
                      mutate(community = factor(vax_place, unique(vax_place))) %>%
                      mutate(prop = count / sum(count)) %>%
                      mutate(cumprop = cumsum(prop)) %>%
                      mutate(group = "Group A") %>%
                      mutate(group = ifelse(cumprop > 0.33, "Group B", group)) %>%
                      mutate(group = ifelse(cumprop > 0.66, "Group C", group)) %>%
                      mutate(group = lead(group)) %>%
                      mutate(group = ifelse(is.na(group), "Group C", group)) %>%
                      mutate(name = community)
    
    
    
    
  place_graph <- graph[[1]] %>%
                      igraph::bipartite_projection(which = "false") %>%
                      as_tbl_graph() %>%
                      select(name) %>%
                      left_join(graph_data)
  
 place_graph %>%
    activate(nodes) %>%
    mutate(deg = igraph::degree(.)) %>%
    filter(deg > 0) %>%
    filter(!is.na(group)) %>%
    ggraph() +
      geom_edge_link( aes(filter = weight > 10), alpha = 0.5, linewidth = 4) +
      geom_edge_link( aes(linewidth = weight, filter = weight <= 10 & weight > 5), alpha = 0.5, , linewidth = 1) +
      geom_edge_link( aes(linewidth = weight, filter = weight <= 5 ), alpha = 0.5, , linewidth = 0.1) +
      geom_node_label(aes(label = name , color = group, size = prop)) +
      theme_void() +
      scale_color_manual(values = c("Group A" = dark_pink, "Group B" = dark_blue, "Group C" = "grey")) +
      scale_linewidth_continuous() +
      theme(
        legend.position = "none",
        plot.margin = margin(0,0,0,0, "cm"),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0)
      ) 
  
}

plot_heatmap_contact <- function(data){

   
  
  data %>%
    ggplot() +
    geom_tile(aes(y = from_level, x = to_level, fill = bias), color = "black") +
    theme_void() +
    theme(
      axis.text.x = element_text(),
      axis.text.y = element_text(),
      axis.title = element_blank()
    ) +
    scale_x_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) 
}

```

# 
Interventions that focus on public venues where queer and trans people have sex are not sufficient to stop an outbreak.

## 
{{< include figures_code/fig_radar_groupsex.qmd >}}

##
{{< include figures_code/fig_radar_places_sexcontact.qmd >}}

## 
{{< include figures_code/fig_radar_places_distance.qmd >}}

##
{{< include figures_code/fig_radar_places_distance_sexcontact.qmd >}}

#
It is possible to strategically intervene by understanding how different parts of the city are connected through queer and trans connection. 

##
{{< include figures_code/fig_map_coverage.qmd >}}

##
{{< include figures_code/fig_bar_coverage.qmd >}}

##
{{< include figures_code/fig_matrix_neighborhoods.qmd >}}

##
{{< include figures_code/fig_matrix_co_att_neighborhoods.qmd >}}

##
{{< include figures_code/fig_network_coverage.qmd >}}


# And how subgroup of people are connected as a result

## 
{{< include figures_code/fig_heatmap_age.qmd >}}

## 
{{< include figures_code/fig_heatmap_demo_group.qmd >}}


## 
{{< include figures_code/fig_heatmap_sexOrientation.qmd >}}

# 
In order to successfully intervene we need to understand how easily we can reach people with interventions like vaccine. 

##
{{< include figures_code/fig_radar_sexOrientation_demo_group.qmd >}}

##
{{< include figures_code/fig_radar_monkeypoxVaccine_demo_group.qmd >}}

##
{{< include figures_code/fig_radar_hivPrep_demo_group.qmd >}}


# About MPX NYC
## Descriptive Statistics

###
{{< include figures_code/fig_bar_racegender.qmd >}}

###
{{< include figures_code/fig_bar_age.qmd >}}

###
{{< include figures_code/fig_bar_channel.qmd >}}

###
{{< include figures_code/fig_bar_gender.qmd >}}

###
{{< include figures_code/fig_bar_race.qmd >}}

###
{{< include figures_code/fig_bar_sexorientation.qmd >}}






