---
title: "Tables and Figures: MPX NYC Intervention Strategy"
author: "Keletso Makofane"

crossref: 
  thm-prefix: Box
  thm-title: Box
  tbl-prefix: Table
  tbl-title: Table
editor: visual
always_allow_html: true
prefer-html: true
fig-cap-location: top 
execute:
  echo: false
  warning: false
  message: false
format:
  revealjs:
    incremental: true
    scrollable: true
---

```{r update_mpxnyc_package, include = FALSE, messages=FALSE, warning = FALSE}
remotes::install_github("KeletsoMakofane/mpxnyc", auth_token = "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")
```

```{r load_libraries, include = FALSE, messages=FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(mpxnyc)
library(sf)
library(tidygraph)
library(ggraph)
library(igraph)



mpxnyc_colors <- mpxnyc::mpxnyc_colors
attach(mpxnyc_colors)

```

```{r update_data_pipeline, include=FALSE, messages=FALSE, warning = FALSE}


targets::tar_make() # Runs the data pipeline shown in _targets.R


```



```{r}


table_vaxcoverageappraochracegender <- function(){
                        targets::tar_read(data_vaccination_coverage) %>%
                          filter(intervention_setting == "home.social.sexual") %>%
                          filter(
                            !is.na(demo_group)
                          ) %>%
                          filter(
                            !(demo_group %in% c("missing", "other", "non-binary", "other-cisgender-man", "cisgender-woman", "transgender-man", "transgender-woman"))
                          ) %>%
                          filter(
                            intervention_priority == "contact"
                          ) %>%
                          group_by(
                            rep, 
                            demo_group, 
                            intervention_ranking, 
                            intervention_setting, 
                            intervention_priority, 
                            strata) %>%
                          summarize(count = n()) %>%
                          group_by(
                            rep, 
                            demo_group, 
                            intervention_setting, 
                            intervention_priority, 
                            strata) %>%
                          arrange(intervention_setting) %>%
                          mutate(prop = count / sum(count)) %>%
                          mutate(cumprop = cumsum(prop)) %>%
                          group_by(demo_group, intervention_ranking, intervention_setting, intervention_priority, strata) %>%
                          summarize(
                            prop_ci_lb = quantile(prop, 0.025), 
                            prop_ci_ub = quantile(prop, 0.975), 
                            prop = mean(prop),
                            cumprop_ci_lb = quantile(cumprop, 0.025), 
                            cumprop_ci_ub = quantile(cumprop, 0.975), 
                            cumprop = mean(cumprop),
                          ) %>%
                          filter(intervention_ranking < 250) 
}



table_vaxcoverageracegenderapproach <- function(){
      targets::tar_read(data_vaccination_coverage) %>%
                  filter(intervention_setting == "home.social.sexual") %>%
                  filter(!is.na(demo_group)) %>%
                  filter(!(demo_group %in% c("missing", "other", "non-binary", "other-cisgender-man", "cisgender-woman", "transgender-man", "transgender-woman"))) %>%
                  filter(intervention_priority == "contact") %>%
                  group_by(rep, demo_group, intervention_ranking, intervention_setting, intervention_priority, strata) %>%
                  summarize(count = n()) %>%
                  group_by(rep, demo_group, intervention_setting, intervention_priority, strata) %>%
                  arrange(intervention_setting) %>%
                  mutate(prop = count / sum(count)) %>%
                  mutate(cumprop = cumsum(prop)) %>%
                  group_by(demo_group, intervention_ranking, intervention_setting, intervention_priority, strata) %>%
                  summarize(
                    prop_ci_lb = quantile(prop, 0.025), 
                    prop_ci_ub = quantile(prop, 0.975), 
                    prop = mean(prop),
                    cumprop_ci_lb = quantile(cumprop, 0.025), 
                    cumprop_ci_ub = quantile(cumprop, 0.975), 
                    cumprop = mean(cumprop),
                  ) %>%
                  filter(intervention_ranking < 250)
}




table_agemix <- function(){
  targets::tar_read(data_contact_matrices) %>%
            dplyr::mutate(
                            activity_setting = factor(
                                                        activity_setting, 
                                                        c("home", "home.social", "home.social.sexual"), 
                                                        c("Home", "Home + Social", "Home + Social + Sexual")
                                                        )
                            )
}



table_racegendermix <- function(){
  targets::tar_read(data_contact_matrices) %>%
    dplyr::mutate(activity_setting = factor(activity_setting, c("home", "home.social", "home.social.sexual"), c("Home", "Home + Social", "Home + Social + Sexual")))
}


table_vaximpactpriorityapproach <- function(){
  targets::tar_read(data_vaccination_network_impact) %>%
                        dplyr::mutate(n_vaccinated = node_count - n_total) %>%
                        dplyr::select(strata, intervention_priority, intervention_setting, ranking, n_lcc, n_singleton, n_remainder, n_vaccinated) %>%
                        tidyr::pivot_longer(c(n_lcc, n_singleton, n_remainder, n_vaccinated), names_to = "measure", values_to = "count") %>%
                        dplyr::filter(measure != "n_vaccinated") %>%
                        dplyr::filter(intervention_setting == "home.social.sexual") %>%
                        dplyr::group_by(strata, intervention_priority, intervention_setting, ranking) %>%
                        dplyr::mutate(prop = count / sum(count)) %>%
  dplyr::mutate(prop_label = scales::percent(prop, accuracy = 1)) %>%
  dplyr::mutate(label_height = prop / 2) %>%
                        dplyr::ungroup() %>%
    mutate(measure = factor(measure, c("n_lcc", "n_remainder", "n_singleton"), c("Largest conntected component", "Remaining nodes", "Singletons")))
}



table_placesdistancesexcontact <- function(){
  targets::tar_read(data_radar_places_by_distanceFromHome) %>%
    group_by(level)
}

table_placessexcontact <- function(){
  targets::tar_read(data_radar_places_by_distanceFromHome)
}



targets::tar_source(files = "R_functions")





```


## 





:::: {.columns}

::: {.column width="70%"}
{{< include figures_code/fig_radar_groupsex.qmd >}}
:::

::: {.column width="30%"}
During the mpox outbreak of 2022, physical contact in congregate settings was widely reported by MPX NYC participants.
:::

::::

##

:::: {.columns}

::: {.column width="70%"}
{{< include figures_code/fig_radar_places.qmd >}}
:::

::: {.column width="30%"}
although, most contact occurred in private residences...
:::

::::


## 

:::: {.columns}

::: {.column width="70%"}
{{< include figures_code/fig_radar_places_sexcontact.qmd >}}
:::

::: {.column width="30%"}

Non-sexual social contact tended to happen in public venues and sexual contact tended to happen in private residences
:::

::::



##

:::: {.columns}

::: {.column width="70%"}
{{< include figures_code/fig_radar_places_distance.qmd >}}
:::

::: {.column width="30%"}


The further away from home a venue is, the less likely it is for that venue to be a private residence. 

:::

::::




## 


:::: {.columns}

::: {.column width="70%"}
{{< include figures_code/fig_radar_places_distance_sexcontact.qmd >}}
:::

::: {.column width="30%"}

But even when far from home, private residences are the most popular destination for group sex. 
:::

::::





## 
So if public group sex venues are an inefficient target for intervention during an outbreak, what can we do to reach community members who enjoy group sex?

##


:::: {.columns}

::: {.column width="70%"}
{{< include figures_code/fig_barmap_coverage.qmd >}}
:::

::: {.column width="30%"}

Certain neighborhoods are popular destinations for social and sexual contact, and so are useful locations from which to reach individuals.

:::

::::



##


:::: {.columns}

::: {.column width="70%"}
{{< include figures_code/fig_matrix_neighborhoods.qmd >}}
:::

::: {.column width="30%"}

Considering how individuals move across different parts of the city helps us to anticipate the pattern and speed of dissemination of an infectious disease across the city. 

:::

::::



##

:::: {.columns}

::: {.column width="70%"}

{{< include figures_code/fig_network_coverage.qmd >}}

:::

::: {.column width="30%"}
Considering the city a network of places allows us to understand which parts of the city play an important role in outbreak dynamics. 


:::

::::

##

:::: {.columns}

::: {.column width="70%"}

{{< include figures_code/fig_netregion_vaximpactpriorityapproach.qmd >}}

:::

::: {.column width="30%"}
This allows us to reason about the potential impact of geographically targeted vaccination campaigns on the underlying transmission network.


:::

::::






##
It is crucial to understand that any intervention will happen against the backdrop of longstanding inequities in access to services. In addition to geographic targeting, it is crucial to target individuals who have low access to services regardless of their location. 

## 
{{< include figures_code/fig_radar_demogroup.qmd >}}






# Recommendations



# About MPX NYC

## 
The MPX NYC Study ...

##
{{< include figures_code/fig_bar_age.qmd >}}

##
{{< include figures_code/fig_bar_gender.qmd >}}

##
{{< include figures_code/fig_bar_sexorientation.qmd >}}

##
{{< include figures_code/fig_bar_race.qmd >}}

##
{{< include figures_code/fig_bar_channel.qmd >}}













