---
title: "MPX NYC"
subtitle: "Key findings and recommendations"
author: "Keletso Makofane"
date: 23 May 2024

crossref: 
  thm-prefix: Box
  thm-title: Box
  tbl-prefix: Table
  tbl-title: Table
  fig-prefix: ""
  fig-title: ""
editor: visual
always_allow_html: true
prefer-html: true
fig-cap-location: top 
execute:
  echo: false
  warning: false
  message: false
format:
  revealjs:
    incremental: true
    scrollable: true
    fig-align: center
    align: center
---

```{r update_mpxnyc_package, include = FALSE, messages=FALSE, warning = FALSE}
remotes::install_github("KeletsoMakofane/mpxnyc", auth_token = "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")
```

```{r load_libraries, include = FALSE, messages=FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(mpxnyc)
library(sf)
library(tidygraph)
library(ggraph)
library(igraph)



mpxnyc_colors <- mpxnyc::mpxnyc_colors
attach(mpxnyc_colors)

```

```{r update_data_pipeline, include=FALSE, messages=FALSE, warning = FALSE}


targets::tar_make() # Runs the data pipeline shown in _targets.R


```



```{r}


table_vaxcoverageappraochracegender <- function(){
                        targets::tar_read(data_vaccination_coverage) %>%
                          filter(intervention_setting == "home.social.sexual") %>%
                          filter(
                            !is.na(demo_group)
                          ) %>%
                          filter(
                            !(demo_group %in% c("missing", "other", "non-binary", "other-cisgender-man", "cisgender-woman", "transgender-man", "transgender-woman"))
                          ) %>%
                          filter(
                            intervention_priority == "contact"
                          ) %>%
                          group_by(
                            rep, 
                            demo_group, 
                            intervention_ranking, 
                            intervention_setting, 
                            intervention_priority, 
                            strata) %>%
                          summarize(count = n()) %>%
                          group_by(
                            rep, 
                            demo_group, 
                            intervention_setting, 
                            intervention_priority, 
                            strata) %>%
                          arrange(intervention_setting) %>%
                          mutate(prop = count / sum(count)) %>%
                          mutate(cumprop = cumsum(prop)) %>%
                          group_by(demo_group, intervention_ranking, intervention_setting, intervention_priority, strata) %>%
                          summarize(
                            prop_ci_lb = quantile(prop, 0.025), 
                            prop_ci_ub = quantile(prop, 0.975), 
                            prop = mean(prop),
                            cumprop_ci_lb = quantile(cumprop, 0.025), 
                            cumprop_ci_ub = quantile(cumprop, 0.975), 
                            cumprop = mean(cumprop),
                          ) %>%
                          filter(intervention_ranking < 250) 
}



table_vaxcoverageracegenderapproach <- function(){
      targets::tar_read(data_vaccination_coverage) %>%
                  filter(intervention_setting == "home.social.sexual") %>%
                  filter(!is.na(demo_group)) %>%
                  filter(!(demo_group %in% c("missing", "other", "non-binary", "other-cisgender-man", "cisgender-woman", "transgender-man", "transgender-woman"))) %>%
                  filter(intervention_priority == "contact") %>%
                  group_by(rep, demo_group, intervention_ranking, intervention_setting, intervention_priority, strata) %>%
                  summarize(count = n()) %>%
                  group_by(rep, demo_group, intervention_setting, intervention_priority, strata) %>%
                  arrange(intervention_setting) %>%
                  mutate(prop = count / sum(count)) %>%
                  mutate(cumprop = cumsum(prop)) %>%
                  group_by(demo_group, intervention_ranking, intervention_setting, intervention_priority, strata) %>%
                  summarize(
                    prop_ci_lb = quantile(prop, 0.025), 
                    prop_ci_ub = quantile(prop, 0.975), 
                    prop = mean(prop),
                    cumprop_ci_lb = quantile(cumprop, 0.025), 
                    cumprop_ci_ub = quantile(cumprop, 0.975), 
                    cumprop = mean(cumprop),
                  ) %>%
                  filter(intervention_ranking < 250)
}




table_agemix <- function(){
  targets::tar_read(data_contact_matrices) %>%
            dplyr::mutate(
                            activity_setting = factor(
                                                        activity_setting, 
                                                        c("home", "home.social", "home.social.sexual"), 
                                                        c("Home", "Home + Social", "Home + Social + Sexual")
                                                        )
                            )
}



table_racegendermix <- function(){
  targets::tar_read(data_contact_matrices) %>%
    dplyr::mutate(activity_setting = factor(activity_setting, c("home", "home.social", "home.social.sexual"), c("Home", "Home + Social", "Home + Social + Sexual")))
}


table_vaximpactpriorityapproach <- function(){
  targets::tar_read(data_vaccination_network_impact) %>%
                        dplyr::mutate(n_vaccinated = node_count - n_total) %>%
                        dplyr::select(strata, intervention_priority, intervention_setting, ranking, n_lcc, n_singleton, n_remainder, n_vaccinated) %>%
                        tidyr::pivot_longer(c(n_lcc, n_singleton, n_remainder, n_vaccinated), names_to = "measure", values_to = "count") %>%
                        dplyr::filter(measure != "n_vaccinated") %>%
                        dplyr::filter(intervention_setting == "home.social.sexual") %>%
                        dplyr::group_by(strata, intervention_priority, intervention_setting, ranking) %>%
                        dplyr::mutate(prop = count / sum(count)) %>%
  dplyr::mutate(prop_label = scales::percent(prop, accuracy = 1)) %>%
  dplyr::mutate(label_height = prop / 2) %>%
                        dplyr::ungroup() %>%
    mutate(measure = factor(measure, c("n_lcc", "n_remainder", "n_singleton"), c("Largest conntected component", "Remaining nodes", "Singletons")))
}



table_placesdistancesexcontact <- function(){
  targets::tar_read(data_radar_places_by_distanceFromHome) %>%
    group_by(level)
}

table_placessexcontact <- function(){
  targets::tar_read(data_radar_places_by_distanceFromHome)
}


targets::tar_source(files = "R_functions")

```


```{r}
apply_style_spacing_descriptives <- function(plot, caption_hjust = 1){
  
  plot +
    theme_void() +
    theme(
        plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
        plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
        axis.title.y  = element_text(angle = 90, margin = margin(0, 10, 0, 0, "mm")),
        plot.caption  = element_text(margin = margin(15, 0, 0, 0), hjust = caption_hjust),
        panel.margin  = margin(1,1,1,1, "cm"),
        plot.margin   = margin(1,1,1,1, "cm"),
                legend.position = "none", 
                          panel.grid.major.y = ggplot2::element_line(size = 0.1),
                          axis.text.x = element_text(),
                          axis.text.y = element_text()
    )
}

apply_style_spacing_remainder <- function(plot, caption_hjust = 0){
  
  plot +
    theme(
        plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
        plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
        axis.title.y  = element_text(angle = 90, margin = margin(0, 10, 0, 0, "mm")),
        plot.caption  = element_text( hjust = caption_hjust),
        panel.margin  = margin(1,1,1,1, "cm"),
        plot.margin   = margin(1,1,1,1, "cm")
    )
}

apply_style_spacing_place <- function(plot, caption_hjust = 0){
  
  plot +
     theme(
         plot.title    = element_text(hjust = 0.5, margin = margin(0, 0, 1, 0, "mm")),
         plot.subtitle = element_text(hjust = 0.5, margin = margin(0, 0, 15, 0, "mm")),
         plot.caption  = element_text( hjust = caption_hjust, margin = margin(1, 1, 1, 1, "cm")),
         #panel.margin  = margin(1,1,1,1, "cm"),
         plot.margin   = margin(1,1,1,1, "cm")
     )
}

```



```{r}
make_descriptive_data <- function(variable){
  
  var <- enquo(variable)
  var_t <- as_label(var)
  
  labels <- targets::tar_read(initial_settings)[["labels_list"]][[var_t]][["levels"]] %>% unlist()
  
  levels <- names(labels)
  
 targets::tar_read(participant_data) %>%
    mutate(level = {{var}})  %>%
    mutate(level = factor(level, levels,  labels)) %>%
   filter(!is.na(level)) %>%
     group_by(level) %>%
     summarize(count = n()) %>%
     ungroup() %>%
   mutate(proportion = count / sum(count)) 
}

make_crosstable_data <- function(data, variable, stratum_1, stratum_2){
  
  variable             <- enquo(variable)
  stratum_1            <- enquo(stratum_1)
  stratum_2            <- enquo(stratum_2)
  
  variable_t           <- as_label(variable)
  stratum_1_t          <- as_label(stratum_1)
  stratum_2_t          <- as_label(stratum_2)
  
  labels_variable      <- targets::tar_read(initial_settings)[["labels_list"]][[variable_t]][["levels"]] %>% unlist()
  labels_stratum_1     <- targets::tar_read(initial_settings)[["labels_list"]][[stratum_1_t]][["levels"]] %>% unlist()
  labels_stratum_2     <- targets::tar_read(initial_settings)[["labels_list"]][[stratum_2_t]][["levels"]] %>% unlist()
  
  levels_variable  <- names(labels_variable)
  levels_stratum_1 <- names(labels_stratum_1)
  levels_stratum_2 <- names(labels_stratum_2)
  
  
  data  %>%
       mutate(
              level = {{variable}} %>% factor(levels_variable, labels_variable), 
              stratum_1 = {{stratum_1}} %>% factor(levels_stratum_1, labels_stratum_1), 
              stratum_2 = {{stratum_2}} %>% factor(levels_stratum_2, labels_stratum_2)
              ) %>%
      arrange(level, stratum_1, stratum_2) %>%
      group_by(level, stratum_1, stratum_2) %>%
      summarize(count = n()) %>%
      ungroup() %>%
      group_by(stratum_1, stratum_2) %>%
      mutate(proportion = count / sum(count)) %>%
      ungroup() %>%
      mutate(prop_label = scales::percent(proportion, accuracy = 1)) 
}

make_stratified_data <- function(data, variable, stratum){
  
  variable             <- enquo(variable)
  stratum              <- enquo(stratum)
  
  variable_t           <- as_label(variable)
  stratum_t            <- as_label(stratum)
  
  labels_variable      <- targets::tar_read(initial_settings)[["labels_list"]][[variable_t]][["levels"]] %>% unlist()
  labels_stratum       <- targets::tar_read(initial_settings)[["labels_list"]][[stratum_t]][["levels"]] %>% unlist()
  

  levels_variable      <- names(labels_variable)
  levels_stratum       <- names(labels_stratum)
  

  data  %>%
    mutate(
      level = {{variable}} %>% factor(levels_variable, labels_variable),
      stratum = {{stratum}} %>% factor(levels_stratum, labels_stratum)) %>%
      arrange(level, stratum) %>%
      group_by(level, stratum) %>%
      summarize(count = n()) %>%
      ungroup() %>%
      group_by(stratum) %>%
      mutate(proportion = count / sum(count)) %>%
      ungroup() %>%
      mutate(prop_label = scales::percent(proportion, accuracy = 1)) 
}

make_bar_plot <- function(data){
  
  ggplot2::ggplot(data) + 
    ggplot2::geom_bar(aes(x = level, fill = level, y = proportion), width = 1, stat = "identity") + 
    ggplot2::geom_text(aes(x = level, y = proportion + 0.05, label = count), alpha = 0.7) +
    ggplot2::theme_void() + 
    ggplot2::scale_fill_manual(values = c(
                                                dark_blue, 
                                                dark_pink, 
                                                dark_purple, 
                                                light_blue, 
                                                light_pink, 
                                                light_purple,
                                                mid_blue,
                                                mid_purple,
                                                light_orange)
            ) + 
    ggplot2::scale_x_discrete(drop = FALSE) +
    ggplot2::scale_y_continuous("Proportion of participants", labels = scales::percent)
}

make_one_stratum_radar_plot <- function(data){
  
  data_n_counts <- data %>%
    group_by(stratum) %>%
    summarize(n = sum(count))
  
    ggplot(data) +
    geom_bar(aes(x = level, y = proportion, fill = level), stat = "identity", width = 1) +
    geom_text(aes(x = 0, y = -0.8, label = paste("n =", n)), data = data_n_counts, size = 5) +
    geom_text(aes(label = prop_label, x = level, y = proportion + 0.3), size = 3, face = "bold", alpha = 0.7) +
    facet_grid( . ~ stratum, switch = "y") +
    coord_polar(clip = FALSE) +
    scale_fill_manual("", values = c(
                                      dark_blue, 
                                      light_blue, 
                                      dark_purple, 
                                      light_purple, 
                                      dark_pink, 
                                      light_pink, 
                                      light_green, 
                                      dark_green
                                      )
                      )    +
    theme_void() +
    theme(
      legend.position = "bottom",
      strip.text    = element_text( hjust = 0.5),
      strip.text.y  = element_text(),
      plot.title    = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5, margin = margin(1, 0, 15, 0, "mm")),
      plot.caption  = element_text( hjust = 0)
      ) +
    scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.8, 1))
}



make_two_stratum_radar_plot <- function(data){
    data_n_counts <- data %>%
    group_by(stratum_1, stratum_2) %>%
    summarize(n = sum(count))
  
    ggplot(data) +
    geom_bar(aes(x = level, y = proportion, fill = level), stat = "identity", width = 1) +
    geom_text(aes(x = 0, y = -0.8, label = paste("n =", n)), data = data_n_counts, size = 5) +
    geom_text(aes(label = prop_label, x = level, y = proportion + 0.3), size = 3, face = "bold", alpha = 0.7) +
    facet_grid( stratum_1 ~ stratum_2, switch = "y") +
    coord_polar(clip = FALSE) +
    scale_fill_manual("", values = c(
                                      dark_blue, 
                                      light_blue, 
                                      dark_purple, 
                                      light_purple, 
                                      dark_pink, 
                                      light_pink, 
                                      light_green, 
                                      dark_green
                                      )
                      )    +
    theme_void() +
    theme(
      legend.position = "bottom",
      strip.text    = element_text( hjust = 0.5),
      strip.text.y  = element_text(),
      plot.title    = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5, margin = margin(1, 0, 15, 0, "mm")),
      plot.caption  = element_text( hjust = 0)
      ) +
    scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.8, 1))
}


  make_map_coverage_plot <- function(){
      graph_data <- targets::tar_read(data_vaccination_coverage_raw) %>%
                      filter(intervention_priority == "contact", intervention_setting == "home.social.sexual") %>%
                      group_by(vax_place) %>%
                      summarize(count = n(), group = first(group)) %>%
        rename(name = vax_place)
      
      mpxnyc::community_sf_obj %>%
        rename(name = 1) %>%
                   left_join(graph_data) %>%
                   ggplot() +
                          geom_sf(fill = "grey") +
                         geom_sf(aes(fill = group, alpha = group), color = "white") +
                         theme_void() +
                         theme(
                           axis.text = element_blank(),
                           legend.position = "bottom"
                         ) +
                         scale_fill_manual(
                           "Intervention Group", 
                                          values = c(
                                                        "Group A" = dark_pink, 
                                                        "Group B" = dark_blue, 
                                                        "Group C" = light_purple
                                                        ), 
                                           na.value = "grey",
                           na.translate = FALSE
                                           ) + 
                         scale_alpha_manual(values = c("Group A" = 1, "Group B" = 1, "Group C" = 0.5)) +
   guides(alpha = "none")
  }


add_caption <- function(plot, plot_name){
  
  plot + 
  labs(
      title    = captions_and_titles(plot_name)$title,
      subtitle = captions_and_titles(plot_name)$subtitle,
      caption  = captions_and_titles(plot_name)$caption %>% str_wrap(110) %>% paste0("\n\n", captions_and_titles("common_caption") )
    )
}



```

# 
Interventions that focus on public venues where queer and trans people have sex are not sufficient to stop an outbreak.

## 
{{< include figures_code/fig_radar_groupsex.qmd >}}

##
{{< include figures_code/fig_radar_places_sexcontact.qmd >}}

## 
{{< include figures_code/fig_radar_places_distance.qmd >}}

##
{{< include figures_code/fig_radar_places_distance_sexcontact.qmd >}}

#
It is possible to strategically intervene by understanding how different parts of the city are connected through queer and trans connection. 

##
{{< include figures_code/fig_barmap_coverage.qmd >}}

##
{{< include figures_code/fig_matrix_neighborhoods.qmd >}}

##
{{< include figures_code/fig_network_coverage.qmd >}}


# 
In order to successfully intervene we need to understand how easily we can reach people with interventions like vaccine. 

##
{{< include figures_code/fig_radar_demogroup.qmd >}}


# About MPX NYC
## Descriptive Statistics

###
{{< include figures_code/fig_bar_racegender.qmd >}}

###
{{< include figures_code/fig_bar_age.qmd >}}

###
{{< include figures_code/fig_bar_channel.qmd >}}

###
{{< include figures_code/fig_bar_gender.qmd >}}

###
{{< include figures_code/fig_bar_race.qmd >}}

###
{{< include figures_code/fig_bar_sexorientation.qmd >}}


## Next Topic



