
```{r}
targets::tar_source("R_functions")
```

### Person-place graph

The MPX NYC spatial participant data network is a network object that contains all collected data. In this network, nodes comprise of community districts and survey participants. Edges can only exist between a person and a communtiy district - they indicate that the person either lives in or has a contact place in that community district. In @fig-example-participant-place, participant nodes are blue and community district nodes are pink. @tbl-example-bipartite-nodes-edges (a) shows the node and @tbl-example-bipartite-nodes-edges (b) the edges of the network.


```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place
#| fig-width: 9
#| fig-height: 7


make_example_network_data("bipartite") |>
  plot_example_network(targets::tar_read(config_list)) +
  ggplot2::coord_cartesian(xlim=c(-2,3), ylim=c(-1.2,1.2)) +
  theme_mpxnyc() +
  ggplot2::theme(
    plot.margin = ggplot2::margin(0,0,0,0)
  )



```



```{r}
#| label: tbl-example-bipartite-nodes-edges
#| layout-ncol: 2
#| tbl-cap: "Sample person-place network data"
#| tbl-subcap:
#|  - "Nodes"
#|  - "Edges"



make_example_network_data() |>
  data.frame() |>
  dplyr::transmute(name =label, age, type = ifelse(type, "Person", "Community District")) |>
  gt::gt()


make_example_network_data() |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(From = from_name, To = to_name, Relation = relation) |>
  gt::gt()
```


