
```{r}
targets::tar_source("R_functions")
```

### Person-place graph

Conceptually, the MPX NYC spatial participant data network is a network object that contains all collected data. In this network, nodes comprise of community districts and survey participants. Edges can only exist between a person and a communtiy district - they indicate that the person either lives in or has a contact place in that community district. In @fig-data, participant nodes are blue and community district nodes are pink. @tbl-example-bipartite-nodes shows the node and @tbl-example-bipartite-edges the edges of the network.


```{r}
#| fig-cap: !expr 'get_figure_details("fig-example-participant")'
#| label: fig-example-participant-place
#| fig-width: 9
#| fig-height: 5


make_example_network_data("bipartite") |>
  plot_example_network(targets::tar_read(config_list)) +
  theme_mpxnyc()



```



```{r}
#| label: tbl-example-bipartite-nodes-edges
#| layout-ncol: 2
#| tbl-cap:
#|  - "Person-place nodes"
#|  - "Person-place edges"



make_example_network_data() |>
  data.frame() |>
  dplyr::transmute(name = label, age, type = ifelse(type, "person", "community_district")) |>
  gt::gt()


make_example_network_data() |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(from = from_name, to = to_name, relation = relation) |>
  gt::gt()
```


