
```{r}
targets::tar_source("R_functions")
```

### Place graph

The MPX NYC community district network has community districts as nodes. A pair of community districts is connected by a weighted edge when at least one participant has a contact venue or residence in both community districts. The weight is the count of participants which are shared by the two community districts. @fig-example-community shows the community district network derived from the MPX NYC spatial participant data network shown in @fig-example-participant-place. @tbl-example-place-nodes (a) shows list the nodes of the former network, and @tbl-example-place-nodes (b) shows the edges.

```{r}
#| fig-cap: Sample place network visualization
#| label: fig-example-community
#| fig-width: 9
#| fig-height: 7

make_example_network_data("places") |>
  plot_example_network(targets::tar_read(config_list))  +
  theme_mpxnyc_blank()

```


```{r}
#| tbl-cap: Sample place network data
#| label: tbl-example-place-nodes
#| layout-ncol: 2
#| tbl-subcap:
#|  - "Nodes"
#|  - "Edges"


make_example_network_data("places") |>
  data.frame() |>
  dplyr::transmute(Name = label, Type = ifelse(type, "Person", "Community District")) |>
  gt::gt()

make_example_network_data("places") |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(From = from_name, To = to_name, Weight = weight) |>
  gt::gt()


```






