
```{r}
targets::tar_source("R_functions")
```

### Place graph

The MPX NYC community district network has community districts as nodes. A pair of community districts is connected by a weighted edge when at least one participant has a contact venue or residence in both community districts. The weight is the count of participants which are shared by the two community districts. @fig-data-places shows the community district network derived from the MPX NYC spatial participant data network shown in @fig-data. @tbl-example-place-nodes shows list the nodes of the former network, and @tbl-example-place-edges shows the edges.

```{r}
#| fig-cap: !expr 'get_figure_details("fig-example-community")'
#| label: fig-example-community
#| fig-width: 9
#| fig-height: 7

make_example_network_data("places") |>
  plot_example_network(targets::tar_read(config_list))  +
  theme_mpxnyc()

```


```{r}
#| label: tbl-example-place-nodes
#| layout-ncol: 2
#| tbl-cap:
#|  - "Place nodes"
#|  - "Place edges"


make_example_network_data("places") |>
  data.frame() |>
  dplyr::transmute(name = label, type = ifelse(type, "person", "community_district")) |>
  gt::gt()

make_example_network_data("places") |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(from = from_name, to = to_name, weight) |>
  gt::gt()


```






