
```{r}
targets::tar_source("R_functions")
```


#### Observed data

@fig-homogenous-dag and @eq-homogenous-dag show the resulting non-parametric structural equation model for our data, if we analyse it under network causal inference. Because of the assumption of identical distributions, we can represent the model using three equations rather than 9. We retain the person subscript on the random variables in @eq-homogenous-dag and we keep all 9 nodes in the DAG on @fig-homogenous-dag and add six additional nodes to represent network exposure values with respect to $\mathbf{A}$ and $\mathbf{L}$. 

We draw the DAG like this to clarify that though our model is for one person, it represents a part of a system that relates all the people in the sample with each other. Our original purpose, after all, was to infer something about causality in the context of a given population.

```{r}
#| fig-height: 8
#| fig-width: 7
#| fig-align: center
#| label: fig-homogenous-dag
#| fig-cap: "Causal DAG with homogenous structure"


make_dag("homogenous_interference")            |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()




```

We can re-write the structural equation model like this:

$$
\begin{aligned}
L_i &= f_{L}( U_{L_i} ) \\
A_i &= f_{A}( U_{A_i}, L_i, g_{A}(\textbf{L}_{N_i}) ) \\
Y_i &= f_{Y}( U_{Y_i},  L_i,  g_{Y}(\textbf{L}_{N_i}),   A_i,  h_{Y}( \textbf{A}_{N_i} ) ) \\
\end{aligned}
$$ {#eq-homogenous-dag}



