
```{r}
targets::tar_source("R_functions")
```


#### Observed data
The homogeneity and indepdndence assumptions allow us to re-write the structural equation model dropping the person subscript from the equations. The model simplifies into one for three measures each taken on one person, rather than a model for 9 measures taken on 3 people. Since the measures on each person are identically distributed, this model can be used three times to separately generate the measures for *Person 1*, *Person 2*, and *Person 3*. By contrast, the original model produced measures for all three people at one go.

@fig-independence-dag and @eq-independence-dag show the resulting non-parametric structural equation model for our data, if we analyse it under classic causal inference. As a consequence of the assumptions stated in @sec-assumptions-classic, we can represent the model using three equations rather than 9. We retain the person subscript on the random variables in @fig-independence-dag and we keep all 9 nodes in the DAG on @eq-independence-dag. This is to remind us that though our model is for one person, our purpose was always to infer something about the sample of three people.

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-independence-dag
#| fig-cap: "Causal DAG with no interference or spillover"

make_dag("independence") |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light") + theme_mpxnyc_blank()


```


$$
\begin{aligned}
L_i &= f_{L}( U_{L_i}) \\
A_i &= f_{A}( U_{A_i}, L_i) \\
Y_i &= f_{Y}( U_{Y_i}, L_i, A_i) \\
\end{aligned}
$$ {#eq-independence-dag}


