
```{r}
targets::tar_source("R_functions")
```


#### Counterfactual data

We define a counterfactual outcomes $Y_1^{(a_1)}$, $Y_2^{(a_2)}$, and $Y_3^{(a_3)}$, which represent the level of job opportunities, *Persons 1*, *2*, and *3*, would have if we set their dress to level $a_1$, $a_2$, and $a_3$, respectively. Then the model for counterfactual variables is given by @eq-independence-swig. 

It is represented using the Single World Intervention Graph (SWIG) pictured in @fig-independence-swig. A SWIG represents a structural equation model where some of the equations are superseded by the value assigned by the experimenter. For so-called "treatment variables", the diagram separates the value of the variable as it would have been observed with no intervention ($A_i$) from the value that as it will be used in subsequent equations ($a_i$) as a result of the experimenter's intervention. 

Note that because of the assumption of no interference and no spillover, each counterfactual outcome is a function only of the treatment value of the same individual. 

```{r}
#| fig-height: 8
#| fig-width: 7
#| label: fig-independence-swig
#| fig-cap: "SWIG with no interference or spillover"
make_swig("independence")      |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()

```

$$
\begin{aligned}
L_i &= f_{L}( U_{L_i}                       ) \\
A_i &= f_{A}( U_{A_i}, L_i) \\
Y_i^{(a_i)} &= f_{Y}(U_{Y_i} , L_i, a_i) \\
\end{aligned}
$$ {#eq-independence-swig}


