
```{r}
targets::tar_source("R_functions")
```

## Outbreak control intervention {#sec-control-intervention}

We used data from the MPX NYC study to assess the effectiveness of two approaches to conducting mass vaccination campaigns quickly. MPX NYC is an online survey of about $1300$ individuals that was conducted in 2022 in New York City. Study participants were asked to indicate their home on a map, and were asked to indicate places they had had social contact in a congregate setting. Spatial coordinates were converted into community district identifiers. Community districts spatially partition the city of New York.

### Application: Outbreak control model using MPX NYC data {.unnumbered}

Under the SSNAC framework, our intervention of interest might not be about setting the value of any particular variable, but setting a policy or a process that produces a set of variables in the causal model. This would be done by changing the structural equations which produce those variables. In the SWING shown in @fig-edge-intervention-swing and @eq-edge-intervention-swing, we show an intervention which replaces the function for the risk rating for each community ($\mathbf{R}$) with the function $h$. Every variable that is downstream of the first variable created using $h$ is marked with a superscript $(h)$ to show that it is partially determined by that function.

We can now ask what the impact of taking policy $h$ would be on the decision whether or not to vaccinate a neighborhood $j$ at time $s$ ($T_{js}$). We can also ask what the impact of the policy is on the the exposure of participant $i$ to the campaign message at time $s$ ($M_{is}$). 

Our interest in the MPX NYC project, however, was initially to provide evidence to inform a targeted vaccination campaign, so the main outcomes of interest are the vaccination status of each individual $i$ at time $s$ ($V^{(h)}_{is}$). We were interested in contrasting two approaches to assigning risk-ratings to community district: the contact-neutralizing approach, and the movement-neutralizing approach. 

Whereas the contact-neutralizing approach ranks community districts by how many individuals are connected to them, the movement-neutralizing approach ranks community districts by how centrally they are connected to other community districts through the mutual connection with certain individuals. 

### Assumptions

We make the simplifying assumption that only one neighborhood is vaccinated at a time - the top-ranked one. We make the further simplifying assumptions that every person associated with a community district (either through residence or social activity) receives the campaign message when a community district is vaccinated, and that every person who receives a campaign message gets vaccinated. Once an individual is vaccinated, they remain vaccinated. 


### Model

According to the model specified by structural equations [-@eq-edge-intervention-swing], no individual $i$ has been vaccinated at time 0, and nobody receives the campaign message. The risk rating for community district $j$ at time $s$ is some function $h$ of the vaccination status at time $s-1$ for each individual who is connected to that community district. An intervention is conducted in community district $j$ as time $s$ if that community district has the highest risk rating. Each individual $i$ is said to have received the campaign message at time $s$ if the intervention was conducted in any of the community districts he is connected to. Finally, we consider individual $i$ vaccinated at time $s$ if they were vaccinated at time $s-1$ or if they received the campaign message in time $s$. The risk rating is given by the function $h$. 



```{r}
#| label: fig-edge-intervention-swing
#| fig-cap: "SWING for Week 1-3 for MPX NYC Application of SSNAC framework"
list_nodes <- list()
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M0", label = r"($M_{0}$)", x = -1, y = 6, node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V0", label = r"($V_{0}$)"      , x = 1 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R1", label = r"($R_{1}^{(h)}$)"      , x = 2 , y = 2 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T1", label = r"($T_{1}^{(h)}$)"      , x = 3 , y = 4 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M1", label = r"($M_{1}^{(h)}$)"      , x = 4 , y = 6 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V1", label = r"($V_{1}^{(h)}$)"      , x = 5 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R2", label = r"($R_{2}^{(h)}$)" , x = 6 , y = 2 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T2", label = r"($T_{2}^{(h)}$)"      , x = 7 , y = 4 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M2", label = r"($M_{2}^{(h)}$)"      , x = 8 , y = 6 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V2", label = r"($V_{2}^{(h)}$)"      , x = 9 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R3", label = r"($R_{3}^{(h)}$)" , x = 10 , y = 2, node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T3", label = r"($T_{3}^{(h)}$)"      , x = 11 , y = 4, node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M3", label = r"($M_{3}^{(h)}$)"      , x = 12 , y = 6, node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V3", label = r"($V_{3}^{(h)}$)"      , x = 13 , y = 8, node_type = "Individual", node_shape = "covariate")

list_edges <- list()
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M0", to = "M1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "R1", edge_label = r"($h$)")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "M1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R1", to = "T1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T1", to = "M1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "V1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R2", to = "T2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T2", to = "M2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "V2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R3", to = "T3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T3", to = "M3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M3", to = "V3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "R2", edge_label = r"($h$)")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "R3", edge_label = r"($h$)")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "M2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "M3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "M2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "M3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "V1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "V2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "V3", edge_label = r"()")


structural_nodes <- list_nodes |> dplyr::bind_rows() |> dplyr::mutate(label = latex2exp::TeX(label, output = "character", bold = TRUE))
structural_edges <- list_edges |> dplyr::bind_rows() 


tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_swig(node_radius = 0.5, nudge_intervention_labels = 0.2) +
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_large()



```



$$
\begin{aligned}
M_{0i} &=  0 \\
V_{0i} &=  0 \\
R_{sj}^{(h)} &=  h(\mathbf{V}_{s-1}) \\
T_{sj}^{(h)} &=  \begin{cases} 1 & R_{sj}^{(h)} = max_k R_{sk}^{(h)} \\ 0 & \text{otherwise} \end{cases} \\
M_{si}^{(h)} &=  \begin{cases} 1 & \mathbf{T}_{s\mathscr{N}_i}^{(h)} \neq \mathbf{0}  \\ 0 & \text{otherwise} \end{cases} \\
V_{si}^{(h)} &=  \begin{cases} 1 & M_{si}^{(h)} = 1 \text{ or } V_{s-1,i}^{(h)} = 1\\ 0 & \text{otherwise} \end{cases} \\
\end{aligned}
$$ {#eq-edge-intervention-swing}


Define $\psi(i, j)$ as an adjacency function - an indicator function that equals to $1$ if Person $i$ lives in or visits neighborhood $j$ and $0$ otherwise. Let $\mathscr{N}_P$ be the indices of all person nodes and $\mathscr{N}_N$ be a set of indices for neighborhood nodes. Under the contact-neutralizing approach

$$
h_{sj}(\mathbf{V}_{s-1}) = \sum_{ i \in \mathscr{N}_P} (1 -V_{(s-1), i}) \times \psi(i, j)   
$$

and under the movement-neutralizing approach

$$
h_{sj}(\mathbf{V}_{s-1}) =   \sum_{ i \in \mathscr{N}_P} (1 -V_{(s-1), i}) \times \psi(i, j) \sum_{ k \in \mathscr{N}_N} \psi(i, k) 
$$

### Estimands

##### Spatial efficiency

Intervention coverage for the $s^{th}$ community district to be immunized, is defined

$$
C_s^{(h)} = \frac{1}{|\mathscr{N}_p|}\sum_i V_{si}^{(h)} 
$$

The cumulative intervention coverage after immunizing $s$ community districts is therefore

$$ 
\bar{C_s}^{(h)} = \sum_{v = 1}^s{C_v }^{(h)}
$$

##### Social network impact

Define graph $G^{s}(N, \psi_s)$ such that 

$$
\psi_s(i, j) = \psi(i, j) \times (1 -V_{(s-1), i})
$$

The cumulative social network impact of immunizing $s$ community districts is measured in terms of the size of the largest of the connected components $LCC_{(s)}$ of the $G^{s}(N, \psi_s)$ network as a proportion of the total number of participants.

$$
\frac{LCC_s}{|N_p|}
$$

### Estimation

We simulated the intervention outlined above using MPX NYC data by calculating the $G^{s}(N, \psi_s)$ where $s$ ranges from $1$ to the total number of community districts. We measured the uncertainty of our estimates by re-sampling study participants with replacement.
