
```{r}
targets::tar_source("R_functions")
```

## Outbreak control intervention {#sec-control-intervention}


### Application: Outbreak control model using MPX NYC data {.unnumbered}

Under the SSNAC framework, our intervention of interest might not be about setting the value of any particular variable, but setting a policy or a process that produces some outcome of interest. This woudld be done by changing the structural equation which produces that variable. In the diagram @fig-edge-intervention-swing and the equations @eq-edge-intervention-swing, we show an intervention which replaces the function for the risk rating for each neighborhood ($\mathbf{R}$) with the function $h$. Every variable that is downstream of the first variable created using $h$ is marked with a superscript $(h)$ to show that it is partially determined by that function.

As usual, we can decide whether we want to focus on person or neighborhood-level outcomes as the overall quantity of interest. In addition to the outcome variables we can now ask what the impact of taking policy $h$ would be on the decision whether or not to vaccinate a neighborhood $j$ ($T_j$) as well as the exposure of participant $i$ to campaign messages ($M_i$). Our interest in the MPX NYC project, however, was initially to provide evidence to inform a targeted vaccination campaign, so vaccination $\mathbf{V}^{(h)}$ is the outcome of interest.



### Model

```{r}
#| label: fig-edge-intervention-swing
#| fig-cap: "SWING for Week 1-3 for MPX NYC Application of SSNAC framework"
list_nodes <- list()
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M0", label = r"($M_{0}$)", x = -1, y = 6, node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V0", label = r"($V_{0}$)"      , x = 1 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R1", label = r"($R_{1}^{(h)}$)"      , x = 2 , y = 2 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T1", label = r"($T_{1}^{(h)}$)"      , x = 3 , y = 4 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M1", label = r"($M_{1}^{(h)}$)"      , x = 4 , y = 6 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V1", label = r"($V_{1}^{(h)}$)"      , x = 5 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R2", label = r"($R_{2}^{(h)}$)" , x = 6 , y = 2 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T2", label = r"($T_{2}^{(h)}$)"      , x = 7 , y = 4 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M2", label = r"($M_{2}^{(h)}$)"      , x = 8 , y = 6 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V2", label = r"($V_{2}^{(h)}$)"      , x = 9 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R3", label = r"($R_{3}^{(h)}$)" , x = 10 , y = 2, node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T3", label = r"($T_{3}^{(h)}$)"      , x = 11 , y = 4, node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M3", label = r"($M_{3}^{(h)}$)"      , x = 12 , y = 6, node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V3", label = r"($V_{3}^{(h)}$)"      , x = 13 , y = 8, node_type = "Individual", node_shape = "covariate")

list_edges <- list()
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M0", to = "M1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "R1", edge_label = r"($h$)")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "M1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R1", to = "T1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T1", to = "M1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "V1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R2", to = "T2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T2", to = "M2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "V2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R3", to = "T3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T3", to = "M3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M3", to = "V3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "R2", edge_label = r"($h$)")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "R3", edge_label = r"($h$)")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "M2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "M3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "M2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "M3", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "V1", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "V2", edge_label = r"()")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "V3", edge_label = r"()")


structural_nodes <- list_nodes |> dplyr::bind_rows() |> dplyr::mutate(label = latex2exp::TeX(label, output = "character", bold = TRUE))
structural_edges <- list_edges |> dplyr::bind_rows() 


tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_swig(node_radius = 0.5, nudge_intervention_labels = 0.2) +
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_large()



```



$$
\begin{aligned}
M_{0i} &=  0 \\
V_{0i} &=  0 \\
R_{sj}^{(h)} &=  h(\mathbf{V}_{s-1}) \\
T_{sj}^{(h)} &=  \begin{cases} 1 & R_{sj} = max_k R_{kj} \\ 0 & otherwise \end{cases} \\
M_{si}^{(h)} &=  \begin{cases} 1 & T_{sN_i} \neq \mathbf{0}  \\ 0 & otherwise \end{cases} \\
V_{si}^{(h)} &=  \begin{cases} 1 & M_{si} = 1 \text{ or } V_{s-1,i} = 1\\ 0 & otherwise \end{cases} \\
\end{aligned}
$$ {#eq-edge-intervention-swing}


We define function $h$ as a vector-valued function whose length is equal to the number of community districts. $h(V_{(s-1)})$. We define function $h^1$ as the risk rating function for a contact-neutralizing approach, and $h^1$ as the risk rating function for a movement-neutralizing approach. Whereas the contact-neutralizing approach ranks community districts by how many individuals are connected to them, the movement-neutralizing appraoch ranks community districts by how centrally they are connected to other community districts through the exchange of people. 

Define $\psi(i, j)$ as an adjacency function - an indicator function that equals to $1$ if Person $i$ lives in or visits neighborhood $j$ and $0$ otherwise. Let $\mathscr{N}_P$ be the indicies of all person nodes and $\mathscr{N}_N$ be a set of indicies for neighborhood nodes. 


$$
\begin{aligned}
h_{sj}^1 &=  \sum_{ i \in \mathscr{N}_P} (1 -V_{(s-1), i}) \times \psi(i, j)       \\
h_{sj}^2 &=  \sum_{ i \in \mathscr{N}_P} (1 -V_{(s-1), i}) \times \psi(i, j) \sum_{ k \in \mathscr{N}_N} \psi(i, k) 
\end{aligned}
$$




### Estimands

##### Spatial efficiency

Intervention coverage for the $s^{th}$ community district to be immunized, is defined as:

$$
C_s = \frac{1}{|N_p|}\sum_i V_{si}^{(h)} 
$$

The cumulative intervention coverage after immunizing $s$ community districts, therefore, is:

$$ 
\bar{C_s} = \sum_{v = 1}^s{C_v }
$$

##### Social network impact

Define graph $G^{s}(N, \psi_s)$ such that 

$$
\psi_s(i, j) = \psi(i, j) \times (1 -V_{(s-1), i})
$$

The cumulative social network impact of immunizing $s$ community districts is measured in terms of the size of the largest of the connected components $LCC_{(s)}$ of the $G_{s}(N, \psi_s)$ network as a proportion of the total number of participants.

$$
\frac{LCC_s}{|N_p|}
$$

### Estimation

[Estimation strategy]