

# Study questionnaire {#sec-appendixquestionnaire}    

```{r}
# Access custom defined functions
targets::tar_source("../R_functions") 
```

```{r}


data <- targets::tar_read(config_list)[[1]][["variables"]]

```

```{r}


```



::: {.card }

##### `r data[["age"]][["label"]]`

###### `r data[["age"]][["question"]]`


```{r}
#| fig-height: 3
#| 
make_table_freq1(age) |>
plot_bar() |>
  apply_style_bar_plot()

```
:::







::: {.card }

##### `r data[["anotherQuestion"]][["label"]]`

###### `r data[["anotherQuestion"]][["question"]]`


:::


::: {.card }

##### `r data[["censusTractHome"]][["label"]]`

###### `r data[["censusTractHome"]][["question"]]`


:::



::: {.card }

##### `r data[["channel"]][["label"]]`

###### `r data[["channel"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(channel) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::




::: {.card }

##### `r data[["countFriends"]][["label"]]`

###### `r data[["countFriends"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(countFriendsCut) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["countPhysical"]][["label"]]`

###### `r data[["countPhysical"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(countPhysicalCut) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::

::: {.card }

##### `r data[["countSex"]][["label"]]`

###### `r data[["countSex"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(countSexCut) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::



::: {.card }

##### `r data[["covidTestPositive"]][["label"]]`

###### `r data[["covidTestPositive"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(covidTestPositive) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::



::: {.card }

##### `r data[["createdAt"]][["label"]]`

###### `r data[["createdAt"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(createdAtCut) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::



::: {.card }

##### `r data[["gender"]][["label"]]`

###### `r data[["gender"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(gender) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["genderId"]][["label"]]`

###### `r data[["genderId"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(genderId) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::




::: {.card }

##### `r data[["groupSex"]][["label"]]`

###### `r data[["groupSex"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(groupSex) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::



::: {.card }

##### `r data[["hivPrep"]][["label"]]`

###### `r data[["hivPrep"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(hivPrep) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["hivStatus"]][["label"]]`

###### `r data[["hivStatus"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(hivStatus) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["hivSuppressed"]][["label"]]`

###### `r data[["hivSuppressed"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(hivSuppressed) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::



::: {.card }

##### `r data[["monkeypoxCare"]][["label"]]`

###### `r data[["monkeypoxCare"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(monkeypoxCare) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["monkeypoxTest"]][["label"]]`

###### `r data[["monkeypoxTest"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(monkeypoxTest) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["monkeypoxVaccine"]][["label"]]`

###### `r data[["monkeypoxVaccine"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(monkeypoxVaccine) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::

::: {.card }

##### `r data[["num_symptoms"]][["label"]]`

###### `r data[["num_symptoms"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(num_symptomsCut) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["placeSex"]][["label"]]`

###### `r data[["placeSex"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(placeSex, person_analysis = FALSE) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::

::: {.card }

##### `r data[["placeType"]][["label"]]`

###### `r data[["placeType"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(placeType, person_analysis = FALSE) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::



::: {.card }

##### `r data[["race"]][["label"]]`

###### `r data[["race"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(race) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::



::: {.card }

##### `r data[["sex"]][["label"]]`

###### `r data[["sex"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(sex) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["sexOrientation"]][["label"]]`

###### `r data[["sexOrientation"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(sexOrientation) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::


::: {.card }

##### `r data[["travelTime"]][["label"]]`

###### `r data[["travelTime"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(travelTimeCut) |>
plot_bar() |>
  apply_style_bar_plot()
```

:::

