---
listing: 
  contents:
    - "hgek.qmd"
  type: default
---

# Study questionnaire {#sec-appendixquestionnaire}

```{r}
# Access custom defined functions
targets::tar_source("../R_functions")
```

```{r}


data <- targets::tar_read(config_list)[[1]][["variables"]]

```





`r cat("::: {.card } \n\n Helloe \n\n Bye \n\n ::: ")`





::: {.card }

##### `r data[["age"]][["label"]]`

###### `r data[["age"]][["question"]]`


```{r}
#| fig-height: 3
#| 
make_table_freq1(age) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::


::: {.card }


##### `r data[["channel"]][["label"]]`

###### `r data[["channel"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(channel) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::



::: {.card }

##### `r data[["countFriends"]][["label"]]`

###### `r data[["countFriends"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(countFriendsCut) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::

::: {.card }


##### `r data[["countPhysical"]][["label"]]`

###### `r data[["countPhysical"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(countPhysicalCut) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::

::: {.card }


##### `r data[["countSex"]][["label"]]`

###### `r data[["countSex"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(countSexCut) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::

::: {.card }


##### `r data[["covidTestPositive"]][["label"]]`

###### `r data[["covidTestPositive"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(covidTestPositive) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::

::: {.card }


##### `r data[["createdAt"]][["label"]]`

###### `r data[["createdAt"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(createdAtCut) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::

::: {.card }


##### `r data[["gender"]][["label"]]`

###### `r data[["gender"]][["question"]]`

```{r}
#| fig-height: 3
#| 
make_table_freq1(gender) |>
plot_bar() |>
  apply_style_bar_plot()
```
:::

















