## Study data



```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place
#| fig-width: 8
#| fig-height: 5


make_example_network_data("bipartite") |>
  plot_example_bipartite_network() +
  scale_color_mpxnyc(name = "Node type", option = "dark") +
  ggplot2::labs(fill = "Node type") +
  ggplot2::scale_size_manual(name = "Node type", values = c(7,10)) +
  theme_mpxnyc_blank(
    plot.margin = ggplot2::margin(0,0,0,0),
    legend.position = "bottom"
    ) 



```


The RESPND-MI/MPX NYC person-place graph is a data graph that contains all collected data. In this graph, there are two types of nodes: community districts and survey participants. Edges can only exist between a participant and a community district - they indicate that the person either lives in or attended a gathering in that community district. @tbl-example-bipartite-nodes-edges (a) shows the node and @tbl-example-bipartite-nodes-edges (b) the edges of the network.


```{r}
#| label: tbl-example-bipartite-nodes-edges
#| layout-ncol: 2
#| tbl-cap: "Sample person-place network data"
#| tbl-subcap:
#|  - "Nodes"
#|  - "Edges"



make_example_network_data() |>
  data.frame() |>
  dplyr::transmute(name =label, age, type ) |>
  gt::gt() |>
  gt::tab_options(table.font.size =12, data_row.padding = gt::px(1))


make_example_network_data() |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(From = from_name, To = to_name, Relation = relation) |>
  gt::gt() |>
  gt::tab_options(table.font.size =12, data_row.padding = gt::px(1))
```



