```{r  include=FALSE}
targets::tar_source("../R_functions")

```

# MPX NYC III: Data {#sec-data}






::: {#leading}
In this appendix, we describe the process of designing and testing a novel survey questionnaire tool we call the MPX NYC person-place mapper. We show the questions participants were presented with in the survey.

:::

::: {#acknowledgements}
[Acknowledgements]{.underline}: The survey instrument was designed by Keletso Makofane and coded by Keletso Makofane (front end) and Imran Ansari (back end). Sudipta Saha found the web service that allowed us to safely collect spatial data. Seema Kara wrote the initial technical specifications for the instrument. neo4j granted a concessionary licence for the graph database system we used for the back end. Pedro Carneiro and Nguyen Tran led the development of survey questions. Cody Nolan and Anton Antón Castellanos Usigli conducted translation from English to Spanish. Robert Pitts helped to design questions on suspected mpox symptoms.

[Lead author]{.underline}: Keletso Makofane, MPH, PhD. [Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).
:::





```{r}
#| fig-width: 3
#| fig-height: 3
#| fig-align: center


plot_icon(icon_name = "taco", color = "light_purple", shape = 16, alpha = 0,  size = 100, image_size = 0.2)

```
## Data graphs

Study data are represented using data graphs as edge and node
characteristics. Individual characteristics such as age, gender, and HIV
status are encoded as node characteristics. In addition, community
district characteristics (e.g. surface area) are included as node
characteristics in the data graph. The edges of a data graph encode
information on the relationship between a given survey participant and
community district.

### Definition



A data graph is defined as an ordered triple with the first entry a set
of node labels $\mathscr{N}$, the second, a set of edges $\mathscr{E}$,
and the third, a function associating each node with node attributes and
each edge with edge attributes.

$$
\mathscr{G}(\mathscr{N}, \mathscr{E}, d(.))
$$

There are two classes of nodes: community districts $\mathscr{N}_C$ and
survey participants $\mathscr{N}_P$. 

$$
\mathscr{N} = \mathscr{N}_P \cup \mathscr{N}_C,\mathscr{N}_P \cap \mathscr{N}_C = \emptyset
$$

#### Structural data

The node data $d(\mathscr{N})$ is a set of vectors of length equal to the number of nodes. For each $t$, the entries of vector $\mathbf{v}_t$ take values contained by the set $S_t$.

$$
d(\mathscr{N}) = \{\mathbf{v}_t \in (S_t)^{|\mathscr{N}|} : t \in [1:K], K \in \mathbf{Z}_+\}
$$

Similarly, the edge data are a collection of vectors of length equal to
the number of edges.

$$
d(\mathscr{E}) = \{\mathbf{v}_t \in (S_t)^{|\mathscr{E}|} : t \in [1:Q], Q \in \mathbf{Z}_+\}
$$




#### Relational data 


An edge encodes a relation between a person and a place. It is possible for one person to have multiple relations with one place. Hence, each edge is associated with an integer-valued index: 

$$
\mathscr{E}=\{(x, a,b) : x \in \mathbf{Z}_+, a \in \mathscr{N}_P, b \in \mathscr{N}_C \text{ and } a \sim b\}
$$

where the $a\sim b$ means "a is connected to b" in the data graph. The elements of this set are ordered triples whose entries are an integer-valued index, the origin node and the terminal node for each edge. The number of edges connecting person $i$ and place $j$ in the person-place graph is given by

$$
\psi(i,j) = |\{(x,i,j) \in \mathscr{E}\} |
$$




{{< include C_3__study_data.qmd >}}
{{< include C_2__person_place_network_mapper.qmd >}}
{{< include C_1__data_collection.qmd >}}


