# Conclusion


## Common causes vs common effects

## Examples: Past studies

[description of notation]

### Agincourt: interdependence beyond categories

```{r}
#| label: fig-ssnac-agincourt-data
#| fig-cap: SSNAC Person-place graph
#| layout-width: 10
#| layout-height: 6

data_snac_example <- function(){
  snacc_nodes <- data.frame(
                      name = paste("node", 1:14, sep = "_"),
                      node_type = c(rep("Person", 10), rep("Household", 4)),
                      household_income = c(rep(NA, 10), 1000, 4500,3000,2000)
                      )

snacc_edges <- data.frame(
                      from = c("node_1", "node_3", "node_4", "node_5", "node_11", "node_11", "node_12", "node_13", "node_11", "node_11", "node_11", "node_12", "node_13", "node_13", "node_13", "node_13", "node_14", "node_14", "node_11", "node_13"),
                      to   = c("node_2", "node_6", "node_7", "node_8", "node_12", "node_13", "node_14", "node_14", "node_1", "node_3", "node_4", "node_2", "node_6", "node_7", "node_8", "node_9", "node_5", "node_10", "node_5", "node_5"),
                      edge_type = c(rep("Mother", 2), rep("Father", 2), rep("Neighbor", 4), rep("Resident", 10), rep("Employee", 2))
                    ) 


tidygraph::tbl_graph(nodes = snacc_nodes, edges = snacc_edges)
}

plot_ssnac_example <- function(){


example_snacc_graph <- data_snac_example() |>
  tidygraph::activate(edges) |>
  tidygraph::filter(edge_type %in% c("Resident", "Mother", "Father"))

coords <- data.frame(
  x = c(1, 1, 2, 2.5, 2.5, 3, 3.5, 3.5, 4, 4, 2, 2, 3, 3),
  y = c(2, 1, 3, 2.5, 1.5, 3, 2.5, 1.5, 2, 1, 2, 1, 2, 1)
)

ggraph::ggraph(example_snacc_graph, coords) +
  ggraph::geom_edge_link2(ggplot2::aes(edge_linetype = edge_type, edge_width = edge_type, edge_color = edge_type)) +
  ggraph::geom_node_circle(ggplot2::aes(r = 0.1, color = node_type, filter = node_type == "Person"), fill = "white") + 
  ggraph::geom_node_circle(ggplot2::aes(r = 0.2, color = node_type, filter = node_type == "Household", fill = household_income), size = 0.5)
}


style_ssnac_example <- function(plot){
  
  mpxnyc_colors <- targets::tar_read(config_list)[[1]][["content"]][["colors"]]
  
  edge_width_key    <- c("Mother" = 0.3, "Father" = 0.3,  "Resident" = 1.5)
  edge_linetype_key <- c("Mother" = 1, "Father" = 2,  "Resident" = 1)
  node_color_key    <- c("Person" = "grey", "Household" = "black")
  edge_color_key    <- c("Mother" = "#000000", "Father" = "#000000",  "Resident" = mpxnyc_colors$light_orange)

plot +
    ggplot2::theme_void() +
    ggplot2::coord_fixed() +
    ggraph::scale_edge_width_manual("Edge type", values = edge_width_key) +
    ggraph::scale_edge_linetype_manual("Edge type", values = edge_linetype_key ) +
    ggplot2::scale_color_manual("Node type", values = node_color_key) +
    ggraph::scale_edge_color_manual("Edge type", values =edge_color_key ) +
  ggplot2::scale_fill_gradient2("Household income", high = mpxnyc_colors$dark_orange, low = "white") +
    ggplot2::theme(
      legend.margin = ggplot2::margin(15, 15, 15, 15),
    ) + 
  ggplot2::xlim(0.5, 4.5)

}


plot_ssnac_example() |>
  style_ssnac_example()




```

```{r}
#| label: fig-ssnac-agincourt-projection
#| fig-cap: SSNAC Person-place graph
#| layout-width: 10
#| layout-height: 6

data_snac_example <- function(){
  snacc_nodes <- data.frame(
                      name = paste("node", 11:14, sep = "_"),
                      node_type = c( rep("Place", 4)),
                      household_income = c( 1000, 4500,3000,2000)
                      )

snacc_edges <- data.frame(
                      from = c("node_11", "node_11", "node_13"),
                      to   = c("node_12", "node_13", "node_14"),
                      weight = c(1, 2, 1),
                      edge_type = c(rep("Family", 3))
                    ) 


tidygraph::tbl_graph(nodes = snacc_nodes, edges = snacc_edges)
}

plot_ssnac_example <- function(){


example_snacc_graph <- data_snac_example() |>
  tidygraph::activate(edges) 

coords <- data.frame(
  x = c( 2, 2, 3, 3),
  y = c( 2, 1, 2, 1)
)

ggraph::ggraph(example_snacc_graph, coords) +
  ggraph::geom_edge_link2(ggplot2::aes( edge_width = weight), color = "darkgrey") +
  ggraph::geom_node_circle(ggplot2::aes(r = 0.2, filter = node_type == "Place", fill = household_income), color = "black", size = 0.5)
}


style_ssnac_example <- function(plot){
  
  mpxnyc_colors <- targets::tar_read(config_list)[[1]][["content"]][["colors"]]
  

  node_color_key    <- c("Person" = "grey", "Household" = "black")

plot +
    ggplot2::theme_void() +
    ggplot2::coord_fixed() +
    #ggraph::scale_edge_width_manual("Edge type", values = edge_width_key) +
  ggplot2::scale_fill_gradient2("Household income", high = mpxnyc_colors$dark_orange, low = "white") +
    ggplot2::theme(
      legend.margin = ggplot2::margin(15, 15, 15, 15),
    ) + 
  ggplot2::xlim(0.5, 4.5)

}


plot_ssnac_example() |>
  style_ssnac_example()




```

### AHRI: spillover in the face of random allocation

```{r}
#| label: fig-ssnac-ahri
#| fig-cap: SSNAC Person-place graph

data_snac_example <- function(){
  snacc_nodes <- data.frame(
                      name = paste("node", 1:14, sep = "_"),
                      node_type = c(rep("Person", 10), rep("Place", 4))
                      )

snacc_edges <- data.frame(
                      from = c("node_1", "node_3", "node_4", "node_5", "node_11", "node_11", "node_12", "node_13", "node_11", "node_11", "node_11", "node_12", "node_13", "node_13", "node_13", "node_13", "node_14", "node_14", "node_11", "node_13"),
                      to   = c("node_2", "node_6", "node_7", "node_8", "node_12", "node_13", "node_14", "node_14", "node_1", "node_3", "node_4", "node_2", "node_6", "node_7", "node_8", "node_9", "node_5", "node_10", "node_5", "node_5"),
                      edge_type = c(rep("Friend", 4), rep("Neighbor", 4), rep("Resident", 10), rep("Employee", 2))
                    ) 


tidygraph::tbl_graph(nodes = snacc_nodes, edges = snacc_edges)
}

plot_ssnac_example <- function(){


example_snacc_graph <- data_snac_example()

coords <- data.frame(
  x = c(1, 1, 2, 2.5, 2.5, 3, 3.5, 3.5, 4, 4, 2, 2, 3, 3),
  y = c(2, 1, 3, 2.5, 1.5, 3, 2.5, 1.5, 2, 1, 2, 1, 2, 1)
)

ggraph::ggraph(example_snacc_graph, coords) +
  ggraph::geom_edge_link2(ggplot2::aes(edge_linetype = edge_type, edge_width = edge_type, edge_color = edge_type)) +
  ggraph::geom_node_circle(ggplot2::aes(r = 0.1, color = node_type, filter = node_type == "Person"), fill = "white") + 
  ggraph::geom_node_circle(ggplot2::aes(r = 0.1, color = node_type, filter = node_type == "Place"), fill = "grey")
}


style_ssnac_example <- function(plot){
  
  mpxnyc_colors <- targets::tar_read(config_list)[[1]][["content"]][["colors"]]
  
  edge_width_key    <- c("Employee" = 0.3, "Friend" = 0.3, "Neighbor" = 1.2, "Resident" = 1.5)
  edge_linetype_key <- c("Employee" = 1, "Friend" = 2, "Neighbor" = 2, "Resident" = 1)
  node_color_key    <- c("Person" = mpxnyc_colors$dark_pink, "Place" = "black")
  edge_color_key    <- c("Employee" = "#000000", "Friend" = "#000000", "Neighbor" = "#000000", "Resident" = mpxnyc_colors$mid_blue)

plot +
    ggplot2::theme_void() +
    ggplot2::coord_fixed() +
    ggraph::scale_edge_width_manual("Edge type", values = edge_width_key) +
    ggraph::scale_edge_linetype_manual("Edge type", values = edge_linetype_key ) +
    ggplot2::scale_color_manual("Node type", values = node_color_key) +
    ggraph::scale_edge_color_manual("Edge type", values =edge_color_key ) +
    ggplot2::theme(
      legend.margin = ggplot2::margin(15, 15, 15, 15),
    )

}


plot_ssnac_example() |>
  style_ssnac_example()




```

### MPX NYC: racism as a policy setting

```{r}
#| label: fig-ssnac-mpxnyc
#| fig-cap: SSNAC Person-place graph

data_snac_example <- function(){
  snacc_nodes <- data.frame(
                      name = paste("node", 1:14, sep = "_"),
                      node_type = c(rep("Person", 10), rep("Place", 4))
                      )

snacc_edges <- data.frame(
                      from = c("node_1", "node_3", "node_4", "node_5", "node_11", "node_11", "node_12", "node_13", "node_11", "node_11", "node_11", "node_12", "node_13", "node_13", "node_13", "node_13", "node_14", "node_14", "node_11", "node_13"),
                      to   = c("node_2", "node_6", "node_7", "node_8", "node_12", "node_13", "node_14", "node_14", "node_1", "node_3", "node_4", "node_2", "node_6", "node_7", "node_8", "node_9", "node_5", "node_10", "node_5", "node_5"),
                      edge_type = c(rep("Friend", 4), rep("Neighbor", 4), rep("Resident", 10), rep("Employee", 2))
                    ) 


tidygraph::tbl_graph(nodes = snacc_nodes, edges = snacc_edges)
}

plot_ssnac_example <- function(){


example_snacc_graph <- data_snac_example()

coords <- data.frame(
  x = c(1, 1, 2, 2.5, 2.5, 3, 3.5, 3.5, 4, 4, 2, 2, 3, 3),
  y = c(2, 1, 3, 2.5, 1.5, 3, 2.5, 1.5, 2, 1, 2, 1, 2, 1)
)

ggraph::ggraph(example_snacc_graph, coords) +
  ggraph::geom_edge_link2(ggplot2::aes(edge_linetype = edge_type, edge_width = edge_type, edge_color = edge_type)) +
  ggraph::geom_node_circle(ggplot2::aes(r = 0.1, color = node_type, filter = node_type == "Person"), fill = "white") + 
  ggraph::geom_node_circle(ggplot2::aes(r = 0.1, color = node_type, filter = node_type == "Place"), fill = "grey")
}


style_ssnac_example <- function(plot){
  
  mpxnyc_colors <- targets::tar_read(config_list)[[1]][["content"]][["colors"]]
  
  edge_width_key    <- c("Employee" = 0.3, "Friend" = 0.3, "Neighbor" = 1.2, "Resident" = 1.5)
  edge_linetype_key <- c("Employee" = 1, "Friend" = 2, "Neighbor" = 2, "Resident" = 1)
  node_color_key    <- c("Person" = mpxnyc_colors$dark_pink, "Place" = "black")
  edge_color_key    <- c("Employee" = "#000000", "Friend" = "#000000", "Neighbor" = "#000000", "Resident" = mpxnyc_colors$mid_blue)

plot +
    ggplot2::theme_void() +
    ggplot2::coord_fixed() +
    ggraph::scale_edge_width_manual("Edge type", values = edge_width_key) +
    ggraph::scale_edge_linetype_manual("Edge type", values = edge_linetype_key ) +
    ggplot2::scale_color_manual("Node type", values = node_color_key) +
    ggraph::scale_edge_color_manual("Edge type", values =edge_color_key ) +
    ggplot2::theme(
      legend.margin = ggplot2::margin(15, 15, 15, 15),
    )

}


plot_ssnac_example() |>
  style_ssnac_example()




```



## Homo epidemiologica

A longstanding division among epidemiologists is about how we should regard causal inference models in light of their assumptions.

I divide the field into two groups: both believe that social causes such as racism are incompatible with the identifiability assumptions of the causal inference model.  Where they seem to disagree is what to do about that fact. The first camp, which I term social epidemiooogists believe that social forces are too important an explanation of the distribution and determinants of health states in the population. They hold that quantitative causal inference practice, to the extent that precludes the investigation of social causes, is not fit for purpose. They ask for a pluralistic practice of quantitative causal inference. 

On the other hand are epidemiologists who belive that the only contribution epidemiologists can make to scholarship is must be through the causal inference models which have grown hegemonic. To the extent that quantitative epidemiologic research uses these causal inference models, it creates more confusion than clarity. This is because the results of these analyses are not interpretable except under the identification assumptions, which include the assumption of SUTVA or consistency.

Social epidemiologist are hamstrung by their readiness to cede the domain of developing causal infgerence models that suit their epistemic goals to anti-social epidemiologists, focusing on critique, if they engage the theory at all. Anti-social epidemiologists, on the other hand, are trapped both by their confusion about the necessarily social determination of the outcomes they study, secondary to their unwillingness to read social epidemiologists carefully. (i.e. to not mistake their confusion for intractability)

The result of this intransigence is the casting of a mathematical convenience (the assumption that people do not influence each other) as an edict handed down from on high (that if people influence each other in a given setting, that setting is not analysable through causal inference methods). 

To put a fine point on the analytical decision: either we decide that individuals are independent of each other, risking that they are interdependent in a way that affects our estimates; or we decide that invidisuals are not independent of each other, risking the misspecification of the function which links individuals outcomes with one another. 

In this section we take the latter decision and illustrate using published studies based on publicly available datasets. 


(note in our analysis observational units are independent but analytical units are not). 



## Towards a statistically principled, gay, liberatory, feminist, socialist, networked, causal inferential epidemiology




