
```{r}
targets::tar_source("R_functions")
```


## The data are a network

The central data structure in a SSNAC is the person-place graph. @fig-ssnac depicts the rightmost frame of @fig-context by showing spatial units as nodes in a network, connecting adjacent spatial units with a network edge, and connecting individuals with the households they belong to. To show the flexibility of this data object, we added an additional type of relationship an individual can have with a household - that of an employee.

The majority of study data are stored as node or edge attributes. For instance, person nodes might have attributes like age and race whereas place nodes could have attributes like density or surface area. An edge linking a person to a place might have an attribute conveying how the person relates to the place. For instance in @fig-ssnac, some edges indicate residence, some indicate next


```{r}
#| label: fig-ssnac
#| fig-cap: SSNAC Person-place graph


plot_ssnac_example() |>
  style_ssnac_example() +
  theme_mpxnyc_blank()


```


