---
bibliography: ../__const/bibliography.bib
---

# Introduction {#sec-introduction}

```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```


```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "peach", color = "dark_blue", shape = 3, mpxnyc_colors = targets::tar_read(mpxnyc_colors), mpxnyc_emojis = targets::tar_read(mpxnyc_emojis))

```

Welcome to the MPX NYC Study on the social and sexual connections of LGBTQ New Yorkers. Through this website we report data we collected among LGBTQ New Yorkers in the Fall of 2022 when the first global human mpox oubreak occured. 

When we started, MPOX testing was not at all available. Our goal was to estimate the proportion of community members who experienced mpox-like symptoms. We also wanted to understand the structure of social and sexual networks that connect our community so that we could understand how to most effectively distribute MPOX vaccines. Within 5 months of conceiving the project, we had strated collecting data. We kept the survey open for about 1 month, obtaining about 1300 responses.

The data have proven useful - we started sharing perioding analyses with the New York City Department of Health, guiding their outreach activities. Preliminary analyses were shared at the IAS international conference in XXX, and have through XXX presentations and discussions since then. 

As MPOX shifted from an outbreak to an epidemic, we took time to come up with the best way to make sense of these data and to convey them to different readers. This report is the result of that effort. 

We have prioritized the reproducibiility of our study findings and our study design. Our hope is that alliances of LGBTQ activists and researchers will use these methods to answer the pressing questions of their contexts. The data and code we used to make this report available here [HYPERLINK TO GITHUB]. We have written detailed appendices on the methods we devised to make sense of our data. As resources allow, we will publish the code for the custom-designed tool we developed to safely measure sensitive locations. 

We hope the report will be accessible to most interested readers - we have included videos explaining the main ideas in each section. We have also included a more technical methodological appendix, which explains the mathematics behind the analyses.

The next section gives an overview of what scientists already know about the themes our research report touches on: the relationship between people's social networks and their health, the infectious disease dynamics of a novel outbreak, and the health of LGBTQ people.

