
```{r}
targets::tar_source("R_functions")
```

### Assumptions

#### Independence assumptions

##### No spillover

Under network causal inference, we make the assumption of no spillover - that measurements taken across participants at the same time (e.g. $L_1$, $L_2$, and $L_3$) are independent of each other given all prior measures. 

This is shown in @fig-interference-dag, as the removal of arrows that connected the $L_i$'s, $A_i$'s and $Y_i$'s. In @eq-interference-dag, the $L_i$'s are not functions of each other, the $A_i$'s are not functions of each other, and the $Y_i$'s are not functions of each other. This implies that given all the measurements taken prior to a set of contemporaneous measures, the contemporaneous measures are independent.

(Note that it is not strictly necessary to make the no-spillover restriction to work with network data at all. Makofane [-@makofane2021] makes the assumption that contemporaneous measures arise from a conditional Markov random field. This complicates estimation in a way that is beyond the scope of this study. See @sec-ssnacx.)

##### Network interference

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-dag
#| fig-cap: "Causal DAG with network interference"

make_dag("network_interference")   |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()


```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2) \\
A_3 &= f_{A_3}(U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, A_1, A_2) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, A_1, A_2) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,  A_3) \\
\end{aligned}
$$ {#eq-interference-dag}

Under network causal inference, we make the assumption that interference respects some mapping between individuals - a mapping given by a network or set of networks. See Aronow and Samii [-@aronow2017].

#### Homogeneity assumptions

##### Identical distribution

As in the case of classical causal inference, we assume that the structual equations that produce each individual's observations are identical accross individuals. i.e. we assume:

```{=tex}
\begin{aligned}
f_A = f_{A_1} &= f_{A_2} = f_{A_3} \\
f_L = f_{L_1} &= f_{L_2} = f_{L_3} \\
f_Y = f_{Y_1} &= f_{Y_2} = f_{Y_3} \\

\end{aligned}
```
##### Homogenous interference

*Separability*

We assume that in each structural equation, each covariate contributes to the exposure mapping in two parts: i) the covariate level for the individual and ii) a summary of the covariate level of the ego-network of that individual.

Define $\mathscr{N_i}$ as the indices of all the nodes connected to node $i$. Then $\mathbf{L}_{\mathscr{N}_i}$ is the sub-vector of $\mathbf{L}$ containing the entries corresponding to the indices in $\mathscr{N}_i$. Similarly, we define $A_{\mathscr{N}_i}$ as the sub-vector of $A$ corresponding to the indices in $\mathscr{N}_i$. 

Functions $g_{A_i}$, $g_{Y_i}$, and $h_{Y_i}$ are network exposure mappings with respect to $\mathbf{L}$ and $\mathbf{A}$. These functions summarize covariate values for observational unit $i$t. They map vectors of any length to the real line. The value of a network exposure mapping is termed the network exposure value.  

$$
g: \bigcup_{k = 0}^{\infty}{\mathbb{R}^k}  \rightarrow  \mathbb{R}
$$

where $\mathbb{R}^0$ is defined as a set that has only one element - the empty vector ($\mathbb{R}^0 = \{[]\}$). 

Re-writing the model in terms of the network exposure values with respect to $\mathbf{L}$ and $\mathbf{A}$ simplifies it, but still forces us to write the structural equations for each observation separately. This is because each observation potentially has a set of unique exposure mappings.


$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, g_{A_1}(\mathbf{L}_{\mathscr{N}_1})) \\
A_2 &= f_{A_2}(U_{A_2}, L_2, g_{A_2}(\mathbf{L}_{\mathscr{N}_2})) \\
A_3 &= f_{A_3}(U_{A_3}, L_3, g_{A_3}(\mathbf{L}_{\mathscr{N}_3})) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, A_1, g_{Y_1}(\mathbf{L}_{\mathscr{N}_1}), h_{Y_1}(\mathbf{A}_{\mathscr{N}_1})) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_2, A_2, g_{Y_2}(\mathbf{L}_{\mathscr{N}_2}), h_{Y_2}(\mathbf{A}_{\mathscr{N}_2})) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,A_3,  g_{Y_2}(\mathbf{L}_{\mathscr{N}_3}), h_{Y_2}(\mathbf{A}_{\mathscr{N}_3})) \\
\end{aligned}
$$


*Equivalency*

We assume that exposure mappings $g_A$, $h_y$, and $g_Y$ are identical across individuals.

```{=tex}
\begin{aligned}
g_L = g_{L_1} &= g_{L_2} = g_{L_3} \\
h_A = h_{A_1} &= h_{A_2} = h_{A_3} \\
g_Y = g_{L_1} &= g_{L_2} = g_{L_3} \\
\end{aligned}
```
*Symmetry*

We also assume that the order of the entries does not matter in the input for functions $g_A$, $g_Y$, and $h_Y$. i.e. the functions are invariant under any permutation of the entries in the input vector.

*Boundedness*

Finally, we assume that exposure mappings are bounded above.

$$
g_A, h_Y, g_Y < c \text{ for } c \in \mathbf{Z}
$$
