
```{r}
targets::tar_source("R_functions")
```


#### Counterfactual data

Say we want to understand the impact of a vaccination campaign conducted over three weeks on vaccination status. This would be done by setting $\mathbf{T}_1 = [T_{11}, T_{12}, T_{13}]$ to $\mathbf{t}_1 = [t_{11}, t_{12}, t_{13}]$, $\mathbf{T}_2$ to $\mathbf{t}_2$, and $\mathbf{T}_3$ to $\mathbf{t}_3$ and noting the resulting counterfactual vaccination status at the end of week 1 ($\mathbf{V}_1^{(\mathbf{t}_1)}$), week 2 ($\mathbf{V}_1^{(\mathbf{t}_1, \mathbf{t}_2)}$), and week 3 ($\mathbf{V}_1^{(\mathbf{t}_1, \mathbf{t}_2, \mathbf{t}_3)}$). This counterfactual model is defined @eq-placeintervention-swing as shown in shown in @fig-placeintervention-swing. Define $\bar{\mathbf{t}}$ as "the history of $\bar{\mathbf{t}}$". i.e. at time 1, $\bar{\mathbf{t}} =\mathbf{t}_1$. At time 2,   $\bar{\mathbf{t}} = [\mathbf{t}_1, \mathbf{t}_2]$, etc.

```{r}
#| label: fig-placeintervention-swing
#| fig-cap: "SWING for Week 1-3 Example 3"

list_nodes <- list()
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M0", label = r"($M_{0}$)", x = -1, y = 6, node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V0", label = r"($V_{0}$)"      , x = 1 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R1", label = r"($R_{1}$)"      , x = 2 , y = 2 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T1", label = r"($T_{1}$)"      , x = 3 , y = 4 , node_type = "Community", node_shape = "preintervention")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "t1", label = r"($t_{1}$)"      , x = 3 , y = 4 , node_type = "intervention", node_shape = "intervention")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M1", label = r"($M_{1}^{(t_1)}$)"      , x = 4 , y = 6 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V1", label = r"($V_{1}^{(t_1)}$)"      , x = 5 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R2", label = r"($R_{2}^{(t_1)}$)" , x = 6 , y = 2 , node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T2", label = r"($T_{2}$)"      , x = 7 , y = 4 , node_type = "Community", node_shape = "preintervention")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "t2", label = r"($t_{2}$)"      , x = 7 , y = 4 , node_type = "intervention", node_shape = "intervention")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M2", label = r"($M_{2}^{(t_1, t_2)}$)"      , x = 8 , y = 6 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V2", label = r"($V_{2}^{(t_1, t_2)}$)"      , x = 9 , y = 8 , node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R3", label = r"($R_{3}^{(t_1, t_2)}$)" , x = 10 , y = 2, node_type = "Community", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T3", label = r"($T_{3}$)"      , x = 11 , y = 4, node_type = "Community", node_shape = "preintervention")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "t3", label = r"($t_{3}$)"      , x = 11 , y = 4, node_type = "intervention", node_shape = "intervention")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M3", label = r"($M_{3}^{(t_1, t_2, t_3)}$)"      , x = 12 , y = 6, node_type = "Individual", node_shape = "covariate")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V3", label = r"($V_{3}^{(t_1, t_2, t_3)}$)"      , x = 13 , y = 8, node_type = "Individual", node_shape = "covariate")

list_edges <- list()
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M0", to = "M1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "R1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "M1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R1", to = "T1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "t1", to = "M1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "V1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R2", to = "T2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "t2", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "V2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R3", to = "T3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "t3", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M3", to = "V3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "R2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "R3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "V1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "V2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "V3")


structural_nodes <- list_nodes |> dplyr::bind_rows() |> dplyr::mutate(label = latex2exp::TeX(label, output = "character", bold = TRUE))
structural_edges <- list_edges |> dplyr::bind_rows()


tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_swig(node_radius = 0.5, nudge_intervention_labels = 0.2) +
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_large()



```

$$
\begin{aligned}
M_{0i} &=  f_{M_0}(U_{M_{0i}}) \\
V_{0i} &=  f_{V_0}(U_{V_{0i}}) \\
R_{sj}^{(\bar{\mathbf{t}})} &=  f_{R}(U_{R_{sj}}, \mathbf{V}_{s-1}^{(\bar{\mathbf{t}})}) \\
T_{sj}^{(\bar{\mathbf{t}})} &=  f_{T}(U_{T_{sj}}, R_{s,j}^{(\bar{\mathbf{t}})}) \\
M_{si}^{(\bar{\mathbf{t}})} &=  f_{M} (U_{M_{\{si\}}} , V_{\{s-1,i\}}^{(\bar{\mathbf{t}})}, M_{\{s-1,i\}}^{(\bar{\mathbf{t}})}, \mathbf{t}_{\{s, \mathscr{N}_i\}})\\
V_{si}^{(\bar{\mathbf{t}})} &=  f_{V}(U_{V_{\{si\}}}, M_{\{si\}}^{(\bar{\mathbf{t}})}, V_{\{s-1,i\}}^{(\bar{\mathbf{t}})}) \\
\end{aligned}
$$ {#eq-placeintervention-swing}







