# Community engagement {#sec-community}

```{r include=FALSE}
# Access custom defined functions
targets::tar_source("../R_functions")

```

```{r}
#| fig-cap: !expr 'get_figure_details("fig-options")'
#| label: fig-options
#| fig-width: 9
#| fig-height: 9
#| fig-align: center



plot_image("campaign_graphic")
```




## MPX NYC marketing and communication

To maximize the speed of recruitment, we invested in a bilingual, culturally competent communication campaign in collaboration with a marketing agency. The brief was to create a name and marketing concept that convey scientific rigor, build trust with the community, and stand out in a crowded online marketplace (see @fig-requirements). As a starting point, the RESPND-MI team suggested a campaign that playfully uses emojis that have sexual connotations in queer and trans communities, and that integrates LGBT social media influencers as a communication channel.

```{r }
#| fig-cap: !expr 'get_figure_details("fig-requirements")'
#| label: fig-requirements
#| fig-width: 9
#| fig-height: 9
#| fig-align: center
#| 


plot_image("creative_requirements")
```

Two campaign names and four marketing concepts (see @fig-options) were developed by the marketing agency and presented to a meeting of the RESPND-MI Community Forum. The final concept and name were decided by consensus during that meeting.

Marketing materials were developed based on the concept. Materials included graphics, videos by queer influencers, and a style guide (including colors, icons, and fonts) for all public-facing materials of the MPX NYC study. We organized these materials into a "social media toolkit" and shared them through the study website to enable individuals and organizations to easily share them through their own social media accounts.

```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center



plot_icon(icon_name = "pignose", color = "light_blue", shape = 16, alpha = 0.3)
```
