---
bibliography: ../__const/bibliography.bib
---

# Community engagment {#sec-community}

```{r}
# Access custom defined functions
targets::tar_source("../R_functions")
```

```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center



plot_icon(icon_name = "pignose", color = "light_blue", shape = 16, alpha = 0.3)
```

## RESPND-MI Community Forum and Investigator team {.unnumbered}

At the outset of the project we prioritized rapid consultation with a wide variety of stakeholders with the goals of: validating our understanding of the unfolding health threat; understanding how planned study and communication activities fit in a broader response to mpox; gathering feedback on our plans; and developing an audience for the study results.

Though, much of the initial engagement occurred through one-on-one meetings, the RESPND-MI team host an open meeting on 27 June 2022, inviting city and state government officials, local LGBTQ+ organizations with health or advocacy programs, individual activists, researchers, leaders in the nightlife/entertainment industry of New York, and queer and trans people in general. Participants requested a weekly call to enable collective learning and discussion about the outbreak. We named the call the RESPND-MI LGBTQ+ Community Forum, opened it to the public, and advertised it on our website, social media, and through the press. About 80 individuals participated in the community forum the initial meeting to the final call at the end of August 2022.

The Community Forum became a mechanism for coordinating action across organizations and allowed the development of a local, comprehensive, collective response to mpox. Members of the Community Forum collaborated to develop and share resources such as vaccine locators, took political action through policy briefs, and strengthened the programmatic response by creating health communications materials, etc. [@roth2023].

The Community Forum strongly shaped study plans, including the recruitment campaign, the design of a novel spatial data collection tool, and the development of our study questionnaire. Sustained engagement in this group led to several concrete improvements in research approach: for example, a criticism of the initial communication approach was that it centered cisgender men to the exclusion of transgender women and transgender men. This was not warranted given that there was no information about the impact of mpox on these communities, and given that transgender people and cisgender people are part of the same social and sexual networks which woudl likely be affected by mpox. We responded by inviting the participant who raised that issue to join the study team, and over time attempted to continually improve gender related language and iconography in the project through discussion among investigators.

## MPX NYC marketing and communication {.unnumbered}

To maximize the speed of recruitment, we invested in a bilingual, culturally competent communication campaign in collaboration with a marketing agency. The brief was to create a name and marketing concept that convey scientific rigor, build trust with the community, and stand out in a crowded online marketplace (see @fig-requirements). As a starting point, the RESPND-MI team suggested a campaign that playfully uses emojis that have sexual connotations in queer and trans communities, and that integrates LGBT social media influencers as a communication channel.

```{r}
#| fig-cap: "Requirements for MPX NYC Study"
#| label: fig-requirements
#| fig-width: 9
#| fig-height: 9
#| fig-align: center

targets::tar_read(mpxnyc_images)[["creative_requirements"]] |>
  magick::image_read()
```

Two campaign names and four marketing concepts (see @fig-options) were developed by the marketing agency and presented to a meeting of the RESPND-MI Community Forum. The final concept and name were decided by consensus during that meeting.

Marketing materials were developed based on the concept. Materials included graphics, videos by queer influencers, and a style guide (including colors, icons, and fonts) for all public-facing materials of the MPX NYC study. We organized these materials into a "social media toolkit" and shared them through the study website to enable individuals and organizations to easily share them through their own social media accounts. We used these materials in advertisements placed through Grindr, Twitter, Instagram, and outdoor electronic billboards.

```{r}
#| fig-cap: "Options for visual identity of MPX NYC"
#| label: fig-options
#| fig-width: 9
#| fig-height: 9
#| fig-align: center

targets::tar_read(mpxnyc_images)[["campaign_graphic"]] |>
  magick::image_read()
```
