

# Data collection {#sec-data}

```{r}
# Access custom defined functions
targets::tar_source("../R_functions")

```

```{r fig.cap=get_figure_details("fig-mapinputformat"), label="fig-mapinputformat"}
#| fig-width: 9
#| fig-height: 9
#| fig-align: center

plot_image("app_graphic")


```


## Participants and setting

Data were collected between August and November of 2022. Participants were recruited via paid and donated advertising placed through Grindr, Twitter, Instagram, and outdoor electronic billboards.

Potential participants were included in the study if they consented to participate, were over 18 years of age, identified as transgender, gay, bisexual, or as men who have sex with other men, and were in New York City in the four weeks preceding their participation. Potential participants were excluded if they were younger than 18 years of age or they withdrew consent.

## MPX NYC Person-Place Network Mapper

We designed, tested and implemented a survey tool we call the MPX NYC Person-Place Network Mapper. We named it this because the data collected through the instrument can be naturally organized into a bipartite network with nodes representing people and places, and edges representing relations between people and places. Organizing the data as a network allows the interpretation of network parameters such as node degree or connectedness as descriptors of the system connecting people to each other through the places they traverse within the city. 

We designed the tool to solve practical and ethical issues related to the collection of sensitive spatial data in the context of an annonymous survey. Practically, we were interested in collecting data on locations participants visited and possibly had group sex in, but understood that we would not collect useful data if we collected markers like address or sip code using usual survey methods. In addition, we had hypothesized that a sizable proportion of sexual contact in a group happens in private settings whose addresses and exact locations participants were likely to forget. 

Ethically, we were aimed to collect a data set that would limit the risk of identifying survey participants through the locations and other data disclosed through the survey. Collecting spatial coordinates would increase the risk of accidentally identifying people by, for instance, capturing the exact coordinate of a college dormitory as a participant's residence, or capturing the exact coordinates of a federal government office as a  venue for sexual contact in a group setting. In both these examples, it becomes easier to narrow down the identity of participants using the location and the particiapnts' characteristics as recorded in survey data. 

### MPX NYC Person-Place Network Map 

Though the investigator team doubted that participants would remember addresses or zip codes of places they  visited, we thought that they might remember landmarks, cross-streets, neighborhood names, subway stations names, and other markers New Yorkers use to navigate the city so we used the Google maps interface and API. 

The MPX NYC Person-Place Network Map question displays a map with detailed geographic information including place names, roads, and neighborhood names. It includes a search bar as well as other navigation tools usually found on a google maps display (see @fig-mapinputformat). 

To collect anonymous information on locations, first the participant is prompted to identify places of a certain type by tapping on the map. For instance, the first Network Map question asks participants to identify their primary residence. Once they select one, they are able to move onto the next question.

The Network Map also allows researchers to elicit a collection of locations. For instance, we ask participants to identify all the places they have had physical or sexual contact in a group setting. Each time the participant taps the map, a marker appears where they tapped, and a pop-up window asks questions about the most recently identified location. In our study, participants were asked if they had sexual contact at the location and to select the type of location it is from a closed list of options.  

### Coarsening to census tract

To ensure participant anonymity, the survey tool coarsens spatial data to the census tract level before sending them to the study database. Census tracts are non-overlapping spatial units that partition the United States into areas ranging from $2500$ to $8000$ in population size [@uscensus2022]. This is done through The Federal Communications Commission API [@fcc2022] which receives longitude-latitude coordinates from the survey instrument, and returns census block identifiers, which are transformed to census tract identifiers by truncating the last X digits. [CITATION] It is only after spatial data are transformed that they are transmitted to the study database (backend).

### Development 

The front end of the MPX NYC Person-Place Network Mapper was developed as a single-page web application using the React/NextJS framework [@vercel2024] with visual design based on the MPX NYC style guide. The back end was a custom-built neo4j graph database [@neo4j2024]. Along with the Network Map question format, the instrument allows the use of standard survey question formats (multiple choice, single choice, text field etc.).

### Testing

The MPC NYC Person-Place Network Mapper underwent two rounds of user testing. About 10 people participated each time, returning feedback via an informal feedback questionnaire and via email. 







## Consent and ethical approval

Prospective participants read and responded to a consent statement before being able to take the survey. The study, including marketing materials and software, was reviewed and approved by the T.H. Chan School of Public Health Institutional Review Board (IRB22-0761).

## Translation 

All study materials were professionally translated from English to Spanish. The translation was reviewed by six professionals in health-related fields whose primary language is Spanish.




```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "devil", color = "dark_orange", shape = 16, alpha = 0.1)

```
