---
bibliography: ../__const/bibliography.bib
---

# Data collection {#sec-data}

```{r}
# Access custom defined functions
targets::tar_source("../R_functions")

```

```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "devil", color = "dark_orange", shape = 16, alpha = 0.1)

```

We conducted a brief online cross-sectional survey in English and Spanish that is used to inform a network-based model of a hypothetical place-based intervention. Data were collected in New York City between August and November 2022. Potential participants were included in the study if they consented to participate, were over 18 years of age, identified as transgender, gay, bisexual, or as men who have sex with other men, and were in New York City in the four weeks preceding their participation. Potential participants were excluded if they were younger than 18 years of age or they withdrew consent.

### Person-place question {.unnumbered}

ITs not enough to know home address, but it is hard to do research because we cant ask about places easily. Names are sometimes sensitive or impossible (in the case of residences), Zip codes are difficult to remember and addresses are worse. We designed, tested, and implemented a novel online survey instrument, including a newly designed question format.[^longnote]

To collect anonymous information on sensitive locations (such as sex parties) by prompting the participant to indicate places of a specified type on a representation of the map of New York City. We use the Google maps interface - the location-input question displays a map with detailed geographic information including place names, roads, and neighborhood names, and includes a search bar (see @fig-mapinputformat). In addition to these, it is searchable by location name, approximate address, cross streets, neighborhood name.

```{r}
#| fig-cap: "Map input question format developed for MPX NYC"
#| label: fig-mapinputformat
#| fig-width: 9
#| fig-height: 9
#| fig-align: center

targets::tar_read(mpxnyc_images)[["app_graphic"]] |>
  magick::image_read()
```

The participant enters a location by tapping on the displayed map to place a marker, and answering a set of questions through a pop-up window, which we call place attributes. The spatial and attribute data are saved as part of the participant's survey record. To ensure participant annonymity, the survey tool coarsens spatial data to the census tract level before sending them to the study database. Census tracts are non-overlapping spatial units that partition the United States into areas ranging from $2500$ to $8000$ in population size [@uscensus2022].

We name this question format the "person-place" question. This is because the data collected through this instrument can be naturally organized into a network with nodes representing people and places, and edges representing relations between people and places. (see methods appendix).



### Translation {.unnumbered}

All study materials were professionally translated from English to Spanish. The translation was reviewed by six professionals in health-related fields whose primary language is Spanish.

### Ethical approval {.unnumbered}

The study was reviewed and approved by the T.H. Chan School of Public Health Institutional Review Board (IRB22-0761).


[^longnote]: The front end of the MPX NYC survey instrument was developed as a single-page web application using the React/NextJS framework [@vercel2024] with visual design based on the MPX NYC style guide. The Google Maps API [@google2024] provides the displayed map and returns longitude-latitude coordinates for each marker placed on the map. The Federal Communications Commission API [@fcc2022] receives longitude-latitude coordinates and transforms them into census tract identifiers. The back end was a custom-built neo4j graph database [@neo4j2024]. Along with the location-input question format, the instrument includes standard survey question formats (multiple choice, single choice, text field etc.).
