
# Analysis {#sec-analysis}

```{r  include=FALSE}
targets::tar_source("../R_functions")
```

## Descriptive statistics


We tabulated participant characteristics against group contact, and visualized the distribution of sexual orientation categories across levels of the race-gender variable. We also tabulated event type against sexual contact, and against distance from home.

To understand how participants move across community districts from home to gatherings, we cross-tabulated home community district (the community district of the participants' residence) against gathering community district and visualized the resulting table. To identify community districts that tend to receive more participants from residences in outside community districts, and those which tend to send participants, we subtracted the proportion of residences in each community district from the proportion of gatherings The result of this calculation is shown as a bar graph.

Finally, we calculated the spatial mixing coefficient across groups defined by age, sexual orientation, and race-gender to understand how individuals in subgroups defined by these variables interact in space.


To illustrate how the pattern of interaction among queer and trans people should inform early responses to novel infectious diseases, we examined the impact of a simplified, spatially-targeted intervention to immunize the population represented by the MPX NYC participants against a novel pathogen. We examine the impact of two different intervention strategies on two population outcome measures of interest

## Outbreak control strategies 

In this hypothetical intervention, community districts are ordered by priority and are immunized one at a time, beginning with the highest priority community district. We assume that to immunize a community district is to immunize each individual who had a gathering or residence in that community district. We assume that once a person is immunized, they are unable to acquire or transmit the pathogen, and we assume that everyone can only be immunized once. We assessed two strategies for prioritizing community districts: the contact-neutralizing strategy and the movement-neutralizing strategy.

### Contact neutralizing strategy

In the contact-neutralizing strategy, we rank districts according to the number of gatherings and residences they contain (counting only the residences of participants who reported group contact, and who are not yet immunized). This strategy prioritizes community districts with a high amount of sexual or physical contact for immunization. It attempts to immunize as many people in as few community districts as possible.

### Movement neutralizing strategy
In the movement-neutralizing strategy, we rank community districts by their spatial centrality. This strategy prioritizes community districts with a high level of connection to other community districts for immunization. It attempts to immunize the community districts that are potential hubs for the dissemination of the pathogen across the city early to geographically contain the outbreak.

## Outbreak control outcomes 

For each community district immunized, we updated the MPX NYC participant network by removing nodes that represent immunized individuals. We then calculated the two outcomes each time: spatial efficiency, and spatial network impact.

### Spatial efficiency
Spatial efficiency is defined as the total count of immunized individuals divided by the count of immunized community districts. To illustrate differences in spatial efficiency across intervention strategies, we visualized the number of community districts it would take to immunize 33% of the population, and 66% of the population respectively.

### Spatial network impact
Spatial network impact is defined as the proportion of individuals included in the largest connected component of the MPX NYC participant network. To illustrate differences in spatial network impact across intervention strategies, for each additional community district immunized, we plotted the proportions of individuals who are immunized, unimmunized and in the largest connected component, and unimmunized but outside of the largest connected component, respectively.

## Statistical inference 

```{r}
number_reps <- targets::tar_read(config_list)[[1]][["settings"]][["n_reps_graph"]]

```

We used the bootstrap to estimate confidence intervals, resampling participants `r number_reps` times with replacement.

{{< include fig-plot-icon.qmd >}}
