```{r include=FALSE}
targets::tar_source("../R_functions")
```

##### Spatial catchment

Spatial catchment is a place-node characteristic which measures the mutual influence between spatial untis as a result of relations with shared person nodes. It counts the number of minimal paths that link the focal node with other place nodes in the graph. Note that the number of paths that link two place nodes who are connected through a given person node is the product of the number of relations each place node has with the given person node.


```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-spatial-catchment
#| fig-width: 8
#| fig-height: 5



make_reach_diagram_data(
  focal_node = "Community e", 
  alter_nodes = c("Community a", "Community b", "Community c", "Community d"),
  intermediate_nodes = c("Person 8", "Person 4", "Person 6", "Person 3")
  ) |> 
  plot_reach_diagram(
   intermediate_color = "darkgrey"
  ) +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```

Spatial catchment of place $j$ via subgroup $A$ is defined as the
strength of connection between place node $j$ and other place nodes in
the graph when we consider their shared relations with person nodes in
subgroup $A$. Strength of connection between two places $j$ and $k$ is
defined as the number of relations place nodes $j$ and $k$ have with
common person nodes which belong to subset $A$. The spatial catchment
of place $j$ is defined as $c_{i\rightarrow \mathscr{N}_P} = c_{i}$

$$
c_{j\rightarrow A} = \sum_{i }\sum_{k }{ \Psi(i,j) \Psi(i,k)A_i} \\
$$



