
```{r include=FALSE}
targets::tar_source("../R_functions")
```

## People




### Race and gender {.unnumbered}


```{r table_bar_demogroup}
#| column: margin


prepare_table_1(demo_group) |>
  draw_table_1("Race-Gender")

```

```{r plot_bar_demogroup}
#| fig-height: 5
#| fig-width: 8
#| column: body

make_table_freq1(demo_group) |>  
  dplyr::filter(!is.na(level)) |>
  plot_bar() +
  theme_mpxnyc_bar() +
  ggplot2::scale_y_continuous("MPX NYC sample proportion", labels = scales::percent) +
  scale_fill_mpxnyc(name = "Race / gender") 

```







### Age {.unnumbered}


```{r table_bar_age}
#| column: margin

prepare_table_1(age) |>
  draw_table_1("Age")

```

```{r plot_bar_age}
#| column: body
#| fig-height: 5
#| fig-width: 8

  make_table_freq1(age) |>
          plot_bar() +
  theme_mpxnyc_bar() +
  ggplot2::scale_y_continuous("MPX NYC sample proportion", labels = scales::percent) +
  scale_fill_mpxnyc(name = "Age group")



```







### Recruitment Channel  {.unnumbered}


```{r table_bar_channel}
#| column: margin

prepare_table_1(channel) |>
  draw_table_1("Channel")


```



```{r plot_bar_channel}
#| fig-height: 5
#| fig-width: 8
#| column: body


make_table_freq1(channel) |>
  plot_bar()  +
  theme_mpxnyc_bar() +
  ggplot2::scale_y_continuous("MPX NYC sample proportion", labels = scales::percent) +
  scale_fill_mpxnyc(name = "Recruitment\nchannel")


```











### Gender identity {.unnumbered}

```{r table_bar_gender}
#| column: margin


prepare_table_1(genderId) |>
  draw_table_1("Gender")

 
```


```{r plot_bar_gender}
#| column: body
#| fig-height: 5
#| fig-width: 7

make_table_freq1(genderId) |>  
  plot_bar() +
  theme_mpxnyc_bar() +
  ggplot2::scale_y_continuous("MPX NYC sample proportion", labels = scales::percent) +
  scale_fill_mpxnyc(name = "Gender\nmodality")
 
```










### Race  {.unnumbered}


```{r table_bar_race}
#| column: margin

prepare_table_1(race) |>
  draw_table_1("Race")

  
```


```{r plot_bar_race}
#| fig-height: 5
#| fig-width: 7
#| column: body

make_table_freq1(race) |>
  plot_bar()  +
  theme_mpxnyc_bar() +
  ggplot2::scale_y_continuous("MPX NYC sample proportion", labels = scales::percent) +
  scale_fill_mpxnyc(name = "Race")
  
```










### Sexual Orientation  {.unnumbered}

```{r draw_table_sexorientation}
#| column: margin

prepare_table_1(sexOrientation) |>
  draw_table_1("Sexual Orientation")

```



```{r plot_bar_sexorientation}
#| fig-height: 5
#| fig-width: 7
#| column: body


make_table_freq1(sexOrientation) |>    
  plot_bar() +
  theme_mpxnyc_bar() +
  ggplot2::scale_y_continuous("MPX NYC sample proportion", labels = scales::percent) +
  scale_fill_mpxnyc(name = "Sexual\norientation")


```











### Sexual or physical contact with more than two other people at the same time  {.unnumbered}

```{r table_bar_groupsex}
#| fig-width: 7
#| fig-height: 7
#| column: margin

prepare_table_1(groupSex) |> 
  draw_table_1("Group Sex / Contact past 4 weeks") 


```





```{r plot_bar_groupsex}
#| fig-width: 7
#| fig-height: 5
#| column: body

make_table_freq1(groupSex) |>  
  plot_bar()  +
  theme_mpxnyc_bar() +
  ggplot2::scale_y_continuous("MPX NYC sample proportion", labels = scales::percent) +
  scale_fill_mpxnyc(name = "Group contact")

```





### Sexual orientation by race and gender {.unnumbered}



```{r draw_radar_grid_sexOrientation_demo_group}
#| column: margin

prepare_table_2(sexOrientation, demo_group) |>
  draw_table_2("Sexual Orientation by Race-Gender") 

```

```{r plot_radar_grid_sexOrientation_demo_group}
#| fig-width: 8
#| fig-height: 12
#| column: body



make_table_freq2(sexOrientation, demo_group) |>
  plot_radar_grid()   +
  ggplot2::scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.5, 1)) +
  scale_fill_mpxnyc(name = "") +
  theme_mpxnyc_radar_people() 

```











###  MPOX vaccination status by race and gender  {.unnumbered}




```{r table_radar_grid_monkeypoxVaccine_demo_group}
#| column: margin

prepare_table_2(monkeypoxVaccine, demo_group) |>
  draw_table_2( "Mpox Vax Status by Race-Gender") 


```

```{r plot_radar_grid_monkeypoxVaccine_demo_group}
#| fig-width: 8
#| fig-height: 12
#| column: body

make_table_freq2(monkeypoxVaccine, demo_group) |>
  plot_radar_grid()  +
  ggplot2::scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.5, 1)) +
  scale_fill_mpxnyc(name = "") +
  theme_mpxnyc_radar_people() 


```
 







### HIV and PrEP status by race and gender {.unnumbered}



```{r table_radar_grid_hivPrep_demo_group}
#| fig-width: 10
#| fig-height: 10
#| column: margin

prepare_table_2(hivPrep, demo_group) |>
  draw_table_2("HIV and PrEP Status by Race-Gender") 

```


```{r plot_radar_grid_hivPrep_demo_group}
#| fig-width: 8
#| fig-height: 12
#| column: body

make_table_freq2(hivPrep, demo_group) |>
  plot_radar_grid()  +
  ggplot2::scale_y_continuous(breaks = c(0,0.25, 0.50, 1), limits = c(-0.5, 1)) +
  scale_fill_mpxnyc(name = "") +
  theme_mpxnyc_radar_people() 


```










