
```{r include=FALSE}
targets::tar_source("../R_functions")
```

## People



### Race and gender {.unnumbered}


```{r table_bar_demogroup}
#| column: margin

make_table_freq1(demo_group) |>
  draw_table_1("Race-Gender")
```

```{r plot_bar_demogroup}
#| fig-height: 5
#| fig-width: 8
#| column: body

make_table_freq1(demo_group) |>  
  plot_bar() +
  theme_mpxnyc_bar() +
  scale_axis_mpxnyc() +
  scale_fill_mpxnyc(name = "Race / gender") 
```







### Age {.unnumbered}


```{r table_bar_age}
#| column: margin

make_table_freq1(age) |>
  draw_table_1("Age")
```

```{r plot_bar_age}
#| column: body
#| fig-height: 5
#| fig-width: 8

  make_table_freq1(age) |>
    plot_bar() +
    theme_mpxnyc_bar() +
    scale_axis_mpxnyc() +
    scale_fill_mpxnyc(name = "Age group")
```







### Recruitment Channel  {.unnumbered}


```{r table_bar_channel}
#| column: margin

make_table_freq1(channel) |>
  draw_table_1("Channel")
```



```{r plot_bar_channel}
#| fig-height: 5
#| fig-width: 8
#| column: body

make_table_freq1(channel) |>
  plot_bar()  +
  theme_mpxnyc_bar() +
  scale_axis_mpxnyc() +
  scale_fill_mpxnyc(name = "Recruitment\nchannel")
```











### Gender identity {.unnumbered}

```{r table_bar_gender}
#| column: margin


make_table_freq1(genderId) |>
  draw_table_1("Gender")
```


```{r plot_bar_gender}
#| column: body
#| fig-height: 5
#| fig-width: 7

make_table_freq1(genderId) |>  
  plot_bar() +
  theme_mpxnyc_bar() +
  scale_axis_mpxnyc("MPX NYC sample proportion") +
  scale_fill_mpxnyc(name = "Gender\nmodality")
```










### Race  {.unnumbered}


```{r table_bar_race}
#| column: margin

make_table_freq1(race) |>
  draw_table_1("Race")
```


```{r plot_bar_race}
#| fig-height: 5
#| fig-width: 7
#| column: body

make_table_freq1(race) |>
  plot_bar()  +
  theme_mpxnyc_bar() +
  scale_axis_mpxnyc() +
  scale_fill_mpxnyc(name = "Race")
```










### Sexual Orientation  {.unnumbered}

```{r draw_table_sexorientation}
#| column: margin

make_table_freq1(sexOrientation) |>
  draw_table_1("Sexual Orientation")
```



```{r plot_bar_sexorientation}
#| fig-height: 5
#| fig-width: 7
#| column: body


make_table_freq1(sexOrientation) |>    
  plot_bar() +
  theme_mpxnyc_bar() +
  scale_axis_mpxnyc() +
  scale_fill_mpxnyc(name = "Sexual\norientation")
```











### Sexual or physical contact with more than two other people at the same time  {.unnumbered}

```{r table_bar_groupsex}
#| fig-width: 7
#| fig-height: 7
#| column: margin

make_table_freq1(groupSex) |> 
  draw_table_1("Group Sex / Contact past 4 weeks") 
```





```{r plot_bar_groupsex}
#| fig-width: 7
#| fig-height: 5
#| column: body

make_table_freq1(groupSex) |>  
  plot_bar()  +
  theme_mpxnyc_bar() +
  scale_axis_mpxnyc() +
  scale_fill_mpxnyc(name = "Group contact")
```





### Sexual orientation by race and gender {.unnumbered}



```{r draw_radar_grid_sexOrientation_demo_group}
#| column: margin

make_table_freq2(sexOrientation, demo_group)  |>
  draw_table_2("Sexual Orientation by Race-Gender") 
```

```{r plot_radar_grid_sexOrientation_demo_group}
#| fig-width: 8
#| fig-height: 12
#| column: body

make_table_freq2(sexOrientation, demo_group) |>
  plot_radar_grid()   +
  scale_radial_mpxnyc() +
  scale_fill_mpxnyc(name = "") +
  theme_mpxnyc_radar_people() 
```











###  MPOX vaccination status by race and gender  {.unnumbered}




```{r table_radar_grid_monkeypoxVaccine_demo_group}
#| column: margin

make_table_freq2(monkeypoxVaccine, demo_group) |>
  draw_table_2( "Mpox Vax Status by Race-Gender") 
```

```{r plot_radar_grid_monkeypoxVaccine_demo_group}
#| fig-width: 8
#| fig-height: 12
#| column: body

make_table_freq2(monkeypoxVaccine, demo_group) |>
  plot_radar_grid()  +
  scale_radial_mpxnyc() +
  scale_fill_mpxnyc(name = "") +
  theme_mpxnyc_radar_people() 
```
 







### HIV and PrEP status by race and gender {.unnumbered}



```{r table_radar_grid_hivPrep_demo_group}
#| fig-width: 10
#| fig-height: 10
#| column: margin

make_table_freq2(hivPrep, demo_group) |>
  draw_table_2("HIV and PrEP Status by Race-Gender") 
```


```{r plot_radar_grid_hivPrep_demo_group}
#| fig-width: 8
#| fig-height: 12
#| column: body

make_table_freq2(hivPrep, demo_group) |>
  plot_radar_grid()  +
  scale_radial_mpxnyc() +
  scale_fill_mpxnyc(name = "") +
  theme_mpxnyc_radar_people() 
```










