
```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```

```{r make_swig}
make_swig <- function(graph_type){
  
  
  graph_nodes_list                           <- list() 

  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L1", label = r"($L_1$)"              , x = 1, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L2", label = r"($L_2$)"              , x = 1, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L3", label = r"($L_3$)"              , x = 1, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A1", label = r"($A_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A2", label = r"($A_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A3", label = r"($A_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a1", label = r"($a_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a2", label = r"($a_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a3", label = r"($a_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet1", label = r"($L_{N_1}$)"       , x = 2, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet2", label = r"($L_{N_2}$)"       , x = 2, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet3", label = r"($L_{N_3}$)"       , x = 2, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet1", label = r"($A_{N_1}$)"       , x = 4, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet2", label = r"($A_{N_2} $)"      , x = 4, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet3", label = r"($A_{N_1} $)"      , x = 4, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  
  if (graph_type == "independence"){
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y1", label = r"($Y_1^{(a_1)}$)"   , x = 5, y = 1,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y2", label = r"($Y_2^{(a_2)}$)"   , x = 5, y = 3,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y3", label = r"($Y_3^{(a_3)}$)"        , x = 5, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  }
  
    if (graph_type == "network_interference"){
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y1", label = r"($Y_1^{(a_1, a_2)}$)"   , x = 5, y = 1,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y2", label = r"($Y_2^{(a_1, a_2)}$)"   , x = 5, y = 3,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y3", label = r"($Y_3^{(a_3)}$)"        , x = 5, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  }
  
    
  graph_nodes <- graph_nodes_list |>
                      dplyr::bind_rows() |>
                      dplyr::mutate(node_radius = 0.2) |>
                      dplyr::mutate(label = latex2exp::TeX(label, output = "character")) |>
    dplyr::mutate(node_type = node_shape) |>
    dplyr::mutate(node_type = ifelse(node_shape == "preintervention", "covariate", node_shape))



graph_edges_list <- list()

graph_edges_list[["independence"]] <- data.frame(
                                              from                 = c("L1", "L2", "L3", "L1", "L2", "L3", "a1", "a2", "a3"),
                                              to                   = c("A1", "A2", "A3", "Y1", "Y2", "Y3", "Y1", "Y2", "Y3")
                                            )

graph_edges_list[["network_interference"]] <- data.frame(
                                                        from                 = c("L1", "L2", "L1", "L2", "a1", "a2"),
                                                        to                   = c("A2", "A1", "Y2", "Y1", "Y2", "Y1")
                                                        ) |>
                                                rbind(graph_edges_list[["independence"]] )

graph_edges_list[["full_interference"]] <- data.frame(
                                              from                 = c("L1", "L3", "L1", "L3", "a1", "a3", 
                                                                       "L2", "L3", "L2", "L3", "a2", "a3"),
                                              to                   = c("A3", "A1", "Y3", "Y1", "Y3", "Y1",
                                                                       "A3", "A2", "Y3", "Y2", "Y3", "Y2")) |>
  rbind(graph_edges_list[["network_interference"]] )

graph_edges_list[["fully_connected"]] <- data.frame(
                                              from                 = c("L1", "a1", "Y1"),
                                              to                   = c("L2", "A2", "Y2")
                                              ) |>
  rbind(graph_edges_list[["full_interference"]] )



graph_edges_list[["homogenous_interference"]] <- data.frame(
                                              from                 = c("L1"   , "L2"   , "a1"   , "a2"   , "LNet2", "LNet1", "LNet2", "LNet1", "ANet2", "ANet1"),
                                              to                   = c("LNet2", "LNet1", "ANet2", "ANet1", "A2"   , "A1"   , "Y2"   , "Y1"   , "Y2"   , "Y1"   )) |>
  rbind(graph_edges_list[["independence"]])




graph_edges <- graph_edges_list[[graph_type]]

if (graph_type != "homogenous_interference") {
  graph_nodes <- graph_nodes |>
    dplyr::filter(!homogenous)
}


tidygraph::tbl_graph(nodes = graph_nodes, edges = graph_edges)  
                  
}
```

```{r makedag}
make_dag <- function(graph_type){
  
  
  graph_nodes_list                           <- list() 

  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L1", label = r"($L_1$)"              , x = 1, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L2", label = r"($L_2$)"              , x = 1, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L3", label = r"($L_3$)"              , x = 1, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A1", label = r"($A_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A2", label = r"($A_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A3", label = r"($A_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y1", label = r"($Y_1$)"   , x = 5, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y2", label = r"($Y_2$)"   , x = 5, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y3", label = r"($Y_3$)"        , x = 5, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet1", label = r"($L_{N_1}$)"       , x = 2, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet2", label = r"($L_{N_2}$)"       , x = 2, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet3", label = r"($L_{N_3}$)"       , x = 2, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet1", label = r"($A_{N_1}$)"       , x = 4, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet2", label = r"($A_{N_2} $)"      , x = 4, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet3", label = r"($A_{N_1} $)"      , x = 4, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  
    
  graph_nodes <- graph_nodes_list |>
                      dplyr::bind_rows() |>
                      dplyr::mutate(node_radius = 0.2) |>
                      dplyr::mutate(label = latex2exp::TeX(label, output = "character")) |>
    dplyr::mutate(node_type = node_shape) |>
    dplyr::mutate(node_type = ifelse(node_shape == "preintervention", "covariate", node_shape))



graph_edges_list <- list()

graph_edges_list[["independence"]] <- data.frame(
                                              from                 = c("L1", "L2", "L3", "L1", "L2", "L3", "A1", "A2", "A3"),
                                              to                   = c("A1", "A2", "A3", "Y1", "Y2", "Y3", "Y1", "Y2", "Y3")
                                            )

graph_edges_list[["network_interference"]] <- data.frame(
                                                        from                 = c("L1", "L2", "L1", "L2", "A1", "A2"),
                                                        to                   = c("A2", "A1", "Y2", "Y1", "Y2", "Y1")
                                                        ) |>
                                                rbind(graph_edges_list[["independence"]] )

graph_edges_list[["full_interference"]] <- data.frame(
                                              from                 = c("L1", "L3", "L1", "L3", "A1", "A3", 
                                                                       "L2", "L3", "L2", "L3", "A2", "A3"),
                                              to                   = c("A3", "A1", "Y3", "Y1", "Y3", "Y1",
                                                                       "A3", "A2", "Y3", "Y2", "Y3", "Y2")) |>
  rbind(graph_edges_list[["network_interference"]] )

graph_edges_list[["fully_connected"]] <- data.frame(
                                              from                 = c("L1", "A1", "Y1", "L2", "A2", "Y2"),
                                              to                   = c("L2", "A2", "Y2", "L3", "A3", "Y3")
                                              ) |>
  rbind(graph_edges_list[["full_interference"]] )



graph_edges_list[["homogenous_interference"]] <- data.frame(
                                              from                 = c("L1"   , "L2"   , "A1"   , "A2"   , "LNet2", "LNet1", "LNet2", "LNet1", "ANet2", "ANet1"),
                                              to                   = c("LNet2", "LNet1", "ANet2", "ANet1", "A2"   , "A1"   , "Y2"   , "Y1"   , "Y2"   , "Y1"   )) |>
  rbind(graph_edges_list[["independence"]])




graph_edges <- graph_edges_list[[graph_type]]

if (graph_type != "homogenous_interference") {
  graph_nodes <- graph_nodes |>
    dplyr::filter(!homogenous)
}


tidygraph::tbl_graph(nodes = graph_nodes, edges = graph_edges)  
                  
}
```

```{r plotswig}
plot_swig <- function(data, arrow_length_head = 0.2, arrow_length_tail = 0.05, edge_width = 0.2, node_radius = 0.3, node_margin = 0.4, nudge_intervention_labels = 0.1){
  
  variable_names <- data |>
                            tidygraph::activate(edges) |>
                            data.frame() |>
                            names() 
  
  analysis_data <- data 
  edge_label_exists <-"edge_label" %in% variable_names


  if (!edge_label_exists) {
      analysis_data <- data |>
                      tidygraph::activate(edges) |>
                      tidygraph::mutate(edge_label = "") |>
                      tidygraph::activate(nodes)
  } else {
     analysis_data  <- data
  }

  
  
  node_characteristics <- analysis_data |>
    data.frame() 
  
  ggraph::create_layout(analysis_data, data.frame(analysis_data)) |>
  ggraph::ggraph(analysis_data) +
    ggraph::geom_edge_link(
                        mapping     = ggplot2::aes(
                                          label     = latex2exp::TeX(edge_label, output = "character")
                                          ), 
                        arrow       = grid::arrow(
                                          angle       = 15, 
                                          length      = ggplot2::unit(arrow_length_head, "inches"), 
                                          ends        = "last", 
                                          type        = "closed"
                                          ), 
                        end_cap     = ggraph::circle(node_margin, 'inches'), 
                        start_cap   = ggraph::circle(node_margin, 'inches'),
                        edge_width  = edge_width,
                        label_size  = 8,
                        edge_alpha       = 0.3
                        ) +
    ggforce::geom_arc_bar(
                        mapping     = ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type, start = 0, end = 1*pi, r0 = 0), 
                        data        = node_characteristics |> dplyr::filter(node_shape == "intervention"), 
                        position    = ggplot2::position_nudge(x = 0.25 * nudge_intervention_labels)
                        ) +
    ggforce::geom_arc_bar(
                        mapping     = ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type, start = pi, end = 2*pi, r0 = 0), 
                        data        = node_characteristics |> dplyr::filter(node_shape == "preintervention"), 
                        position    = ggplot2::position_nudge(x = - 0.25 * nudge_intervention_labels)
                        ) +
    ggforce::geom_circle(
                        mapping     = ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type), data = node_characteristics |> dplyr::filter(node_shape == "covariate")
                        ) +
    ggraph::geom_node_text(
                        mapping     = ggplot2::aes(label = label, fill = node_type),
                        color       = "black",
                        size        = 3.5,
                        parse       = TRUE,
                        data        = node_characteristics |> dplyr::filter(node_shape == "preintervention"),
                        nudge_x     = -nudge_intervention_labels
                        ) +
    ggraph::geom_node_text(
                        mapping     = ggplot2::aes(label = label, fill = node_type),
                        color       = "black",
                        size        = 3.5,
                        parse       = TRUE,
                        data        = node_characteristics |> dplyr::filter(node_shape == "intervention"),
                        nudge_x     = nudge_intervention_labels
                        ) +
    ggraph::geom_node_text(
                        mapping     = ggplot2::aes(label = label, fill = node_type),
                        color       = "black",
                        size        = 3.5,
                        parse       = TRUE,
                        data        = node_characteristics |> dplyr::filter(node_shape == "covariate")
                        ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      legend.position = "none",
      plot.margin = ggplot2::margin(20, 20, 20, 20)
    ) +
    ggplot2::coord_fixed()
}

```

#### Running example 1

We are interested in settling an argument about the relationship between dressing in formal wear and job opportunities. One friend thinks that dressing formally clearly brings more job opportunities. Everyone they know who dressed formally she has seen, has many more opportunities than people who dress casually. The other friend thinks that what really brings job opportunities is currently having a job. In their reasoning, having a job causes people to dress formally and causes people to have job opprotunities, but dressing formally does not in itself improve one's opportunities. 

We conduct a study to try and understand this question. We recruit three people, Person 1, Person 2, and Person 3. Person 1 and Person 2 are married to each other. Person 1 and Person 3 are newly acquainted colleagues. Say Person 1 has job status $L_1$, Person 2 has job status $L_2$ and Person 3 has job status $L_3$. Each of these variables can only take on two values: "employed vs. unemployed". Similarly we define $A_i$ as Person i's dress (formal vs. informal), and $Y_i$ as their job opportunities (high vs. low). The job status measurement precedes $L_i$ dress $A_i$ in time, and dress precedes job opportunities $Y_i$. 


```{r}
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-spillover-classic-dag 
#| fig-cap: "Fully connected causal DAG"

make_dag("fully_connected")         |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")

```


$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, A_1) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, A_1, A_2) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1, Y_2) \\
\end{aligned}
$$ {#eq-nospillover-dag}


We can make a model for how each of these people's measures. If we made no assumptions at all about the causal process, except the time-ordering of measurements, we can represent this model using @eq-nospillover-dag. This model is visualized as a causal Directed Acyclic Graph (DAG) in @fig-spillover-classic-dag. Since there are no missing edges between nodes in the DAG, the structural equation model represents any possible joint distribution between the variables in the DAG. This is the most flexible model.

But the most flexible model is not the most useful one. To fully characterize this system, we would need to estimate 9 functions using one observation of the 9-dimensional joint distribution that gave rise to the three participant's observations. Epidemiologists take several approaches to improve the ability to understand the system is to simplify it. 

In the first sub-section below, we show how standard assumptions made in classic causal inference narrow down the set of distributions that can be represented by the model. We do the same thing for assumptions made in network causal inference and in the SSNAC framework.  


