
```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```


### Example 1: Wealth, Dress, and Jobs {.unnumbered}

We are interested in settling an argument among friends about the relationship between dressing in formal wear and job opportunities. One friend thinks that dressing formally clearly brings more job opportunities; everyone she knows who dresses formally has many more opportunities than people who dress casually. The other friend thinks that what really brings job opportunities is currently having a job. In their reasoning, having a job causes people to dress formally and causes people to have job opportunities, but dressing formally does not in itself improve opportunities. We conduct a study to try investigate.

We recruit three people, Person 1, Person 2, and Person 3. Person 1 and Person 2 are married to each other. Person 1 and Person 3 are newly acquainted colleagues. Say Person 1 has job status $L_1$, Person 2 has job status $L_2$ and Person 3 has job status $L_3$. Each of these variables can only take on two values: "employed vs. unemployed". Similarly we define $A_i$ as Person i's dress (formal vs. informal), and $Y_i$ as their job opportunities (high vs. low). The job status measurement precedes $L_i$ dress $A_i$ in time, and dress precedes job opportunities $Y_i$. 

#### Non-parametric structural equation model with independent errors

A non-parametric structural equation model is a system of equations which relates all the entries in a given vector-valued random variable with each other. It does so without specifying parametric functions for each equation in the system. In contrast, for parametric models, for instance, the normal distribution model are characterized using their probability density functions, non-parametric models are characterized according to their conditional independencies. i.e. statements of the form

$$
X_1 \perp X_3 | X_2, X_4
$$
For some joint distribution $F$

$$
\left[
\matrix{
X_1 \\
X_2 \\
X_3 \\
X_4 
}
\right] \sim F
$$

```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-dag
#| fig-cap: "Fully connected causal DAG"

make_dag("fully_connected")         |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()

```


$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, A_1) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, A_1, A_2) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1, Y_2) \\
\end{aligned}
$$ {#eq-fullly-connected-dag}


If we made no assumptions at all about the causal process, except the time-ordering of measurements, we can represent our data using @eq-nospillover-dag. Note that each arrow in the DAG represents an argument in the function that produces the variable the arrow is pointing to. 

A directed acyclic graph (DAG) is a representation of a non-parametric structural equation model. It is a useful representation because it allows us to graphically find the minimum set of conditional independencies that imply all the conditional Independence in the distribution. Conditional independencies are identified by missing arrows in the DAG, using a set of rules called D-separation. 

Since there are no missing edges between nodes in the @fig-fullly-connected-dag, the structural equation model represents any possible joint distribution between the variables in the DAG - there are no conditional independencies. But the most flexible model is not the most useful one. To fully characterize this system using observed data, we would need to estimate 9 functions using one observation of the 9-dimensional joint distribution that gave rise to the participant's observations. It would not help to recruit additional people to the study because each person would add three new equations to the model. 

#### Exposure mappings

Following [ddd] we define an exposure mapping as..... 

Epidemiologists take several approaches to to simplify this system of equations by assuming that there are fewer functions to estimate and more observations per function. In other words, they add restrictions to the model. In the next few sections, we will use the idea of exposure mappings to illustrate the restrictions made under classic causal inference, network causal inference, and SSNAC. In each case, simplifying the system of equations equates to deleting some of the arrows in the DAG shown in @fig-fullly-connected-dag and/or assuming that some of the functions in the system are identical to each other. 


### Assumptions

Under classic causal inference, we assume that observations are independent and identically distributed. We review these assumptions, naming them slightly differently for the purpose of comparing them with the assumptions made in sections to come.  We assume independence, we assume "no spillover" and "no interference". We further classify the "identically distributed" assumption as a homogeneity assumption. 

#### Independence assumptions

##### No spillover

Under classic causal inference, we make the assumption of no spillover - that measurements taken across participants at the same time (e.g. $L_1$, $L_2$, and $L_3$) are independent of each other given all prior measures. i.e.

$$
\begin{align}
L_1 \perp L_2 \\
L_2 \perp L_3 \\
L_1 \perp L_3 
\end{align}
$$
This is shown in @fig-iwpillover-classic-dag, as the removal of arrows that connected the $L_i$'s, $A_i$'s and $Y_i$'s. In  $L_2$ is no longer a function of $L_1$, for instance. In @eq-nointerference-dag, the $L_i$'s are not functions of each other, the $A_i$'s are not functions of each other, and the $Y_i$'s are not functions of each other. This implies that given all the measurements taken prior to a set of contemporaneous measures, the contemporaneous measures are independent.

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-iwpillover-classic-dag
#| fig-cap: "Causal DAG with no spillover"


make_dag("full_interference")      |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(labels = c("h"), option = "light") +
  theme_mpxnyc()


```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3) \\
\end{aligned}
$$ {#eq-nointerference-dag}

##### No interference

Classic causal inference makes the no interference assumption. We assume that measurements made across participants, but not at the same time are independent of each other. This is shown as the absence of arrows that connect $L_i$'s to $A_j$'s, $L_i$'s to $Y_j$'s and $A_i$'s to $Y_j$ for participants $i,j$ with $i \neq j$

This allows us to simplify the structural equation model so that each participants measures are a function of only measures taken on them. 

$$
\begin{aligned}
L_1 &= f_{L_1}( U_{L_1}) \\
L_2 &= f_{L_2}( U_{L_2}) \\
L_3 &= f_{L_3}( U_{L_3}) \\
A_1 &= f_{A_1}( U_{A_1}, L_1) \\
A_2 &= f_{A_2}( U_{A_2}, L_2) \\
A_3 &= f_{A_3}( U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}( U_{Y_1}, L_1, A_1 ) \\
Y_2 &= f_{Y_2}( U_{Y_2}, L_2, A_2 ) \\
Y_3 &= f_{Y_3}( U_{Y_3}, L_3, A_3 ) \\
\end{aligned}
$$ 

#### Homogeneity assumption

##### Identical distribution

Finally, we see above that the functions that generate observations $L_i$ are similar in structure to each other, as are the the functions that generate $A_i$'s and $Y_i$s. We make the homogeneity assumption that the functions are identical to each other. i.e.



```{=tex}
\begin{aligned}
 f_L &= f_{L_1} = f_{L_2} = f_{L_3} \\
 f_A &= f_{A_1} = f_{A_2} = f_{A_3} \\
 f_Y &= f_{Y_1} = f_{Y_2} = f_{Y_3}  \\
\end{aligned}
```
This allows us to re-write the structural equation model dropping the person subscript from the equations. The model simplifies into one for three measures each taken on one person, rather than a model for 9 measures taken on 3 people. Since the measures on each person are identically distributed, this model can be used three times to produce the measures for person 1, person 2, and person 3. The original model produced measures for all three people at one go.


