### Observed data

#### Independence assumptions

##### No spillover

Under classic causal inference, we make the assumption of no spillover - that measurements taken across participants at the same time (e.g. $L_1$, $L_2$, and $L_3$). In @fig-iwpillover-classic-dag, the arrows that connected the $L_i$'s, $A_i$'s and $Y_i$'s, respectively have been removed. Note that this is shown in @eq-fully-connected-dag. $L_2$ is no longer a function of $L_1$, for instance. In general, the $L_i$'s are not functions of each other, the $A_i$'s are not functions of each other, and the $Y_i$'s are not functions of each other. This implies that given all the measurements taken prior to a set of contemporaneous measures, the contemporaneous measures are independent.

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-iwpillover-classic-dag
#| fig-cap: "Causal DAG with no spillover"


make_dag("full_interference")      |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3) \\
\end{aligned}
$$ {#eq-fully-connected-dag}

##### No interference

In addition to the no spillover assumption, classic causal inference makes the no interference assumption. We assume tat measurements made across participants, but not at the same time are independent of each other. This is shown as the absence of arrows that connect $L_i$'s to $A_j$'s, $L_i$'s to $Y_j$'s and $A_i$'s to $Y_j$ for $i \neq j$

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-classic-dag
#| fig-cap: "Causal DAG with no interference or spillover"

make_dag("independence") |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

This allows us to simplify the structural equation model so that each participants measures are a function of only measures taken on them. We make the distinction between spillover and interference because that distinction will be useful in the next section. However, by asserting that "observations are independent of each other", we simultaneously assert no spillover and no intereference.

$$
\begin{aligned}
L_1 &= f_{L_1}( U_{L_1}) \\
L_2 &= f_{L_2}( U_{L_2}) \\
L_3 &= f_{L_3}( U_{L_3}) \\
A_1 &= f_{A_1}( U_{A_1}, L_1) \\
A_2 &= f_{A_2}( U_{A_2}, L_2) \\
A_3 &= f_{A_3}( U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}( U_{Y_1}, L_1, A_1 ) \\
Y_2 &= f_{Y_2}( U_{Y_2}, L_2, A_2 ) \\
Y_3 &= f_{Y_3}( U_{Y_3}, L_3, A_3 ) \\
\end{aligned}
$$ {#eq-nointerference-dag}

#### Homogeneity assumption

##### Identical distribution

Once we restrict the number of possible distributions that our system of equations can represent so that only measures within the individual influences that individual's measures, we see that the functions that generate observations $L_i$ are similar in structure to each other, as are the the functions that generate $A_i$'s and $Y_i$s.

We make the homogeneity assumption that the functions are identical to each other. i.e.

```{=tex}
\begin{aligned}
 f_L &= f_{L_1} = f_{L_2} = f_{L_3} \\
 f_A &= f_{A_1} = f_{A_2} = f_{A_3} \\
 f_Y &= f_{Y_1} = f_{Y_2} = f_{Y_3}  \\
\end{aligned}
```
This allows us to re-write the structural equation model, dropping the person subscript, simplifying the structural equation model for three measures, each taken on three people, into a structural equation model for one person. This is useful because we actually observed three people, yet our model is for one person's measures. Since the measures on each person are identically distributed, this model can be used three times to produce the measures for person 1, person 2, and person 3. The original model produced measures for all three people at one go.

```{=tex}
\begin{aligned}
L_i &= f_{L}( U_{L_i}) \\
A_i &= f_{A}( U_{A_i}, L_i) \\
Y_i &= f_{Y}( U_{Y_i}, L_i, A_i) \\
\end{aligned}
```