## Observed data

See [@aronow2017] for exposure mapping ideas.





```{r make_swig}
make_swig <- function(graph_type){
  
  
  graph_nodes_list                           <- list() 

  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L1", label = r"($L_1$)"              , x = 1, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L2", label = r"($L_2$)"              , x = 1, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L3", label = r"($L_3$)"              , x = 1, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A1", label = r"($A_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A2", label = r"($A_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A3", label = r"($A_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a1", label = r"($a_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a2", label = r"($a_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a3", label = r"($a_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet1", label = r"($L_{N_1}$)"       , x = 2, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet2", label = r"($L_{N_2}$)"       , x = 2, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet3", label = r"($L_{N_3}$)"       , x = 2, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet1", label = r"($A_{N_1}$)"       , x = 4, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet2", label = r"($A_{N_2} $)"      , x = 4, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet3", label = r"($A_{N_1} $)"      , x = 4, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  
  if (graph_type == "independence"){
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y1", label = r"($Y_1^{(a_1)}$)"   , x = 5, y = 1,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y2", label = r"($Y_2^{(a_2)}$)"   , x = 5, y = 3,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y3", label = r"($Y_3^{(a_3)}$)"        , x = 5, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  }
  
    if (graph_type == "network_interference"){
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y1", label = r"($Y_1^{(a_1, a_2)}$)"   , x = 5, y = 1,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y2", label = r"($Y_2^{(a_1, a_2)}$)"   , x = 5, y = 3,   homogenous = FALSE, node_shape = "covariate")))
      graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y3", label = r"($Y_3^{(a_3)}$)"        , x = 5, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  }
  
    
  graph_nodes <- graph_nodes_list |>
                      dplyr::bind_rows() |>
                      dplyr::mutate(node_radius = 0.2) |>
                      dplyr::mutate(label = latex2exp::TeX(label, output = "character")) |>
    dplyr::mutate(node_type = node_shape) |>
    dplyr::mutate(node_type = ifelse(node_shape == "preintervention", "covariate", node_shape))



graph_edges_list <- list()

graph_edges_list[["independence"]] <- data.frame(
                                              from                 = c("L1", "L2", "L3", "L1", "L2", "L3", "a1", "a2", "a3"),
                                              to                   = c("A1", "A2", "A3", "Y1", "Y2", "Y3", "Y1", "Y2", "Y3")
                                            )

graph_edges_list[["network_interference"]] <- data.frame(
                                                        from                 = c("L1", "L2", "L1", "L2", "a1", "a2"),
                                                        to                   = c("A2", "A1", "Y2", "Y1", "Y2", "Y1")
                                                        ) |>
                                                rbind(graph_edges_list[["independence"]] )

graph_edges_list[["full_interference"]] <- data.frame(
                                              from                 = c("L1", "L3", "L1", "L3", "a1", "a3", 
                                                                       "L2", "L3", "L2", "L3", "a2", "a3"),
                                              to                   = c("A3", "A1", "Y3", "Y1", "Y3", "Y1",
                                                                       "A3", "A2", "Y3", "Y2", "Y3", "Y2")) |>
  rbind(graph_edges_list[["network_interference"]] )

graph_edges_list[["fully_connected"]] <- data.frame(
                                              from                 = c("L1", "a1", "Y1"),
                                              to                   = c("L2", "A2", "Y2")
                                              ) |>
  rbind(graph_edges_list[["full_interference"]] )



graph_edges_list[["homogenous_interference"]] <- data.frame(
                                              from                 = c("L1"   , "L2"   , "a1"   , "a2"   , "LNet2", "LNet1", "LNet2", "LNet1", "ANet2", "ANet1"),
                                              to                   = c("LNet2", "LNet1", "ANet2", "ANet1", "A2"   , "A1"   , "Y2"   , "Y1"   , "Y2"   , "Y1"   )) |>
  rbind(graph_edges_list[["independence"]])




graph_edges <- graph_edges_list[[graph_type]]

if (graph_type != "homogenous_interference") {
  graph_nodes <- graph_nodes |>
    dplyr::filter(!homogenous)
}


tidygraph::tbl_graph(nodes = graph_nodes, edges = graph_edges)  
                  
}
```

```{r makedag}
make_dag <- function(graph_type){
  
  
  graph_nodes_list                           <- list() 

  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L1", label = r"($L_1$)"              , x = 1, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L2", label = r"($L_2$)"              , x = 1, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L3", label = r"($L_3$)"              , x = 1, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A1", label = r"($A_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A2", label = r"($A_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A3", label = r"($A_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y1", label = r"($Y_1$)"   , x = 5, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y2", label = r"($Y_2$)"   , x = 5, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y3", label = r"($Y_3$)"        , x = 5, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet1", label = r"($L_{N_1}$)"       , x = 2, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet2", label = r"($L_{N_2}$)"       , x = 2, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet3", label = r"($L_{N_3}$)"       , x = 2, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet1", label = r"($A_{N_1}$)"       , x = 4, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet2", label = r"($A_{N_2} $)"      , x = 4, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet3", label = r"($A_{N_1} $)"      , x = 4, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  
    
  graph_nodes <- graph_nodes_list |>
                      dplyr::bind_rows() |>
                      dplyr::mutate(node_radius = 0.2) |>
                      dplyr::mutate(label = latex2exp::TeX(label, output = "character")) |>
    dplyr::mutate(node_type = node_shape) |>
    dplyr::mutate(node_type = ifelse(node_shape == "preintervention", "covariate", node_shape))



graph_edges_list <- list()

graph_edges_list[["independence"]] <- data.frame(
                                              from                 = c("L1", "L2", "L3", "L1", "L2", "L3", "A1", "A2", "A3"),
                                              to                   = c("A1", "A2", "A3", "Y1", "Y2", "Y3", "Y1", "Y2", "Y3")
                                            )

graph_edges_list[["network_interference"]] <- data.frame(
                                                        from                 = c("L1", "L2", "L1", "L2", "A1", "A2"),
                                                        to                   = c("A2", "A1", "Y2", "Y1", "Y2", "Y1")
                                                        ) |>
                                                rbind(graph_edges_list[["independence"]] )

graph_edges_list[["full_interference"]] <- data.frame(
                                              from                 = c("L1", "L3", "L1", "L3", "A1", "A3", 
                                                                       "L2", "L3", "L2", "L3", "A2", "A3"),
                                              to                   = c("A3", "A1", "Y3", "Y1", "Y3", "Y1",
                                                                       "A3", "A2", "Y3", "Y2", "Y3", "Y2")) |>
  rbind(graph_edges_list[["network_interference"]] )

graph_edges_list[["fully_connected"]] <- data.frame(
                                              from                 = c("L1", "A1", "Y1", "L2", "A2", "Y2"),
                                              to                   = c("L2", "A2", "Y2", "L3", "A3", "Y3")
                                              ) |>
  rbind(graph_edges_list[["full_interference"]] )



graph_edges_list[["homogenous_interference"]] <- data.frame(
                                              from                 = c("L1"   , "L2"   , "A1"   , "A2"   , "LNet2", "LNet1", "LNet2", "LNet1", "ANet2", "ANet1"),
                                              to                   = c("LNet2", "LNet1", "ANet2", "ANet1", "A2"   , "A1"   , "Y2"   , "Y1"   , "Y2"   , "Y1"   )) |>
  rbind(graph_edges_list[["independence"]])




graph_edges <- graph_edges_list[[graph_type]]

if (graph_type != "homogenous_interference") {
  graph_nodes <- graph_nodes |>
    dplyr::filter(!homogenous)
}


tidygraph::tbl_graph(nodes = graph_nodes, edges = graph_edges)  
                  
}
```

```{r plotswig}
plot_swig <- function(data, arrow_length_head = 0.2, arrow_length_tail = 0.05, edge_width = 0.2, node_radius = 0.3, node_margin = 0.4, nudge_intervention_labels = 0.1){
  
  variable_names <- data |>
                            tidygraph::activate(edges) |>
                            data.frame() |>
                            names() 
  
  analysis_data <- data 
  edge_label_exists <-"edge_label" %in% variable_names


  if (!edge_label_exists) {
      analysis_data <- data |>
                      tidygraph::activate(edges) |>
                      tidygraph::mutate(edge_label = "") |>
                      tidygraph::activate(nodes)
  } else {
     analysis_data  <- data
  }

  
  
  node_characteristics <- analysis_data |>
    data.frame() 
  
  ggraph::create_layout(analysis_data, data.frame(analysis_data)) |>
  ggraph::ggraph(analysis_data) +
    ggraph::geom_edge_link(
                        mapping     = ggplot2::aes(
                                          label     = latex2exp::TeX(edge_label, output = "character")
                                          ), 
                        arrow       = grid::arrow(
                                          angle       = 15, 
                                          length      = ggplot2::unit(arrow_length_head, "inches"), 
                                          ends        = "last", 
                                          type        = "closed"
                                          ), 
                        end_cap     = ggraph::circle(node_margin, 'inches'), 
                        start_cap   = ggraph::circle(node_margin, 'inches'),
                        edge_width  = edge_width,
                        label_size  = 8,
                        edge_alpha       = 0.3
                        ) +
    ggforce::geom_arc_bar(
                        mapping     = ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type, start = 0, end = 1*pi, r0 = 0), 
                        data        = node_characteristics |> dplyr::filter(node_shape == "intervention"), 
                        position    = ggplot2::position_nudge(x = 0.25 * nudge_intervention_labels)
                        ) +
    ggforce::geom_arc_bar(
                        mapping     = ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type, start = pi, end = 2*pi, r0 = 0), 
                        data        = node_characteristics |> dplyr::filter(node_shape == "preintervention"), 
                        position    = ggplot2::position_nudge(x = - 0.25 * nudge_intervention_labels)
                        ) +
    ggforce::geom_circle(
                        mapping     = ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type), data = node_characteristics |> dplyr::filter(node_shape == "covariate")
                        ) +
    ggraph::geom_node_text(
                        mapping     = ggplot2::aes(label = label, fill = node_type),
                        color       = "black",
                        size        = 3.5,
                        parse       = TRUE,
                        data        = node_characteristics |> dplyr::filter(node_shape == "preintervention"),
                        nudge_x     = -nudge_intervention_labels
                        ) +
    ggraph::geom_node_text(
                        mapping     = ggplot2::aes(label = label, fill = node_type),
                        color       = "black",
                        size        = 3.5,
                        parse       = TRUE,
                        data        = node_characteristics |> dplyr::filter(node_shape == "intervention"),
                        nudge_x     = nudge_intervention_labels
                        ) +
    ggraph::geom_node_text(
                        mapping     = ggplot2::aes(label = label, fill = node_type),
                        color       = "black",
                        size        = 3.5,
                        parse       = TRUE,
                        data        = node_characteristics |> dplyr::filter(node_shape == "covariate")
                        ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      legend.position = "none",
      plot.margin = ggplot2::margin(20, 20, 20, 20)
    ) +
    ggplot2::coord_fixed()
}

```


#### Running example 1

We are interested in settling an argument about the relationship between dressing in formal wear and job opportunities. One friend thinks that dressing formally clearly brings more job opportunities. Everyone they know who dressed formally she has seen, has many more opportunities than people who dress casually. The other friend thinks that what really brings job opportunities is currently having a job. In their reasoning, having a job causes people to dress formally and causes people to have job opprotunities, but dressing formally does not in itself improve one's opportunities. 

We conduct a study to try and understand this question. We recruit three people, Person 1, Person 2, and Person 3. Person 1 and Person 2 are married to each other. Person 1 and Person 3 are newly acquainted colleagues. Say Person 1 has job status $L_1$, Person 2 has job status $L_2$ and Person 3 has job status $L_3$. Each of these variables can only take on two values: "employed vs. unemployed". Similarly we define $A_i$ as Person i's dress (formal vs. informal), and $Y_i$ as their job opportunities (high vs. low). The job status measurement precedes $L_i$ dress $A_i$ in time, and dress precedes job opportunities $Y_i$. 


```{r}
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-spillover-classic-dag 
#| fig-cap: "Fully connected causal DAG"

make_dag("fully_connected")         |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")

```


$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, A_1) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, A_1, A_2) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1, Y_2) \\
\end{aligned}
$$ {#eq-nospillover-dag}


We can make a model for how each of these people's measures. If we made no assumptions at all about the causal process, except the time-ordering of measurements, we can represent this model using @eq-nospillover-dag. This model is visualized as a causal Directed Acyclic Graph (DAG) in @fig-spillover-classic-dag. Since there are no missing edges between nodes in the DAG, the structural equation model represents any possible joint distribution between the variables in the DAG. This is the most flexible model.

But the most flexible model is not the most useful one. To fully characterize this system, we would need to estimate 9 functions using one observation of the 9-dimensional joint distribution that gave rise to the three participant's observations. Epidemiologists take several approaches to improve the ability to understand the system is to simplify it. 

In the first sub-section below, we show how standard assumptions made in classic causal inference narrow down the set of distributions that can be represented by the model. We do the same thing for assumptions made in network causal inference and in the SSNAC framework.  



### Classic causal inference

#### Independence assumptions

##### No spillover

Under classic causal inference, we make the assumption of no spillover - that measurements taken across participants at the same time (e.g. $L_1$, $L_2$, and $L_3$). In @fig-iwpillover-classic-dag, the arrows that connected the $L_i$'s, $A_i$'s and $Y_i$'s, respectively have been removed. Note that this is shown in @eq-fully-connected-dag. $L_2$ is no longer a function of $L_1$, for instance. In general, the $L_i$'s are not functions of each other, the $A_i$'s are not functions of each other, and the $Y_i$'s are not functions of each other. This implies that given all the measurements taken prior to a set of contemporaneous measures, the contemporaneous measures are independent. 

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-iwpillover-classic-dag
#| fig-cap: "Causal DAG with no spillover"


make_dag("full_interference")      |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3) \\
\end{aligned}
$$  {#eq-fully-connected-dag}

##### No interference

In addition to the no spillover assumption, classic causal inference makes the no interference assumption. We assume tat measurements made across participants, but not at the same time are independent of each other. This is shown as the absence of arrows that connect $L_i$'s to $A_j$'s, $L_i$'s to $Y_j$'s and $A_i$'s to $Y_j$ for $i \neq j$ 

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-classic-dag
#| fig-cap: "Causal DAG with no interference or spillover"

make_dag("independence") |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

This allows us to simplify the structural equation model so that each participants measures are a function of only measures taken on them. We make the distinction between spillover and interference because that distinction will be useful in the next section. However, by asserting that "observations are independent of each other", we simultaneously assert no spillover and no intereference. 

$$
\begin{aligned}
L_1 &= f_{L_1}( U_{L_1}) \\
L_2 &= f_{L_2}( U_{L_2}) \\
L_3 &= f_{L_3}( U_{L_3}) \\
A_1 &= f_{A_1}( U_{A_1}, L_1) \\
A_2 &= f_{A_2}( U_{A_2}, L_2) \\
A_3 &= f_{A_3}( U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}( U_{Y_1}, L_1, A_1 ) \\
Y_2 &= f_{Y_2}( U_{Y_2}, L_2, A_2 ) \\
Y_3 &= f_{Y_3}( U_{Y_3}, L_3, A_3 ) \\
\end{aligned}
$$  {#eq-nointerference-dag}


#### Homogeneity assumption

Once we restrict the number of possible distributions that our system of equations can represent so that only measures within the individual influences that individual's measures, we see that the functions that generate observations $L_i$ are similar in structure to each other, as are the the functions that generate $A_i$'s and $Y_i$s. 

We make the homogeneity assumption that the functions are identical to each other. i.e. 


```{=tex}
\begin{aligned}
 f_L &= f_{L_1} = f_{L_2} = f_{L_3} \\
 f_A &= f_{A_1} = f_{A_2} = f_{A_3} \\
 f_Y &= f_{Y_1} = f_{Y_2} = f_{Y_3}  \\
\end{aligned}
```
This allows us to re-write the structural equation model, dropping the person subscript, simplifying the structural equation model for three measures, each taken on three people, into a structural equation model for one person. This is useful because we actually observed three people, yet our model is for one person's measures. Since the measures on each person are identically distributed, this model can be used three times to produce the measures for person 1, person 2, and person 3. The original model produced measures for all three people at one go.

```{=tex}
\begin{aligned}
L_i &= f_{L}( U_{L_i}) \\
A_i &= f_{A}( U_{A_i}, L_i) \\
Y_i &= f_{Y}( U_{Y_i}, L_i, A_i) \\
\end{aligned}
```
### Network causal inference

#### Independence assumptions

##### No spillover

Just as under classical causal inference, network causal inference as we articulate here, assumes no spillover. See figure [] and equations []. It is not necessary to make this restriction to work with network data. Makofane (2021) makes the assumption that contemporaneous measures are arise from conditional Markov Random Field models. We will elaborate a framework (SSNAC-Extension, or SSNACX) at a later stage. In brief, the difference between this articulation and that will be in estimation. 


##### Network interference

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-dag
#| fig-cap: "Causal DANG with network interference"

make_dag("network_interference")   |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

Conditioning on the meausres on i and the measures on nodes connecgted to i, contemporaneous measures are independent.

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2) \\
A_3 &= f_{A_3}(U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, A_1, A_2) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, A_1, A_2) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,  A_3) \\
\end{aligned}
$$ {#eq-networkinterference}


#### Homogeneity assumptions

##### Identical distribution

```{r}
#| fig-height: 8
#| fig-width: 7
#| fig-align: center
#| label: fig-homogenous-dag
#| fig-cap: "Causal DANG with homogenous structure"


make_dag("homogenous_interference")            |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")



```

The identical distribution assumption asserts that each person's measures (though they are not independent from one another) arise from the same structural equation model. i.e.:

In notation:

```{=tex}
\begin{aligned}
f_{A_1} &= f_{A_2} = f_{A_3} \\
f_{Y_1} &= g_{Y_2} = f_{Y_3} \\
f_{Y_1} &= f_{Y_2} = f_{Y_3} \\

\end{aligned}
```
This assumption implies that:

```{=tex}
\begin{aligned}
g_{A_1} &= g_{A_2} = g_{A_3} \\
g_{Y_1} &= g_{Y_2} = g_{Y_3} \\
g_{Y_1} &= g_{Y_2} = g_{Y_3} \\

\end{aligned}
```
since the each function $f_*$ depends on the value of the function $g_*$.

This allows us to re-write the model like this:

##### Permutation invariance

We assume that the order of the entries in the input of functions $g_*$ and $h_*$ does not matter. i.e. these functions are invariant under permutation of the entries in the input vector.

$$
g(\mathbf{l}) = g(\mathbf{m}) \text{ for } \mathbf{l} \text{ permutation of } \mathbf{m}
$$

We can re-write the model like this:

$$
\begin{aligned}
L_i &= f_{L}( U_{L_i} ) \\
A_i &= f_{A}( U_{A_i}, L_i, g_{A}(\textbf{L}_{N_i}) ) \\
Y_i &= f_{Y}( U_{Y_i},  L_i,  g_{Y}(\textbf{L}_{N_i}),   A_i,  h_{Y}(\textbf{L}_{N_i}, \textbf{A}_{N_i} ) ) \\
\end{aligned}
$$ {#eq-causal-dang-homogenous}


### SSNAC

#### Compact graphic representation

```{r }
#| fig-height: 5
#| fig-width: 5

structural_nodes <- data.frame(
  name  = c("L", "A", "Y"),
  label = c(r"($L_{3 \times 1}$)", r"($A_{3 \times 1})", r"($Y_{3 \times 1}$)") |> latex2exp::TeX(output = "character", bold = TRUE),
  x = c(1, 2, 3),
  y = c(2, 1, 1),
  node_type = "person",
  node_shape = "covariate"
) 

structural_edges <- data.frame(
  from = c("L", "A", "L"),
  to   = c("A", "Y", "Y")
)

network_nodes <- data.frame(
  name  = c("11", "12", "13", "21", "22", "23", "31", "32", "33"),
  label = c("1", "2", "3", "1", "2", "3", "1", "2", "3"),
  x  = c( 1, 1, 1, 2, 2, 2, 3, 3, 3),
  y = c(1, 2, 3, 1, 2, 3, 1, 2, 3),
  node_type = c("Person", "Person", "Person", "Person", "Person", "Person", "Person", "Person", "Person"),
  node_shape = "covariate"
)

network_edges <- data.frame(
  from = c("11", "21", "31", "32", "11", "12", "21", "22"),
  to   = c("22", "12", "22", "21", "21", "22", "31", "32")
)

tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_swig(node_radius = 0.2) +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  scale_fill_mpxnyc(option = "light")

tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
  plot_swig(0, 0, node_radius = 0.2)  +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +

  scale_fill_mpxnyc(option = "light")

```

#### Multiple scales and entities

```{r}


structural_nodes <- data.frame(
  name  = c("C", "A", "Y"),
  label = c(r"($T_{3 \times 1}$)", r"($M_{5 \times 1})", r"($V_{5 \times 1}$)") |> latex2exp::TeX(output = "character", bold = TRUE),
  x = c(1, 2, 3),
  y = c(1, 1, 1),
  node_type = c("Community", "Individual", "Individual"),
  node_shape = "covariate"
) 

structural_edges <- data.frame(
  from = c("C", "A"),
  to   = c("A", "Y")
)

network_nodes <- data.frame(
  name = c("1A", "1B", "1C", "21", "22", "23", "24", "25", "31", "32", "33", "34", "35"),
  label = c("A", "B", "C", "1", "2", "3", "4", "5", "1", "2", "3", "4", "5"),
  x  = c( 1, 1, 1, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3),
  y =  c(1, 2, 3, 1, 2, 3, 4, 5, 1, 2, 3, 4, 5),
  node_type = c(rep("Community", 3), rep("Individual", 5), rep("Individual", 5)),
  node_shape = "covariate"
)

network_edges <- data.frame(
  from = c("1A", "1B", "1B", "1C", "1C", "1C", "1A", "1B", "1C", "22", "21", "23", "23", "24", "25"),
  to =   c("22", "21", "23", "23", "24", "25", "21", "22", "22", "32", "31", "33", "33", "34", "35")
)

tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_swig(node_radius = 0.15) +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +

  scale_fill_mpxnyc(option = "light")



```

```{r}
#| fig-width: 7
#| fig-height: 12

tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
  plot_swig(node_radius = 0.2, node_margin = 0)  +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +

  scale_fill_mpxnyc(option = "light")
```

#### Repeated observations

#### Running example 2



```{r}


list_nodes <- list()
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V0", label = r"($V_{0}$)", x = 1, y = 8, node_type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R1", label = r"($R_{1}$)", x = 2, y = 2, node_type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T1", label = r"($T_{1}$)", x = 3, y = 4, node_type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M1", label = r"($M_{1}$)", x = 4, y = 6, node_type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V1", label = r"($V_{1}$)", x = 5, y = 8, node_type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R2", label = r"($R_{2}$)", x = 6, y = 2, node_type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T2", label = r"($T_{2}$)", x = 7, y = 4, node_type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M2", label = r"($M_{2}$)", x = 8, y = 6, node_type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V2", label = r"($V_{2}$)", x = 9, y = 8, node_type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R3", label = r"($R_{3}$)", x = 10, y = 2, node_type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T3", label = r"($T_{3}$)", x = 11, y = 4, node_type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M3", label = r"($M_{3}$)", x = 12, y = 6, node_type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V3", label = r"($V_{3}$)", x = 13, y = 8, node_type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R4", label = r"($R_{4}$)", x = 14, y = 2, node_type = "Community")

list_edges <- list()
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "R1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R1", to = "T1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T1", to = "M1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "V1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R2", to = "T2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T2", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "V2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R3", to = "T3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T3", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M3", to = "V3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "R2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "R3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V3", to = "R4")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "V1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "V2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "V3")


structural_nodes <- list_nodes |> 
  dplyr::bind_rows() |> 
  dplyr::mutate(label = latex2exp::TeX(label, output = "character", bold = TRUE)) |>
  dplyr::mutate(node_shape = "covariate")

structural_edges <- list_edges |> dplyr::bind_rows()


tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_swig(node_radius = 0.4) +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  scale_fill_mpxnyc(option = "light")



```

```{r}


network_nodes_0 <- data.frame(
  name = c("01", "02", "03", "04", "05"),
  label = c("1", "2", "3", "4", "5"),
  x  = c( 0,0,0,0,0),
  y =  c(1,2,3,4,5),
  node_type = rep("Individual", 5),
  node_shape = "covariate"
)

network_nodes_1 <- data.frame(
  name = c("1A", "1B", "1C", "2A", "2B", "2C", "31", "32", "33", "34", "35", "41", "42", "43", "44", "45"),
  label = c("A", "B", "C", "A", "B", "C", "1", "2", "3", "4", "5", "1", "2", "3", "4", "5"),
  x  = c( 1, 1, 1, 2, 2, 2, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4),
  y =  c(1.5,2.5,3.5,1.5,2.5,3.5,1.5,2.25,3,3.75,4.5, 1,2,3,4,5),
  node_type = c( rep("Community", 3), rep("Community", 3), rep("Individual", 5), rep("Individual", 5)),
  node_shape = "covariate"
)

network_nodes_2 <- data.frame(
  name = c("5A", "5B", "5C", "6A", "6B", "6C", "71", "72", "73", "74", "75", "81", "82", "83", "84", "85"),
  label = c("A", "B", "C", "A", "B", "C", "1", "2", "3", "4", "5", "1", "2", "3", "4", "5"),
  x  = 4 + c( 1, 1, 1, 2, 2, 2, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4),
  y =  c(1.5,2.5,3.5,1.5,2.5,3.5,1.5,2.25,3,3.75,4.5, 1,2,3,4,5),
  node_type = c( rep("Community", 3), rep("Community", 3), rep("Individual", 5), rep("Individual", 5)),
  node_shape = "covariate"
)

network_nodes_3 <- data.frame(
  name = c("9A", "9B", "9C", "10A", "10B", "10C", "111", "112", "113", "114", "115", "121", "122", "123", "124", "125"),
  label = c("A", "B", "C", "A", "B", "C", "1", "2", "3", "4", "5", "1", "2", "3", "4", "5"),
  x  = 8 + c( 1, 1, 1, 2, 2, 2, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4),
  y =  c(1.5,2.5,3.5,1.5,2.5,3.5,1.5,2.25,3,3.75,4.5, 1,2,3,4,5),
  node_type = c( rep("Community", 3), rep("Community", 3), rep("Individual", 5), rep("Individual", 5)),
  node_shape = "covariate"
)

network_nodes_4 <- data.frame(
  name = c("13A", "13B", "13C"),
  label = c("A", "B", "C"),
  x  = 12 + c( 1, 1, 1),
  y =  c(1.5,2.5,3.5),
  node_type = c( rep("Community", 3)),
  node_shape = "covariate"
)


network_edges_1 <- data.frame(
  from = c("35", "34", "33","32",  "33", "32", "31", "32", "31", "2A", "2B", "2C", "41", "42", "43", "44", "45"),
  to =   c("2C", "2C", "2C", "2C",  "2B", "2B", "2B", "2A", "2A", "1A", "1B", "1C", "31", "32", "33", "34", "35")
)

network_edges_2 <- data.frame(
  from = c("01", "02", "03", "04", "05"),
  to   = c("1A", "1A", "1A", "1A", "1A")
)

network_edges_3 <- data.frame(
  from = c("01", "02", "03", "04", "05"),
  to   = c("1B", "1B", "1B", "1B", "1B")
)

network_edges_4 <- data.frame(
  from = c("01", "02", "03", "04", "05"),
  to   = c("1C", "1C", "1C", "1C", "1C")
)

network_edges_5 <- data.frame(
  from = c("41", "42", "43", "44", "45"),
  to   = c("01", "02", "03", "04", "05")
)

network_nodes <- network_nodes_0 |> rbind(network_nodes_1) |> rbind(network_nodes_2) |> rbind(network_nodes_3) |> rbind(network_nodes_4)
network_edges <- network_edges_1 |> rbind(network_edges_2) |> rbind(network_edges_3) |> rbind(network_edges_4) |> rbind(network_edges_5)

tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
  plot_swig(0, 0, node_radius = 0.1, node_margin = 0)  +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  scale_fill_mpxnyc(option = "light")
```





$$
\begin{aligned}
V_{0i} &=  f_{V_0}(U_{V_{0i}}) \\
M_{1i} &=  f_{M_1}(U_{M_{1i}}, \mathbf{T}_{1N_i}) \\
V_{1i} &=  f_{V_1}(U_{V_{1i}}, V_{0i}, M_{1i}) \\
M_{2i} &=  f_{M_2}(U_{M_{2i}}, V_{1i}, M_{1i}, \mathbf{T}_{2N_i}) \\
V_{2i} &=  f_{V_2}(U_{V_{1i}}, V_{1i}, M_{2i}) \\
M_{3i} &=  f_{M_3}(U_{M_{3i}}, V_{2i}, M_{2i}, \mathbf{T}_{3N_i}) \\
V_{3i} &=  f_{V_3}(U_{V_{3i}}, V_{1i}, M_{3i}) \\
R_{1j} &=  f_{R_1}(U_{R_{1j}}, \mathbf{V}_{0}) \\
T_{1j} &=  f_{T_1}(U_{T_{1j}}, R_{1j}) \\
R_{2j} &=  f_{R_2}(U_{R_{2j}}, \mathbf{V}_{1} ) \\
T_{2j} &=  f_{T_2}(U_{T_{2j}}, R_{2j}) \\
R_{3j} &=  f_{R_3}(U_{R_{3i}}, \mathbf{V}_{2} ) \\
T_{3j} &=  f_{T_3}(U_{T_{3i}}, R_{3i}) \\
R_{4j} &=  f_{R_4}(U_{R_{4j}}, \mathbf{V}_{1} ) \\
\end{aligned}
$$ {#eq-repeated-observations}



