```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```


### Network causal inference

See [@aronow2017] for exposure mapping ideas.

#### Independence assumptions

##### No spillover

Just as under classical causal inference, network causal inference as we articulate here, assumes no spillover. See figure \[\] and equations \[\]. It is not necessary to make this restriction to work with network data. Makofane (2021) makes the assumption that contemporaneous measures are arise from conditional Markov Random Field models. We will elaborate a framework (SSNAC-Extension, or SSNACX) at a later stage. In brief, the difference between this articulation and that will be in estimation.

##### Network interference

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-dag
#| fig-cap: "Causal DANG with network interference"

make_dag("network_interference")   |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

Conditioning on the meausres on i and the measures on nodes connecgted to i, contemporaneous measures are independent.

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2) \\
A_3 &= f_{A_3}(U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, A_1, A_2) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, A_1, A_2) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,  A_3) \\
\end{aligned}
$$ {#eq-networkinterference}

#### Homogeneity assumptions

##### Identical distribution

```{r}
#| fig-height: 8
#| fig-width: 7
#| fig-align: center
#| label: fig-homogenous-dag
#| fig-cap: "Causal DANG with homogenous structure"


make_dag("homogenous_interference")            |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")



```

The identical distribution assumption asserts that each person's measures (though they are not independent from one another) arise from the same structural equation model. i.e.:

In notation:

```{=tex}
\begin{aligned}
f_{A_1} &= f_{A_2} = f_{A_3} \\
f_{Y_1} &= g_{Y_2} = f_{Y_3} \\
f_{Y_1} &= f_{Y_2} = f_{Y_3} \\

\end{aligned}
```
This assumption implies that:

```{=tex}
\begin{aligned}
g_{A_1} &= g_{A_2} = g_{A_3} \\
g_{Y_1} &= g_{Y_2} = g_{Y_3} \\
g_{Y_1} &= g_{Y_2} = g_{Y_3} \\

\end{aligned}
```
since the each function $f_*$ depends on the value of the function $g_*$.

This allows us to re-write the model like this:

##### Permutation invariance

We assume that the order of the entries in the input of functions $g_*$ and $h_*$ does not matter. i.e. these functions are invariant under permutation of the entries in the input vector.

$$
g(\mathbf{l}) = g(\mathbf{m}) \text{ for } \mathbf{l} \text{ permutation of } \mathbf{m}
$$

We can re-write the model like this:

$$
\begin{aligned}
L_i &= f_{L}( U_{L_i} ) \\
A_i &= f_{A}( U_{A_i}, L_i, g_{A}(\textbf{L}_{N_i}) ) \\
Y_i &= f_{Y}( U_{Y_i},  L_i,  g_{Y}(\textbf{L}_{N_i}),   A_i,  h_{Y}(\textbf{L}_{N_i}, \textbf{A}_{N_i} ) ) \\
\end{aligned}
$$ {#eq-causal-dang-homogenous}
