```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```

### Example 1: Wealth, Dress, and Jobs {.unnumbered}

We are interested in settling an argument among friends about the relationship between dressing in formal wear and job opportunities. One friend thinks that dressing formally clearly brings more job opportunities; everyone she knows who dresses formally has many more opportunities than people who dress casually. The other friend thinks that what really brings job opportunities is currently having a job. In their reasoning, having a job causes people to dress formally and causes people to have job opportunities, but dressing formally does not in itself improve opportunities. We conduct a study to try investigate.

We recruit three people, Person 1, Person 2, and Person 3. Person 1 and Person 2 are married to each other. Person 1 and Person 3 are newly acquainted colleagues. Say Person 1 has job status $L_1$, Person 2 has job status $L_2$ and Person 3 has job status $L_3$. Each of these variables can only take on two values: "employed vs. unemployed". Similarly we define $A_i$ as Person $i$'s dress (formal vs. informal), and $Y_i$ as their job opportunities (high vs. low). The job status measurement ($L_i$) precedes dress ($A_i$) in time, and dress precedes job opportunities ($Y_i$).

#### Non-parametric structural equation model with independent errors

A non-parametric structural equation model is a system of equations which relates all the entries in a given vector-valued random variable with each other. It does so without specifying parametric functions for each equation in the system.

An example of such a model is shown by @eq-fullly-connected-dag. In this set of equations, values that are produced by equations higher up in the list are the arguments of equations lower down on the list. The functions $f_*$ are deterministic functions whose form we do not necessarily know. The arguments $U_*$ represent error terms - random variables which are independent of each other within and across observational units.

Whereas parametric models, for instance, a linear regression model with normally distributed errors, are characterized by their probability density functions, non-parametric models of this type are usually characterized by their conditional independencies. i.e. for a realization $[X_1, X_2, X_3, X_4, X_5]$ of some statistical model $F$, an example of conditional independency could be:

$$
X_1 \perp X_3 | X_2, X_4
$$

Non-parametric structural equation models are usually represented using the Directed Acyclic Graph (DAG), which show the relationships between the structural equations in the model. The DAG shown in @fig-fullly-connected-dag, for instance, represents the model defined by @eq-fullly-connected-dag. DAGs encode the conditional independencies that characterize non-parametric structural equation models. i.e. Using a DAG and a set of rules called D-separation [@hernán2021], it is possible to read the minimum set of conditional independencies that imply all the conditional independencies that characterize the model.

Conditional indpendencies are indicated by missing edges in the DAG. If we made no assumptions at all about the causal process in Example 1 except the time-ordering of measurements, we could represent our data using @eq-nospillover-dag. Since there are no missing edges between nodes in the @fig-fullly-connected-dag, the structural equation model represents any possible joint distribution between the variables in the DAG - there are no conditional independencies.

```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-dag
#| fig-cap: "Fully connected causal DAG"

make_dag("fully_connected")         |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()

```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, A_1) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, A_1, A_2) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1, Y_2) \\
\end{aligned}
$$ {#eq-fullly-connected-dag}

But the most flexible model is not the most useful one. To fully characterize this system using observed data, we would need to estimate 9 functions using one observation of the 9-dimensional joint distribution that gave rise to the participant's observations. It would not help to recruit additional people to the study because each person would add three new equations to the model and we would have the problem of estimating 12 functions using one observation of a 12-dimensional joint distribution.

Epidemiologists take several approaches to to simplify this system of equations by making assumptions that leave them with fewer functions to estimate and more observations per function. They add restrictions to the model. In the next few sections, we will discuss the restrictions made under classic causal inference, network causal inference, and the SSNAC framework. In each case, simplifying the system of equations equates to deleting some of the arrows in the DAG shown in @fig-fullly-connected-dag (or equivalently, deleting some arguments from the functions in @eq-fullly-connected-dag). In addition, we will assume that some of the functions in the system are identical to each other.

### Assumptions {#sec-assumptions-classic}

Under classic causal inference, we assume that observations are independent and identically distributed. We review these assumptions, naming them slightly differently for the purpose of comparing them with the assumptions made in sections to come. In each case, we divide assumptions up into independence assumptions (assumptions that delete arrows from the DAG) and homogeneity assumptions (assumptions that equate structural equations with each other).

#### Independence assumptions

##### No spillover

Under classic causal inference, we make the assumption of no spillover - that measurements taken across participants at the same time (e.g. $L_1$, $L_2$, and $L_3$) are independent of each other given all prior measures. i.e.


$$
\begin{align}
L_1 \perp L_2 \\
L_2 \perp L_3 \\
L_1 \perp L_3 
\end{align}
$$


$$
\begin{align}
A_1 \perp A_2 | L_1, L_2, L_3\\
A_2 \perp A_3 | L_1, L_2, L_3 \\
A_1 \perp A_3 | L_1, L_2, L_3 
\end{align}
$$


$$
\begin{align}
Y_1 \perp Y_2 | L_1, L_2, L_3, A_1, A_2, A_3\\
Y_2 \perp Y_3 | L_1, L_2, L_3, A_1, A_2, A_3 \\
Y_1 \perp Y_3 | L_1, L_2, L_3, A_1, A_2, A_3 
\end{align}
$$

This is shown in @fig-no-spillover-dag, as the removal of arrows that connected the $L_i$'s, $A_i$'s and $Y_i$'s. In @eq-no-spillover-dag, the $L_i$'s are not functions of each other, the $A_i$'s are not functions of each other, and the $Y_i$'s are not functions of each other. This implies that given all the measurements taken prior to a set of contemporaneous measures, the contemporaneous measures are independent.

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-no-spillover-dag
#| fig-cap: "Causal DAG with no spillover"


make_dag("full_interference")      |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(labels = c("h"), option = "light") +
  theme_mpxnyc()


```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3) \\
\end{aligned}
$$ {#eq-no-spillover-dag}

##### No interference

Classic causal inference makes the no interference assumption. We assume that measurements made across participants, but not at the same time are independent of each other. This is shown as the absence of arrows that connect $L_i$'s to $A_j$'s, $L_i$'s to $Y_j$'s and $A_i$'s to $Y_j$ for participants $i,j$ with $i \neq j$

This allows us to simplify the structural equation model so that each participants measures are a function of only measures taken on them.

$$
\begin{aligned}
L_1 &= f_{L_1}( U_{L_1}) \\
L_2 &= f_{L_2}( U_{L_2}) \\
L_3 &= f_{L_3}( U_{L_3}) \\
A_1 &= f_{A_1}( U_{A_1}, L_1) \\
A_2 &= f_{A_2}( U_{A_2}, L_2) \\
A_3 &= f_{A_3}( U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}( U_{Y_1}, L_1, A_1 ) \\
Y_2 &= f_{Y_2}( U_{Y_2}, L_2, A_2 ) \\
Y_3 &= f_{Y_3}( U_{Y_3}, L_3, A_3 ) \\
\end{aligned}
$$

#### Homogeneity assumption

##### Identical distribution

Finally, we see above that the functions that generate observations $L_i$ are similar in structure to each other, as are the the functions that generate $A_i$'s and $Y_i$s. We make the homogeneity assumption that the functions are identical to each other. 

```{=tex}
\begin{aligned}
 f_L &= f_{L_1} = f_{L_2} = f_{L_3} \\
 f_A &= f_{A_1} = f_{A_2} = f_{A_3} \\
 f_Y &= f_{Y_1} = f_{Y_2} = f_{Y_3}  \\
\end{aligned}
```
This allows us to re-write the structural equation model dropping the person subscript from the equations. The model simplifies into one for three measures each taken on one person, rather than a model for 9 measures taken on 3 people. Since the measures on each person are identically distributed, this model can be used three times to produce the measures for person 1, person 2, and person 3. By contrast, the original model produced measures for all three people at one go.
