## Statistical modelling

See [@aronow2017] for exposure mapping ideas.

```{r colors}
mpxnyc_all <- function(n){
  c("#F73C95", 
    "#FF99C5", 
    "#009BE8", 
    "#41BFFF", 
    "#C5EFFF", 
    "#5D207A", 
    "#7F3F98", 
    "#9E7ACC", 
    "#459B0E", 
    "#59C618", 
    "#EA773D", 
    "#FFAA7B", 
    "#844D28", 
    "#D89000", 
    "#FFCD2E")[1:n]
}

mpxnyc_light <- function(n){
  c(
    "#FF99C5", 
    "#009BE8", 
    "#C5EFFF", 
    "#9E7ACC", 
    "#59C618", 
    "#EA773D", 
    "#FFAA7B", 
    "#D89000", 
    "#FFCD2E"
  )[1:n]
}

mpxnyc_dark <- function(n){
  c("#F73C95",
    "#009BE8", 
    "#5D207A", 
    "#7F3F98", 
    "#459B0E", 
    "#844D28")[1:n]
}

mpxnyc_colors <- function(option){
  if (option == "all") return(mpxnyc_all)
  if (option == "light") return(mpxnyc_light)
  if (option == "dark") return(mpxnyc_dark)
}

scale_fill_mpxnyc <- function(..., option = "all", aesthetics = "fill") {
  ggplot2::discrete_scale(
    aesthetics = aesthetics, 
    palette = mpxnyc_colors(option = option)
  )
}

scale_color_mpxnyc <- function(...){
  scale_fill_mpxnyc(..., aesthetics = "color")
}

```


```{r daggit}


mpxnyc_general_dag_nodelist <- function(graph_type){
  graph_nodes_list                           <- list() 
  graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name                 = "L1", 
                                                      label                = latex2exp::TeX(r"($L_1$)", output = "character"), 
                                                      x                    = 1, 
                                                      y                    = 1, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
    graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name                 = "L2", 
                                                      label                = latex2exp::TeX(r"($L_2$)", output = "character"), 
                                                      x                    = 1, 
                                                      y                    = 3, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
      graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "L3", 
                                                      label = latex2exp::TeX(r"($L_3$)", output = "character"), 
                                                      x                    = 1, 
                                                      y                    = 5, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
        graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "A1", 
                                                      label = latex2exp::TeX(r"($A_1$)", output = "character"), 
                                                      x                    = 3, 
                                                      y                    = 2, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
          graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "A2", 
                                                      label = latex2exp::TeX(r"($A_2$)", output = "character"), 
                                                      x                    = 3, 
                                                      y                    = 3, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
            graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "A3", 
                                                      label = latex2exp::TeX(r"($A_3$)", output = "character"), 
                                                      x                    = 3, 
                                                      y                    = 4, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
              graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "Y1", 
                                                      label = latex2exp::TeX(r"($Y_1$)", output = "character"), 
                                                      x                    = 5, 
                                                      y                    = 1, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
                graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "Y2", 
                                                      label = latex2exp::TeX(r"($Y_2$)", output = "character"), 
                                                      x                    = 5, 
                                                      y                    = 3, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
                  graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "Y3", 
                                                      label = latex2exp::TeX(r"($Y_3$)", output = "character"), 
                                                      x                    = 5, 
                                                      y                    = 5, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
                    graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "LNet1", 
                                                      label = latex2exp::TeX(r"($L_{N_1}$)", output = "character"), 
                                                      x                    = 2, 
                                                      y                    = 1.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                      graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "LNet2", 
                                                      label = latex2exp::TeX(r"($L_{N_2}$)", output = "character"), 
                                                      x                    = 2, 
                                                      y                    = 3, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                        graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "LNet3", 
                                                      label = latex2exp::TeX(r"($L_{N_3}$)", output = "character"), 
                                                      x                    = 2, 
                                                      y                    = 4.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                          graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "ANet1", 
                                                      label = latex2exp::TeX(r"($A_{N_1}$)", output = "character"), 
                                                      x                    = 4, 
                                                      y                    = 1.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                            graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "ANet2", 
                                                      label = latex2exp::TeX(r"($A_{N_2}$)", output = "character"), 
                                                      x                    = 4, 
                                                      y                    = 3, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      homogeneity          = TRUE,
                                                      independence         = FALSE,
                                                      type                 = "person"
                                                      )
                              graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "ANet3", 
                                                      label = latex2exp::TeX(r"($A_{N_1}$)", output = "character"), 
                                                      x                    = 4, 
                                                      y                    = 4.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      homogeneity          = TRUE,
                                                      independence         = FALSE,
                                                      type                 = "person"
                                                      )
  
    
                            result <- graph_nodes_list |>
                                dplyr::bind_rows() |>
                                dplyr::filter({{graph_type}}) |>
                                dplyr::mutate(node_radius = 0.2) 
                            
                            names(result$label) <- result$name
                            rownames(result) <- NULL
                            
                            result
                            

}


  
make_mpxnyc_dag <- function(node_characteristics = NULL, ...){
    
  
  labels <- node_characteristics$label
  
  working_node_characteristics <- node_characteristics |> dplyr::select(-c(x, y, label))
          
          if (!is.null(node_characteristics)) {
          result <- ggdag::dagify(L1 ~ L2, labels = labels) |>
            ggdag::tidy_dagitty() |> 
            dplyr::left_join(working_node_characteristics, by = "name") 
              
          } else {
            result <- ggdag::dagify(...) |>
              ggdag::tidy_dagitty() |> 
              dplyr::left_join(working_node_characteristics |> dplyr::select(-c(x, y, label)), by = "name")
          }
    
return(result)
     
}


plot_mpxnyc_dag <- function(dag, ..., text_color = "white"){
  dag |>
    ggplot2::ggplot( ggplot2::aes(x = x, y = y, xend = xend, yend = yend)) +
    #ggdag::geom_dag_point(ggplot2::aes(...)) +
    ggdag::geom_dag_edges() +
    ggdag::geom_dag_text( ggplot2::aes(label = label), color = text_color,  parse = TRUE) 
}
  
  


```

```{r}
#|fig-height: 8
#|fig-width: 8
#| fig-align: center




make_standard_dag <- function(){
    list_nodes <- list()
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "L1", label = r"($V_{0}$)", x = 1, y = 1, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "L2", label = r"($R_{1}$)", x = 1, y = 3, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "L3", label = r"($T_{1}$)", x = 1, y = 5, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "A1", label = r"($V_{0}$)", x = 3, y = 2, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "A2", label = r"($R_{1}$)", x = 3, y = 3, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "A3", label = r"($T_{1}$)", x = 3, y = 4, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "Y1", label = r"($V_{0}$)", x = 5, y = 1, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "Y2", label = r"($R_{1}$)", x = 5, y = 3, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "Y3", label = r"($T_{1}$)", x = 5, y = 5, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "LNet1", label = r"($V_{0}$)", x = 2, y = 8, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "LNet2", label = r"($R_{1}$)", x = 2, y = 2, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "LNet3", label = r"($T_{1}$)", x = 2, y = 4, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "ANet1", label = r"($V_{0}$)", x = 4, y = 8, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "ANet2", label = r"($R_{1}$)", x = 4, y = 2, type = "Community")
    list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "ANet3", label = r"($T_{1}$)", x = 4, y = 4, type = "Community")

list_edges <- list()
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "R1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R1", to = "T1")
}

make_dag <- function(graph_type){
  
  
  graph_nodes_list                           <- list() 
  graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name                 = "L1", 
                                                      label                = r"($L_1$)", 
                                                      x                    = 1, 
                                                      y                    = 1, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
    graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name                 = "L2", 
                                                      label                = r"($L_2$)", 
                                                      x                    = 1, 
                                                      y                    = 3, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
      graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "L3", 
                                                      label = r"($L_3$)", 
                                                      x                    = 1, 
                                                      y                    = 5, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
        graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "A1", 
                                                      label = r"($A_1$)", 
                                                      x                    = 3, 
                                                      y                    = 2, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
          graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "A2", 
                                                      label = r"($A_2$)", 
                                                      x                    = 3, 
                                                      y                    = 3, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
            graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "A3", 
                                                      label = r"($A_3$)", 
                                                      x                    = 3, 
                                                      y                    = 4, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
              graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "Y1", 
                                                      label = r"($Y_1$)", 
                                                      x                    = 5, 
                                                      y                    = 1, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
                graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "Y2", 
                                                      label = r"($Y_2$)", 
                                                      x                    = 5, 
                                                      y                    = 3, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
                  graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "Y3", 
                                                      label = r"($Y_3$)", 
                                                      x                    = 5, 
                                                      y                    = 5, 
                                                      full_interference    = TRUE, 
                                                      full_spillover       = TRUE, 
                                                      network_interference = TRUE,
                                                      network_spillover    = TRUE,
                                                      homogeneity          = TRUE,
                                                      independence         = TRUE,
                                                      type                 = "person"
                                                      )
                    graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "LNet1", 
                                                      label = r"($L_{N_1}$)", 
                                                      x                    = 2, 
                                                      y                    = 1.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                      graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "LNet2", 
                                                      label = r"($L_{N_2}$)", 
                                                      x                    = 2, 
                                                      y                    = 3, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                        graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "LNet3", 
                                                      label = r"($L_{N_3}$)", 
                                                      x                    = 2, 
                                                      y                    = 4.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                          graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "ANet1", 
                                                      label = r"($A_{N_1}$)", 
                                                      x                    = 4, 
                                                      y                    = 1.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      independence         = FALSE,
                                                      homogeneity          = TRUE,
                                                      type                 = "person"
                                                      )
                            graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "ANet2", 
                                                      label = r"($A_{N_2}$)", 
                                                      x                    = 4, 
                                                      y                    = 3, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      homogeneity          = TRUE,
                                                      independence         = FALSE,
                                                      type                 = "person"
                                                      )
                              graph_nodes_list[[length(graph_nodes_list) + 1]] <- data.frame(
                                                      name = "ANet3", 
                                                      label = r"($A_{N_1}$)", 
                                                      x                    = 4, 
                                                      y                    = 4.5, 
                                                      full_interference    = FALSE, 
                                                      full_spillover       = FALSE, 
                                                      network_interference = FALSE,
                                                      network_spillover    = FALSE,
                                                      homogeneity          = TRUE,
                                                      independence         = FALSE,
                                                      type                 = "person"
                                                      )
  
    
                              graph_nodes <- graph_nodes_list |>
                                dplyr::bind_rows() |>
                                dplyr::filter({{graph_type}}) |>
                                dplyr::mutate(node_radius = 0.2) |>
                                dplyr::mutate(label = latex2exp::TeX(label, output = "character"))
                              
                       




graph_edges_list <- list()

graph_edges_list[["mechanism"]] <- data.frame(
                                              from                 = c("L1", "L2", "L3", "L1", "L2", "L3", "A1", "A2", "A3"),
                                              to                   = c("A1", "A2", "A3", "Y1", "Y2", "Y3", "Y1", "Y2", "Y3"),
                                              full_interference    = TRUE, 
                                              full_spillover       = TRUE, 
                                              network_interference = TRUE,
                                              network_spillover    = TRUE,
                                              homogeneity          = TRUE,
                                              independence         = TRUE
                                            )

graph_edges_list[["network_interference"]] <- data.frame(
                                              from                 = c("L1", "L2", "L1", "L2", "A1", "A2"),
                                              to                   = c("A2", "A1", "Y2", "Y1", "Y2", "Y1"),
                                              full_interference    = TRUE, 
                                              full_spillover       = TRUE, 
                                              network_interference = TRUE,
                                              network_spillover    = TRUE,
                                              homogeneity          = FALSE,
                                              independence         = FALSE
                                            )

graph_edges_list[["non_network_interference"]] <- data.frame(
                                              from                 = c("L1", "L3", "L1", "L3", "A1", "A3", 
                                                                       "L2", "L3", "L2", "L3", "A2", "A3"),
                                              to                   = c("A3", "A1", "Y3", "Y1", "Y3", "Y1",
                                                                       "A3", "A2", "Y3", "Y2", "Y3", "Y2"),
                                              full_interference    = TRUE, 
                                              full_spillover       = TRUE, 
                                              network_interference = FALSE,
                                              network_spillover    = FALSE,
                                              homogeneity          = FALSE,
                                              independence         = FALSE
                                            )

graph_edges_list[["network_spillover"]] <- data.frame(
                                              from                 = c("L1", "A1", "Y1"),
                                              to                   = c("L2", "A2", "Y2"),
                                              full_interference    = FALSE, 
                                              full_spillover       = TRUE, 
                                              network_interference = FALSE,
                                              network_spillover    = TRUE,
                                              homogeneity          = FALSE,
                                              independence         = FALSE
                                              )

graph_edges_list[["non_network_spillover"]] <- data.frame(
                                              from                 = c("L2", "A2", "Y2"),
                                              to                   = c("L3", "A3", "Y3"),
                                              full_interference    = FALSE, 
                                              full_spillover       = TRUE, 
                                              network_interference = FALSE,
                                              network_spillover    = FALSE,
                                              homogeneity          = FALSE,
                                              independence         = FALSE
                                              )

graph_edges_list[["homogenous_interference"]] <- data.frame(
                                              from                 = c("L1"   , "L2"   , "A1"   , "A2"),
                                              to                   = c("LNet2", "LNet1", "ANet2", "ANet1"),
                                              full_interference    = FALSE, 
                                              full_spillover       = FALSE, 
                                              network_interference = FALSE,
                                              network_spillover    = FALSE,
                                              homogeneity          = TRUE,
                                              independence         = FALSE
                                              )




graph_edges <- graph_edges_list |>
  purrr::map2(names(graph_edges_list),
              function(x, y) x |> dplyr::mutate(type = y)) |>
        dplyr::bind_rows() |>
                                dplyr::filter({{graph_type}})



tidygraph::tbl_graph(nodes = graph_nodes, edges = graph_edges)  
                  
}


 


plot_dag <- function(data, arrow_length_head = 0.2, arrow_length_tail = 0.05, edge_width = 0.2, node_radius = 0.3, node_margin = 0.4, colors = c("#C5EFFF", "#FF99C5")){
  analysis_data <- data |>
    tidygraph::activate(nodes) |>
    tidygraph::mutate(node_radius = node_radius) 
  
  ggraph::create_layout(analysis_data, data.frame(analysis_data)) |>
  ggraph::ggraph(analysis_data) +
                      ggraph::geom_edge_link(
                              ggplot2::aes(), 
                              arrow       = grid::arrow(angle = 15, length = ggplot2::unit(arrow_length_head, "inches"), ends = "last", type = "open"), 
                              end_cap     = ggraph::circle(node_margin, 'inches'), 
                              start_cap   = ggraph::circle(node_margin, 'inches'), 
                              edge_width  = edge_width
                              ) +
                      ggraph::geom_edge_link(
                              ggplot2::aes(), 
                              arrow       = grid::arrow(angle = 85, length = ggplot2::unit(arrow_length_tail, "inches"), ends = "first", type = "closed"), 
                              end_cap     = ggraph::circle(node_margin, 'inches'), 
                              start_cap   = ggraph::circle(node_margin, 'inches'), 
                              edge_width  = edge_width
                              ) +

                      ggraph::geom_node_circle(
                              ggplot2::aes( r=node_radius, fill = type, shape = type),
                              color = "black"
                              ) +
                      ggraph::geom_node_text(
                              ggplot2::aes(label = label, fill = type), 
                              color       = "black", 
                              size        = 5, 
                              parse       = TRUE
                              ) + 
                      ggplot2::theme_void() +
    ggplot2::theme(
      legend.position = "none",
      plot.margin = ggplot2::margin(30, 30, 30, 30)
      #plot.background = ggplot2::element_rect(fill = mpxnyc::mpxnyc_colors[["light_blue"]], size = 0)
    ) +
    #ggplot2::scale_fill_manual(values = colors) +
    #ggplot2::scale_color_manual(values = colors) +
    ggplot2::coord_fixed()
}




```


```{r makeswig}
make_swig <- function(graph_type){
  
  
  graph_nodes_list                           <- list() 

  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L1", label = r"($L_1$)"              , x = 1, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L2", label = r"($L_2$)"              , x = 1, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "L3", label = r"($L_3$)"              , x = 1, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A1", label = r"($A_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A2", label = r"($A_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "A3", label = r"($A_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "preintervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a1", label = r"($a_1$)"              , x = 3, y = 2,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a2", label = r"($a_2$)"              , x = 3, y = 3,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "a3", label = r"($a_3$)"              , x = 3, y = 4,   homogenous = FALSE, node_shape = "intervention")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y1", label = r"($Y_1 (a_1, a_2)$)"   , x = 5, y = 1,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y2", label = r"($Y_2 (a_2, a_1)$)"   , x = 5, y = 3,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "Y3", label = r"($Y_3 (a_3)$)"        , x = 5, y = 5,   homogenous = FALSE, node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet1", label = r"($L_{N_1}$)"       , x = 2, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet2", label = r"($L_{N_2}$)"       , x = 2, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "LNet3", label = r"($L_{N_3}$)"       , x = 2, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet1", label = r"($A_{N_1}$)"       , x = 4, y = 1.5, homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet2", label = r"($A_{N_2} $)"      , x = 4, y = 3,   homogenous = TRUE , node_shape = "covariate")))
  graph_nodes_list <- append(graph_nodes_list, list(data.frame(name = "ANet3", label = r"($A_{N_1} $)"      , x = 4, y = 4.5, homogenous = TRUE , node_shape = "covariate")))
  
    
  graph_nodes <- graph_nodes_list |>
                      dplyr::bind_rows() |>
                      dplyr::mutate(node_radius = 0.2) |>
                      dplyr::mutate(label = latex2exp::TeX(label, output = "character")) |>
    dplyr::mutate(node_type = node_shape) |>
    dplyr::mutate(node_type = ifelse(node_shape == "preintervention", "covariate", node_shape))



graph_edges_list <- list()

graph_edges_list[["independence"]] <- data.frame(
                                              from                 = c("L1", "L2", "L3", "L1", "L2", "L3", "a1", "a2", "a3"),
                                              to                   = c("A1", "A2", "A3", "Y1", "Y2", "Y3", "Y1", "Y2", "Y3")
                                            )

graph_edges_list[["network_interference"]] <- data.frame(
                                                        from                 = c("L1", "L2", "L1", "L2", "a1", "a2"),
                                                        to                   = c("A2", "A1", "Y2", "Y1", "Y2", "Y1")
                                                        ) |>
                                                rbind(graph_edges_list[["independence"]] )

graph_edges_list[["full_interference"]] <- data.frame(
                                              from                 = c("L1", "L3", "L1", "L3", "a1", "a3", 
                                                                       "L2", "L3", "L2", "L3", "a2", "a3"),
                                              to                   = c("A3", "A1", "Y3", "Y1", "Y3", "Y1",
                                                                       "A3", "A2", "Y3", "Y2", "Y3", "Y2")) |>
  rbind(graph_edges_list[["network_interference"]] )

graph_edges_list[["fully_connected"]] <- data.frame(
                                              from                 = c("L1", "a1", "Y1"),
                                              to                   = c("L2", "A2", "Y2")
                                              ) |>
  rbind(graph_edges_list[["full_interference"]] )



graph_edges_list[["homogenous_interference"]] <- data.frame(
                                              from                 = c("L1"   , "L2"   , "a1"   , "a2"   , "LNet2", "LNet1", "LNet2", "LNet1", "ANet2", "ANet1"),
                                              to                   = c("LNet2", "LNet1", "ANet2", "ANet1", "A2"   , "A1"   , "Y2"   , "Y1"   , "Y2"   , "Y1"   )) |>
  rbind(graph_edges_list[["independence"]])




graph_edges <- graph_edges_list[[graph_type]]

if (graph_type != "homogenous_interference") {
  graph_nodes <- graph_nodes |>
    dplyr::filter(!homogenous)
}


tidygraph::tbl_graph(nodes = graph_nodes, edges = graph_edges)  
                  
}

```

```{r plotswig}

plot_swig <- function(data, arrow_length_head = 0.2, arrow_length_tail = 0.05, edge_width = 0.2, node_radius = 0.3, node_margin = 0.4, nudge_intervention_labels = 0.1){
  
  edge_label_exists <- data |>
    tidygraph::activate(edges) |>
    data.frame() |>
    names() |>
    {function(x) "edge_label" %in% x}()
  
  if (!edge_label_exists) {
      analysis_data <- data |>
    tidygraph::activate(edges) |>
        tidygraph::mutate(edge_label = "") |>
        tidygraph::activate(nodes)
  } else {
    analysis_data <- data
  }
  
  
  node_characteristics <- analysis_data |>
    data.frame() 
  
  ggraph::create_layout(analysis_data, data.frame(analysis_data)) |>
  ggraph::ggraph(analysis_data) +
                      ggraph::geom_edge_link(
                              ggplot2::aes(label = latex2exp::TeX(edge_label, output = "character")), 
                              arrow       = grid::arrow(angle = 15, length = ggplot2::unit(arrow_length_head, "inches"), ends = "last", type = "open"), 
                              end_cap     = ggraph::circle(node_margin, 'inches'), 
                              start_cap   = ggraph::circle(node_margin, 'inches'),
                              edge_width = edge_width,
                              label_size = 8
                              ) +
                      ggraph::geom_edge_link(
                              ggplot2::aes(), 
                              arrow       = grid::arrow(angle = 85, length = ggplot2::unit(arrow_length_tail, "inches"), ends = "first", type = "closed"), 
                              end_cap     = ggraph::circle(node_margin, 'inches'), 
                              start_cap   = ggraph::circle(node_margin, 'inches'),
                              edge_width = edge_width
                              ) +

          ggforce::geom_arc_bar(ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type, start = 0, end = 1*pi, r0 = 0), data = node_characteristics |> dplyr::filter(node_shape == "intervention"), position = ggplot2::position_nudge(x = 0.25 * nudge_intervention_labels)) +
    ggforce::geom_arc_bar(ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type, start = pi, end = 2*pi, r0 = 0), data = node_characteristics |> dplyr::filter(node_shape == "preintervention"), position = ggplot2::position_nudge(x = - 0.25 * nudge_intervention_labels)) +
        ggforce::geom_circle(ggplot2::aes(x0 = x, y0 = y, r = node_radius + 0.05, fill = node_type), data = node_characteristics |> dplyr::filter(node_shape == "covariate")) +

                          ggraph::geom_node_text(
                              ggplot2::aes(label = label, fill = node_type),
                              color       = "black",
                              size        = 3.5,
                              parse       = TRUE,
                              data        = node_characteristics |> dplyr::filter(node_shape == "preintervention"),
                              nudge_x     = -nudge_intervention_labels
                              ) +
                              ggraph::geom_node_text(
                              ggplot2::aes(label = label, fill = node_type),
                              color       = "black",
                              size        = 3.5,
                              parse       = TRUE,
                              data        = node_characteristics |> dplyr::filter(node_shape == "intervention"),
                              nudge_x     = nudge_intervention_labels
                              ) +
                              ggraph::geom_node_text(
                              ggplot2::aes(label = label, fill = node_type),
                              color       = "black",
                              size        = 3.5,
                              parse       = TRUE,
                              data        = node_characteristics |> dplyr::filter(node_shape == "covariate")
                              ) +
                      ggplot2::theme_void() +
    ggplot2::theme(
      legend.position = "none",
      plot.margin = ggplot2::margin(20, 20, 20, 20)
      #plot.background = ggplot2::element_rect(fill = mpxnyc::mpxnyc_colors[["dark_blue"]], size = 0)
    ) +
    #ggplot2::scale_fill_manual(values = colors) +
    ggplot2::coord_fixed()
}







```

We can write any joint distribution for a study of three people, each with three measures - L, taken at time 1, A, taken at time 2, and Y, taken at time 3.

```{r}
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-spillover-classic-dag 
#| fig-cap: "Fully connected causal DAG"

make_dag(full_spillover)         |> plot_dag(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")

```

```{=tex}
\begin{aligned}
L_1 &= \textcolor{#EA773D}{f_{L_1}(U_{L_1}) }\\
L_2 &= f_{L_2}(U_{L_2}, L_1) \\
L_3 &= f_{L_3}(U_{L_3}, L_1, L_2 ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3, A_1) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3, A_1, A_2) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3, Y_1, Y_2) \\
\end{aligned}
```
### Classic causal inference

#### Independence assumptions

##### No spillover

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-iwpillover-classic-dag
#| fig-cap: "Causal DAG with no spillover"


make_dag(full_interference)      |> plot_dag(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

```{=tex}
\begin{aligned}
L_1 &= \textcolor{#EA773D}{f_{L_1}(U_{L_1}) }\\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3) \\
\end{aligned}
```
##### No interference

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-classic-dag
#| fig-cap: "Causal DAG with no interference or spillover"

make_dag(independence) |> plot_dag(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

This allows us to simplify the structural equation model like this:

```{=tex}
\begin{aligned}
L_1 &= f_{L_1}( U_{L_1}) \\
L_2 &= f_{L_2}( U_{L_2}) \\
L_3 &= f_{L_3}( U_{L_3}) \\
A_1 &= f_{A_1}( U_{A_1}, L_1) \\
A_2 &= f_{A_2}( U_{A_2}, L_2) \\
A_3 &= f_{A_3}( U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}( U_{Y_1}, L_1, A_1 ) \\
Y_2 &= f_{Y_2}( U_{Y_2}, L_2, A_2 ) \\
Y_3 &= f_{Y_3}( U_{Y_3}, L_3, A_3 ) \\
\end{aligned}
```
#### Homogeneity assumption

The identical distribution assumption asserts that each person's measures arise from the same structural equation model. i.e.:

```{=tex}
\begin{aligned}
 f_{L_1} = f_{L_2} = f_{L_3} \\
 f_{A_1} = f_{A_2} = f_{A_3} \\
 f_{Y_1} = f_{Y_2} = f_{Y_3}  \\
\end{aligned}
```
This allows us to re-write the structural equation model, dropping the person subscript.

```{=tex}
\begin{aligned}
L_1 &= f_{L}( U_{L_1}) \\
L_2 &= f_{L}( U_{L_2}) \\
L_3 &= f_{L}( U_{L_3}) \\
A_1 &= f_{A}( U_{A_1}, L_1) \\
A_2 &= f_{A}( U_{A_2}, L_2) \\
A_3 &= f_{A}( U_{A_3}, L_3) \\
Y_1 &= f_{Y}( U_{Y_1}, L_1, A_1) \\
Y_2 &= f_{Y}( U_{Y_2}, L_2, A_2) \\
Y_3 &= f_{Y}( U_{Y_3}, L_3, A_3) \\
\end{aligned}
```
This allows us to simplify the structural equation model for three measures, each taken on three people, into a structural equation model for one person. This is useful because we actually observed three people, yet our model is for one person's measures. Since the measures on each person are identically distributed, this model can be used three times to produce the measures for person 1, person 2, and person 3. The original model produced measures for all three people at one go.

```{=tex}
\begin{aligned}
L_i &= f_{L}( U_{L_i}) \\
A_i &= f_{A}( U_{A_i}, L_i) \\
Y_i &= f_{Y}( U_{Y_i}, L_i, A_i) \\
\end{aligned}
```
### Network causal inference

#### Independence assumptions

##### No spillover

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-spillover-dag
#| fig-cap: "Causal DANG with no spillover"
make_dag(full_interference) |> plot_dag(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

```{=tex}
\begin{aligned}
L_1 &= \textcolor{#EA773D}{f_{L_1}(U_{L_1}) }\\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2, L_3) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2, L_3) \\
A_3 &= f_{A_3}(U_{A_3}, L_1, L_2, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, L_3, A_1, A_2, A_3) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_1, L_2, L_3, A_1, A_2, A_3) \\
\end{aligned}
```
We assume that conditioning on all prior measures, contemporaneous measures are indpendent. In notation:

$$
 \phi_* = c \in R^t
$$

##### Network interference

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-dag
#| fig-cap: "Causal DANG with network interference"
make_dag(network_interference)   |> plot_dag(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")


```

Conditioning on the meausres on i and the measures on nodes connecgted to i, contemporaneous measures are independent.

```{=tex}
\begin{aligned}
L_1 &= \textcolor{#EA773D}{f_{L_1}(U_{L_1}) }\\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2) \\
A_3 &= f_{A_3}(U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, A_1, A_2) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, A_1, A_2) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,  A_3) \\
\end{aligned}
```
#### Homogeneity assumptions

##### Identical distribution

```{r}
#| fig-height: 8
#| fig-width: 7
#| fig-align: center
#| label: fig-homogenous-dag
#| fig-cap: "Causal DANG with homogenous structure"


make_dag(homogeneity)            |> plot_dag(node_radius = 0.2) + scale_fill_mpxnyc(option = "light")



```

The identical distribution assumption asserts that each person's measures (though they are not independent from one another) arise from the same structural equation model. i.e.:

In notation:

```{=tex}
\begin{aligned}
f_{A_1} &= f_{A_2} = f_{A_3} \\
f_{Y_1} &= g_{Y_2} = f_{Y_3} \\
f_{Y_1} &= f_{Y_2} = f_{Y_3} \\

\end{aligned}
```
This assumption implies that:

```{=tex}
\begin{aligned}
g_{A_1} &= g_{A_2} = g_{A_3} \\
g_{Y_1} &= g_{Y_2} = g_{Y_3} \\
g_{Y_1} &= g_{Y_2} = g_{Y_3} \\

\end{aligned}
```
since the each function $f_*$ depends on the value of the function $g_*$.

This allows us to re-write the model like this:

##### Permutation invariance

We assume that the order of the entries in the input of functions $g_*$ and $h_*$ does not matter. i.e. these functions are invariant under permutation of the entries in the input vector.

$$
g(\mathbf{l}) = g(\mathbf{m}) \text{ for } \mathbf{l} \text{ permutation of } \mathbf{m}
$$


We can re-write the model like this:

```{=tex}
\begin{aligned}
L_i &= f_{L}( U_{L_i}  &&      &&                         &&     &&                                                       &&) \\
A_i &= f_{A}( U_{A_i}, && L_i, && g_{A}(\textbf{L}_{N_i})        &&      &&                                               &&) \\
Y_i &= f_{Y}( U_{Y_i}, && L_i, && g_{Y}(\textbf{L}_{N_i}),       && A_i, && h_{Y}(\textbf{L}_{N_i}, \textbf{A}_{N_i} )          &&) \\
\end{aligned}
```
### SSNAC


#### Compact graphic representation

```{r }
#| layout-ncol: 2
#| fig-height: 5
#| fig-width: 5

structural_nodes <- data.frame(
  name  = c("L", "A", "Y"),
  label = c(r"($L_{3 \times 1}$)", r"($A_{3 \times 1})", r"($Y_{3 \times 1}$)") |> latex2exp::TeX(output = "character", bold = TRUE),
  x = c(1, 2, 3),
  y = c(2, 1, 1),
  type = "Person"
) 

structural_edges <- data.frame(
  from = c("L", "A", "L"),
  to   = c("A", "Y", "Y")
)

network_nodes <- data.frame(
  name = c("1", "2", "3"),
  label = c("1", "2", "3"),
  x  = c( 1, 2, 3),
  y = c(1, 2, 1),
  type = c("Person", "Person", "Person")
)

network_edges <- data.frame(
  from = c("1"),
  to = c("2")
)

tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_dag(node_radius = 0.2) +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  ggplot2::ylim(0.5, 2.5) +
  ggplot2::xlim(0.5, 3.5) + 
  scale_fill_mpxnyc(option = "light")

tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
  plot_dag(0, 0, node_radius = 0.2)  +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  ggplot2::ylim(0.5, 2.5) +
  ggplot2::xlim(0.5, 3.5) + 
  scale_fill_mpxnyc(option = "light")

```

#### Multiple scales and entities

```{r}
#| fig-height: 5
#| fig-width: 9

structural_nodes <- data.frame(
  name  = c("C", "A", "Y"),
  label = c(r"($T_{3 \times 1}$)", r"($M_{5 \times 1})", r"($V_{5 \times 1}$)") |> latex2exp::TeX(output = "character", bold = TRUE),
  x = c(1, 2, 3),
  y = c(1, 1, 1),
  type = c("Community", "Individual", "Individual")
) 

structural_edges <- data.frame(
  from = c("C", "A"),
  to   = c("A", "Y")
)

network_nodes <- data.frame(
  name = c("A", "B", "C", "1", "2", "3", "4", "5"),
  label = c("A", "B", "C", "1", "2", "3", "4", "5"),
  x  = c( 1, 1, 1, 2, 2, 2, 2, 2),
  y =  c(1, 2, 3, 1, 2, 3, 4, 5),
  type = c(rep("Community", 3), rep("Individual", 5))
)

network_edges <- data.frame(
  from = c("A", "B", "B", "C", "C", "C", "A", "B", "C"),
  to =   c("2", "1", "3", "3", "4", "5", "1", "2", "2")
)

tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_dag(node_radius = 0.15) +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  ggplot2::ylim(0.5, 2.5) +
  ggplot2::xlim(0.5, 3.5) + 
  scale_fill_mpxnyc(option = "light")

tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
  plot_dag(node_radius = 0.2, node_margin = 0)  +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  ggplot2::ylim(0.5, 5.5) +
  ggplot2::xlim(0.5, 3.5) + 
  scale_fill_mpxnyc(option = "light")

```

#### Repeated observations

```{r}
#| fig-height: 7
#| fig-width: 10

list_nodes <- list()
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V0", label = r"($V_{0}$)", x = 1, y = 8, type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R1", label = r"($R_{1}$)", x = 2, y = 2, type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T1", label = r"($T_{1}$)", x = 3, y = 4, type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M1", label = r"($M_{1}$)", x = 4, y = 6, type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V1", label = r"($V_{1}$)", x = 5, y = 8, type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R2", label = r"($R_{2}$)", x = 6, y = 2, type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T2", label = r"($T_{2}$)", x = 7, y = 4, type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M2", label = r"($M_{2}$)", x = 8, y = 6, type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V2", label = r"($V_{2}$)", x = 9, y = 8, type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R3", label = r"($R_{3}$)", x = 10, y = 2, type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "T3", label = r"($T_{3}$)", x = 11, y = 4, type = "Community")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "M3", label = r"($M_{3}$)", x = 12, y = 6, type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "V3", label = r"($V_{3}$)", x = 13, y = 8, type = "Individual")
list_nodes[[length(list_nodes) + 1]] <- data.frame(name = "R4", label = r"($R_{4}$)", x = 14, y = 2, type = "Community")

list_edges <- list()
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "R1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R1", to = "T1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T1", to = "M1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "V1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R2", to = "T2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T2", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "V2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "R3", to = "T3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "T3", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M3", to = "V3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "R2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "R3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M1", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "M2", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "M2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "M3")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V3", to = "R4")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V0", to = "V1")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V1", to = "V2")
list_edges[[length(list_edges) + 1]] <- data.frame(from = "V2", to = "V3")


structural_nodes <- list_nodes |> dplyr::bind_rows() |> dplyr::mutate(label = latex2exp::TeX(label, output = "character", bold = TRUE))
structural_edges <- list_edges |> dplyr::bind_rows()


tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
  plot_dag(node_radius = 0.4) +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  ggplot2::ylim(1.5, 8.5) +
  ggplot2::xlim(0.5, 14.5) + 
  scale_fill_mpxnyc(option = "light")



```

```{r}
#| fig-height: 6
#| fig-width: 9
tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
  plot_dag(0, 0, node_radius = 0.2, node_margin = 0)  +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  ggplot2::ylim(0.5, 5.5) +
  ggplot2::xlim(0.5, 8.5) + 
  scale_fill_mpxnyc(option = "light")
```
