
```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```







### Observed data

@fig-independence-dag and  show the resulting non-parametric structural equation model for our data, if we analyse it under classic causal inference. Because of the assumption of independence between observations and identical distribution, we can represent the model using three equations rather than 9. We retain the person subscript on the random variables in @fig-independence-dag and we keep all 9 nodes in the DAG on @eq-independence-dag. This is to remind us that though our model is for one person, our purpose was always to infer something about the population of three people.

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-independence-dag
#| fig-cap: "Causal DAG with no interference or spillover"

make_dag("independence") |> plot_swig(node_radius = 0.2) + scale_fill_mpxnyc(option = "light") + theme_mpxnyc()


```


$$
\begin{aligned}
L_i &= f_{L}( U_{L_i}) \\
A_i &= f_{A}( U_{A_i}, L_i) \\
Y_i &= f_{Y}( U_{Y_i}, L_i, A_i) \\
\end{aligned}
$$ {#eq-independence-dag}