```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```


### Counterfactual data


Under network causal inference, we create a structural equation model fo the system under intervention. In teh network causal inference perspectively, it is possible for one observational unit's treatment value to affect another unit's outcome. Recall Person 1 and Person 2 are a married couple. In this perceptvie, setting Person 1;s dress would afect Person2's job oppottunities and vice versa. For PErson 3, however, their job opportunities are only related to factoers related to them. 

```{r}
#| fig-height: 8
#| fig-width: 7
make_swig("network_interference")      |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()

```

$$
\begin{aligned}
L_i &= f_{L}(  U_{L_i}  ) \\
A_i &= f_{A}( U_{A_i}, L_i, g_{A}(\textbf{L}_{N_i}) ) \\
Y_i^{(a_i,\textbf{a}_{N_i} )} &= f_{Y}(U_{Y_i}, L_i,  a_i,  g_{Y}(\textbf{L}_{N_i}),      h_{Y}(\textbf{a}_{N_i})         ) \\
\end{aligned} 
$$ {#eq-network-interference-dang}

