```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```




### Observed data

@fig-homogenous-dang and @eq-homogenous-dang show the resulting non-parametric structural equation model for our data, if we analyse it under network causal inference. Because of the assumption of identical distributions, we can represent the model using three equations rather than 9. We retain the person subscript on the random variables in @eq-homogenous-dang and we keep all 9 nodes in the DAG on @fig-homogenous-dang and add six additional nodes to represent network exposures with respect to $\mathbf{A}$ and $\mathbf{L}$. This is to clarify that though our model is for one person, it represents a system that relates all the people in the sample with each other. Again, our original purpose was to infer something about causality in the context of the given population of three people.

```{r}
#| fig-height: 8
#| fig-width: 7
#| fig-align: center
#| label: fig-homogenous-dang
#| fig-cap: "Causal DANG with homogenous structure"


make_dag("homogenous_interference")            |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()




```

We can re-write the structural equation model like this:

$$
\begin{aligned}
L_i &= f_{L}( U_{L_i} ) \\
A_i &= f_{A}( U_{A_i}, L_i, g_{A}(\textbf{L}_{N_i}) ) \\
Y_i &= f_{Y}( U_{Y_i},  L_i,  g_{Y}(\textbf{L}_{N_i}),   A_i,  h_{Y}( \textbf{A}_{N_i} ) ) \\
\end{aligned}
$$ {#eq-homogenous-dang}

