```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```

### Observed data

#### Independence assumptions

##### No spillover

Just as under classical causal inference, network causal inference as we articulate here, assumes no spillover. See figure \[\] and equations \[\]. It is not necessary to make this restriction to work with network data. Makofane (2021) makes the assumption that contemporaneous measures are arise from conditional Markov Random Field models. We will elaborate a framework (SSNAC-Extension, or SSNACX) at a later stage. In brief, the difference between this articulation and that will be in estimation.

##### Network interference

```{r}
#| fig-height: 6
#| fig-width: 6.5
#| fig-align: center
#| label: fig-interference-dag
#| fig-cap: "Causal DANG with network interference"

make_dag("network_interference")   |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()


```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, L_2) \\
A_2 &= f_{A_2}(U_{A_2}, L_1, L_2) \\
A_3 &= f_{A_3}(U_{A_3}, L_3) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, L_2, A_1, A_2) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_1, L_2, A_1, A_2) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,  A_3) \\
\end{aligned}
$$ {#eq-networkinterference}

Rather than asume that there is no interference, under network causal inference, we make the assumption that interference respects some mapping between individuals - a mapping given by a network or set of networks. This line of reasoning comes from Makofane dissertation. It was strongly influenced by Tchetgen Tchetgen. We follow a similar approach to [@aronow2017] who termed this mapping, an "exposure mapping".

#### Homogeneity assumptions

Without loss of generality, we can re-write the functions @eq-networkinterference so that they are similar in structure to each other. We define $N_i$ as the indices of all the nodes connected to node $i$. Then $\mathbf{L}_{N_i}$ is the sub-vector of $\mathbf{L}$ containing the entries corresponding to the indices in $N_i$. Similarly, we define $A_{N_i}$ as the sub-vector of $A$ corresponding to the indices in $N_i$. Note that though they are represented as part of the structural equation model in @eq-networkinterference-homogenous, these are deterministic functions, since they do not have an error term ($U_*$) as an input.

Once in this format, we make two homogeneity assumptions which reduce the complexity of the structural equation model.

```{r}
#| fig-height: 8
#| fig-width: 7
#| fig-align: center
#| label: fig-homogenous-dag
#| fig-cap: "Causal DANG with homogenous structure"


make_dag("homogenous_interference")            |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()




```

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, g_{A_1}(\mathbf{L}_{N_1})) \\
A_2 &= f_{A_2}(U_{A_2}, L_2, g_{A_2}(\mathbf{L}_{N_2})) \\
A_3 &= f_{A_3}(U_{A_3}, L_3, g_{A_3}(\mathbf{L}_{N_3})) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, A_1, g_{Y_1}(\mathbf{L}_{N_1}), h_{Y_1}(\mathbf{A}_{N_1})) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_2, A_2, g_{Y_2}(\mathbf{L}_{N_2}), h_{Y_2}(\mathbf{A}_{N_2})) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,A_3,  g_{Y_2}(\mathbf{L}_{N_3}), h_{Y_2}(\mathbf{A}_{N_3})) \\
\end{aligned}
$$

##### Identical distribution

As in the case of classical causal inference, we assume that the structual equations that produce each individual's observations are identical accross individuals. i.e. we assume:

```{=tex}
\begin{aligned}
f_A = f_{A_1} &= f_{A_2} = f_{A_3} \\
f_L = f_{L_1} &= f_{L_2} = f_{L_3} \\
f_Y = f_{Y_1} &= f_{Y_2} = f_{Y_3} \\

\end{aligned}
```
This changes the structural equation model so that it looks like this:

$$
\begin{aligned}
L_1 &= f_{L}(U_{L_1}) \\
L_2 &= f_{L}(U_{L_2}) \\
L_3 &= f_{L}(U_{L_3} ) \\
A_1 &= f_{A}(U_{A_1}, L_1, g_{A_1}(\mathbf{L}_{N_1})) \\
A_2 &= f_{A}(U_{A_2}, L_2, g_{A_2}(\mathbf{L}_{N_2})) \\
A_3 &= f_{A}(U_{A_3}, L_3, g_{A_3}(\mathbf{L}_{N_3})) \\
Y_1 &= f_{Y}(U_{Y_1}, L_1, A_1, g_{Y_1}(\mathbf{L}_{N_1}), h_{Y_1}(\mathbf{A}_{N_1})) \\
Y_2 &= f_{Y}(U_{Y_2}, L_2, A_2, g_{Y_2}(\mathbf{L}_{N_2}), h_{Y_2}(\mathbf{A}_{N_2})) \\
Y_3 &= f_{Y}(U_{Y_3}, L_3,A_3,  g_{Y_2}(\mathbf{L}_{N_3}), h_{Y_2}(\mathbf{A}_{N_3})) \\
\end{aligned}
$$

This simplifies the model, but still forces us to write the structural equations for each observation separately since each observation potentially has a set of unique exposure mappings.

##### Homogenous interference

*Equivalency*: We assume that the functions that map measures from connected individuals into the structural equation are identical across individuals.

```{=tex}
\begin{aligned}
g_A = g_{L_1} &= g_{L_2} = g_{L_3} \\
h_Y = h_{A_1} &= h_{A_2} = h_{A_3} \\
g_Y = g_{L_1} &= g_{L_2} = g_{L_3} \\
\end{aligned}
```
*Symmetry*: We also assume that the order of the entries does not matter in the the input for functions $g_A$, $g_Y$, and $h_Y$. i.e. the functions are invariant under any permutation of the entries in the input vector. e.g.



*Boundedness*: we assume that node degree is bounded.

$$
g_A, h_Y, g_Y < c \text{ for } c \in \mathbf{Z}
$$

We can re-write the structural equation model like this:

$$
\begin{aligned}
L_i &= f_{L}( U_{L_i} ) \\
A_i &= f_{A}( U_{A_i}, L_i, g_{A}(\textbf{L}_{N_i}) ) \\
Y_i &= f_{Y}( U_{Y_i},  L_i,  g_{Y}(\textbf{L}_{N_i}),   A_i,  h_{Y}(\textbf{L}_{N_i}, \textbf{A}_{N_i} ) ) \\
\end{aligned}
$$ {#eq-causal-dang-homogenous}
