
```{r}

# Access custom defined functions
targets::tar_source("../R_functions")

```

### Example 3: Longitudinal Data-Driven Vaccination Campaign {.unnumbered}

You are a public health officer at the department of health in Nowhereville, and are planning to conduct and assess a three week flu vaccination campaign. None of the townspeople have been vaccinated against flu.

In the city of Nowhereville there is a population of 5 residents. The city is divided into three neighborhoods. Each resident has a primary home in one of the neighborhoods, but might visit other residents in another. Person 1 lives in Neighborhood A and visit Neighborhood B. Person 2 lives in Neighborhood B, but vists Neighborhoods A and B. Person 3 lives in Neighborhood C and visits Neighborhood B. Persons 5 and 6 live in Neighborhood C and they do not visit any other neighborhoods.

The city of Nowhereville has a very structured approach to vaccination campaigns. At the beginning of each week, each neighborhood gets a risk rating based on the prevalence of vaccination among its residents and visitors. Based on that rating, each neighborhood decides whether to conduct a local vaccination drive or not. Vaccination drives are done in the same way regardless of neighborhood - visitors and residents are offered immediate vaccination at a nearby mobile van through a pop-up message on the local dating app. Not everyone will receive the messages because some will not open the app during the period of the campaign. Those who do will have the choice of getting vaccinated or not. Each person can only get vaccinated once. 



### New tools from the SSNAC framework {.unnumbered}

As we see in @fig-homogenous-dag, causal DAGs become visually cluttered, and therefore unwieldy, quickly once we start depicting causal systems with multiple observational units. If we added a fourth observational unit to @fig-homogenous-dag, it would be nearly impossible to see which arrow connects which variables. This is an important limitation because one of the most useful things about causal DAGs is that they allow the epidemiologist to reason graphically about the structure of confounding and selection.

#### Introducing the Causal Directed Acyclic Network Graph (DANG)

We introduce the Causal Directed Acyclic Network Graph (causal DANG) - a simple extension of the DAG that allows for the representation of complex systems. Like the causal DAG, the causal DANG encodes the structure of a non-parametric structural equation model. DANGs encode the structure of the causal process within individuals separately from the structure of the causal process across individuals. The former us called the "structural part" of the DANG and the latter called the "relational part" of the DANG.

We represent the structural model defined by @eq-homogenous-dag shown in @fig-homogenous-dag. The first aspect (structural part) of the causal DANG shows the causal structure within individuals. It is a DAG of vector-valued variables $\mathbf{L}$, $\mathbf{A}$, and $\mathbf{Y}$ of length equal to the number of people in the sample. This DAG has standard interpretation under d-separation rules. It gives the conditional independencies across these vector-valued random variables. This is an incomplete set of independencies, however, since some of the entries in $\mathbf{A}$ are independent of a given entry in $\mathbf{L}$, and others are correlated. The second part of the causal DANG (relational part) of the causal DANG shows which pairs of individuals have correlated measures and which do not. 


```{r }
#| fig-height: 8
#| fig-width: 5

structural_nodes <- data.frame(
  name  = c("L", "A", "Y"),
  label = c(r"($L_{3 \times 1}$)", r"($A_{3 \times 1})", r"($Y_{3 \times 1}$)") |> latex2exp::TeX(output = "character", bold = TRUE),
  x = c(1, 2, 3),
  y = c(2, 1, 1),
  node_type = "person",
  node_shape = "covariate"
) 

structural_edges <- data.frame(
  from = c("L", "A", "L"),
  to   = c("A", "Y", "Y")
)

network_nodes <- data.frame(
  name  = c("1", "2", "3"),
  label = c("1", "2", "3"),
  x  = c( 1, 1, 2),
  y = c(1, 2, 1),
  node_type = c("Person", "Person", "Person"),
  node_shape = "covariate"
)

network_edges <- data.frame(
  from = c("1"),
  to   = c("2")
)

structural <- tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
              plot_swig(node_radius = 0.2) +
              ggplot2::theme(
                plot.margin = ggplot2::margin(10, 10, 10, 10),
                legend.position = "none"
              ) +
              scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc()+
  ggplot2::ggtitle("Structural Part") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))

relational <- tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
  plot_swig(0, 0, node_radius = 0.2)  +
  ggplot2::theme(
    plot.margin = ggplot2::margin(10, 10, 10, 10),
    legend.position = "none"
  ) +
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc() +
  ggplot2::ggtitle("Relational Part") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))

cowplot::plot_grid(structural, relational, ncol = 1)

```



The causal DANG relaxes the assumption that all measures in the causal system can be grouped into non-overlapping sets (i.e. that each measure can be attributed to an individual in the sample). In this framework, different types of entities, represented by vectors of different lengths, can be depicted on the same DANG. 

The causal DANG shown in @fig-example-dang-structural represents the first week of the campaign mentioned in Example 3. Let $\mathbf{T}$ be a $3\times1$ vector whose entries $T_j$ are 1 if neighborhood $j$ is to be vaccinated and $0$ otherwise. $\mathbf{M}$ is a $5\times1$ vector whose entries $M_i$ indicate whether the $i^{\text{th}}$ person received a message or not. $\mathbf{V}$ is a $5\times1$ vector whose entries $V_i$ show whether participant $i$ is vaccinated or not. 

```{r}
#| fig-height: 6
#| fig-width: 8
#| fig-align: center
#| label: fig-example-dang-structural
#| fig-cap: "Causal DANG for Week 1 in Example 3"

structural_nodes <- data.frame(
  name  = c("C", "A", "Y"),
  label = c(r"($T_{3 \times 1}$)", r"($M_{5 \times 1})", r"($V_{5 \times 1}$)") |> latex2exp::TeX(output = "character", bold = TRUE),
  x = c(1, 2, 3),
  y = c(1, 1, 1),
  node_type = c("Neighborhood", "Individual", "Individual"),
  node_shape = "covariate"
) 

structural_edges <- data.frame(
  from = c("C", "A"),
  to   = c("A", "Y")
)

network_nodes <- data.frame(
  name = c("A", "B", "C", "1", "2", "3", "4", "5"),
  label = c("A", "B", "C", "1", "2", "3", "4", "5"),
  y  = c( 1, 1, 1, 2, 2, 2, 2, 2),
  x =  c(1, 2, 3, 1, 2, 3, 4, 5),
  node_type = c(rep("Community", 3), rep("Individual", 5)),
  node_shape = "covariate"
)

network_edges <- data.frame(
  from = c("C", "C", "C", "C", "A", "A", "B", "B"),
  to =   c("2", "3", "4", "5", "1", "2", "1", "3")
)

structural <- tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
                    plot_swig(node_radius = 0.15) +
                    scale_fill_mpxnyc(option = "light") +
                    theme_mpxnyc() +
  ggplot2::ggtitle("Structural Part") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))


relational <- tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
                    plot_swig(node_radius = 0.2, node_margin = 0)  +
                    scale_fill_mpxnyc(option = "light") +
  ggplot2::theme(legend.position = "right")

legend <- cowplot::get_legend(relational) 


relational <- relational + 
                  theme_mpxnyc() +
  ggplot2::ggtitle("Relational Part") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))
   



left_side <- cowplot::plot_grid(structural, relational, ncol=1, rel_heights = c(3,3))

cowplot::plot_grid(left_side, legend, nrow = 1, rel_widths = c(4,1))
```

#### Introducing the Single World Intervention Network Graph (SWING)

Similarly, the causal SWING has two parts - a structural part and a relational part. Like with the causal DANG, the causal SWING represents vector-valued random variables (rather than scalars) as nodes. Like the causal SWIG, it shows the counterfactual distribution of the variables in the model under an intervention setting $\mathbf{A}$ at the value $\mathbf{a}$.

```{r}

structural_nodes <- data.frame(
  name  = c("T", "t", "A", "Y"),
  label = c(r"($T$)", r"($t$)", r"($M)", r"($V$)") |> latex2exp::TeX(output = "character", bold = TRUE),
  x = c(1, 1, 2, 3),
  y = c(1, 1, 1, 1),
  node_type = c("Neighborhoo", "Neighborhood", "Individual", "Individual"),
  node_shape = c("preintervention", "intervention" ,"covariate", "covariate")
) 

structural_edges <- data.frame(
  from = c("t", "A"),
  to   = c("A", "Y")
)


structural <- tidygraph::tbl_graph(nodes = structural_nodes, edges = structural_edges) |>
                    plot_swig(node_radius = 0.15) +
                    scale_fill_mpxnyc(option = "light") +
                    theme_mpxnyc() +
  ggplot2::ggtitle("Structural Part") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))


relational <- tidygraph::tbl_graph(nodes = network_nodes, edges = network_edges) |>
                    plot_swig(node_radius = 0.2, node_margin = 0)  +
                    scale_fill_mpxnyc(option = "light") +
  ggplot2::theme(legend.position = "right")

legend <- cowplot::get_legend(relational) 


relational <- relational + 
                  theme_mpxnyc() +
  ggplot2::ggtitle("Relational Part") +
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))
   



left_side <- cowplot::plot_grid(structural, relational, ncol=1, rel_heights = c(3,3))

cowplot::plot_grid(left_side, legend, nrow = 1, rel_widths = c(4,1))

```
### Assumptions

#### Independence assumptions

##### No spillover

Under the SSNAC framework, we make the assumption of no spillover - that contemporaneous measurements taken across observational units are independent of each other given all prior measures. The time-ordering of the measuremnts is given by the structural part of the causal DANG.


##### Network interference

We make the assumption that interference respects the mapping given by the relational part of a causal DANG. 

#### Homogeneity assumptions

##### Identical distribution

As in the case of classical causal inference, we assume that the structural equations that produce each observatoinal unit's measures are identical across observational units i.e. we assume:

```{=tex}
\begin{aligned}
f_A = f_{A_1} &= f_{A_2} = f_{A_3} \\
f_L = f_{L_1} &= f_{L_2} = f_{L_3} \\
f_Y = f_{Y_1} &= f_{Y_2} = f_{Y_3} \\

\end{aligned}
```
##### Homogenous interference

*Separability*

We assume that in each structural equation, each covariate contributes to the exposure mapping in two parts: i) the covariate level for the individual and ii) a covariate level of the ego-network of that individual.

Define $\mathscr{N_i}$ as the indices of all the nodes connected to node $i$. Then $\mathbf{L}_{\mathscr{N}_i}$ is the sub-vector of $\mathbf{L}$ containing the entries corresponding to the indices in $\mathscr{N}_i$. Similarly, we define $A_{\mathscr{N}_i}$ as the sub-vector of $A$ corresponding to the indices in $\mathscr{N}_i$.

$$
\begin{aligned}
L_1 &= f_{L_1}(U_{L_1}) \\
L_2 &= f_{L_2}(U_{L_2}) \\
L_3 &= f_{L_3}(U_{L_3} ) \\
A_1 &= f_{A_1}(U_{A_1}, L_1, g_{A_1}(\mathbf{L}_{\mathscr{N}_1})) \\
A_2 &= f_{A_2}(U_{A_2}, L_2, g_{A_2}(\mathbf{L}_{\mathscr{N}_2})) \\
A_3 &= f_{A_3}(U_{A_3}, L_3, g_{A_3}(\mathbf{L}_{\mathscr{N}_3})) \\
Y_1 &= f_{Y_1}(U_{Y_1}, L_1, A_1, g_{Y_1}(\mathbf{L}_{\mathscr{N}_1}), h_{Y_1}(\mathbf{A}_{\mathscr{N}_1})) \\
Y_2 &= f_{Y_2}(U_{Y_2}, L_2, A_2, g_{Y_2}(\mathbf{L}_{\mathscr{N}_2}), h_{Y_2}(\mathbf{A}_{\mathscr{N}_2})) \\
Y_3 &= f_{Y_3}(U_{Y_3}, L_3,A_3,  g_{Y_2}(\mathbf{L}_{\mathscr{N}_3}), h_{Y_2}(\mathbf{A}_{\mathscr{N}_3})) \\
\end{aligned}
$$

This simplifies the model, but still forces us to write the structural equations for each observation separately since each observation potentially has a set of unique exposure mappings.

*Equivalency*

We assume that exposure mappings $g_A$, $h_y$, and $g_Y$ are identical across individuals.

```{=tex}
\begin{aligned}
g_L = g_{L_1} &= g_{L_2} = g_{L_3} \\
h_A = h_{A_1} &= h_{A_2} = h_{A_3} \\
g_Y = g_{L_1} &= g_{L_2} = g_{L_3} \\
\end{aligned}
```
*Symmetry*

We also assume that the order of the entries does not matter in the the input for functions $g_A$, $g_Y$, and $h_Y$. i.e. the functions are invariant under any permutation of the entries in the input vector.

*Boundedness*

We assume that exposure mappings are bounded above.

$$
g_A, h_Y, g_Y < c \text{ for } c \in \mathbf{Z}
$$


*(time homogeneity)*

In applications with repeated measures, if the structure of the causal DANG allows, we can make the assumption that the structural equations are identical accross time. We apply this assumption in the example 3 below. 


