

##### Person graph {.unnumbered}

The RESPND-MI/MPX NYC has study participants as nodes. A pair of nodes is connected by a weighted edge if each of the participants represented by the nodes share at least one community district in which they both had a gathering or residence. The weight of the edge is equal to the count of community districts the pair of nodes have in common. 



```{r}
#| fig-cap: Sample person-person network visualizatoin
#| label: fig-example-participant
#| fig-width: 8
#| fig-height: 4



make_example_network_data("people") |>
  plot_example_projection_network() +
  theme_mpxnyc_blank(legend.position = "right") +
  ggplot2::scale_size_manual(name = "Node type", values = c(7)) +
  scale_color_mpxnyc(name = "Node type", option = "dark") +
  ggraph::scale_edge_width()  +
  ggraph::scale_edge_width_manual(name = "Weight", values = c(1,2,3))






```



 

```{r  include=FALSE}
#| label: tbl-example-participant-nodes
#| layout-ncol: 2
#| tbl-cap: Sample person-person network data
#| tbl-subcap:  
#| - "Nodes"
#| - "Edges"

make_example_network_data("people") |>
  data.frame() |>
  dplyr::transmute(Name = label, Type = type) |>
  gt::gt()

make_example_network_data("people") |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(From = from_name, To = to_name, Weight = weight) |>
  gt::gt()

```


Then $\psi_P(i,k)$, the adjacency function for the RESPND-MI/MPX NYC person graph is defined:


$$
\psi_P(i,k) = \sum_{j \in N_C}{\psi(i,j) \psi(k,j)}
$$

