##### Social connectedness

Social connectedness is the extent to which all the person nodes are connected through a common set of space nodes. Equivalently, it is the extent to which space nodes are connected through a common set of person nodes. 

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-20
#| fig-width: 8
#| fig-height: 3.5

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "black"
    focal_color = "black"

connectedness_connected <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::mutate(group = ifelse(runif(n = dplyr::n()) > 0.5, "Group A", "Group B")) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
    ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#C5EFFF") +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE, edge_width = 1) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = group,filter = type == "Place"), color = "#C5EFFF", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "black",  "Group B" = "black", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(20,20,20,20)
                      ) +
  ggplot2::coord_fixed()




```

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-21
#| fig-width: 15
#| fig-height: 9

    base_color = grey(0.9,1)
     base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

edge_hidden_data <- data.frame(
  from = c(4,4,6, 2, 3, 6),
  to = c(10, 13, 13, 10, 9, 12),
  hidden = TRUE
)
    
connectedness_disconnected <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::left_join(edge_hidden_data) |>
  tidygraph::mutate(hidden = ifelse(is.na(hidden), FALSE, hidden)) |>
  tidygraph::activate(nodes) |>
  tidygraph::mutate(group = ifelse(runif(n = dplyr::n()) > 0.5, "Group A", "Group B")) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
  ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#C5EFFF") +
  ggplot2::coord_fixed() +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color, filter = !hidden), show.legend = FALSE, edge_width = 1) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = type == "Place"), color = "#C5EFFF", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "black",  "Group B" = "black", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color)  +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(20,20,20,20)
                      ) 



cowplot::plot_grid(connectedness_connected, connectedness_disconnected, rel_widths = c(1,1), nrow = 1)


```

Proportion in largest connected component: In a given network, a
connected component is a subset of nodes such that each node in the
subset is reachable from any other node in the subset, and such that
there are no nodes outside the subset which are reachable from a node
inside it. By reachable, we mean possible to reach by tracing a path
from one node to another over existing network ties. Say the size of the
$k^{th}$ connected component is $C_k$. The proportion in the largest
connected component is given by:

$$
\pi_Q = E[\frac{\max_k{Q_k}}{n_P}]
$$
