---
editor: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}
targets::tar_source("../R_functions")
```

# SSNAC III: Analysis {#sec-appendix-network-analysis}

::: {#leading}
We describe the main data objects of the MPX NYC study -- the
Person-place graph, the Person graph and the Place graph -- as well as
the statistics we used to analyze them.
:::

::: {#acknowledgements}
[Lead author]{.underline}: Keletso Makofane, MPH, PhD.
[Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).

[Acknowledgements]{.underline}: The analytic framework for this project
developed over an extended period of time, beginning during my PhD
dissertation at Harvard University under the supervision of Lisa
Berkman, Eric Tchetgen Tchetgen, and a former mentor). In particular,
the analysis borrows from the central paper in my dissertation, which
shows how the wealth of non-coresident extended family members is
protective against mortality...(continued at bottom of page)
:::

```{r}
#| fig-width: 3
#| fig-height: 3
#| fig-align: center


plot_icon(icon_name = "devil", color = "light_purple", shape = 16, alpha = 0,  size = 100, image_size = 0.2)

```



## Preface

The RESPND-MI/MPX NYC person-place data graph contains all study data,
which are represented as node and edge characteristics. There are two
types of nodes – community districts, and survey participants. Each edge
in the graph connects one community district with one survey
participant.

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-1
#| fig-width: 6
#| fig-height: 5.5


make_example_network_data("bipartite") |>
  plot_example_bipartite_network(label_size = 0) +
  scale_color_mpxnyc(name = "Node type", option = "dark") +
  ggplot2::labs(fill = "Node type") +
  ggplot2::scale_size_manual(name = "Node type", values = c(7,12)) +
  theme_mpxnyc_blank( 
    plot.margin = ggplot2::margin(40,50,40,50),
    legend.position = "bottom"
    ) 



```




@fig-example-participant-place-1 shows a simplified data graph.
Community district nodes are shown in blue and survey participant nodes
in pink. Each edge connects one community district with one survey
participant. Three kinds of edges are shown – those that indicate either
that the survey participant has a home in the community district, or
that they attended a gathering sexual contact or attended a gathering
without sexual contact in the community district. For instance,
*Participant 3* has a home in *Community District B*, he attended a
gathering with no sexual contact in *Community District A*, and he
attended two gathering (one sexual and one non-sexual) in *Community
District E*.


## Individual characteristics



## Local network structure

##### Spatial reach

**Spatial reach of person** $i$ is the number of relations person node
$i$ has with place nodes in the person-place graph. Let $\psi(i,j)$ be the number of edges connecting person $i$ and place $j$ in the person-place graph. Then:


$$
R_{i} = \sum_{\begin{aligned} j &\in \mathscr{N}_C \end{aligned}}{\psi (i,j)}
$$



```{r}
#| fig-width: 8
#| fig-height: 5


make_reach_diagram_data <- function(
                                    focal_node = "Person 6", 
                                    intermediate_nodes = c(),
                                    alter_nodes = c("Community d", "Community e")
) {
  make_example_network_data("bipartite") |>
    tidygraph::mutate(type_color = ifelse(name == focal_node, "Focal node", ifelse(name %in% alter_nodes, "Reached nodes", ifelse(name %in% intermediate_nodes, "Intermediate nodes", NA)))) |>
  tidygraph::activate(edges) |>
  tidygraph::mutate(type_color = NA) 
}

plot_reach_diagram <- function(
    reach_diagram_data,
    base_color = grey(0.9,1), 
    reached_color = "#009BE8", 
    intermediate_color = "#C5EFFF",
    focal_color = "black"
    ){
  
  reach_diagram_data |>
  ggraph::ggraph(layout = "kk") +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
  ggraph::geom_node_point(ggplot2::aes( size = type), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = type_color, size = type)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = type, filter = !is.na(type_color)), color = "white", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c("Focal node" = focal_color, "Reached nodes" = reached_color, "Intermediate nodes" = intermediate_color), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color)
}



make_reach_diagram_data() |>
  plot_reach_diagram() +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 

```

##### Social reach

**Social reach of person $i$ among subgroup $A$** is the number of
person nodes in set $A \subset \mathscr{N}_P$ that are connected to
person node $i$ through shared places. i.e. either because both nodes
have a residence or gathering in at least one common community district. **Social reach of person** $i$ is defined as $R_{i} = R_{i\rightarrow \mathscr{N}_P}$


$$
R_{i\rightarrow A} = \sum_{\begin{aligned} j &\in A \end{aligned}}{\sum_{k \in \mathscr{N}_C}{\psi(i,k)\psi(j,k)} }
$$




```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-10
#| fig-width: 8
#| fig-height: 5


make_reach_diagram_data(
                        alter_nodes = c("Person 8", "Person 4", "Person 3"), 
                        intermediate_nodes = c("Community d", "Community e")
                        ) |>
  plot_reach_diagram(reached_color = "#F73C95", intermediate_color = "darkgrey") +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```

##### Social catchment

**Social catchment of place $j$ among subgroup $A$** is defined as the number of connections the focal community district has with participants who belong to subgroup $A \subset \mathscr{N}_P$.
**Social catchment of place $j$** is defined as $r_{j} = r_{j\rightarrow \mathscr{N}_P}$

$$
r_{j\rightarrow A} = \sum_{i \in A} {\psi (i, j)}
$$
```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-3
#| fig-width: 8
#| fig-height: 5




make_reach_diagram_data(focal_node = "Community c", alter_nodes = c("Person 8", "Person 4", "Person 7", "Person 5")) |>
  plot_reach_diagram(reached_color = "#F73C95") +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```





##### Spatial catchment

**Spatial catchment of place $j$ via subgroup $A$** is defined as the
strength of connection between place node $j$ and other place nodes in
the graph when we consider their shared relations with person nodes in
subgroup $A$. Strength of connection between two places $j$ and $k$ is
defined as the number of relations place nodes $j$ and $k$ have with
common person nodes which belong to subset $A$. The **spatial catchment of place** $j$ is defined as
$r_{i\rightarrow \mathscr{N}_P} = r_{i}$



$$
r_{j\rightarrow A} = \sum_{i \in \mathscr{N}_C} \sum_{k \in A}{\psi(k,i)\psi(k,j)} \\
$$



```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-4
#| fig-width: 8
#| fig-height: 5



make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  plot_reach_diagram(
   intermediate_color = "darkgrey"
  ) +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```



## Global network structure
##### Spatial mixing






The **spatial mixing coefficient from A to B** quantifies the degree to
which egos in group A preferentially live in or attend gatherings in
community districts they are likely to encounter members of group B. It
is defined as the ratio of preference to prevalence minus one.

$$
P_{A \rightarrow B} = \frac{|\mathscr{N}_p|}{|A||B|} \sum_{i \in A} P_{i \rightarrow B} - 1
$$

We define **preference** of person $i$ for group \$ B
\subset \mathscr{N}\_p\$) as the proportion of alters from group B among
all alters

$$
P_{i \rightarrow B} = {\frac{ R_{i \rightarrow B}}{R_i}}
$$

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-5
#| fig-width: 8
#| fig-height: 5

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

unmixed <- make_reach_diagram_data(
                  focal_node = "Community c", 
                  alter_nodes = c("Community d", "Community b", "Community e"),
                  intermediate_nodes = c("Person 8", "Person 4")
                  ) |> 
                  tidygraph::mutate(type_color = NA) |>
                  tidygraph::activate(nodes) |>
                  tidygraph::mutate(group = ifelse(runif(n = dplyr::n()) > 0.5, "Group A", "Group B")) |>
                  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
                  ggraph::ggraph(layout = "kk") +
      ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#FF99C5", alpha = 0.3) +
                  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
                  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
                  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
                  #ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = !is.na(group)), color = "white", show.legend = FALSE) +
                  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 3)) +
                scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "#F73C95",  "Group B" = "#009BE8", "Place" = "black"), na.translate = FALSE) +
                  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
                  theme_mpxnyc_blank( 
                                      ) +
  ggplot2::coord_fixed()




```

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-6
#| fig-width: 15
#| fig-height: 9

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

    
    group_affiliation <- data.frame(
      name = c(paste("Person", 1:8)),
      group = c("Group B", "Group B", "Group B", "Group B", "Group A", "Group A", "Group A", "Group A")
    )
    
mixed <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::left_join(group_affiliation) |>
  tidygraph::mutate(group = ifelse(is.na(group), "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
  ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#FF99C5", alpha = 0.3) +

  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
  #ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = !is.na(group)), color = "white", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 3)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "#F73C95",  "Group B" = "#009BE8", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
  theme_mpxnyc_blank( 
                      ) +
  ggplot2::coord_fixed()



cowplot::plot_grid(mixed, unmixed, rel_widths = c(1,1), nrow = 1)

```

##### Social connectedness

**Proportion in largest connected component**: In a given network, a
connected component is a subset of nodes such that each node in the
subset is reachable from any other node in the subset, and such that
there are no nodes outside the subset which are reachable from a node
inside it. By reachable, we mean possible to reach by tracing a path
from one node to another over existing network ties. Say the size of the
$k^{th}$ connected component is $C_k$. The proportion in the largest
connected component is given by: $$
\theta_p = \frac{\max_k{C_k}}{|\mathscr{N}_p|}
$$

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-20
#| fig-width: 8
#| fig-height: 3.5

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "black"
    focal_color = "black"

connectedness_connected <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::mutate(group = ifelse(runif(n = dplyr::n()) > 0.5, "Group A", "Group B")) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
    ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#C5EFFF") +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE, edge_width = 1) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
  #ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = !is.na(group)), color = "white", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "black",  "Group B" = "black", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(20,20,20,20)
                      ) +
  ggplot2::coord_fixed()




```



```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-21
#| fig-width: 15
#| fig-height: 9

    base_color = grey(0.9,1)
     base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

edge_hidden_data <- data.frame(
  from = c(4,4,6, 2, 3, 6),
  to = c(10, 13, 13, 10, 9, 12),
  hidden = TRUE
)
    
connectedness_disconnected <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::left_join(edge_hidden_data) |>
  tidygraph::mutate(hidden = ifelse(is.na(hidden), FALSE, hidden)) |>
  tidygraph::activate(nodes) |>
  tidygraph::mutate(group = ifelse(runif(n = dplyr::n()) > 0.5, "Group A", "Group B")) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
  ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#C5EFFF") +
  ggplot2::coord_fixed() +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color, filter = !hidden), show.legend = FALSE, edge_width = 1) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
  #ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = !is.na(group)), color = "white", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "black",  "Group B" = "black", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color)  +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(20,20,20,20)
                      ) 



cowplot::plot_grid(connectedness_connected, connectedness_disconnected, rel_widths = c(1,1), nrow = 1)


```

## Dynamics on the network
##### Movement

The **movement matrix** is a square matrix whose $kl^{th}$ entry,
$m(k,l)$, is defined as the count of outings from home in community
district $k$ to a gathering in community district $l$. Say $d^H(i)$ is
the home community district of participant $i$. $$
m(k,l) = \sum_{\begin{aligned}i \in \mathscr{N}_P \\ d^H(i) = k \end{aligned}} \psi (i,l)
$$

##### Spatial concentration

The **spatial concentration proportion** $c(k)$ quantifies the degree to
which a community district is over-represented among destination
community districts compared to home districts in the movement matrix.
It is the difference of the margins of the movement matrix. $$
c(k) = \frac{\sum_l{m(l,k)} - \sum_k{m(l,k)}}{\sum_{l,k}{m(l,k)}}
$$

## Statistical inference

-   The target of inference is the person-place population graph:
    -   $\mathscr{G}^*(\mathscr{N}^*, \mathscr{E}^*, d(.))$
-   Node set is
    -   $\mathscr{N}^* = \mathscr{N}_P^* \cup \mathscr{N}_C$
    -   $|\mathscr{N}_P^*| = n_P^* \rightarrow \infty$
    -   $\mathscr{N}_C = n_C$
-   Homogeneous ego networks
    -   structural equation for adjacency graph is the same for each
        node
    -   gibbs sampler
        -   f(adjacency \| other adjacencies, my data)
        -   f(data \| adjacencies, data
-   Edges are
    -   only between places and people
-   we want a functional of node and edge universe data
    -   But we have a function of node and edge sample data
-   under what condition do we have unbiasedness?
    -   random sample
    -   conditionally random sample
-   Simulated person-place graph
    $\mathscr{G}^*(\mathscr{N}^*, \mathscr{E}^*)$
    -   Nodes $\mathscr{N}^* = \mathscr{N}_P^* \cup \mathscr{N}_C^*$
        -   Place nodes $\mathscr{N}_C^*$: $m$ copies of each element in
            $\mathscr{N}_C$
        -   Person nodes $\mathscr{N}_P^*$: random sample of size
            $m \times |\mathscr{N}_P|$ from $\mathscr{N}_P$ drawn [with
            replacement]{.underline}
        -   Since $\mathscr{N}^*$ is comprised of re-labelled elements
            of $\mathscr{N}$,
            $\exists \phi : \mathscr{N}^* \rightarrow \mathscr{N}$ such
            that $a \in \mathscr{N}^* \implies \phi(a) \in \mathscr{N}$
            (node name mapping)
    -   Edges
        -   for $a, b \in \mathscr{N}^*$:
            $(\phi(a), \phi(b)) \in \mathscr{E} \implies (x, a, b) \in \mathscr{E}^*$
            for some $x \in \mathbf{Z}_+$
-   Remarks:
    -   We can create simulated person graph and simulated place graph
        as bipartite projections of the simulated person-place graph
        since the latter is a bipartite graph
    -   Statistical inference is conducted using the empirical
        distribution for each measure.
        -   The empirical distribution is estimated by calculating each
            measures within strata defined by simulation repetition, and
            summarizing the sample distribution across repetitions
    -   Simulation repetitions each comprise disjoint components of the
        simulted person-place graph

##  {.unnumbered}


::: {#acknowledgements}

[Acknowledgements]{.underline}: The analytic framework for this project
developed over an extended period of time, beginning during my PhD
dissertation at Harvard University under the supervision of Lisa
Berkman, Eric Tchetgen Tchetgen, and a former mentor). In particular,
the analysis borrows from the central paper in my dissertation, which
shows how the wealth of non-coresident extended family members is
protective against mortality.

This work was part of U.S. government-funded research conducted in South
Africa through the HAALSA study, which has since been defunded by the
Trump administration. It is path-breaking because it shows an approach
to using a large scale (over 100,000 people observed over three decades)
dataset as a family network. There are many more datasets that could be
analyzed using these methods. Any investigator who ever hosted a study
at the Agincourt surveillance site in the north-east of South Africa,
for instance, can use these methods to interpret their own data in light
of family networks. It has the potential to illustrate the value of deep
collaboration between U.S. and South African researchers. It is also of
pedagogical value. I wrote the appendices of my dissertation in the same
style as these appendices -- with students and teachers of epidemiology
in mind.

**Unfortunately, my PhD dissertation paper is a hostage of the American
Journal of Epidemiology’s former editor-in-chief, Ichiro Kawachi, who is
a colleague of my former mentor.**

After taking some time away from work to recover from the social
violence I experienced at the hands of my former mentor, I was surprised
to find that the edits that had held up publication of my dissertation
paper (with implications for my ability to get an academic job) were
minor copy edits. The "technical review" itself, which is misleadingly
labelled, was riddled with errors, by the admission of the handling
editor. Many tedious things happened after that, but the result of them
is that the editors of the American Journal of Epidemiology have the
final version of my manuscript, which I copy edited myself after
arranging for the journal to receive thousands of dollars in publication
fees... after spending years conducting the research and months
responding to peer review. I submitted the manuscript by email after the
handling editor agreed to receive it by email.

Mysteriously, the manuscript remains unpublished. Ichiro Kawachi remains
a member of the editorial board of the Journal. The Journal is
associated with the Society of Epidemiologic Research, whose meetings
were an important venue for the development of the SSNAC framework.

**For publication-ready copies of the paper referenced below, which was
accepted on 19 October 2023, please contact the editorial board of the
American Journal of Epidemiology directly. Please share your
correspondence with members of the Society of Epidemiologic Research and
any South African and U.S. researchers you think might have an interest
in seeing the work in print.**

> Makofane, K., Tchetgen Tchetgen, E. J., Bassett, M. T., Berkman, L. F.
> (Accepted 2023, final manuscript submitted January 2025). Networked
> wealth and mortality in the Agincourt Health and Demographic
> Surveillance System 2009 – 2018. *American Journal of Epidemiology*.

:::
