---
editor: 
  markdown: 
    wrap: 72
---



```{r include=FALSE}
targets::tar_source("../R_functions")
```

# SSNAC III: Analysis {#sec-appendix-network-analysis}

::: {#leading}
We describe the main data objects of the MPX NYC study -- the
Person-place graph, the Person graph and the Place graph -- as well as
the statistics we used to analyze them. 

Main idea is: - You have some observational nodes that are people - You have some observational nodes are are places  - People have affiliations with places - Affiliations are unlimited - If a place is a neighborhood, a person node could be affiliated to that place because they have a home there. They could additionally be affiliated to that place because they have attended a gathering there. - If a place is a household, a person could be affiliated to the household because they work in the househodl or because they have a friend there, or because they live there.  - There are quantitative data associated with the people, places and affiliations

      
- Outline of sections
  - Cleanup
    - Check abandoned texts
    - Put outbreak control seciton in abandoned texts
  - Example
  - Data graph 
    - goals:
      - to model correlation between measures made on persons that is induced by joint affiliation with places
      - to express target estimands in terms of model quantities 
      - to specify estimators for those estimands based on sample data
    - definitions
      - person-place graph: a bipartite graph whose two node classes are places and persons
        - Nodes
          - places are a fixed, fully observed set of spatial units
          - persons are a countable set of observational units 
          - each node is associated with node characteristics 
          - Node characteristics
            - $\mathbf{C}_k$ random vector
            - $C_{k}(i)$ random scalar
            - $\mathbf{c}_k$ vector realization
            - $c_{k}(i)$ scalar realization
        - Edges
          - persons' affiliations with places are indicated using edges
          - each edge is associated with edge characteristics
          - Edge characteristics
            - $\mathbf{D}_k$  $n \times n$ random matrix
            - $D_{k}(i,j)$ $ij$th entry of random matrix
            - $\mathbf{d}_k$  $n \times n$ matrix realization
            - $d_{k}(i,j)$ scalar relization
            - $\mathbf{\Psi}_k$  is a speical case of $\mathbf{D}_k$
  - Node characteristics
    - Descriptive statistics
  - Edge characteristics
    - Descriptive statistics
  - Local structure
    - Spatial reach
    - Social reach
    - Spatial catchment
    - Social catchment
  - Global structure
    - Spatial mixing
    - Social connectedness
  - Dynamics
    - Outings
    - Spatial concentration
  - Statistical inference
    - Rather than star with an idea of the sampling universe, we will define sample statistics that are substantively interpretable 
    - We will then extend our definitions of these to:
      - Define a notion of the population parameter vs. the sample statistic  
      - Ask whether the sample statistics are unbiased with respect to the population parameters  
      - Ask how far the sample statistics are from the population parameter as a function of sample size?
      
:::

::: {#acknowledgements}
[Lead author]{.underline}: Keletso Makofane, MPH, PhD.
[Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).

[Acknowledgements]{.underline}: The analytic framework for this project
developed over an extended period of time, beginning during my PhD
dissertation at Harvard University under the supervision of Lisa
Berkman, Eric Tchetgen Tchetgen, and a former mentor). In particular,
the analysis borrows from the central paper in my dissertation, which
shows how the wealth of non-coresident extended family members is
protective against mortality...(continued at bottom of page)
:::

```{r}
#| fig-width: 3
#| fig-height: 3
#| fig-align: center


plot_icon(icon_name = "devil", color = "light_purple", shape = 16, alpha = 0,  size = 100, image_size = 0.2)

```



## Example: Rapid research response

-   you are town epidemiologist live in a town of 8000 people who live and work across 5 communities within the town

-   There is news of a novel human transmitted infection coming to the town

-   You decide to map the spatial and sexual networks of the towns peopple to prepare for a response to the new infection

- You take a random sample of 8 townspeople to conduct survey research.

- Participants are selected independently of each other and all invited participants accepted the invitation




```{r}
#| label: tbl-example-person-place-network
#| layout-ncol: 2
#| tbl-cap: "Sample person-place network data"
#| tbl-subcap:
#|  - "Nodes"
#|  - "Edges"

make_example_network_data() |>
  data.frame() |>
  dplyr::select(-label) |>
  dplyr::select(-type) |>
  gt::gt() |>
  gt::tab_options(table.font.size =12, data_row.padding = gt::px(1))


make_example_network_data() |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(From = from_name, To = to_name, Relation = relation) |>
  gt::gt() |>
  gt::tab_options(table.font.size =12, data_row.padding = gt::px(1))

```


```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-person-place-network
#| fig-width: 6
#| fig-height: 5.5


make_example_network_data("bipartite") |>
  plot_example_bipartite_network(label_size = 0) +
  scale_color_mpxnyc(name = "Node type", option = "dark") +
  ggplot2::labs(fill = "Node type") +
  ggplot2::scale_size_manual(name = "Node type", values = c(7,12)) +
  theme_mpxnyc_blank( 
    plot.margin = ggplot2::margin(40,50,40,50),
    legend.position = "bottom"
    ) 



```

@fig-example-person-place-network shows a simplified data graph.
Community district nodes are shown in blue and survey participant nodes
in pink. Each edge connects one community district with one survey
participant. Three kinds of edges are shown – those that indicate either
that the survey participant has a home in the community district, or
that they attended a gathering sexual contact or attended a gathering
without sexual contact in the community district. For instance,
*Participant 3* has a home in *Community District B*, he attended a
gathering with no sexual contact in *Community District A*, and he
attended two gathering (one sexual and one non-sexual) in *Community
District E*.



## Individual characteristics


We can examine patterns in the characteristics of participants. These include variables like age and vaccination status. They could also include relations indivdiuals have with places, as long as each person is assigned to one place. In our example, each participant has only one primary residence, and therefore is related to only one of the five communities in this city. 

```{r}
#| label: tbl-example-spatial-reach
#| layout-ncol: 2
#| tbl-cap: "Sample person-place network data"
#| tbl-subcap:
#|  - "Nodes"
#|  - "Edges"

make_example_network_data() |>
  data.frame() |>
  dplyr::select(-label) |>
  dplyr::filter(type == "Person") |>
  dplyr::select(-type) |>
  gt::gt() |>
  gt::tab_options(table.font.size =12, data_row.padding = gt::px(1))


make_example_network_data() |>
  dplyr::mutate(name = label, type, age) |>
  tidygraph::activate(edges) |>
  dplyr::mutate(from_name = tidygraph::.N()$name[from], to_name = tidygraph::.N()$name[to]) |>
  data.frame() |>
  dplyr::arrange(from, to) |>
  dplyr::transmute(From = from_name, To = to_name, Relation = relation) |>
  dplyr::filter(Relation == "HOME") |>
  gt::gt() |>
  gt::tab_options(table.font.size =12, data_row.padding = gt::px(1))
```






## Local structure

Examine patterns in the characteristics of the participant along with the places he is related to. We can also examine patterns in the characteristics of places in the context of the people those places are related to. In brief, examining local structure entails understanding how each node is related to the rest of the graph. We define spatial reach, social reach, spatial catchment, and social catchment. 



##### Spatial reach

Spatial reach is a person-node characteristic. It measures the number of relations to places the participant has. Note that we count relations and not places since one participant might have several relations with the same place.  

```{r}
#| fig-width: 8
#| fig-height: 5
#| label: fig-example-spatial-reach


make_reach_diagram_data <- function(
                                    focal_node = "Person 6", 
                                    intermediate_nodes = c(),
                                    alter_nodes = c("Community d", "Community e")
) {
  make_example_network_data("bipartite") |>
    tidygraph::mutate(type_color = ifelse(name == focal_node, "Focal node", ifelse(name %in% alter_nodes, "Reached nodes", ifelse(name %in% intermediate_nodes, "Intermediate nodes", NA)))) |>
  tidygraph::activate(edges) |>
  tidygraph::mutate(type_color = NA) 
}

plot_reach_diagram <- function(
    reach_diagram_data,
    base_color = grey(0.9,1), 
    reached_color = "#009BE8", 
    intermediate_color = "#C5EFFF",
    focal_color = "black"
    ){
  
  reach_diagram_data |>
  ggraph::ggraph(layout = "kk") +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
  ggraph::geom_node_point(ggplot2::aes( size = type), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = type_color, size = type)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = type, filter = !is.na(type_color)), color = "white", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c("Focal node" = focal_color, "Reached nodes" = reached_color, "Intermediate nodes" = intermediate_color), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color)
}



make_reach_diagram_data() |>
  plot_reach_diagram() +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 

```





**Spatial reach of person** $i$ is the number of relations person node
$i$ has with place nodes in the person-place graph. Let $\psi(i,j)$ be
the number of edges connecting person $i$ and place $j$ in the
person-place graph. Then:

$$
R_{i} = \sum_{ j }{ \Psi (i,j)}
$$

##### Social reach

Social reach is a person-node characteristic which measures the potential for interaction with other people through shared relations to places. It counts the number of minimal paths that link the focal node with other person nodes in the graph. Note that the number of paths that link two person nodes who are connected through a given place node is the product of the number of relations each person node has with the given place node.

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-social-reach
#| fig-width: 8
#| fig-height: 5


make_reach_diagram_data(
                        alter_nodes = c("Person 8", "Person 4", "Person 3"), 
                        intermediate_nodes = c("Community d", "Community e")
                        ) |>
  plot_reach_diagram(reached_color = "#F73C95", intermediate_color = "darkgrey") +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```



**Social reach of person** $i$ among subgroup $A$ is the number of
person nodes in set $A \subset \mathscr{N}_P$ that are connected to
person node $i$ through shared places. i.e. either because both nodes
have a residence or gathering in at least one common community district.
**Social reach of person** $i$ is defined as
$R_{i} = R_{i\rightarrow \mathscr{N}_P}$

$$
R_{i\rightarrow A} = \sum_{j}{\sum_{k }{ \Psi(i,j) {\Psi(k,j)} A_k}}  
$$

##### Social catchment

Social catchment is a place-node characteristic which measures the number of relations with person nodes. 

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-social-catchment
#| fig-width: 8
#| fig-height: 5




make_reach_diagram_data(focal_node = "Community c", alter_nodes = c("Person 8", "Person 4", "Person 7", "Person 5")) |>
  plot_reach_diagram(reached_color = "#F73C95") +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```

**Social catchment of place** $j$ among subgroup $A$ is defined as the
number of connections the focal community district has with participants
who belong to subgroup $A \subset \mathscr{N}_P$. **Social catchment of
place** $j$ is defined as $r_{j} = r_{j\rightarrow \mathscr{N}_P}$

$$
r_{j\rightarrow A} = \sum_{i } { \Psi (i, j) A_i}
$$

##### Spatial catchment

Spatia catchment is a place-node characteristic which measures the mutual influence between spatial untis as a result of relations with shared person nodes. It counts the number of minimal paths that link the focal node with other place nodes in the graph. Note that the number of paths that link two place nodes who are connected through a given person node is the product of the number of relations each place node has with the given person node.


```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-spatial-catchment
#| fig-width: 8
#| fig-height: 5



make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  plot_reach_diagram(
   intermediate_color = "darkgrey"
  ) +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(40,20,40,20),
                      legend.position = "right"
                      ) 




```

**Spatial catchment of place** $j$ via subgroup $A$ is defined as the
strength of connection between place node $j$ and other place nodes in
the graph when we consider their shared relations with person nodes in
subgroup $A$. Strength of connection between two places $j$ and $k$ is
defined as the number of relations place nodes $j$ and $k$ have with
common person nodes which belong to subset $A$. The **spatial catchment
of place** $j$ is defined as $r_{i\rightarrow \mathscr{N}_P} = r_{i}$

$$
r_{j\rightarrow A} = \sum_{i }\sum_{k }{ \Psi(i,j) \Psi(i,k)A_i} \\
$$


## Global structure

Measures of global structure quantify some aspect of the overall pattern of connection among the people and spaces connected by the data graph. 



##### Spatial mixing

Spatial mixing is the extent to which person nodes with a given set of characteristics are connected to a common set of place nodes with person nodes with some other set of characteristics. 

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-5
#| fig-width: 3
#| fig-height: 3

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

        group_affiliation <- data.frame(
      name = c(paste("Person", 1:8)),
      group = c(
                "Group B", 
                "Group A", 
                "Group A", 
                "Group B", 
                "Group A", 
                "Group B", 
                "Group B", 
                "Group A"
                )
    )
    
unmixed <- make_reach_diagram_data() |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::left_join(group_affiliation) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
    ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#FF99C5", alpha = 0.3) +
                  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
                  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
                  ggraph::geom_node_point(ggplot2::aes(color = age, size = group)) +
                  ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = type == "Place"), color = "#FF99C5", show.legend = FALSE) +
                  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12), guide = "none") +
                scale_color_mpxnyc( name = "Age", option = "manual", na.value = base_color, values = c( "18-25" = "#F73C95",  "26-50" = "#009BE8", "Place" = "black"), na.translate = FALSE) +
                  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
                  theme_mpxnyc_blank( legend.position = "bottom"
                                      ) +
  ggplot2::coord_fixed()




```

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-6
#| fig-width: 15
#| fig-height: 9

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

    
    group_affiliation <- data.frame(
      name = c(paste("Person", 1:8)),
      group = c("Group B", "Group B", "Group B", "Group B", "Group A", "Group A", "Group A", "Group A")
    )
    
mixed <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::left_join(group_affiliation) |>
  tidygraph::mutate(group = ifelse(is.na(group), "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
  ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#FF99C5", alpha = 0.3) +

  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = vax, size = group)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = type == "Place"), color = "#FF99C5", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12), guide = "none") +
scale_color_mpxnyc(name = "Vax", option = "manual", na.value = base_color, values = c( "No" = "#F73C95",  "Yes" = "#009BE8", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
  theme_mpxnyc_blank( legend.position = "bottom"
                      ) +
  ggplot2::coord_fixed() 


cowplot::plot_grid(mixed, unmixed, rel_widths = c(1,1), nrow = 1)

```

We define **preference** of person $i$ for group \$ B
\subset \mathscr{N}\_p\$) as the proportion of alters from group B among
all alters

$$
P_{A \rightarrow B} = \sum_i {\frac{ R_{i \rightarrow B}}{R_i}} 
$$


$$
P_{A \rightarrow B} = \frac{1}{E[B_i]} \sum_i E[{\frac{ R_{i \rightarrow B}}{R_i}} |A_i = 1]
$$

The **spatial mixing coefficient from A to B** quantifies the degree to
which egos in group A preferentially live in or attend gatherings in
community districts they are likely to encounter members of group B. It
is defined as the ratio of preference to prevalence minus one.

$$
P_{A \rightarrow B} = \frac{n_p}{n_A n_B} \sum_{i } A_i {\frac{ R_{i \rightarrow B}}{R_i}} - 1
$$



##### Social connectedness

Social connectedness is the extent to which all the person nodes are connected through a common set of space nodes. Equivalently, it is the extent to which space nodes are connected through a common set of person nodes. 

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-20
#| fig-width: 8
#| fig-height: 3.5

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "black"
    focal_color = "black"

connectedness_connected <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::mutate(group = ifelse(runif(n = dplyr::n()) > 0.5, "Group A", "Group B")) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
    ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#C5EFFF") +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE, edge_width = 1) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = group,filter = type == "Place"), color = "#C5EFFF", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "black",  "Group B" = "black", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(20,20,20,20)
                      ) +
  ggplot2::coord_fixed()




```

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-21
#| fig-width: 15
#| fig-height: 9

    base_color = grey(0.9,1)
     base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

edge_hidden_data <- data.frame(
  from = c(4,4,6, 2, 3, 6),
  to = c(10, 13, 13, 10, 9, 12),
  hidden = TRUE
)
    
connectedness_disconnected <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::left_join(edge_hidden_data) |>
  tidygraph::mutate(hidden = ifelse(is.na(hidden), FALSE, hidden)) |>
  tidygraph::activate(nodes) |>
  tidygraph::mutate(group = ifelse(runif(n = dplyr::n()) > 0.5, "Group A", "Group B")) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
  ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#C5EFFF") +
  ggplot2::coord_fixed() +
  ggraph::geom_edge_fan(ggplot2::aes(color = type_color, filter = !hidden), show.legend = FALSE, edge_width = 1) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = group, size = group)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = type == "Place"), color = "#C5EFFF", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12)) +
scale_color_mpxnyc(name = "Color", option = "manual", na.value = base_color, values = c( "Group A" = "black",  "Group B" = "black", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color)  +
  theme_mpxnyc_blank( 
                      plot.margin     = ggplot2::margin(20,20,20,20)
                      ) 



cowplot::plot_grid(connectedness_connected, connectedness_disconnected, rel_widths = c(1,1), nrow = 1)


```

**Proportion in largest connected component**: In a given network, a
connected component is a subset of nodes such that each node in the
subset is reachable from any other node in the subset, and such that
there are no nodes outside the subset which are reachable from a node
inside it. By reachable, we mean possible to reach by tracing a path
from one node to another over existing network ties. Say the size of the
$k^{th}$ connected component is $C_k$. The proportion in the largest
connected component is given by:

$$
\pi_Q = \frac{\max_k{Q_k}}{n_P}
$$

## Dynamics

In studies which elicit participants' primary residence along with other places they are related to, it may be of interest to understand the pattern of movement from home to related places and back again. 

##### Return journeys

The **movement matrix** is a square matrix whose $kl^{th}$ entry,
$m(k,l)$, is defined as the count of outings from home in community
district $k$ to a gathering in community district $l$. Say $d^H(i)$ is
the home community district of participant $i$. 




$$
m(j,k) = \sum_i D(i,j) \sum_{k }( \Psi(i,k) - D(i,k) )
$$



##### Spatial concentration

The **spatial concentration proportion** $c(k)$ quantifies the degree to
which a community district is over-represented among destination
community districts compared to home districts in the movement matrix.
It is the difference of the margins of the movement matrix. 

$$
c(k) = \frac{\sum_l{m(l,k)} - \sum_k{m(l,k)}}{\sum_{l,k}{m(l,k)}}
$$

##### Vaccination



## Statistical inference

- Data are a realization of law $C_t \in M_{n\times 1}$, $\Psi_t \in M_{n\times n}$, and $Q_t \in M_{n^2 \times 1}$ for $t \in [1,k]$, $k \in \mathbf{Z}$ and arbitrarily large $n \in \mathbf{Z}$
- Goal is to infer population parameters using a sample.
  - We begin by defining a variable $\mathbf{s} \in M_{n\times 1}$ such that $s_i$, the selection indicator for $i^{th}$ observational unit is one when that unit is included in the sample, and zero otherwise
    - We make independence and homogeneity assumptions 
    - We make assumptions about the determinants of $\mathbf{s}$
  -  we only see this when $s_i = 1$: $C_{ti}$ 
  - we only see this when $s_i = 1$ and $s_j = 1$ : $\Psi(i,j)$ 
    
- Queston for the researcher:
  - Are there estimators that you want to prioritize showing? A class? A specific measure?
  - Are you willing to read non-parametric efficiency theory to write this section?
  - With that in mind, how much effort should you spend on the statistical inference section?
  - What will the statistical inference section buy the reader?
  - General enough to cover and extend dissertation household setup?
  - Can i trust proportion of edge characteristic d?
  
- We are interested in population quantities:

  - Node characteristics $m(C, \theta)$ 
  
  - Edge characteristics $m(Q, \theta)$
  
  - Edge formation process $m(\Psi, \theta)$
  
  - Combinations of characteristics $m(C, Q, \Psi, \theta)$
  
- We estimate these based on a random sample of person nodes

  - Node characteristics $m(\hat C, \theta)$ 
  
  - Edge characteristics $m(\hat Q, \theta)$
  
  - Edge formation process $m(\hat \Psi, \theta)$
  
  - Combinations of characteristics $m(\hat C, \hat Q, \hat \Psi, \theta)$

- We estabilsh assumptions for:

  - unbiasedness of estimators
  
  - efficiency bounds

  
- We use the bootstrap to estimate the standard error and use these to estimate confidence intervals


  

##  {.unnumbered}

::: {#acknowledgements}

[Acknowledgements]{.underline}: The analytic framework for this project
developed over an extended period of time, beginning during my PhD
dissertation at Harvard University under the supervision of Lisa
Berkman, Eric Tchetgen Tchetgen, and a former mentor). In particular,
the analysis borrows from the central paper in my dissertation, which
shows how the wealth of non-coresident extended family members is
protective against mortality.

This work was part of U.S. government-funded research conducted in South
Africa through the HAALSA study, which has since been defunded by the
Trump administration. It is path-breaking because it shows an approach
to using a large scale (over 100,000 people observed over three decades)
dataset as a family network. There are many more datasets that could be
analyzed using these methods. Any investigator who ever hosted a study
at the Agincourt surveillance site in the north-east of South Africa,
for instance, can use these methods to interpret their own data in light
of family networks. It has the potential to illustrate the value of deep
collaboration between U.S. and South African researchers. It is also of
pedagogical value. I wrote the appendices of my dissertation in the same
style as these appendices -- with students and teachers of epidemiology
in mind.

**Unfortunately, my PhD dissertation paper is a hostage of the American
Journal of Epidemiology’s former editor-in-chief, Ichiro Kawachi, who is
a colleague of my former mentor.**

After taking some time away from work to recover from the social
violence I experienced at the hands of my former mentor, I was surprised
to find that the edits that had held up publication of my dissertation
paper (with implications for my ability to get an academic job) were
minor copy edits. The "technical review" itself, which is misleadingly
labelled, was riddled with errors, by the admission of the handling
editor. Many tedious things happened after that, but the result of them
is that the editors of the American Journal of Epidemiology have the
final version of my manuscript, which I copy edited myself after
arranging for the journal to receive thousands of dollars in publication
fees... after spending years conducting the research and months
responding to peer review. I submitted the manuscript by email after the
handling editor agreed to receive it by email.

Mysteriously, the manuscript remains unpublished. Ichiro Kawachi remains
a member of the editorial board of the Journal. The Journal is
associated with the Society of Epidemiologic Research, whose meetings
were an important venue for the development of the SSNAC framework.

**For publication-ready copies of the paper referenced below, which was
accepted on 19 October 2023, please contact the editorial board of the
American Journal of Epidemiology directly. Please share your
correspondence with members of the Society of Epidemiologic Research and
any South African and U.S. researchers you think might have an interest
in seeing the work in print.**

> Makofane, K., Tchetgen Tchetgen, E. J., Bassett, M. T., Berkman, L. F.
> (Accepted 2023, final manuscript submitted January 2025). Networked
> wealth and mortality in the Agincourt Health and Demographic
> Surveillance System 2009 – 2018. *American Journal of Epidemiology*.

:::
