##### Spatial mixing

Spatial mixing is the extent to which person nodes with a given set of characteristics are connected to a common set of place nodes with person nodes with some other set of characteristics. 

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-5
#| fig-width: 3
#| fig-height: 3

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

        group_affiliation <- data.frame(
      name = c(paste("Person", 1:8)),
      group = c(
                "Group B", 
                "Group A", 
                "Group A", 
                "Group B", 
                "Group A", 
                "Group B", 
                "Group B", 
                "Group A"
                )
    )
    
unmixed <- make_reach_diagram_data() |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::left_join(group_affiliation) |>
  tidygraph::mutate(group = ifelse(type == "Place", "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
    ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#FF99C5", alpha = 0.3) +
                  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
                  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
                  ggraph::geom_node_point(ggplot2::aes(color = age, size = group)) +
                  ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = type == "Place"), color = "#FF99C5", show.legend = FALSE) +
                  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12), guide = "none") +
                scale_color_mpxnyc( name = "Age", option = "manual", na.value = base_color, values = c( "18-25" = "#F73C95",  "26-50" = "#009BE8", "Place" = "black"), na.translate = FALSE) +
                  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
                  theme_mpxnyc_blank( legend.position = "bottom"
                                      ) +
  ggplot2::coord_fixed() +
  ggplot2::theme(
    legend.text = ggplot2::element_text(size = 20),
    legend.title = ggplot2::element_text(size = 20),
    legend.ticks = ggplot2::element_line(size = 20),
    legend.byrow = TRUE,
    legend.position = "right"
  ) +
  ggplot2::guides(color = ggplot2::guide_legend(override.aes = list(size = 5))) # Adjust legend dot size





```

```{r}
#| fig-cap: Sample person-place network visualization
#| label: fig-example-participant-place-6
#| fig-width: 15
#| fig-height: 9

    base_color = "black"
    reached_color = "#009BE8"
    intermediate_color = "#C5EFFF"
    focal_color = "black"

    
    group_affiliation <- data.frame(
      name = c(paste("Person", 1:8)),
      group = c("Group B", "Group B", "Group B", "Group B", "Group A", "Group A", "Group A", "Group A")
    )
    
mixed <- make_reach_diagram_data(
  focal_node = "Community c", 
  alter_nodes = c("Community d", "Community b", "Community e"),
  intermediate_nodes = c("Person 8", "Person 4")
  ) |> 
  tidygraph::mutate(type_color = NA) |>
  tidygraph::activate(nodes) |>
  tidygraph::left_join(group_affiliation) |>
  tidygraph::mutate(group = ifelse(is.na(group), "Place", group)) |>
  ggraph::ggraph(layout = "kk") +
  ggforce::geom_circle(ggplot2::aes(x0 = 0.5, y0 = 0, r = 2.3), data = data.frame(xmin = -3, xmax = 3, ymin = -1, ymax = 5), linewidth = 0, fill = "#FF99C5", alpha = 0.3) +

  ggraph::geom_edge_fan(ggplot2::aes(color = type_color), show.legend = FALSE) +
  ggraph::geom_node_point(ggplot2::aes( size = group), color = base_color) +
  ggraph::geom_node_point(ggplot2::aes(color = vax, size = group)) +
  ggraph::geom_node_text(ggplot2::aes(label = label, size = group, filter = type == "Place"), color = "#FF99C5", show.legend = FALSE) +
  ggplot2::scale_size_manual(name = "Size", values = c(7,7, 12), guide = "none") +
scale_color_mpxnyc(name = "Vax", option = "manual", na.value = base_color, values = c( "No" = "#F73C95",  "Yes" = "#009BE8", "Place" = "black"), na.translate = FALSE) +
  ggraph::scale_edge_color_manual(values = c("black"), na.value = base_color) +
  theme_mpxnyc_blank( legend.position = "bottom"
                      ) +
  ggplot2::coord_fixed() +
  ggplot2::theme(
    legend.text = ggplot2::element_text(size = 20),
    legend.title = ggplot2::element_text(size = 20),
    legend.ticks = ggplot2::element_line(size = 20),
    legend.byrow = FALSE,
    legend.position = "right"
  ) +
  ggplot2::guides(color = ggplot2::guide_legend(override.aes = list(size = 5, ncol = 1))) # Adjust legend dot size


cowplot::plot_grid(mixed, unmixed, rel_widths = c(1,1), nrow = 1)

```



The spatial mixing coefficient from A to B quantifies the degree to
which egos in group A preferentially live in or attend gatherings in
community districts they are likely to encounter members of group B. 

We define **preference** of group A for group B (for $A, B \subset \mathscr{N}_p$) as the average proportion of alters from group B among egos from group A.

$$
\Phi(A,B) = \frac{1}{|A|}\sum_{i \in A}{\frac{ R_{i \rightarrow B}}{R_i}}
$$

The **prevalence** of group B is the size of the group divided by the total number of participants.

$$
 \frac{|B|}{|\mathscr{N}_p|}
$$

The **spatial mixing coefficient** is the ratio of preference to prevalence minus one. 

$$
\phi(A,B) = \frac{|\mathscr{N}_p|}{|B|} \Phi(A,B) - 1
$$



