

### Stochastic Network FFRCISTG model{.unnumbered}

As we see in @fig-homogenous-dag, causal DAGs become quickly visually cluttered, and therefore unwieldy, once we start depicting causal systems with multiple observational units. If we added a fourth observational unit to @fig-homogenous-dag, it would be nearly impossible to see which arrow connects which nodes. This is an important limitation because one of the most useful things about causal DAGs is that they allow the observational epidemiologist to reason graphically about the structure of confounding and selection.




#### Introducing the Causal Directed Acyclic Network Graph (DANG)

::: {#def-dang .theorem}
# Causal Directed Acyclic Network Graph

- A DANG is a DAG expressed in terms of the whole vector of observations
- Associated with a graph
- Interference according to the graph
:::


We introduce the causal Directed Acyclic Network Graph (causal DANG) - a simple extension of the DAG that allows for the representation of complex causal systems. Like the causal DAG, the causal DANG encodes a non-parametric structural equation model.



*Compact graphic representation*

DANGs encode the structure of the causal process within individuals separately from the structure of the causal process across individuals. The former is termed the "structural part" of the DANG and the latter the "relational part." The relational part shows which pairs of observational units have correlated measures with each other. For instance, in @fig-causal-dang-instructions we see that individuals 1 and 2 are related.

The structural part is a DAG of vector-valued variables $\mathbf{L}$, $\mathbf{A}$, and $\mathbf{Y}$ of length equal to the number of people in the sample. It has standard interpretation under d-separation rules. It gives the conditional independencies across these vector-valued random variables. 



```{r}
#| fig-height: 8
#| fig-width: 5
#| label: fig-causal-dang-instructions
#| fig-cap: Causal DANG

structural <- example_dang_1_structural() |>
                    plot_swig(node_radius = 0.2) +
                    scale_fill_mpxnyc(option = "light") +
                    theme_mpxnyc_blank()+
                    ggplot2::ggtitle("Structural Part") 

relational <- example_dang_1_relational() |>
                    plot_swig(0, 0, node_radius = 0.2)  +
                    scale_fill_mpxnyc(name = "Entity type", option = "light") +
                    theme_mpxnyc_blank() +
                    ggplot2::ggtitle("Relational Part") 

cowplot::plot_grid(structural, relational, ncol = 1)

```

*Multiple entity types*

The causal DANG relaxes the assumption that all measures in the causal system can be grouped into non-overlapping sets (i.e. that each measure can be attributed to an individual in the sample). In this framework, different types of entities, represented by vectors of different lengths, can be depicted on the same DANG.

The causal DANG shown in @fig-example-dang-structural represents the first week of the campaign mentioned in Example 3. Let $\mathbf{T}$ be a $3\times1$ vector whose entries $T_j$ are 1 if neighborhood $j$ is to be vaccinated and $0$ otherwise. $\mathbf{M}$ is a $5\times1$ vector whose entries $M_i$ indicate whether the $i^{\text{th}}$ person received a vaccination campaign message or not. $\mathbf{V}$ is a $5\times1$ vector whose entries $V_i$ show whether participant $i$ is vaccinated or not.

```{r}
#| fig-height: 6
#| fig-width: 8
#| fig-align: center
#| label: fig-example-dang-structural
#| fig-cap: "Causal DANG for Week 1 in Example 3"


structural  <- example_dang_2_structural() |>
                    plot_swig(node_radius = 0.15) +
                    scale_fill_mpxnyc(option = "light") +
                    theme_mpxnyc_blank() +
                    ggplot2::ggtitle("Structural Part")


relational  <- example_dang_2_relational() |>
                    plot_swig(node_radius = 0.2, node_margin = 0)  +
                    scale_fill_mpxnyc(name = "Entity type", option = "light") +
                    theme_mpxnyc_blank() +
                    ggplot2::ggtitle("Relational Part") 

figure   <- cowplot::plot_grid(structural, relational, ncol=1, rel_heights = c(3,3))



legend_pre  <- relational + ggplot2::theme(legend.position = "right")

legend      <- cowplot::get_legend(legend_pre) 
 
   
cowplot::plot_grid(figure, legend, nrow = 1, rel_widths = c(4,1))
```

*Stochastic edges*


Random edges 







#### Introducing the Single World Intervention Network Graph (SWING)


::: {#def-swing .theorem}
# Single World Intervention Network Graph

- A SWING is a DAG with node splitting
- A SWING is a SWIG at the level of whole vector of observations
:::

We introduce the Single World Intervention Network Graph (SWING) - a simple extension of the SWIG that allows for the representation of the counterfactual outcomes of interventions in complex causal systems.

The SWING has two parts: a structural part and a relational part. Like the causal DANG, the SWING represents vector-valued random variables (rather than scalars) as nodes. Like the SWIG, the SWING splits the nodes that are to be intervened upon by the experimenter. @fig-example-swig-structural shows the counterfactual distribution of the variables in the model under an intervention setting $\mathbf{T}$ to the value $\mathbf{t}$.

```{r}
#| fig-height: 6
#| fig-width: 8
#| fig-align: center
#| label: fig-example-swig-structural
#| fig-cap: "SWING for Week 1 in Example 3"
#| 


structural  <- example_swing_structural() |>
                    plot_swig(node_radius = 0.15) +
                    scale_fill_mpxnyc(option = "light") +
                    theme_mpxnyc_blank() +
                    ggplot2::ggtitle("Structural Part") 


relational  <- example_swing_relational() |>
                    plot_swig(node_radius = 0.2, node_margin = 0)  +
                    scale_fill_mpxnyc(name = "Entity type", option = "light") +
                    ggplot2::theme(legend.position = "right") +
                    theme_mpxnyc_blank() +
                    ggplot2::ggtitle("Relational Part")


legend_pre  <- relational +
                    ggplot2::theme(legend.position = "right")
legend      <- cowplot::get_legend(legend_pre) 



figure   <- cowplot::plot_grid(structural, relational, ncol=1, rel_heights = c(3,3))

cowplot::plot_grid(figure, legend, nrow = 1, rel_widths = c(4,1))

```

#### Incorporating networks 




::: {#def-snffrcistg}
# Stochastic Network FFRCISTG model

- The SNFFRCISTG is a generalization of a NFFRCISTG 
- Expressed in terms of whole sample vector rather than observation scalar
- Graph is stochastic with:
  - Random nodes: a set of nodes, each representing an observational unit in a random sample
  - Random edges: a set of edges, each representing a relation between a random node and fixed node 
- Each node is associated with a data record
- Eacch edge is associated with a data record
:::


::: {#def-snffrcistg}
# Social and Spatial Stochastic Network FFRCISTG model

- The SaSSNFFRCISTG is a submodel of a SNFFRCISTG 
- Graph is stochastic and bipartite with:
  - Fixed nodes: a set of nodes representing a set of fixed and known entities
  - Random nodes: a set of nodes, each representing an observational unit in a random sample
  - Random edges: a set of edges, each representing a relation between a random node and fixed node 
- Each node is associated with a data record
- Eacch edge is associated with a data record
:::






$$
\begin{aligned}
\mathbf{\mathbf{\Psi}} &= f_{\mathbf{\Psi}}(\mathbf{U}_{\mathbf{\Psi}}) \\
\mathbf{T} &= f_{\mathbf{T}}(\mathbf{U}_{\mathbf{T}}, \mathbf{\mathbf{\Psi}} ) \\
\mathbf{M} &= f_{\mathbf{M}}(\mathbf{U}_{\mathbf{M}}, \mathbf{\mathbf{\Psi}},\mathbf{T} ) \\
\mathbf{V} &= f_{\mathbf{V}}(\mathbf{U}_{\mathbf{V}}, \mathbf{\mathbf{\Psi}},\mathbf{T}, \mathbf{M} ) \\
\end{aligned}
$$ {#eq-nffrcistg}

