---
editor: 
  markdown: 
    wrap: 72
---

```{r  include=FALSE}
targets::tar_source("../R_functions")
```

# SSNAC II: Causality {#sec-causal-interpretation}

::: {#leading}
We summarize the leading approach to causal inference in epidemiologic
studies, extending that approach to accommodate data which are
characterized by complex patterns of interdependence.
:::

::: {#notes .notes}
Outline

-   Classic causal inference

    -   Intro to example

        -   job status, formal dress, job offers

    -   Intro to DAGs and NPSEM-IEs

    -   Worked example

        -   Intervention

        -   Assumptions

        -   Structural equations

        -   Estimands

        -   Identification

    -   The FFRCISTG model

        -   Statistical model

            -   A set of NPSEM-IE that represents a causal system under

                -   observation (no-intervention)

                -   node- or edge-level intervention A

                -   node- or edge-level intervention B

            -   A set of target estimands

            -   An identification strategy

        -   Assumptions

            -   Measures can be grouped into observational units

            -   No spillover

            -   No interference

            -   Observational units arise from a common statistical
                distribution

-   Network causal inference

    -   Intro to example

        -   Marriage, job status, formal dress, job offers

    -   Worked example

        -   Intervention

        -   Assumptions

        -   Structural equations

        -   Estimands

        -   Identification

    -   NFFRCISTG definition

        -   Causal model

            -   A graph representing a causal system with interrelated
                measures

            -   An NPSEM-IE that represents a causal system under no
                intervention

            -   A set of modified NPSEM-IEs that represent the causal
                system under different interventions

            -   A set of target estimands

            -   An identification strategy

        -   Assumptions

            -   Measures grouped into observational units

            -   Contemporaneous measures are conditionally independent
                given prior measures

            -   Measures are correlated across observational units
                according to a graph

            -   Groups of measures denoted as observational units arise
                from a common statistical model. This model exhibits

                -   separability

                -   loyalty to graph

                -   positional invariance

                -   boundedness

    -   Introducing DANGs and SWINGs

-   Stochastic network causal inference

    -   Intro to example

        -   Vaccination campaign

        -   Three weeks

        -   New membership every week

    -   Worked example

        -   Intervention

            -   Vaccination of places

        -   Assumptions

        -   Structural equations

        -   Estimands

        -   Identification

    -   SNFFRCISTG definition

        -   Causal model

            -   An NPSEM-IE that represents a causal system under no
                intervention

            -   A set of modified NPSEM-IEs that represent the causal
                system under different interventions

            -   A set of target estimands

            -   An identification strategy

        -   Assumptions

            -   Measures grouped into observational units

            -   Contemporaneous measures are conditionally independent
                given prior measures

            -   Measures are correlated across observational units
                according to a graph

            -   Groups of measures denoted as observational units arise
                from a common statistical model. This model exhibits

                -   separability

                -   loyalty to graph

                -   positional invariance

                -   boundedness

-   Additional notes

    -   D-separation
:::

<div>

[Acknowledgements]{.underline}: The statistical framework for SSNAC was
first presented at the Society for Epidemiologic Research Meeting
(Boston, June 2025) at a workshop titled "Single World Intervention
Graphs (SWIGs) for the practicing epidemiologist" organized and taught
by Aaron Sarvet (University of Massachusetts), Mats J. Stensrud (École
polytechnique fédérale de Lausanne), and Kerollos Wanis (University of
Texas), and also taught by Keletso Makofane (Ctrl+F), James M. Robins
(Harvard University), and Thomas Richardson (University of Washington).

[Lead author]{.underline}: Keletso Makofane, MPH, PhD.
[Editor]{.underline}: Nicholas Diamond, MPH. (Published: June 2025).

</div>

```{r}
#| fig-width: 2
#| fig-height: 2
#| fig-align: center


plot_icon(icon_name = "droplets", color = "dark_purple", shape = 0)

```

{{< include B_0__preface.qmd >}}
{{< include B_1__classical_causal_inference.qmd >}}
{{< include B_2__network_causal_inference.qmd >}}
{{< include B_3__ssnac.qmd >}}
