
##### DAGs and SWIGs

A causal directed acyclic graph (DAG) (@fig-fullly-connected-dag) is a graph whose nodes represent the variables in an observational non-parametric structural equation model with independent errors (@eq-fullly-connected-dag). Directed edges point from the arguments to the result of each structural equation. 




```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-dag
#| fig-cap: "Fully connected causal DAG"

make_dag("fully_connected")         |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```

A single world intervention graph (SWIG) (@fig-fullly-connected-swig) is a DAG whose nodes represent the variables in a counterfactual non-parametric structural equation model with independent errors (@eq-fullly-connected-swig). Directed edges point from the arguments to the result of each structural equation. 





```{r }
#| fig-height: 6
#| fig-width: 6
#| fig-align: center
#| label: fig-fullly-connected-swig
#| fig-cap: "Fully connected SWIG"

make_swig("fully_connected")      |> 
  plot_swig(node_radius = 0.2) + 
  scale_fill_mpxnyc(option = "light") +
  theme_mpxnyc_blank()

```

DAGs and SWIGs are useful because they encode statistical relationships among the variables in an NPSEM through a set of graphical rules called d-separation. Two variables in an NPSEM are (conditionally) independent if they are (conditionally) d-separated in the causal DAG representing the NPSEM.


